\chapquote{Noblesse Oblige}{I suppose leadership at one time meant muscles; but today it means getting along with people.\\
\textendash\,  Mahatma Gandhi}
\phantomsection
\label{cha:NoblesseOblige}

\begin{multicols}{2}

\section*{The Light and the Dark}%(general cosmology)
\phantomsection
\label{sec:LightAndTheDark}

That's the thing about morality: it's complicated. Sages and philosophers have debated for thousands of years to answer the simplest of questions. \textquotedblleft What is good?\textquotedblright, \textquotedblleft What is evil?\textquotedblright\, But is morality always so complicated? Are there not easier questions to ask? For every tough question like \textquotedblleft Is it justified to kill one to save five?\textquotedblright\, is there not an easier question like \textquotedblleft Is it justified to kill another for your own personal profit?\textquotedblright

Ask any of the Nobility, and they will tell you that of course there are such things as objective good and evil. To the Radiant, the world they inhabit makes this as clear as daylight. A Princess draws her magic from the Light, a force created by love, friendship, and effort to improve the world -- or just help a stranger out. The Light probably isn't the absolute axis for all that is good, but if it could think, you could say that it's making a sincere effort to reach that exalted height. For the Nobility, this is enough to point at for proof that good really does exist, because what Princesses compare the Light to is the Dark.

The Dark is the Light's opposite in every way. It is a force of banal corruption, the absence of all hope, the absence of all belief that things can get better. It festers where people commit acts of cruelty and inflict suffering on each other. Everything it touches is tainted with its own nature. If left unchecked, it would cause an unending torrent of corruption until the Dark finally succumbed to its own nature and starved upon an empty wasteland. Scholars among the Nobility are divided upon one key question about the Dark: its origins. Some say that it is a dreadful alien being attacking our world through humanity's cruelties for its own sustenance. Others say that we ourselves are the Dark's true origin: Our sins created it, and we shall forever be haunted by our crimes until such a day as we rise above them. 

The contrast between Light and Dark is something every Noble is glad for. For as much as she looks to the Light, even the Nobility live somewhere between Light and Dark. Sooner or later, every Princess will have to make some tough moral choices; it comes with the job. On a bad day, a Princess could find herself trapped for an unconscionable time with no clear answers, struggling to stitch together some semblance of a moral solution to an impossible problem. On those days, the existence of the Light can be the only thing reminding them that good exists and that it is worth fighting for. 

\subsection*{The Kingdom's Fall}%(what is known of the Kingdom and its fall to the Darkness)

When the Nobility speak of the Kingdoms, they refer to at least eight sovereign nations: Alhambra, Andarta, Aztallan, the Confederacy of Four Winds, Crystal Heril, Danann, Gonel and Wen-Mung. There are others, but their names, histories, and even existence are debated with little consensus. Each lived the ideals of the Light in their own way, guided by the Queen who ruled them. None were perfect, but by all accounts, they were fantastic places to live: they were prosperous, just, kind and peaceful. 

Yet, for all its Light, the Kingdoms did not last forever. Even in a world of Light, some things are universal, and one is the necessity of compromise. A land of individual freedom must accept a lack of organisation as its due. Each of the Queens chose what they deemed to be good and accepted the cost. In time, they forgot that this was a choice of preference and believed they alone had chosen the one true way. In their own way, each turned rigid and dogmatic. From this simple vice, the Darkness gained its first foothold in its eternal war against the Kingdom. 

The Kingdoms rallied and drove the Darkness back to whatever terrible domain it came from as they had done countless times before, but this time, they were blinded by their dogma. Small traces of Taint were overlooked, festering as \textquotedblleft inevitable drawbacks\textquotedblright\, of the Light's civilization. Rotting away in secret, the Darkness began to grow within the heart of the Kingdom. Its attacks became more frequent, more destructive, and every time it was defeated, the same growing rot remained unnoticed. In the end, the Darkness broke over the Kingdom like a tidal wave. Armies routed and the cities fell, still trying to understand how the Darkness's presence was even possible. 

Today, little remains of the Kingdom. The domains of the five Radiant Queens live on in the Dreamlands, but the warping Gales make it hard to tell how accurate a portrayal those dreams are. If any true records of the Kingdom exist, they would be locked away deep within Alhambra's vaults, for, of the Kingdoms, only Alhambra has survived to this day, protected by its Queen's formidable magic deep within the Heart of the Darkness. 

\subsection*{The Long Night and the Dream}%(Princesses in the World of Darkness before the Release)

The Darkness cannot create, only corrupt. This was always its greatest weakness. Among those Tainted by the Darkness during the Fall were three mighty creatures known as the Red Queen, the White Queen and the Black Queen. They were, respectively, the avatars of violence, self-loathing, and despair. These creatures knew the Light intimately. They knew that even as the Darkness turned upon itself, the Light would ready itself to build something new and wonderful to reclaim its place.

Guided by the Darkness's instinctive opposition to the Light, the three constructed a trap deep within the Dreamlands: a mirror to reflect the Light of the world. The trap tricked the souls of the Nobility traveling toward reincarnation and drew them away from Earth. They incarnated within the Dreamlands, where wonderful and elaborate illusions clouded their minds, letting them believe they lived and did their duties on Earth, even while the centuries ticked away.

The Radiant call this period of history \textquotedblleft The Long Night\textquotedblright. The trap that held them is simply called \textquotedblleft the Dream\textquotedblright. For much of human history, the Radiant hardly had any presence at all. Reincarnations have always formed the vast majority of the Nobility, and with the reincarnations locked away, anyone who Blossomed was most likely alone and untrained. If they were lucky, a group of friends might Blossom together. They would do what they can, but standing alone there, was little chance of changing the world.

%Note: "Blossom" was not a term defined in the lexicon in the introduction, which seems like an oversight. I'm leaving further instances of the term alone on the assumption that the term will be added to the lexicon later. 

Only the Twilight Queens maintained continuity for the Nobility during the Long Night. The Lady of Alhambra kept the last remnants of the Kingdoms alive. The Saraphic General inducted mortal forces to throw against the Darkness. The Queen of Mirrors searched for her True Heir. The Twilight Queens were a temptation to the Princesses who Blossomed during the Long Night, but they were a temptation because they were so vital. They were the only constant source of support a young Princess could turn to. 

\subsection*{The War of Hope}%(The Release, the first decades of the Princesses' return, the present)

In July of 1969, mankind first set foot on the moon. The hope released by this single event was so great that, for the briefest instant, the Light shone brighter on Earth than it did in the Dreamlands. In a flash, every soul trapped within knew that they were not on Earth as they believed. The five Queens mustered their armies against their jailors and shattered the machinery of their prison. Their victory was swift and brutal; after millennia of imprisonment, the Kingdom was once again free. 
%The Release (as a term) is referenced multiple times after this, but it isn't named explicitly in these two paragraphs. Consider revision to include the term both here and in the Lexicon.  

The effects were far from instantaneous. The first reincarnated Princess to once again Blossom was in 1987. The second was not until 1994. Today, the Nobility are still small in number, but they're growing fast with multiple Blossomings a year. They've become a minor force in the world and have had some noticeable successes in areas where Princesses are common. (Blossomings have shown a tendency toward geographical clustering.) The first generation of Princesses have now reached middle age, and many have gained positions of prestige and influence. In doing so, they have caused a backlash from established power blocks, mortal and otherwise. The Twilight Queens have also experienced a renaissance; each was active through the Long Night and were perfectly placed to take advantage of the release. New and vulnerable Princesses have been eagerly snapped up by all three Courts of Twilight. 

As the saying goes, we live in interesting times. 

\bigsidebarstart

\subsubsection*{Alternative Dates}
As 1969 recedes further into the past, the implications of the moon landing triggering the Release change: The average age of Princesses increases. Princesses have more time to improve the world, and questions of what they have or have not accomplished become more pressing. One solution to these questions is to choose a later date for The Release, or perhaps a much earlier date to facilitate a game set in a historical era without inflicting the problems of the Long Night upon your players. Some possible alternative triggers for the release are: \\

\textbullet The enlightenment of Gautama Buddha, 528 or 445 BCE \textemdash\, The Light meets the original enlightened. Princesses' focus on community and the world contrasts with Buddha's philosophy of detachment. What shall they learn from each other? 

\textbullet The end of the Black Death, 1350 \textemdash\, Though a time of terror and suffering, even the Black Death had its silver lining, such as increasing social mobility and freeing peasants from serfdom. Could Princesses have helped usher in these changes? 

\textbullet The Reformation, 1517 \textemdash\, A time of religious dogma enforced by the Inquisition, Machiavellian and mercantile intrigue, a time crying out for reform and the Light.

\textbullet The ascension of Tokugawa Ieyasu, 1603 \textemdash\, Tokugawa's coronation marked the end of a brutal civil war and the start of the Edo period. This was a time of peace, prosperity, strict social order, and flourishing arts. It is the period that first comes to mind upon hearing the words \textquotedblleft feudal Japan\textquotedblright . Did Nobles play a part in creating this peace and prosperity?

\textbullet The 13th amendment, 1865 \textemdash\, The abolition of slavery, but the beginning of a long struggle for equality. This is a struggle worthy of any Princess's dedication. 

\textbullet The Battle of Shiroyama, 1877 \textemdash\, The Meiji Restoration was a time of growth and renewal as Japan reconsolidated and prepared to enter the outside world. while Saigō Takamori's last stand at Shiroyama would dignify bushido in the eyes of the nation, creating a conflict between old and new — a conflict a Princess could find herself on either side of. 

\textbullet VE day, 1945 \textemdash\, The end of World War II would release Princesses just in time for Nobles to come of age in the 60s, a time of massive social change, clashing cultures and counter-cultures, and the Cold War.  

\textbullet The eradication of smallpox, 1980, or the fall of the Berlin Wall, 1989 \textemdash\, This Release date fits groups who want to preserve Princess's default setting by moving the release forward by a small amount and keeping Nobles as a new Phenomena.

\bigsidebarend

\section*{Being a Princess}
\phantomsection
\label{sec:BeingAPrincess}

\subsection*{Blossoming}

A Princess might be born as the reincarnation of her past self with a dormant seed of magic in her heart, or she might be a mortal whose purity and passion has such strength that it will erupt into a Light strong enough to shine through every life she lives, but a Princess is always born as a seemingly ordinary mortal. She lives, grows, and learns in the safety of her parents' home until she is ready to step forth into the darkness and face the evil therein. 

Nobles call the transition between mundanity and Nobility a Blossoming, the moment a child achieves her potential and first becomes the woman she will be. It is an unmistakeable and turbulent yet joyous time in any Princess's life. Facing a problem that seems beyond her, and beyond the adults or authorities who shelter her, the Princess-to-be declares or discovers that no, she is able to solve this, and she decrees that with her capability comes the responsibility to act. Princesses describe this as self-affirming, the realization of their agency and the actualization of their ideals and self-development in one critical moment. 

Many report a feeling that they could \textquotedblleft never forgive themselves\textquotedblright\, or \textquotedblleft would no longer be me\textquotedblright\, if they had acted any other way. If the Princess is faced with a time critical emergency, she might Transform on the spot, striding forward to meet the challenge with new magic. Others Blossom over hours, days, or even weeks, as the Princess works toward a solution or explores her newfound sense of self in the aftermath of her victory. As she progresses toward her Blossoming, the world opens up before her and she finds answers to questions and doubts that had plagued her. The Princess will feel ever more certain of her place in the world until she accumulates a critical mass of positive emotions that condense into her Noble magic.

Because Blossomings begin when a Princess realises that she is capable and responsible for solving real issues, most Blossomings occur from the mid-teens to early adulthood, as people establish their own social identity and face new challenges. Younger Princesses are usually sheltered from the kind of problems that prompt a Blossoming, but circumstances push some to accept responsibility beyond their years. Anything from taking care of a younger sibling while mother works to running away from home can result in a young Princess claiming the magic she needs to overcome whatever troubles she faces. Not all these child Princesses have a specific trigger to their Blossoming. Some reincarnated Nobles describe their Blossoming as a natural product of a growing awareness of themselves and their role as their brains developed and they explored the world around them, as though they already were a Princess and only needed to realize it. 

Blossomings in adulthood are relatively rare, because many Princesses Blossom before they settle into their adult lives. Adult Blossomings normally occur when a major life event, like falling in love, encountering the supernatural, or becoming pregnant, forces the Princess to reevaluate herself and her place in the world. These Blossomings can be harder on the Princess, as an older Princess has more responsibilities and less time for magical quests. Alhambran tales claim that the girl who would become the Queen of Tears Blossomed at her birth, and the delay in Blossomings today is merely a sign of the corruption of the world, but most Radiant Nobles dismiss this as self-aggrandisement common to the Court of Tears and choose to believe that it has always been this way. 
 
% NOTE FROM EDITOR: This is a really large portion of the text that's been commented out. I'll make an editing pass through it anyways, but if it was all draft text, feel free to delete it. 
 
% Most Blossomings occur in times of great stress and change in one's life. As a consequence, there are several broad age bands in which Blossoming commonly occurs. The first of these is from the mid-to-late teens, as the individual establishes their social identity and goes through the stresses of education. Such Princesses often (though, sadly, not always) have their parents as support; however, they still need their peers for help with their duties, especially when those duties interfere with their youth and societal demands. Not too many people are pleased with their teenagers sneaking out. They're even less pleased when they find out that the child has been going to the part of town where the drug dealers hang out, and they're even \textit{less} pleased when it's on a night that later has reports of gang violence. 

% The seceond age band is made up of young adults, who are typically pursuing higher education or entering the workforce. In some ways, they are luckier: they have the freedom and independence they need to do their duties; on the other hand, many a Princess has lost her job or been forced to drop out of university due to the stresses and demands of her Calling. And unlike younger ones, they are less likely to have the same safety net of family, as many move out to seek employment or attend university. This also means that the issue of rent and bills starts to come up. In recent years, though, elder Blossomings have started happening. The causes of these Blossomings appear to be diverse indeed and can be anywhere from moving to a new place, falling in love, a messy divorce, pregnancy or becoming a parent, and onsets of mental sickness. Such older individuals frequently have other responsibilities and try hard to try to cling to their old life.

% Most Blossomings have a specific trigger: a single event that the Princess felt or came to feel symbolised all the stress and changes they were undergoing at that point in their life; and when faced with this event, they chose to respond in a way that reaffirmed their ideals or identity. Many report feeling that they could \textquotedblleft never forgive themselves\textquotedblright\, or \textquotedblleft never would no longer be me\textquotedblright\, if they had acted any other way. In some cases the Blossoming occurred the moment she made her decision, especially if she needs her magic there and then. In most cases the Princess instead experiences a victory rush or a whirlwind of positive emotions that grows and grows until it spills over into a Blossoming hours or days later. These trigger points are usually linked to a Princess' Calling; a Grace might inspire her friends to stand up to bullies and over the next few weeks, start to have odd dreams, or she might be beaten up while trying to rally her fellow immigrant workers against oppressive employers, and in a flare of blinding light suddenly straighten up in the garb of a knight of old. 

% Despite this, very young Blossomings do occur, and the Nobles in question often have to face not only the close supervision of parents but even their fellow Nobles objecting to an eight year old going into battle. Many such Princesses are either \textquotedblleft Nanohas\textquotedblright\, and show an adult maturity and intellect in their Transformed form or \textquotedblleft Creamy\textquotedblright\, and acquire an older body when they Transform. However there are Nobles running around with magical powers, Sensitivity, and the mind and maturity of the children they are. 

But to the Nobility, textit{when} a Blossoming occurs is less interesting than textit{why} some people Blossom and others do not. Princesses know that the single most important trait that predicts a future Blossoming is to be a reincarnation of a Princess. Once a person has achieved a Blossoming, she needs fairly little to regain her powers in future lives. It is believed that most, if not all, Princesses regain their power every time they're reborn. 

% I think it'd be useful to insert an explicit definition of "Onceborn" here. Adding it to the Lexicon would also be useful. 
The requirements to become a Onceborn are far more stringent, and far more interesting to the Enlightened, for Onceborn are the only way to truly increase the Noble population. The individual must not be a creature of the Darkness - though a few spontaneous Blossomings have been noted among those who, of their own free will, managed to cast off the taint. Onceborn must be paragons of virtue and morality, and this is by far the most rigorous and important requirement to Blossoming, but not the only one. Onceborn are frequently idealistic or visionaries in some way and proactive about putting their visions into practice, although they are not necessarily naive; one can be aware of the flaws of the world and still want to improve it. Enough Sworn have Blossomed as Onceborn to be significant, but this is still a small minority of Sworn. The orthodox view among Nobility is that the Sworn's life itself is conducive to Blossoming, as opposed to any supernatural trait of the Sworn. In the end, all that the Hopeful have been able to detect among the circumstances which granted their powers are broad trends and patterns. Almost inevitably, there will be an exception to any rule they devise.

\subsection*{Callings}

A Princess Blossoms when she is faced with a crisis and chooses to act. She accepts responsibility for the problems around her and declares that it is her duty to fix them. Through accepting duty and responsibility, the Princess finds the inner strength she'll need to fulfil her new role and unlocks her magic. Although Blossoming (usually) has no effect on a Princess's brain development or hormonal balance, many Nobles consider their Blossoming to signify the moment they became adults: ready to handle their own responsibilities, make their own decisions, and go out and make their mark on the world. 

This combination of a Princess's new duties and the strength and magic that flow from them is called her Calling, which is the foundation of the Princess's power. Through her Calling, a Princess can recharge her spent magical and emotional energy. By fulfilling her responsibilities, she refreshes her spirit and surety about her place in the world. A Calling also brings a Princess affinity for the magic that is most helpful to fulfilling her duties, making it easier for her to learn those abilities. Finally, a Calling also imposes a code of behaviour, for a Princess's magic is to help her fulfill her purpose and make the world a better place, not to indulge herself in the privileges of noble rank.

A Calling does not confine a Princess into a narrow role, and few Princesses would argue that it should. The world is chaotic and always has more problems than Princesses, so the ability to step outside one's comfort zone to deal with a different kind of crisis is always praiseworthy; while accepting a Calling makes it easier for a Princess to learn certain types of magic, it does nothing to hinder her exploration into other types. 

Perhaps most importantly of all, a Calling is an understanding and an acceptance that a Princess's duties are not a job she performs or a role she fills. A Princess's duties are who she is and who she wants to be. 

\subsection*{Common Lives}

For most hours of the day, a Princess exists as her mundane identity, with little in the way of magical power. For most Princesses, their activities during this time are as mundane as their bodies. They have work to do, friends to see, and family to have dinner with. As a rule, Nobles are social creatures. The kind of person who'd cut contact with her friends and family to hunt monsters twenty-four hours a day is less likely to Blossom than one who'd want to balance her friends and family with her new duties. What's more, the good times and pleasant emotions she experiences, say, eating a simple family meal, are the fuel for Noble magic. A competent princess cherishes and invests time into the friendships that give her strength. 

Such Princesses often (though, sadly, not always) have their parents as support; however, they still need their peers for help with their duties, especially when those duties interfere with their youth and societal demands. Not too many people are pleased with their teenagers sneaking out. They're even less pleased when they find out that the child has been going to the part of town where the drug dealers hang out, and they're even \textit{less} pleased when it's on a night that later has reports of gang violence. 

Most Princesses are teenagers and often (though, sadly, not always) have their parents as support. But they must deal with their Noble responsibilities and the ways those responsibilities interact with their youth. Not too many people are pleased with their teenagers sneaking out. They're even less pleased when they find out that the child has been going to the part of town where the drug dealers hang out, and they're even \textit{less} pleased when it's on a night that later has reports of gang violence. Even Princesses whose duties do not involve violence still face scrutiny, for in the World of Darkness, the supernatural is known to be dangerous. A Princess's protests that she's just working as a hospital volunteer that happens to have healing magic often fall on deaf ears. That said, a lucky few Princesses have parents who're willing and able to help them keep their secret and act as an intermediary between their daughter and the adult world. 

But most Nobles keep their second life hidden. Other Princesses can help, and many Nobles have a system of sleepovers or after-school clubs where the Nobles who don't have any duties that day cover for the ones who do. Magic is of course used too, and many Princesses use the intelligence or maturity of their Transformed self to get through homework quickly. It's not unheard of for Nobles to impersonate each other with magical disguises or weave illusions to hide their absence from family. Some Princesses even hide their Transformed identity behind a screen when texting their friends or partner, as the empathy and social acumen she acquires through Transformation can help smooth the hurt from, say, a hastily canceled date. 

At a slightly older age, there are the young adults, typically at university or just entering the workplace. In some ways, they are luckier, because they are legal adults; on the other hand, many a Princess has lost her job or been forced to drop out of university due to the stresses and demands of her calling, and unlike younger ones, their family is often in another city, which means that rent and bills start to be an issue. For every problem a young adult avoids through their increased freedom, they must face another one due to their increased responsibilities. However, young adulthood, is a time of transition, and a disruption at this point in a Princess'a life is often easier than at other times. Drifting away from friends you've met recently in university hurts far less than a Calling forcing a wedge between a Princess and her parents. At this age, Nobles find it easiest to transition into a new social circle that is compatible with their duties, either because it is full of people in the know or just full of people who're comfortable with hectic schedules and share the Princess's passion and Beliefs. 

Nobles who Blossomed as adults can find it the hardest of all. Even before they Blossom, a Princess tends to be outgoing and socially skilled, so an adult Princess is likely to have responsibilities and maybe even a family of their own. While teenagers can have strict boundaries set by their parents, such boundaries often allow regular sleepovers or nights out with friends. Sleeping regularly at a friend's house is a whole different question when you're married with young kids. A teenager's funds are more modest than an adult, but they can easily transfer money spent on video games and socializing to fulfilling one's Calling. Money tied up in school fees and a mortgage is not so easily moved. Nobles who Blossomed younger then grew up into adulthood often build their adult lives around their dual identities and make full use of the freedom and flexibility adulthood provides, but those who Blossomed late are often too tied down to start a life of adventure, and instead balance their Calling around their mundane life. The pain of knowing you can help, and knowing it's your responsibility to do so, but being too tied down can be devastating to these Princesses. Most think very hard about simply telling their family. 

Preteen Princesses can find it just as hard as adults. Many live in families who expect that they, or a known trusted adult, will know where they are at all times. Even other Princesses can oppose their activities: Teenage Princesses are often as uncomfortable with a six-year-old fighting monsters as anyone else (for their part, the Radiant Queens have seen enough young Nobles to easily recognize who'll sneak out to fight against a Queen's advice and teach them how to survive rather than waste their breath telling them to stay home). One thing that must be taken into account is that young Blossomings (usually) don't happen without a reason, so more child Princesses than you might expect have parents who need their kid's help and are forced by circumstances to be open minded. This can grow into a partnership. With supportive parents and placement with a new peer group that matches her maturity, there's no reason a preteen can't thrive. But when the Princess doesn't want her parents to know, or they know but insist their child has a normal childhood, a young Princess can be well and truly trapped.

No matter what age she is, balancing work and friendship will require skill and maybe magic. While Princesses can get lucky or build a life designed to be compatible with their second career, most Princesses find that there can be as much drama and difficulty in their mundane life as there is in their magical life, if perhaps not as much danger. While many Princesses wish to change society so the next generation will be free from the problems they face, few begrudge the time and effort it takes to keep their mundane life and friendships. If they were the kind of person who did, they probably would never have Blossomed in the first place. 

\subsection*{Emotions Are Magic}

The first bloom of magic in a Noble is joyous, but soon she realizes the price she must pay for it. A Princess's power comes not from some exotic energy that only she can see, but from her emotions. Just as a mother, upon seeing her child trapped under a car, suddenly gains the strength to lift that car, so too can a Princess draw upon her emotions to find the strength she needs to conjure fire, heal wounds with a wave of her magic wand, and fly. 

 Just a Princess's emotions can affect the world in ways unimaginable to mere mortals; her magic, her very nature, means that the world can always come into her heart and affect her emotions. Imagine a grown woman whose heart still flutters at every kiss as though it was her very first. Imagine a lifetime of fighting evil or practicing medicine, when every life lost hurts like the very first. In the World of Darkness, for every kiss that burns with the passion of the first, there are a dozen aches that strike her exposed heart. This is the price a Princess pays. She can never form the armor around her heart that comes so easily to mortals; her own magic rips such protection open as it travels outward. All she can do is grow strong enough to bear the weight and \ mature enough to deal with her emotions constructively. 

As a Princess grows in power and magic, her emotions grow even stronger. This Sensitivity can quite literally make life unbearable. Simply walking among people batters her with every hardship she sees, each and every one feels like her personal responsibility. When she goes home the faces of everyone she couldn't help lie like Shadows over her thoughts. They flash before her eyes as she lies in bed, pushing her to go back out and fix things. Too many Princesses get trapped in a downward cycle, inaction or failure to help form Shadows upon their mind, leading to more failures and more Shadows, until she collapses in exhaustion and despair. 

But just as her emotions are stronger than mortal emotions — strong enough to summon storms and raise palaces from the ground — a Princess can also be stronger than any mortal. Every Princess has ironclad Beliefs: a set of ideals that, if she can only follow them, will lead to a brighter tomorrow. Even when a Princess is suffering emotional pain a regular mortal couldn't conceive of, let alone bear, her Belief can give her the strength to get out there and fight to fix whatever is upsetting her. The Sensitivity that opens her heart to the suffering of the world also opens her heart to the love of friends and family, and by spending time in their company and reconnecting with what is most important, a Princess restores her will and moves on from past pain. For every face that looks to her in pain and need, another looks to her in gratitude for the aid she has given, lifting the burdens on her soul and refreshing her for the fight ahead. 

%Editor: I think the bringing up of Shadows here is really abrupt. A transition reminding the reader of what a Shadow is (and how Shadows relate to what we're talking about now) would be helpful. 
The cycle of Sensitivity and Shadows is easiest to stop at the beginning, but with support and strength of character, it can be broken at any time. As for those who cannot bear the weight, or can't break the cycle, their only choice is to run and hide: stick to the quiet hours, find a nice walled palace or quiet village somewhere away from all the pain and cruelty of the world. But anyone who could so easily abandon the world is unlikely to Blossom. 

\subsection*{Transformation}

From the moment she Blossoms, every Princess has the ability to Transform. She is gifted with a phylactery, an icon of her nobility and a permanent reminder of her dreams and aspirations. With the merest effort, she takes those dreams and aspirations and adorns herself in her nobility. They flow through her body, transforming her into the woman she's always wanted to be.  

%In the second-to-last sentence, it wasn't clear whether a Princess's transformed identity will make her ALL of the following or only some: stronger, more charismatic, smarter. Leaving untouched for now. 

The Nobility often tell each other that Princesses don't do magic, but instead that textit{they} are magical and Transformation is the proof. In her mundane identity, a Princess is barely more magical than the average person, but in her transformed identity... Ah, what a difference that is. Magic flows through her body; it is on the level of blood or bone. Her magic makes her stronger, more charismatic, or smarter. Under magical examination, a Princess can see that spells and enchantments are as much a part of her body as carbon atoms and neurotransmitters.

A Princess's Transformed personality is different from her mundane one, but usually not by much. Part of it is just the natural result of her magic: She is more confident because she is more capable, she makes more witty remarks because she can think of them faster, etc. Both selves are still fundamentally her. In her mundane self the Princess is a product of her innate nature and her life experiences. In her Transformed self, she is also the product of her innate nature and her life experiences, but she adds a smoothed-out average of her past lives' experiences, as well as her own dreams and aspirations, to create her idealized self. 

The resulting Transformed identity is still recognizable as the same person — or it would be, if Princesses didn't have an innate magical defense to protect their secret identity. The personality traits she shares with the average of her past lives are emphasized, and the traits that conflict are de-emphasized. The result is a Transformed self who acts like the mundane self in certain situations. For example, a Transformed Princess with many past lives as diplomats or courtiers might act like her mundane self when in a formal situation. (They also might know things like how to formally address the emperor of Japan.)
%The last two sentences of this paragraph were very long and a bit confusing. I broke them up and tried rewording to clarify the meaning. Please check to be sure the text is still saying what you want it to say. 

It's when a Princess's current life is radically different from her past lives that a strong personality difference emerges. Because a Princess has the same innate nature in every life, this usually requires strong external factors to shape her life experiences differently. For example, a Princess with a curious innate nature that led her to many lives as scholars and investigators but spent this life growing up in a cult that crushed independent thought will discover that she Transforms into the independent free thinker she usually is. Such Princesses can experience an identity crisis but, with time and support, they usually bring their mundane self closer to their Transformed self. After all, her Transformed self incorporates her beliefs and ideals, no matter how hard the world has tried to beat them out of her, and the more lives a Princess has experienced, the closer the average of those lives comes to harmony with her innate nature. A Princess's Transformed self can be a guide, helping her become the best and truest version of herself. Some Princesses need that more than others. 

Some Princesses experience personality changes from having a different biology in their two identities. Many child Princesses are \textquotedblleft Shazams\textquotedblright\, or \textquotedblleft Shazs\textquotedblright\, and Transform into older bodies or are \textquotedblleft Nanohas\textquotedblright\, whose Transformed body has a fully developed brain despite having a similar age to their mundane self. In such cases, her Transformed personality is more strongly affected by her past lives, as she has less current-life experiences to balance out her previous incarnations. But even then, someone who knows both identities will usually recognize the Transformed identity as a person the mundane identity could grow into. That said, there are also Princesses running around with magical powers, Sensitivity, and the mind and maturity of the children they are. Something similar happens to many teenage Princesses. Some transform into young adults, and some just have less turbulent hormones in their Transformed selves. 
%Editor: I couldn't find who Shaz was. Consider revision or removal (limiting reference to just Shazam). 

Transgender Princesses usually experience a personality shift as their Transformed self will have the correct biological sex and the hormones to match. As most people are born in a body of the correct sex, a transgender Princess will have had the correct body in most, if not all, of her past lives, and her Transformed self will incorporate those experiences into her personality. 

Princesses who have a physical disability often find that upon their first Transformation that their magical body is unaffected by that condition, or that it comes with some innate magical regalia that compensates. However, this does not apply to injuries acquired after Blossoming, which must be treated with means either magical or mundane. The question of mental health is too broad to summarize; every mind is unique.

\begin{comment}
\subsection*{Belief}

The mind of a Princess is not so different from a normal person's. Yet there are important differences, with one of the most important being how a Princess relates to morality. 

For a Princess, morality is not just a question of knowing what is right or wrong. The burden of Sensitivity forces every Princess to confront the world's ills. Faced with the ugly underbelly of humanity, a Princess needs more than just an awareness of what is right and wrong. She needs a strength of conviction, that the world can improve, that textit{she} can help the world improve. 

This is Belief. And it is from Belief that a Princess's power flows. 

\subsection*{Sensitivity}

Uneasy lies the head that wears the crown. It tosses and turns in the dark of night, weighed down by all the world's ills. All power comes with a price, and for a Princess, that price is Sensitivity. 

Sensitivity is a sort of supercharged empathy. We all react to other people's emotions; when someone else is happy or angry or hurt, we feel something in ourselves. Among Princesses, this reaction is stronger, but it's more than that. To a Princess, \textit{emotions are magic}. When a Princess basks in friendship or gratitude, her magic replenishes, and when she is exposed to the worst of human emotions, to willful cruelty, her own magic turns against her. 

As a Princess's magic grows, her Sensitivity can quite literally make life unbearable. Simply walking among people batters her with cruelties, with each and every one becoming her personal responsibility. If she is strong enough, she can bear the weight. Undoing evil makes the pain bearable, and one day, she might even find find relief in a brigher future. As for those who cannot bear the weight, their only choice is to run and hide: stick to the quiet hours, find a nice walled palace or quiet village somewhere away from all the pain and cruelty.

\subsection*{Shadows}

Shadows are the painful product of Sensitivity, the result of a Princess seeing cruelties and internalizing them. A Shadow is a cancerous train of thought that can grow and spread its tendrils through a Princess's mind. A Princess with Shadows upon her soul suffers flashbacks; at the worst moments, she remembers the event that created the Shadows and feels her confidence fade. If she couldn't help then, why should she expect to do better now? These thoughts become self-fufilling. Because she feels lesser, her magic becomes lesser. It can too easily become the beginning of a vicious cycle: The Princess believes she cannot help, so her magic weakens, so she has trouble helping people, so she believes she cannot help. 

It is fortunate, then, that so many Princesses cultivate friendships and allies who can help them recover. 

\subsection*{Wisps}

A Wisp is a physical measure of magic, a feeling, and emotional energy. To a Princess, the three can sometimes be hard to tell apart. A Wisp's purpose is simple; it is the fuel a Princess burns to power her magic. When a Princess is full of Wisps, she is raring to go, and when she is out of Wisps, she feels empty. There's a hollow gap in her soul and her emotions are distant and muted. 
%Editor: In the first sentence of this paragraph, it's not clear what a Wisp is. Is it a physical measure of three different things (magic, a feeling, and emotional energy), or is it three different things at once (a feeling, emotional energy, and a physical measure of magic)? I edited based on the assumption it was the former. Please revise if needed. 

A Princess can create new Wisps within herself by connecting with what's important: her friends, her family, and her calling. She remembers why life matters and what she fights for. That feeling fills the gap in her soul. Her emotions return, pure, bright, and beautiful. She's ready to face a new day. 


\subsection*{Invocations}

An Invocation is the philosophical ideal of a Queen. Invocations are valuable tools to every Princess. So long as a Queen exists, her Beliefs resonate through the soul of every person who shares her ideals. Princesses can use this resonance to draw upon a measure of the Queen's magic. Through their shared values, Princesses can also feel the reassurance of knowing they have their Queen's support. A Queen's Invocation strengthens her Princesses both emotionally and magically. 
%Editor: Significant revision to this paragraph. Rewrote starting sentence and broke it into two with a reminder of the definition of an Invocation. Changed second sentence to say the Queen's Beliefs instead of ideals (Queens are superpowered Princesses, right? So they should have Beliefs too). Rewrote several sentences so that they don't keep starting with "through." 

For the Sworn, Invocations are even more important. With no Inner Light of their own, the Sworn draw upon their Queen's magical power as a substitute. The magic of a Queen resonating within her Sworn is what makes the difference between a normal mortal and a Sworn. 

\subsection*{Invoking Charms}

Charms are the magical spells of a Princess. But what does it feel like for a Princess to use her Charms or draw power from her Invocation? First, Radiant magic does not feel that different from the mundane. A Charm that changes a Princess's appearance might make her feel like she's an actress getting into character. A Charm that unlocks new ways of seeing doesn't feel like she's gotten a sixth or seventh sense, but instead that she's started to notice things she never paid attention to before. Even blatant magical effects like learning to fly don't feel that different to, say, learning to swim.

A Charm can feel like a mental trick a Princess performs in her own head, an attitude she applies to a problem, or a new ability that came with practice, like learning to cross your middle fingers. It could feel like anything. The only constant is that there is always some emotion behind her Charm (though, truth be told, almost everything a Princess does has emotion behind it). It's not always the same emotion behind the same Charm, though. 

Simply put, a Princess must believe and feel in her actions for the magic to flow. A Charm causes vines to burst forth and entwine her foes will only function if she wants to trap her foes on an emotional level. Which emotions she feels will flavor the Charm: The vines will be more vicious and threatening against a hated foe she hates than against a friend she's sparring with.

As for the Invocations, they are a magnification of something we've all felt, of how our beliefs and convictions give us strength. When we fight to save someone we love, our love gives us strength. When a Princess versed in Fuoco fights to save someone she loves, the Invocation focuses those same feelings into her magic, making her strength all the greater.

\subsection*{Learning New Charms}

One of the first things a Princess learns is that she does not do magic; rather, she herself is magical. In their Transformed state, the Nobility do not experience a clear separation between their magical and mundane abilities. An observer might see a Princess jump to avoid a blade and then throw a fireball, and conclude that the jump was mundane while the fireball was magical. But to the Princess, they wouldn't feel that different. She chose to jump and her body reacted. Similarly, she chose to throw fire and her body reacted. No speaking in Enochian, no need to memorize arcane principles of correspondence or chant spells in her head. The observer might even be wrong; if the Princess put all her hopes and Belief into that jump, it could be more magical than throwing fire.

So, if magic is not a skill, what does it feel like to learn a new Charm? It can be likened to a mundane person learning a foreign language. A text written in a foreign language can, with time and practice, become as familiar and easy to understand as one's native language. New potential magical abilities already exist within Princesses; she only has to discover and practice them until they become second nature. 
%Editor: Significant revision to this paragraph. I hope the revision gets the message across, but in a more concise way. 

A Princess might be able to sense ghosts but not see them, so she practices interpreting her senses until she no longer feels a ghost as a pricking on the back of her neck. This practice eventually turns into her being able to see ghosts as easily as she sees mundane people. Charms often don't come from a deliberate attempt to produce a specific effect either. When a Princess comes across a new problem and tries to solve it, sometimes the solution she reaches is a new Charm: She cannot defeat a Darkspawn in combat, so she returns to her Palace to practice her swordplay. As she experiments and tries new things, she might realize that a certain deft twist of her wrist will slip under her opponent's guard.
%Editor: I think this paragraph ends a bit abruptly. How does the example of the wrist twist lead to developing a new Charm?  

\end{comment}

\subsection*{Charms and Invocations}
%When she is Transformed, a Noble's magic doesn't just perfect her body and mind; it overflows into powers beyond mortal ken — magic, in the most obvious sense. Yet, to the Noble, these Charms are no more (or less) magical than anything else she can do. One of the first things a Princess learns is that she does not do magic. She is magical. A Charm that lets her take on another's appearance might feel like she's an actress getting into character. A Charm that unlocks new ways of seeing doesn't feel like she's gotten a sixth or seventh sense, but that she's started to notice things she never paid attention to before. Even blatant magical effects like learning to fly don't feel that different from, say, learning to swim.
 
%An observer might see a Princess jump to avoid a blade then throw a fireball, and conclude that the jump was mundane while the fireball was magical. Yet to the Princess they wouldn't feel that different. She chose to jump and her body reacted, she chose to throw fire and her body reacted. No speaking in Enochian, no need to memorize arcane principles of correspondence or chant spells in her head. The observer might even be wrong; if the Princess put all her hopes and Belief into that jump it could be a more magical action than throwing fire.

%So, if magic is not a skill what does it feel like to learn a new Charm? A new magical ability already exists within the Princess as raw potential, she only has to discover it. Practice it until it becomes second nature. Any of us has the potential to read a foreign language, if we practice then over time we no longer see meaningless symbols. We look at the page and see meaning. Even if that's not actually supernatural it is amazing enough that it deserves to be called magical. Learning a Charm is much the same.

%A Princess might have the ability to sense ghosts but not to see them, so she seeks out ghosts and when she feels that pricking on the back of her neck she tries to focus her senses. She walks around searching for where the sensation is closest, she traces her fingers through the air searching for inexplicable cold spots, she looks for a distortion in the air. If she's lucky the ghost may materialise and discorporate for her, allowing her to watch the transition. And then, something clicks. The symbols are now meaningful, she sees the ghost as clear as she sees you or me. Charms don't have to come from a deliberate attempt to produce a specific effect either. A Princess comes across a new problem and tries to solve it, sometimes the solution she reaches is a new Charm: She cannot defeat a Darkspawn in combat so she returns to her Palace to practice her swordsmanship. As she experiments and tries new things she might realize that the deft twist of her wrist she just stumbled upon will slip under her opponents guard, or she might come upon a stance that sets her blade alight.

%A Charm can feel like a mental trick she performs in her own head, an attitude she applies to a problem, a new physical ability that came with practice like learning to cross your middle fingers. It could feel like anything, the only constant is that there is always some emotion behind her Charm (though truth be told there's nearly always an emotion behind anything a Princess does), it's not always the same emotion behind the same Charm. Simply that, a Princess must Believe and Feel in her actions for the magic to flow. A Charm that will cause vines to burst forth and entwine her foes will only function if she wants to trap her foes on an emotional level. Which emotions she feels will flavour the Charm: the vines will be more vicious and visibly threatening against a foe she hates and wishes to entwine in battle than when she invokes the same Charm with the excitement of a tough but enjoyable practice match.

%Invocations are a different matter. They come not from a Princess' innate magic but from outside, from the Queens. So long as a Queen exists, her philosophies resonate through the souls of everybody who shares her ideals. For those Princesses and Sworn with an innate connection to the Light this resonance allows her to draw upon a measure of the Queen's magic. Through their shared values she feels the reassurance of knowing a trusted authority supports her actions, and through her shared values she channels the magical power of the Queen. Both emotionally and magically the Invocation forges a stronger Charm. When we fight to save someone we love our love gives us strength, and when a Princess versed in Fuoco fights to save someone she loves the Invocation resonates with those feelings, drawing power from the Queen of Swords into her magic, making her strength all the greater.

%Editor: This section seems very similar to the previous one. I'm going to comment it out and NOT edit it. Let me know if this section (and not the first section) was the one you intended to have in the book. 

\subsection*{The Dreamlands}

Within her dreams, a Princess can travel beyond her mind and into the very soul of humanity. Within the Dreamlands, humanity's hopes and aspirations take life and form vast cities. The Dreamlands are more than just a metaphor; they are a true world. The inhabitants have lives and hopes and dwell in functional societies. Many Princesses are surprised to discover something so ordinary amongst dreams and flights of fancy, but is it really so surprising than a Princess's dreams would form after how she sees the world? For the Princess who cares so much about friendship and community when she is awake, what else would she dream about? 

Traveling to the Dreamlands offers many practical advantages to a Princess; she can find friends and mentors among the population, including the Radiant Queens. Objects of power, often created and traded by Dreamlanders, can be formed into Bequests. However, the Dreamlands is not just frolicking and sunshine; it contains all humanity's fears and hates as well as its hopes and dreams. It was also once used by the Darkness to construct a trap for the souls of the Kingdom. Though the trap is broken, its creaky machinery and the remnant of the prison's old wardens still seek to imprison the Enlightened in a blissful dream. 

\section*{Noble Culture}
\phantomsection
\label{sec:NobleCulture}

Princesses are not meant to exist in isolation. A Princess's strength comes from the friends she makes and the grateful smiles of the people she protects. During the Long Night, Princesses Blossomed so rarely that most would never meet another of their kind. Most suffered dearly to fulfill their Calling alone or turned to the only easily available support on offer: the Twilight Queens. In the modern day, things are different. Since the Release, it has become rare for a Princess to exist in isolation. Some cities, especially those with great need, can have hundreds of Nobles. Princesses find that support is readily available from thier peers, the Queens and their agents, and even ordinary people who were helped by one Princess and are now eager to help another.

\subsection*{D\'ebutante} 

Princesses who live near to each other rarely remain strangers for long. New Princesses are often eager to meet peers who can provide support for her new responsibilities and magical abilities. Tracking down a Princess's mundane identity is near universally considered horrific behaviour beneath all but the Court of Tears, but no such taboo exists against making contact with a stranger's Transformed identity. (It's the easier one to find anyway). A large community of Princesses creates a wealth of rumours and urban legends to investigate, meaning that a freshly Blossomed Princess unaware of her peers but eager to find some has a place to start. It is even easier for an experienced Princess to find a newbie. In cities where there is an established Princess population, there's usually more than enough people plugged into the social grapevine (or prone to prophetic dreams) to notice the waves a new Princess makes, and there's plenty of magical tricks that can be applied to finding another Princess. A smaller town may have fewer Princesses, but news travels far faster, so it usually balances out.  

Even if there are no other local Princesses, the social waves made by the Nobility often end up online, like most information in the modern world. A freshly Blossomed Princesses can search the internet for signs of other Princesses. These early investigations can be dangerous: The young Noble is away from familiar environments, and many dangers lurk in the shadows of the World of Darkness. What's more, rumours about Princesses often place them near whatever threat they're trying to deal with. However, most people raised in the World of Darkness are raised to be cautious, so a young Princess will take care when looking for peers. 

All this presumes that the responsibility for introducing new Nobles to the local community falls upon that community or the new girl. While this is increasingly the case as Nobles get more established and better at finding each other, responsibility for finding each other has never fallen on Princesses alone. Shortly after the Release, the Queens gathered officials from their courts and bid them to follow the souls of Princesses to earth. These officials became the first Shikigami. Their spirits took possession of animals and followed dreams in search of newly reincarnated Princesses to mentor. They're quick to introduce their prot\'eg\'e to the Queens and their courts. 

\subsection*{Cliques}

Once a new Princess has been introduced to the community, it's only natural for her to start making friends; as a rule, Princesses are sociable and agreeable. In a city with a large Princess population, Cliques will inevitably form. 

Cliques are social groups of Princesses. They go shopping, see movies, plait each other's hair, and compete in fun magic contests. Cliques are not obligated to work together to fulfill their duties. A Princess of one Calling might find she has the most in common with Princesses of other Callings. They might disagree on politics and the best way to make the world better, but they'd still seek each other out for emotional support and time with friends. But when it's time to work, the Champion patrols the night while the Grace campaigns with people who share her Beliefs and politics, be they Nobles or mortals.  
%Editor: I think it's weird that "Clique" is defined in this paragraph but "Grace," "Champion," and "Troubadour" aren't. I strongly suggest revising the paragraph so that it doesn't mention the latter three terms. Alternatively, you can revise to define the three terms instead. Also, the fourth sentence (about a Grace getting along best with a Champion and a Troubadour) implies that cliques are made up of Princesses of the same Calling. Is that intentional? Finally, I think "Cliques don't have to work together" seems confusing with the last sentence, about how the different Princesses go about their work. Does that mean the Champ and Grace AREN'T really working together? I've left the last sentence mostly intact for feedback from you folks, and I'll revise the rest of the paragraph. 

The Clique's primary purpose Clique is to let Princesses de-stress and recharge after the pressures of the job by providing friends who understand what it means to be a Princess and know when to (and have the power to) force a Princess to get a good night's sleep. If the two Graces in a Clique are supporting rival political parties, then getting into political debates can ruin what should be a relaxing night. While Nobles usually have the social skills to avoid getting into an unwanted argument, part of those skills involve knowing when a Clique should have a rule against talking shop.

However, when Princesses are reacting to a problem, be it the Darkness, the Twilight Queens, or mundane problems like an earthquake, and her usual allies aren't enough, the Princess's Clique is usually her first point of call for backup. Members of a Clique trust each other and know each other well enough to work well together — and, of course, they all have each other's phone numbers. 

\subsection*{Nakama}

Not all Princesses can or want to distinguish between friends and coworkers. For these Princesses, a Nakama can be an alternative to a Clique. The Japanese word "Nakama" means  "group of friends." "Buddies" and "gang" (both used in the tone of a playful child) are similar English words. Among the Nobility, Nakama has a different meaning: a small group of Nobles who came together (perhaps all Blossoming in the same town, or facing the same great crisis) and became as close as family. They share each other's duties, lending the skills of their Callings and Courts to Princesses of different backgrounds. The members of a Nakama either have compatible Beliefs or have negotiated a compromise between their various Beliefs. Many Nakama go so far as to share the secret of their mundane identity with each other, especially if they wish to live together to save on rent or pool their magic into creating a magically defended home. 

City Princesses are more often in Cliques than Nakama. For Princesses in rural areas and small towns, the reverse is true. If there's only one Champion in town, and she's too new to have found or trained reliable mortal monster hunters to work with, the only backup she can call upon on is the other local Princesses. A Mender is perfectly capable of learning the same battle magic as a Champion if she puts her mind to it, and her regular healing magic can work in the middle of a fight. While a lot of Princesses swear by the importance of having a space and some Noble friends who are separated from their work life, having backup when facing down monsters or a political rival's lies is even more important. So, when needs must, Princesses can and will negotiate through their conflicting Beliefs to work together. 

A Nakama can include both a Noble's family and close friends, even if they have no trace of magic in them. This is especially common if the Nakama was formed in response to a common threat, as Princesses are very defensive of their loved ones. If a Princess has to reveal her secret to protect her loved one, she might as well go a bit further and bring them into the Nakama's communal home. There, a Princess from the Nakama can better keep an eye out for danger.

\subsection*{Coworkers}

Princesses are be driven by strong and often conflicting beliefs, but the same is true of humans, and that's never stopped them from organizing. The Nobility can be far more empathetic and persuasive than mortals. When Princesses want to find collaborators without committing to the intimacy of a Nakama, they usually seek out Princesses with compatible Beliefs. Online forums, the Dreamlands, and local Princess hangouts mean that Princesses searching for like-minded peers have no shortage of places to look.

But Princesses are not limited to seeking out fellow Nobles. While a Princess's virtuous nature and magical power makes her an ideal coworker, no one should discount the abilities of ordinary mortals. In fact, many Radiant consider refusing to work with mortals to be a slippery slope toward the vanity of the Court of Mirrors. Rather than found their own organizations, most Princesses skip reinventing the wheel by joining a local mortal institution. Perhaps she'll meet like other Nobles there. 

Even Champions who wish to pit their mettle against the Outer Darkness and its monsters can find old boy networks of police clubs who trade information and jade knives, hunting clubs with a higher purpose than sport, and all manner of mortal societies dedicated to protecting humanity from supernatural predation. Admittedly, as a supernatural being herself, a Princess might not be welcomed with open arms, so Champions are more likely than other Callings to build their own organizations or work exclusively with Nobles and Sworn. 

As a result, Princesses can be found at all levels of society (though the number of public figures rumoured to be Nobles is far greater than the actual number). Menders often work in hospitals and clinics, as opposed to some hidden shrine found only through rumour and word of mouth. The friends she makes among the doctors and nurses might be in on the secret. They might deflect rumours of miraculous recoveries, or they might just free up their genius but entirely mundane colleague to work the hardest cases. Graces manage corporations and defend vulnerable citizens pro bono in court rooms, with the lawyers around her being inspired to go the extra mile by her belief in justice. Champions might serve as police officers, and when a Champion sees a nest of Darkspawn, she knows exactly which officers will face it alongside her. After all, Princesses consider themselves to be human — it's their society too. 

Of course, given the demographics of the Noble community, a fair number use magic to appear older than they are or working with organizations who accept younger volunteers. 

\subsection*{The Queens and Their Courts}

Every Princess knows that to make the world better she must improve herself, she must rise to the challenge. And Princesses knows that if she works hard enough and holds faith in herself she can become so much better, for the Nobility are guided by the Queens. The greatest champions of the Light, and a living testament to the heights any Princess might one day reach. 

It is not known exactly how many Queens (or Kings) once ruled the Kingdoms, of this unknown number only eight Queens still have the power to affect the world. Of this eight: Five are dead, one is living, another is presumed to be living, and one is... Transformed. Collectively the five dead Queens are known as the Radiant, for they remain loyal to the light in spirit as well as word, for centuries the Radiant Queens were trapped deep within the Dreamlands, but now their trap has fallen. From their Palaces within the Dreamlands they call out to Princesses, seeking Hopeful agents who will restore the Light upon Earth. 

The Queens are the leaders and linchpins of Hopeful society in more ways than one. Their courts and kingdoms in the dreamlands can be reached by any Princess from the comfort of her bed, and Princesses frequent them looking for places where they can help, Nakama's to join, tutors to train them in their new magical abilities, or just where to find new friends in their local area. On a personal level a Queen is a living (or otherwise, these days) font of magic. Her Beliefs have become a coloured mirror that shines additional Light onto the world; everyone who shares her ideals can draw upon the Queen's Invocation to gain greater power or unlock new abilities that they would not otherwise have been possible. So while a Princess may disagree with a Queen's philosophy she is sure to be familiar with it and have given it due consideration. 

The Court's philosophies tend towards general applicability. The Queen of Diamonds, who emphasises clear and careful thought, is more interested in teaching Princesses how to think than what to think. The Queen of Hearts emphasises the role of communities and traditions while supporting her courtiers in following their traditions, not her own. Partly because each remembers what happened the last time they became dogmatic, but mostly this is because the Queens must now speak to a wider audience than a single nation state built around a shared culture. As a result Princesses as far flung as Tokyo and Timbuktu have taken the same core philosophies and adapted it to their needs, while retaining enough of a common reference to enable communication and collaboration. 

While no Queen is capable of using her full power on Earth. The five Radiant Queens are dead, the Queen of Tears will not leave Alhambra, the Queen of Storms will not abandon her battle in the Dark World, and while nobody knows what is up with the Queen of Mirrors it is generally accepted that she doesn't act directly. The Queens can still provide advice and guidance. They are people who have built and won the hearts of nations. As monarchs and rulers they were perhaps the very best in all of history; their Kingdoms may have fallen but all kingdoms fall in time, few were utopian at their apex. As mentors and teachers the Radiant Queens have more to often than a young Princess could imagine.  

\subsection*{The Wider Community}

Like the modern mortal societies they serve, much of a Princess' social life happens online. Once you go beyond the close friendships of a Princess' Clique or Nakama, and Nobles or mortals who work alongside her in the day job, the Princess' community continues on the internet. 

In the short time since the Release a sprawling culture has grown across a network of blogs, forums and social networking sites. The Hopeful community covers more than just Princesses; Beacons and Sworn are welcome and even ordinary people can often be found on the comment threads. The online Radiant community is hardly a walled garden; it spills forth onto related subjects. Princesses can often be found blogging about and arguing in forums related to art, politics, current affairs, activism and social justice. Many blogs or forums are considered to be both hubs of the Radiant community \textendash\, for the author or prominent members are Princesses \textendash\, and considered to be ordinary websites by their mundane viewers \textendash\, for the Princesses are still in the closet (at least under this username). 

Inevitably debates between so many young, passionate ideologues often becomes full of intractable arguments. Since Princesses are almost invariably socially competent these arguments are, if not productive, at least good at getting Princesses to think from multiple points of view. People often wonder how Princesses, a group who live by the maxim \textquotedblleft School, friends, royal duties, sleep, choose three\textquotedblright\, ever find the time to argue on the internet. In truth it's common for Princesses to vanish entirely from their online community when an actual problem comes to their town; lives have even been saved because somebody decided check up why a someone stopped posting. 

When compared to the Dreamlands the internet has two advantages. Firstly it's more convenient, meeting another Princess in the Dreamlands requires luck or a pre-arranging a meeting time. If two Princesses only know each other through the Dreamlands it can take several nights of back and forth messages through a court functionary to arrange a meeting. The second advantage is precisely that it is open to more than just Princesses. A Princess taking part in a national conversation on the issues on the day will want to reach both mortals and other Nobles; and she might feel more comfortable with debating her peers in public than getting together with other Princesses to debate in secret and decide on the party line. Even if nobody outside the loop knows who's Noble, having the discussion in the open is the important thing.

As a rule the internet is used for bigger impersonal issues and as a second way to relax and socialise outside of Cliques. It helps a Princess quickly and conveniently keep her finger on the pulse of social issues, Noble or otherwise, build her network of contacts and emergency phone numbers, and means that if you suddenly stop posting another Princess or two might notice and check if you're overworked or in trouble and need help, if you're lucky. But when things get serious Princesses move the conversation to the Dreamlands or phone calls (while calls can be traced, the people with the resources to do that usually aren't interested in random youngsters like a Princess' mundane identity). In the Dreamlands a Noble can ask the other Nobles who'll be joining the same university at her if any wish to form a Nakama with a degree of confidence that everyone in the room is at least a Princess. Or she can just discuss Charms and magical techniques without attracting the wrong sort of attention. 

\subsection*{Campaigns}

Princesses may disagree with each other about how to improve the world, and even about what a better world would even look like, but in the face of an emergency they are quick to put their philosophising and debates aside and unite behind a Campaign. Whole Nakamas, Cliques, and independent Princesses travel from all over the land to pit their combined strength against a problem. 

A Campaign always starts when Princesses face a large immediate problem. In a long career a Princess might see Campaigns against large Darkspawn incursions or to rebuild after natural disasters. More complicated problems where every political ideology has it's own mutually opposing solution may draw campaigns of like minded Princesses, sometimes this require negotiations to prevent two Campaigns arriving in the same town and working at cross purposes and sometimes the negotiations fail and two campaigns do end up competing for resources and a political mandate. Most campaigns though, form around large attention grabbing problems. Princesses have a lot of responsibilities on their plate, it can take something big to call them away from home. 

The concept of a Campaign is well known to the Noble community, and most begin deliberately. Princesses announce that there will be a meeting in a Queen's palace (usually the Queen of Hearts) at a certain time and see if enough people turn up. It is generally considered a bad sign if only one Noble starts trying to arrange a Campaign, if a problem doesn't convince several Nobles they need to start a campaign it is unlikely to convince a large group of Nobles they should join a campaign. Of course, this rule of thumb depends on the size of the Princess population at ground zero. 

A Queen's palace not chosen just because it's a convenient meeting point, the gathered Radiant often ask the Queen to select a Campaign's leader and officers. Even Princesses with an ideological commitment to democracy, and there are a lot of them, usually agree that if a Queen can't pick a leader who's acceptable to everyone then this issue isn't the sort of direct problem suitable for a campaign and it would be better for Nobles to work on solving the issue in their own way than spend their time arguing about how to solve the issue. 

A Campaign doesn't always formally end when it achieves it's aim. After working or fighting with fellow gregarious Nobility everyone is sure to have made friends and that provides a powerful incentive to keep the campaign running and give everyone a reason to stay away from their responsibilities back home a little longer. When the campaign succumbs to this temptation the leader begin expanding the Campaign's scope and a ideological commitments, after the Darkspawn are chased out the leader proposes the Campaign beings fighting for political reforms to prevent new Taint forming. Once this happens Princesses who disagree with the new direction quickly depart, usually the Court of Spades leave first and serve as the proverbial canary in the coal mine. This has happened often enough that it's become a running joke among the Radiant and Campaigns that do formally disband after achieving their aims often announce their end with a bombastic speech announcing a radical expansion of their mission, followed by a good natured prank from the Spades. 

It's not unusual for a completed Campaign to leave behind a few Nakamas who do continue it's original mission with an expanded scope. And many Princesses who arrived alone go home as part of a Nakama or Clique, but it's considered a very worrying sign when a Princess insists she is still the leader after everyone's departed or tries to prevent people from leaving.

\subsection*{Language}

The Hopeful are for the most part a young culture and even the parts of it that regularly communicate don't have any formal body to standardise language. While there is a linguistic legacy that pre-dates the Release, three in fact: One is in the Royal Tongue (which many Princesses find cumbersome, or just annoying) another is in Alhambran (which many Radiant refuse to use on principle), the third comes from the Embassy to the Dreamlands (which is specialised and relatively obscure). Consequently the Radiant use a fast changing system of slang, memes and technical terms that vary across geographical regions and even parts of the internet. The language of the Radiant is young enough that most words can easily be traced back to their origin. The following terms are usually used by Princesses in the anglosphere, having been spread across that portion of the internet. Some of the more specific terms are unique to American Princesses. 

The tradition of naming Queens after playing cards came early after Princesses searched for an alternative to the Queen's titles in the Royal Tongue. The Queen of Diamonds suggested \textquotedblleft The Queen of Diamonds\textquotedblright\, (as well as \textquotedblleft The Crystal-eyed One\textquotedblright ) as a two very rough summaries of her most important titles. One of the Princesses present at the time started referring to the other Queens with different playing cards, since none of the other Queens had made English suggestions yet (or been asked yet, this happened quite early) it stuck. There are actually several alternative card based naming schemes, most attempt to try and match the Queens to card based symbolism. Either through their invocation's element or by trying to match their character to a feudal class. Neither are popular, partly because the symbolism doesn't work too well, partly because if the symbolism of playing cards has any useful magical properties it doesn't apply to Noble magic, and 
partly because the Queen of Diamonds prefers to be called the Queen of Diamonds. The common system is found throughout the English speaking world. Different naming schemes can be found elsewhere, but it is more common for each Queen to offer a set of unrelated rough translations into the local language. 

Terms in Japanese originate from Bonnie Getsuei, an American (and complete Japanophile) who forged much of the Radiant's community in San Francisco and even provided a common entry point to the online Radiant community for English speaking princesses (presumably actual Japanese Princesses also use their native tongue). 

Italian words can often trace their origin to the Queen of Heart's earliest followers in the United Kingdom (The Court of Hearts had a late start in America, as the first impressions of that court often clash with America's national ideals. Today few Princesses even remember what the fuss was about.) Influenced by Andartan culture those Princesses chose to use a romance language, and since they didn't want to use French; Princesses everywhere sprinkle their magic with Italian terms. 

Greek and Latin words both share origins in the Court of Diamonds; the early Lights were the first to attempt to begin classifying and studying Noble magic and related phenomena. This project was split between those who were more influenced by their Danann aesthetics and wanted to use Greek and those who were more influenced by human academia and wanted to use Latin. The argument was never settled and various words from both languages have become part of the Princess lexicon, mostly for things a Princess can go a while without encountering as everything else was named through informal, and therefore faster, channels. Exceptionally nerdy Princesses sometimes use Greek instead of the Latin terms or Latin instead of the Greek, and Latin or Greek instead of English, Italian and Japanese terms. 

The Embassy to the Dreamlands, perhaps the only lasting Radiant organisation to exist through the Long Night, tended to use names taken from people both living, Dreamlander and even fictional (these are rarely distinct categories). Few of these terms are still in use. 

Finally English is, obviously, the de-facto language of English speaking Princesses. Anything that did not get a catchy enough name quickly enough is likely to be in English. One unusual, and uniquely American, fact about English is that many Princesses adopt a more \textquotedblleft royal\textquotedblright\, manner of speaking in their Transformed identity, which is to say a British accent ranging from \textquotedblleft BBC English\textquotedblright\ to \textquotedblleft not even The Queen lays it on that thick\textquotedblright. Princesses who are actually from the United Kingdom usually use their natural accent, though as the British will parody anything some have been known to play up, or adopt, incomprehensible regional accents when around Americans. 

%\subsection*{Sworn Knights and Maidens Fair}

%The distinction between Nobility and mortals is a spectrum. Certainly there are some things that every Princess can do and no mortals can accomplish, but consider a Princess who hears screams from a burning building. She focuses her empathy and fear for the safety of those inside and orders the fire to quell itself, her tongue glows as she speaks and the fires extinguish at her command. No mortal could command the elements, so instead a fireman focuses his empathy into his body, adrenaline surges through his veins, his muscles become strong enough to carry a grown man without slowing, the heat cannot pain him. Is this not magic too? 

%All humans generate Light through virtuous and empathetic actions, not enough to command the elements or fly, but enough to contribute to society and enrich the lives of those around them. Beacons are those mortals who's virtue and kindness is so great that their Light can be seen with a supernatural eye. They are the nurse who never too tired to give a patient individual attention and the young girl who spends every school break with the classmate to ill to play outside. Most Beacons never realise they are anything but a mortal man, and in defence of this viewpoint Beacons only differ from a mortal, albet an exceptionally nice one, in exceptional and supernatural circumstnaces. However when there is a notable Princess community present Beacons are often drawn into it, for one of those exceptional circumstances is that monsters loyal to the Outer Darkness can sometimes recognise and target a Beacon. Nobles like to keep a protective eye on Beacons, and they also like the company of people who share their shining heart without all the stresses of royal duties to cloud it. 

%Where as a Beacon's Light comes from their personality and behaviour a Sworn is something different. A Sworn is gifted with a fragment of a Noble's light, held in a web of enchantments that lies anchored to their mortal heart. This borrowed Light transforms an ordinary mortal into a supernatural being. Sworn are a Princess' dearest friends given a princeless gift so they 


\begin{comment}
\subsection*{Principalities}

In the slang of the Nobility a Principality once refereed to organisations run by a Princess, over time this definition has become looser and can now be used to refer to any organisation where the Princess has notable status or influence, or even an organisation where a Princess is working hard to acquire influence. As Princesses consider themselves human and part of human society rather than any secret Noble society Principalities are regular mortal institutions rather than secret organisations hidden from those unaware of the Nobel world. Any type of organisation can be a Principality. They include public corporations with a charitable ethos, voluntary groups, government bodies, law enforcement, music producers, and more. 

Just as the Clique or the Nakama is the standard building block of Noble social life, the Principality is the standard unit of Noble work life. When Princesses with similar duties organise to share their workload and pool their resources they typically do so through a Principality. Since Princesses consider themselves human and part of human society they see no reason not to join mortal organisations who've already set up the infrastructure needed for the task or fill out the proper forms when founding a charitable institution; and when Princesses with similar goals sit down to discuss how to avoid wasting time by working the same case sooner or later someone will point out that they should also avoid wasting time on a case that mortals have covered. Many Princesses also consider it a moral duty to work within the system, particularly if their role involves wielding authority over other people, and while everyone understands how useful it is to have support from fellow Princesses who understand the burdens of Nobility. The idea of forming a larger Noble society held apart from mortal society without a good reason feels too close to the Court of Mirrors' for many Princesses. 

In size Principalities range just as widely as they do in structure. At their smallest you'll find groups with less than ten members such as a Champion leading a cell of mortal monster hunters against the Darkness. Or a Grace running the pub that serves as the hub of the local community. At their largest Principalities can work on an international scale. However despite speculation that every popular public figure is the mundane identity of a Princess most large Principalities are of the \textquotedblleft working hard to acquire influence \textquotedblright\, verity.

While acquiring a Principality in the original sense, in other words a position of influence in a mortal institution relative to one's calling, is a common Aspiration for Princesses of any Court or Calling Graces notably the most likely Calling to seek out leadership roles in mortal society. Among the Queens it is unsurprisingly the Court of Hearts who are most interested. A Heart of any Calling is as likely to be involved in a Principality as a Grace of any other Court. After the Court of Hearts, the Court of Diamonds is the second most interested

Typically the membership of a Principality skewed heavily towards the mundane members. If a Princess joined a mortal institution and worked (or is working) her way to the top this is unsurprising. But even when a Princess founded her own institution it usually ends up predominantly full of mortals. this is not because Princesses avoid Noble rivals for influence, quite the contrary, it is simply because regular mortals are far more common than Princesses, Sworn and Beacons combined. To the Nobility a bias towards fellow Princesses is seen as low behaviour befitting only the Court of Mirrors, and so even though most Princesses do have at least some bias (Blossoming is a very accurate judge of character even if Princesses can fall from grace later in life, and magical abilities are a useful advantage to any organisation) they still gladly accept mortals into their employment. After that numbers alone ensure that all but the smallest Principality where it's feasible to make the entire Membership Sworn will soon be full of regular mortals. 

Conflict between Principalities is inevitable. They often compete for resources or have fundamentally opposed methods or goals, after all both the Democratic and Republican party (or their youth branches) are full of Princesses hoping to get the Presidency in a few decades time. Typically these conflicts are civilised and fought with debates and campaigning but even the most vicious conflicts between two Radiant led Principalities rarely fall below the level of slander and obstructionism. 

% Among the Courts of Diamonds and Hearts accusing someone of being more interested in winning a conflict than fulfilling their duties is an almost unforgivable insult, it is practically an accusation that someone has the same attitude as the Court of Storms. Among the Court of Swords it is if anything even worse. Swords are supposed to follow their passions, so to suggest her passions are leading her astray is to suggest she is in some ways fundamentally broken as a person. 

% However Princesses can and do let their emotions get the better of them and Princesses who put themselves into positions that require conflict without demonstrating they have some way of handling their emotions, such as a superhuman Composure, self awareness, or a Nakama to keep them grounded, often make other Radiant nervous. They're not likely to directly hurt people, but they can create no end of delays or bad policies; then again they're just as likely to end up clearing the air through a harmless magic fight or a passionate and volatile romance with their opposite number. 
\end{comment}

\subsection*{The Twilight Courts}

Among the Nobility there is no agreed way to help the world. Princesses who advocate for collective solutions spar across the debating stage with Nobles who focus upon individual liberty. In laboratories Princesses push the boundaries of technology while on the other side of the university campus their peers argue for a return to the good old ways. But among the Nobility an informal understanding holds, to Princesses it's so natural and obvious that nobody gave it a name. The understanding states that even when you disagree with a fellow Radiant's idea of a better world you can still respect her as a person, and while her utopia may not be yours it is at least better than today's world under a shroud of Darkness. 

But this understanding only holds to the Radiant. No such benefit of the doubt is given to the Princesses of the Twilight Courts. 

The Twilight Courts are thrice separated from the Radiant. They are separated by politics, the Radiant and Twilight courts will at best clench their teeth and swallow their distaste before teaming up against a mutual foe and at worst violently oppose each other. They are separated by magic, for the five Radiant Queens are neighbours in the Dreamlands and their Invocations demand nothing more than virtuous behaviour as each Queen defines it. The three Twilight Queens each exist alone and their Invocations take a toll upon the user's mind, body, or soul. Finally they are separated by morality, for the philosophies of the Twilight Courts directly harm innocents in a way that the Radiant Courts do not (On this point the Court of Mirrors is more complicated, and so it is sometimes held to be on the Radiant side). Thus even the most inexperienced Princess cannot help but see that there is a division between Radiant and Twilight on the deepest levels.

And though the five Radiant Queens and their Courts stand together. No such camaraderie exists amongst the Twilight Courts: The Courts of Tears and Storms have been in open war for perhaps as long as they have existed. And the harsh dogmatic outlook of those two Courts means that they are less tolerant of the Court of Mirrors than Radiant Princesses. Each Twilight Court stands in isolation or with the Radiant. 

But perhaps the deepest reason for conflict between the Radiant and Twilight Courts is that for once even Nobles want to remain in conflict. Alone or among their trusted friends the Radiant admit that a part of them is tempted by the philosophies of the Twilight Courts. What Princess hasn't put her beloved sister's safety above a stranger's? Felt hatred for the Darkness' evil? Clung a little too hard to a reassuring Belief or assumed a fellow Radiant is good and virtuous when they first met just because she's Noble? And when the Radiant reject the part of them that's tempted to walk down that long road paved with good intentions they also reject their kinship to every Princess who's walked that road to the very end. 

For all their light, Princesses are still human and think in very human ways. 

\begin{comment}\section*{Despair and Darkness}
\phantomsection
\label{sec:DarknessDeathDespair}

Princesses are sent to bring Light to the world. Every kind word she speaks, every inspiring song she sings, makes the world just that bit brighter. But a Princess' mission will not be easy, and not every obstacle she faces is born of ignorance, misunderstandings, or legitimate differences of opinion. Just as Princesses are sent to deliver Light unto the world the Outer Darkness also has it's servants, sent forth to smother the land in misery and despair. 

In the centuries where the Darkness stood unopposed by the Light's champions mankind learned to defend itself. Very few parts of the world can call themselves safe and free from the Darkness' predations but in many places the Darkness is forced back into the Shadows by the vigilance and sacrifice of mortal monster hunters, and in modern nights the victories come quicker and at less cost as Princesses pledge their blades to the cause. In these places a Princess who believes her time and magic is best invested elsewhere can have a long and productive career without ever fighting a monster. 

But elsewhere the Darkness rules, humans are little more than prey for monsters stalking the night. Despair fills the air and every day another friend gives up hope and joins the ranks of the desperate, his body warping into a form as monstrous as his behaviour. Any Princess who lives here is sure to become a target if she lets her Light shine, but few Princesses let danger deter them from their duties, for such areas cry out for a saviour and many among the Radiant give up their comfortable surroundings to go where they are most needed. If they do not the Court of Storms are sure to do so; for no matter how deeply rooted the Darkness is, fire can always burn it out, along with anyone unlucky enough to be nearby. 



The Darkness comes to every place where one person makes another suffer, and where people sink into despair. At sites of enormous cruelty - where depraved scientists performed dreadful experiments on human subjects; where kidnapped girls were sold into sexual slavery; where hardened killers waited to ambush their victims - the call of pain and fear brings it in crashing like a wave of foul water. Lesser evils, if constantly repeated \textemdash\, offices whose managers wield their authority to reduce everyone to quivering bootlickers; streets haunted by muggers who strip passersby of valuables; houses of drunkards and addicts who think of nothing past the next fix; quiet suburbs full of backbiters, talebearers and petty rivalries \textemdash\, let it drift in and build up slowly, like thickening smog.


Quickly or slowly, once the Darkness has its grip on an area, it pulls the virtue out of it. It’s just so much eas-
ier to slip into habits of cruelty when hope seems far away, when the light in the air is flat and dirty, when every-
one seems so coldly indifferent. The Darkness ensures that those who walk where it has touched are blighted
and overshadowed; it sows temptations in their path, and tightens its hold if they yield. And as its corruption
grows, a Dark World, a ruined mockery of the Earth frozen under a flickering ember where the Sun ought to
shine, grows a little warmer as the Darkness brings it the stolen virtue, and the monsters stir and hunger.\end{comment}


\end{multicols}
