\chapquotenolabel{Introduction}{My name is Shoutan Himei. I'm sixteen years old, and I'm very tired. \\ \textendash\, Sailor Nothing}
\label{cha:introduction}

\begin{multicols}{2}

\noindent No matter how old we may be now, all of us were once young. The world was unexplored and exciting, full of possibility. What we lacked in experience and wisdom, we made up for in possibility and enthusiasm. We dreamed of fame, fortune, wealth, glory, respect. We wanted to be astronauts, cowboys, firemen, doctors, singers, rock stars, or all of the above at once. After all, we didn't know what was possible – and that meant ANYTHING was possible. We looked at the world through guileless eyes, felt it as fully and intensely as anyone ever could. When we came to a new idea, we embraced it zealously and whole-heartedly, convinced we'd found the secret that would change the world. When we loved, we were convinced it was the most passionate ever felt; when we hurt, we thought it was a tragedy the likes of which had never been seen. We were convinced that we had the whole thing figured out, that we could make everything perfect if we just had a chance, if the grown-ups would just listen. After all, we could do 
anything if we put our mind to it. We were fearless. We couldn't wait to grow up so we could grab life by the horns.

And as we mature, we realize the follies of our youth. We learn that our love and pain are not unique, that everyone in the world has gone through the same; this was comforting, but it was also disappointing. We found out that there are no more cowboys, that we didn't have the money or determination for medical school, that we couldn't pass the physical to be an astronaut, that becoming a famous musician is just a matter of luck and we'd probably have to get a job doing something boring, or, even worse, something LAME. We learned that growing up isn't about suddenly being able to do everything you ever wanted; it's mostly about learning how stupid you were when you were young. We learned from our mistakes and shook our heads, wondering how we could ever be dumb enough to make them in the first place. Our potential was replaced with reality. We found out that no, life wasn't going to be an open book for us. We became jaded, we figured out we're not that special, that the things we love aren't really the best things in the universe, that our fresh new ideas had been tried before a thousand times.

Yet, even after learning this, we still long for the fire and passion of our youths. Yes, we know that we're not that special, and yes, we know the things we believed were silly... but wouldn't it be nice if they weren't? The promises of our youth could never be fulfilled... but it still felt good to think they could, right?

They can. We didn't get wiser when we grew up, we just became more cynical. We weren't stupid back then, and our greatest mistake, our only mistake, was telling ourselves that we were. We stopped putting all of our selves into everything we did because we became too afraid of failing, of letting ourselves get hurt by the effort. So we told ourselves that trying was silly. We abandoned the dreams we had rather than see them fail. We gave in to our fears.

And now, it's time to overcome them.

\section*{A Game Of Fighting Fear}

Princess: The Hopeful is a game about the promises of our youth fulfilled, inspired by the “maho shoujo” (“magical girl”) genre of Japanese anime and manga. Princes and Princesses are those who haven't given in to that fear of inadequacy and failure. They come from a world unlike the World of Darkness: a better world, a kinder world, a just world. They come from the world we all wished we could make before we knew it was impossible – and they seek to prove us wrong. A better world wasn't impossible, and it still isn't. As a Princess, power isn't a gift to you, it's a responsibility.

\textbf{You can fix problems}. There's too much we just resign ourselves to. We say, \textquotedblleft That's just the way it is," and live with the pain. You don't have to. You can do things, real things, to solve people's problems. You don't have to feel frustrated. You can be their white knight against the cruel world. Few people have the power to do this, and the chance to see the world work the way we think it should is too tempting to pass up.

\textbf{But some problems don't want to be fixed}. Life is a Gordian knot. There's not always an easy way to do things, even against apparently supernatural threats. People are complicated and confused. They will often act against their best interests without thinking. Many insist on the status quo because they know how to live with it, and something new would make all their supposed wisdom worthless.

\textbf{Because doing good can be terrifying}. An angel is another kind of monster — a kind who relentlessly does what they believe is right and doesn't apologize for it, frequently frightening those around them. It's understandable. You have power and they don't. No matter how kind you try and be, you're taking the decision out of their hands. Not everybody will be thankful. Many will try to destroy you or chain you down. They might be right. They might be wrong. To act, you need the resolution to decide what is what. Many will call that inhuman.

\textbf{And sometimes the good guys can't win}. You're powerful, but you aren't all-powerful. You can't be everywhere at once. You can't account for simple bad luck. No matter how much you want to believe otherwise, you can and will fail. People will die. People will suffer. And because you're in the thick of it, you're going to feel their pain worse than if you stayed at home and turned on the TV. Doing the right thing can be a trial without end.

\textbf{But you can't walk away. Because sometimes they do}. Blissful ignorance is no longer an option. You can't hide behind the excuse that there's nothing you can do. And, sensitive to the hearts of others, you can't shut out their pain -- or their joy. Those rare moments of beauty and happiness are what make the fight worth it. You need to protect that, because without those occasions of hope, life is not worth living. Once your eyes are open to that fact, it's hard to shut them again.

\textbf{Nothing will be the same}. The world will never be the same after you. You are going to change things, even if you're too small for the cosmos to notice just yet. You're a force of chaos, shaking people from the sleep they've been in. Once you start performing your little miracles, people will take notice. Living with and for others means you can't always be discreet. You're different. You're not playing by the rules anymore. You're laying down new ones. Once people understand these new rules, they'll try and exploit them, like they did with the old ones. You are a revolutionary force.

\textbf{You'll just have to find out for yourself}. In the end, a world of darkness is a world of possibilities. Many of them are not pleasant -- we've spent millennia creating societies of light expressly out of fear of them. Under the blanket of night lies an undiscovered country. It might be empty, waiting for you to build your own palaces. It might be flush with danger, patiently lying just out of sight. And it might be hiding the very treasures we've thought were impossible. The darkness, the shadows, the occult -- they're like Pandora's Box. In it might lay evils we can't imagine. But slam the lid too fast, and you lock away Hope forever.

\section*{Theme: Fighting Fear}

Princess is a game about making a difference. A Princess can defeat the monster, win the election and start instituting reforms, and rescue the cute boy. However, to do it, she’s going to have to face her fears. The monster isn’t a harmless creature from a Saturday morning cartoon. Death is a real possibility, serious injuries are likely, and nightmares are almost inevitable. The election isn’t won with a short speech about hope, it’s a dirty campaign where the princess's good name is viscously dragged through the mud. Sometimes, the hardest part about being a hero is just ignoring how embarrassing it is to stand up for what you believe in when everyone says you're wrong. A Princess can save the day, but she’s probably going to have to stare down her own nightmares to do it. 

\section*{Mood: Exhaustion}

Sure you can solve one problem, but can you solve all of them? Can you find the energy to run for mayor, mentor the people who need it and spend all night fighting monsters? When will you sleep, and when will you have room for some desperately needed me time to think about your own problems? A Princess’ magic makes her feel like every problem in the world is her personal responsibility, it’s an impossible burden that will wear her mental, physical and even emotional stamina to nothing. The only way she can survive is if she can find friends to support her and allies to share the load. 

\section*{How To Use This Book}

Information on the Nobility, and their obligations are divided into several sections:\\

\noindent Chapter One: Noblesse Oblige provides information on the Nobility: their magic, their culture, and their world. \\

\noindent Chapter Two: Coronation explains how to create a Princess character and describes the innate traits of  Princess.\\

\noindent Chapter Three: The Power of Love lists the many wonderful magics and new character traits available to a Princess. \\

\noindent Chapter Four: Fighting Fear lists the monsters and antagonists who oppose the Hopeful and all they stand for.

\section*{Credits}

Princess: the Hopeful is a collaborative effort of posters on the RPGnet forums. \\
Special Thanks To: Azunth, Cruton, Darinas, EarthScorpion, Huitzil, Kearin,\\ Luc \textquotedblleft Nickname\textquotedblright\, French, Michael Brazier, Naomi Li, TheKingsRaven,\\ and everyone else on RPGnet and elsewhere \\ helped in the development of Princess: the Hopeful. 

Title page by: Kaya Oldaker

\section*{Sources and Inspiration}
%I  was a bit confused by this section. I think it is about media that might inspire players and GMs when they run Princess, but the section title makes it sound like it's a list of works that inspired you, the devs. It might be useful to add a brief paragraph at the beginning of this section to clarify exactly what you mean, like "Various works inspired us to create Princess: the Hopeful. Here is just a handful of these works; they might inspire you in your gameplay." 
\subsection*{Maho Shoujo}

\subsubsection*{Sailor Nothing}

\textit{Sailor Nothing} is one of the oldest deconstructions, and also reconstructions, of the magical girl genre. \textit{Nothing} sets itself apart from many later deconstructions by showing the horror inherent in the concept of young girls fighting monsters rather than relying on some dark secret at the heart of the magical girl powers. With the focus given to mundane evils and the importance of friendship, \textit{Nothing} is perhaps the quintessential inspiration for Princess. It inspired us when we wrote Princess, and we hope it will inspire you as well. 

\subsubsection*{Mai-Otome}

\textit{Mai-Otome} takes the magical girl genre into places it does not normally venture: politics. \textit{Mai-Otome} is about two girls (one a literal princess) forced to grow up by the harsh realities of realpolitik, in the process learning that being a magical girl is so much more than looking amazing. With friendship, growing up, magical girls, and Realpolitik, \textit{Mai-Otome} serves well as an inspiration for Princess: the Hopeful. 

\subsubsection*{Puella Magi Madoka Magica}

As one of the most popular maho shoujo to be created in recent years, this list would not be complete without a mention of \textit{Puella Magi Madoka Magica}. The truth at the heart of the Puella Magi makes it harder to use \textit{Madoka} for inspiration, but, around the edges, those Puella Magi who never learn the truth show all the struggles and heartache you might find in a Princess. 

\subsection*{Film}

\subsubsection*{Brave} 

\textit{Brave} is a story about a rebellious princess with a difference. It shows the consequences of a princess rebelling against her obligations; that alone makes 
it a worthwhile inspiration for Princess: the Hopeful. The themes of growing up and the importance of family only sweeten the deal. 

\subsubsection*{Coraline}

\textit{Coraline} falls under the archetype of \textquotedblleft girls underground\textquotedblright\, stories. This archetype provides themes for the Dreamlands, and for that purpose, Coraline does not disapoint. Coraline's adventures help her grow as a person, and she returns better able to face the real world. Her antagonist also provides the quintessential inspiration for a Warden. 

\subsubsection*{Peter Pan}

Another girls underground story, \textit{Peter Pan} (the live action film released in 2001) is a brilliant portrayal of what we fear about growing up and why we overcome those fears. It can serve as an inspiration metaphorically or more literally to show why living a utopian life in the Dreamlands isn't always the perfect choice, even for Beacons with no royal duties to call them back. 

\subsubsection*{Spider-Man: Homecoming}

When Spider-Man debuted in 1962, the concept of an ordinary person with realistic, relatable, problems as a superhero was revolutionary. Today, Spider-Man's struggles to balance his superheroics with his secret identity is a good example of the struggles a Princess might face; while his over-active sense of personal responsibility is a common trait in the Nobility. The recent film \textit{Spider-Man: Homecoming} demonstrates both traits, but many other portrayals of the iconic character cover the same ground. 

\subsection*{Literature}

\subsubsection*{Animorphs}

Five human teenagers (and later, one alien teenager) are granted body-morphing powers by a dying alien prince to fight a guerrilla war against a clandestine invasion of brain-controlling alien slugs. The series delves freely into the darker realities of being a child soldier: dead friends and allies, captured family members, impossible moral choices, the fog of war, and PTSD. Over the course of over 50 books, the main characters go from being innocent children to battle-hardened soldiers before they're even old enough to vote. Animorphs serves as a stark reminder that being a teenager with superpowers is not quite the wish-fulfillment fantasy it's made out to be... but it's also a reminder of the importance of keeping up the fight, even when the best you can do is stall for time until backup arrives, just to keep the spark of hope from going out completely.

\subsubsection*{The School for Good and Evil}

When the lonely outcast Agatha and her only friend, the beautiful and popular Sophie, are sent to The School for Good and Evil, both girls are shocked to discover that Agatha has been labeled good and Sophie evil. Together, they struggle to cope with the school's strict rules and the narrow archetypes to which they are expected to perform. 

The School for Good and Evil makes inspirational material for Princess: the Hopeful for a simple reason: Sophie is a note-perfect example of how a Princess of Mirrors could think and act.

\subsection*{Live-Action Television}

\subsubsection*{Black Lighting}

Black Lightning's quest to free his hometown from the all-powerful drug gang The 100 covers many notes appropriate to a Princess story. The conflicting demands between Black Lightning's superheroics and mundane life, as well as Black Lightning consistently using both his superpowers and his day-job as a high school principal to help his community, are useful inspirations for Princess (even if they would fall under different Callings in the Princess setting). The outburst of hope seen in the early episodes, when Black Lightning returns from retirement, is also good inspiration for how a Princess's fans might react to her activities.

\section*{Lexicon}
\label{sec:lexicon}

\begin{itemize}
  \item Acqua: The Invocation of the Queen of Diamonds.
  \item Aria: The Invocation of the Queen of Spades.
  \item Alhambra: The last surviving city of the Kingdoms, ruled by the Queen of Tears and sustained by stealing hope from the world. 
  \item Beacon: A human with enough kindness and optimism to manifest a tiny fragment of the Light.
  \item Belief: A Princess's ideals, principles, and hope that the world can be saved. Belief serves as the Integrity replacement for Princesses. 
  \item Bequest: A magical item that grants the wielder access to a Charm. Only Beacons, Princesses, Shikigami, and Sworn may use a Bequest. 
  \item Blessed Place: A place where a great good has taken place; people within feel uplifted and discover themselves to be more capable. 
  \item Calling: The method by which a Princess attempts to help the world. 
  \item Cataphractoi: Rare and powerful creatures of the Darkness. Cataphractoi are ocasioanlly created when a human commits suicide and attempt to mimic habits from that person's life. They don't really distinguish between self and other and have an innate ability to command Darkspawn, so they often end up leading Darkspan in their activities. 
  \item Campaign: A large gathering of Princesses who've come together to solve an emergency. 
  \item Champion: Princesses who seek to help the world through their own physical prowess, often by fighting evil — though other manifestations of the Calling exist. 
  \item Charm: A magic spell that a Princess can learn and use. 
  \item Clique: A social group of Princesses. Cliques keep an eye out for each other and help each other relax after a hard day's work. Contrast with Nakama.
  \item Clubs, Queen of: The Queen who teaches her followers to find harmony with others and the world around them.
  \item Commonality: The strength of the emotional bond between a group. A Princess can use some Charms upon an entire group. The stronger the bond, the easier it is to do so. 
  \item Court: The collective term for a Queen and all her followers. 
  \item Crawlspace: The astral representation of a Princess's own mind and soul. A Crawlspace is always uncomfortable and hard to traverse because one use of the Crawlspace is to travel through it to the Dreamlands, and the Princess's subconscious tries to warn her away from The Trap (even though the Trap is no longer functional). 
  \item Darkened: A human infected by the Darkness. They can wield dark magic and risk losing their humanity. Darkened can be cured by Charms or by rebuilding their Integrity. 
  \item Darkness, the: A force of despair, cruelty, decay and corruption. Little is known about what the Darkness actually is. 
  \item Darkspawn: The most common minion of the Darkness. Darkspawn are animalistic and always evil. They cannot be cured and must be slain. 
  \item Dark Door: A portal found within Tainted Places that leads to the Nightscape.
  \item Dark World: A parallel reality controlled by the Darkness. An apocalyptic hell-scape no Princess would willingly enter, except in the most dire need. 
  \item Dethroned: A Princess who has abandoned all hope and become a warped and twisted monster. Most Dethroned live in isolation and suffering, but occasionally they can become a terrifying danger to humans and Princesses alike. Dethroned can be redeemed with great difficulty. 
  \item Diamonds, Queen of: The Queen who teaches her followers to solve problems through knowledge and reason.
  \item Dreamlander: An inhabitant of the Dreamlands. Most are a personification of something from humanity's collective unconscious. That said, all sorts of other creatures have ended up settling in the Dreamlands, including the souls of most of the Kingdoms' inhabitants. 
  \item Dreamlands: The collective unconscious of all humanity, as perceived by Princesses. 
  \item Dual Identity: An innate magical effect common to all Princesses, Dual Identity makes it exceptionally difficult to realise a Princess's mundane and transformed identities are the same person. 
  \item Echo: A side effect of a Princess's Inner Light, an Echo makes her actions more noticeable and emotionally impactful, for good or ill. 
  \item Embassy: The Z-Splat of Princess: the Hopeful. Princesses join an Embassy by accepting a foreign concept into their own magic. Most do so because they wish to redeem that concept. 
  % What's a Z-Splat? Can't find a definition online. 
  \item Enlightened, the: Another term for a Princesses. 
  \item Fuoco: The Invocation of the Queen of Swords.
  \item Gales: A natural feature of the Dreamlands which warps the mind and memories of anyone who stays in the Dreamlands too long. The Trap worked by keeping the inhabitants of the Kingdoms in the Dreamlands long enough to be affected by the Gales. 
  \item Goalenu: A part of the Queen of Storms given temporary independence to serve her will. Goalenu are ephemeral beings, but they can inhabit specially crafted bodies. 
  \item Grace: Princesses who seek to help the world through encouragement or leadership. 
  \item Hearts, Queen of: The Queen who teaches her followers to build and lead societies.
  \item Heraldry: Items and apparel that are part of a Princess's transformed identity but are merely decorative, such as clothing. 
  \item Hopeful, the: A collective term for Princesses. 
  \item Inner Light: The overall strength of a Princess's magic. 
  \item Intimacy: The strength of the emotional bond between a Princess and another. A Princess can use some Charms at distance over an intimate bond, and the stronger the bond is, the easier it is to do so. 
  \item Invocation: The philosophical ideals of a Queen. A Princess who acts in accordance with an Invocation can strengthen her Charms and unlocks the potential to learn new Charms that align with the Invocation. 
  \item Kingdoms, the: The nations ruled by the Queens before the fall. Commonly held to be as close to utopian as humanly possible.
  \item Lacrima: The Invocation of the Queen of Tears.
  \item Legno: The Invocation of the Queen of Clubs.
  \item Light, the: A force of hope and virtue responsible for the existence of Princesses. Little is known about what the Light actually is.
  \item Light Touched: A collective term for: Beacons, Princesses, Sworn, and Shikigami.
  \item Luminous Beat: One fifth of a Luminous Experience. 
  \item Luminous Experience: A unique source of Experience available to Princesses. Princesses earn Luminous Experience through helping others.
  \item Mender: Princesses who seek to help the world by restoring damaged things, be it a man, a mind, or a machine.
  \item Mirrors, Queen of: The Queen who tells her followers to sit back and let destiny hand them victory on a sliver platter.  
  \item Mnemosyne: The most human-like minions of the Darkness. Mnemosyne favour using social acumen to corrupt or torment people. Though intelligent, they have absolutely no humanity or morality and cannot be cured, they must be slain. 
  \item Mundane Identity: A Princess's identity when she is not Transformed. In most regards, she is little more than a mortal. 
  \item Nakama: A social group of Princesses who support each other in both their personal lives and noble duties. Contrast with cliques. 
  \item Nightscape: The part of the Dark World immediately below a Tainted Place. A Nightscape is safer than the Dark World itself and many Princesses willingly enter them to destroy the Taint at its source. 
  \item Noble: Another term for Princesses. 
  \item Outer Darkness, the: Another term for the Darkness. 
  \item Palace: A place to which a Princess feels a great emotional bond. Some Charms are more effective when used upon a Palace. "Palace" can also colloquially refer to anywhere a Princess lives. 
  \item Perfected Self: Another name for a Princess's transformed self. 
  \item Phylactery: A physical item that represents a Princess's Beliefs. A Princess must use her Phylactery to transform. 
  \item Practical Magic: A magical ability that a Princess can use even when not transformed. Each Court provides a different form of Practical Magic. 
  \item Prince: A male Princess. 
  \item Princess: A human touched by the Light who can transform into a perfected magical self. Only people of great virtue with a strong drive to improve the world can become Princesses. After becoming a Princess, they will reincarnate upon death and reclaim their power, even if they did not live up to the standards of their first life.
  %\item Principality: An organisation run by a Princess to further her noble duties. Principalities are typically ordinary institutions.
  % Was the term "Principality" intentionally commented out? 
  \item Protectorate: A different kind of Embassy. There is no metaphysical difference between Embassies and Protectorates, but they have a significant ideological differences: Whereas Embassies wish to redeem, Protectorates wish to rule. Protectorates are created by the Court of Tears. 
  \item Queen: A Princess who has mastered her magic, completed her character development, and become the beloved leader of a nation's worth of people. Queens are significantly more powerful than Princesses, and their very existence empowers an Invocation. 
  \item Radiant: The Courts of: Clubs, Diamonds, Hearts, Spades, and Swords, as well as any member of those courts.
  %Is this meant to be "Radiant, the Courts of:"? 
  \item Regalia: Items that form when a Princess assumes her Transformed Identity. Each piece of Regalia is linked to a specific Charm and must be used to invoke that Charm, but most Charms have no associated Regalia. 
  \item Royal Favour: A unique benefit granted to the Court of Storms whereby the Queen of Storms will enact a Charm through one of her followers, at the cost of that follower's health and possibly their life. 
  %Editor: "Favour" (instead of "favor") is the British spelling. Is that intentional? 
  \item Seeker: Princesses who seek to help the world by uncovering or teaching knowledge. 
  \item Sensitivity: Sensitivity refers to a Princess's special vulnerability to emotional shocks, which can send her magic haywire.
  \item Shadows: The lasting negative effects of an emotional shock, which can dampen a Princess's power and cause severe issues if they grow unchecked. 
  \item Shikigami: A Dreamlander granted a physical body, so that they might assist and advise Princesses. Most Shikigami come from a Radiant Court, but any Dreamlander can become a Shikigami. 
  \item Storms, Queen of: The Queen who teaches her followers to destroy the Darkness without mercy or hesitation.
  \item Stormwracked: A Sworn of Storms. Notably, Stormwracked are usually created directly by the Queen of Storms and often act independently from Princesses. 
  \item Spades, Queen of: The Queen who teaches her followers to live free and think outside of the box. 
  \item Specchio: The Invocation of the Queen of Mirrors.
  \item Swords, Queen of: The Queen who teaches her followers to help the world through personal heroism.
  \item Sworn: A human bestowed power by a Princess. Sworn often serve as assistants or support to Princesses. 
  \item Tainted Places: Areas where acts of evil have been committed. They inflict penalties on everyone inside except the Darkness's minions. Humans who suffer a Breaking Point within risk becoming Darkened. Tainted Places must be purified or destroyed. 
  % Second sentence: I assumed meaning is "Tainted places inflict penalties on everyone inside a Tainted Place, except the Darkness's minions." Please change back if not true. 
  \item Tears, Queen of: The last Queen to rule a living kingdom, and who demands her subjects defend Alhambra at any cost. 
  \item Terra: The Invocation of the Queen of Hearts.
  \item Tempesta: The Invocation of the Queen of Storms.
  \item Transformed Identity: What a Princess becomes by transforming. In this form, she has greater skill and ability and can use Charms. 
  \item Trap, the: The Trap was a powerful illusion constructed within the Dreamlands. It trapped the five Radiant Queens and their followers for millennia. Currently, the Trap is barely functional.
  \item Troubadour: Princesses who seek to help the world through art. 
  \item Twilight: The Courts of: Tears, Storms or Mirrors, as well as any member of those courts. 
  % Is this meant to be "Twilight, The Courts of:"? 
  \item White Rabbit: A message created by a Princess's subconscious to alert her that she should see something in the Dreamlands. Most commonly, White Rabbits lead to an event in the Dreamlands that portents a future event on Earth. 
  \item Wisp: Perfectly ordinary human emotional energy. Princesses use it to fuel their magic. 
  %  I don't understand this definition. Is a wisp emotional energy from a perfectly ordinary human, or is it perfetly ordinary emotional energy from a human? 
\end{itemize}

\end{multicols}
