\chapquote{The Power of Love}{I never renounce my feelings. True Love can not be taken away by anyone. \\ \textemdash Sailor Moon }

A Princess is still human, and she is able to use all of humanity's varied and dangerous talents to her own advantage. A Princess is also magical, and she is capable of focusing her hopes and beliefs into all sorts of unique and potent advantages. 

In this chapter we present all the unique abilities possessed by the Enlightened, from the magical Charms they wield to new Merits.


\section*{Echoes}

The name you choose is a promise, and the Enlightened have chosen the name \textquotedblleft Noble." The Radiant know they are the example, they literally cannot help it, and so they have promised to be a good example. When a Noble is at her best people take notice, they are impressed and want to imitate her. When a Noble looses heart people notice and it scares them.  

This is magic, but only a little bit. A Princess' Inner Light makes her every action, good or bad, shine brighter. Human empathy does the rest. 

Whenever the Princess fulfils one of her Virtues roll Belief. On a success everyone who witnessed the Princess takes the Inspired condition which they may use on any roll to act in accordance with that Virtue. 

However if the Princess has a clear opportunity to fulfil her Virtue and chooses not to do so she must also roll Belief. If she fails the roll then everyone nearby takes the Shaken Condition unless they Succeed on a Composure + Supernatural Advantage roll. 

As a rule of thumb Echoes don't provide Princess' with any advantage over their enemies. If a police officer forces a vigilante Champion to stand aside for the authorities he won't be Shaken by her hurt feelings. Her feelings will be more noticeable but the officer's own belief in the importance of due process is more than enough of a shield. This goes double for people who actually want the Princess to suffer, while some Princesses have witnessed their enemies having a \textquotedblleft my god, what am I doing" moment any Princess who expects or relies on her Echo protecting her from her enemies is an idiot. 

\section*{Transformation}
The most essential expression of a Princess' power is the ability to transform. She calls on the magic she's gathered to herself and assumes the form of her \textquotedblleft perfected self", an idealized version of herself unfettered by this world of sorrows. Although she can only maintain this immense power for a limited time, a transformed Princess is a force to be reckoned with.

The first time a Princess transforms is called her Blossoming. This is an unconscious act, usually in response to some great need or danger. After her Blossoming, a princess' Phylactery will manifest. This is the physical representation of the power sealed away inside of her, and may take the form of any small simple object. She must have her Phylactery with her later to transform. When a Princess wishes to transform, she has two options: she may either spend a Wisp or make a transformation roll. If she spends a Wisp, she transforms automatically, as a reflexive action. The transformation roll is Belief + Inner Light - Shadows. 

\begin{myindentpar}{10pt}
    \emph{Dramatic Failure:} The Princess' Phylactery discorporates. She must spend a Wisp and a Willpower point to resummon it, which takes a full round and requires her absolute concentration. 
    
    \emph{Failure:} The Princess fails to transform and spends the full round. 
    
    \emph{Success:} The Princess transforms as an instant action. 
    
    \emph{Exceptional Success:} The Princess transforms as a reflexive action.
\end{myindentpar}

A Princess can return to her ordinary self at any time as a reflexive action. She must de-transform if she spends her last Wisp, or when she falls asleep. Also, transformation grows harder to sustain as time passes. When a Princess reaches the end of a scene transformed, or after half an hour spent transformed, she rolls Belief + Inner Light: 

\begin{myindentpar}{10pt}
    \emph{Dramatic Failure:} The Princess returns to her mundane self and her Phylactery discorporates. She must spend a Wisp and a Willpower point to resummon it, which takes a full round and requires her absolute concentration. 
    
    \emph{Failure:} The Princess must spend a Wisp to remain transformed in the next scene, or the next half-hour, and future rolls to remain transformed take a -2 cumulative penalty until she ends a scene in her mundane self. 
    
    \emph{Success:} The Princess remains transformed at no cost. 
    
    \emph{Exceptional Success:} The Princess remains transformed, and need not make this check at the end of the next scene, or for a full hour. 
\end{myindentpar}

While transformed, a Princess has full access to all of her Charms and abilities, and also gains the benefits below. 

\subsection*{Dual Identity}
One aspect of the Hopeful's transformation is subtle but amazingly convenient: the mundane and transformed selves appear to be different people, and those who have seen one of the Princess' forms generally fail to recognize her in the other form. A simple perception roll never reveals a Hopeful's identity; to discover it requires active scrutiny, akin to seeing through a normal disguise.

Whenever an observer has evidence that the two forms of a Princess are connected, he may roll his Wits + Subterfuge, contested by the Princess' Wits + Subterfuge. 

\begin{myindentpar}{10pt}
    \emph{The witness rolls Dramatic Failure:} The witness dismisses his evidence entirely, and takes the Incredulous Condition making future attempts to identify that Princess even harder. 
    
    \emph{The Princess wins the roll:} The witness fails penetrate the Princess' dual identity. 
    
    \emph{The witness wins the roll:} The witness he identifies the Princess correctly.
    
    \emph{Exceptional Success:} The witness also takes the Informed Condition regarding the Princess. 
\end{myindentpar}

If the Princess rolls an Exceptional Success downgrade her rivals result by one step: Exceptional Successes becomes Successes, Successes becomes Failures and Failures become Dramatic Failures. On the other hand if the Princess rolls a Dramatic Failure then upgrade the witness' result by one step.

This protection does not apply to research rolls designed to gather evidence, or to direct observation of a transformation. If someone sees a Princess change, he will know who she is thereafter without any roll. If a Princess's mundane and transformed selves are seen close together, or she reveals knowledge in one form that she learned in the other, that counts as evidence and justifies an identification attempt; and the storyteller should give an observer bonuses if he has found multiple pieces of evidence through research. 

Supernatural powers that could reveal a Princess' identity are confused by her Transformation. An entity cannot even begin to discover her identity by using such a power before he realizes that she can transform. Once the Princess' nature is known, the supernatural observer may roll either Wits + Subterfuge as above, or his usual roll for examination, to deduce her identity and the Princess contests either way. 

When targeting magic against a Princess. Intimacy or similar traits connecting to one of the Princess' forms does not connect to her in the other form, even for those who know her secret; even the Hopeful's own Charms, when modified by Intimacy, respect another Princess' privacy. If a power is currently targeting a Princess through a Intimacy connection, transforming instantly looses track of her. 


\subsection*{Phylacteries}

Every Princess has a Phylactery, a physical item that symbolises exactly what being a Princess means to her. A Phylactery is also the source of a Princesses power to Transform, she must activate it, open it, apply it to herself, or at least touch it if she wishes to Transform, this limit affects anything described as a Transformation action. Many Phylacteries also Transform with the Princess, becoming larger and more ornate or becoming the Regalia linked to a Charm strongly associated with her duties (a Phylactery is simply a specialised piece of Regalia and share most of their rules). The rest remain as they are, but are incorporated into her Heraldry. 

A Phylactery has a Durability equal to Inner Light and a Structure equal to Belief, typically it will have a Size of 0 - 2. If her Phylactery is destroyed or lost, the Princess can recreate or summon it. She must spend a Wisp, a point of Willpower and concentrate for a full round. 

If another was to steal a Princess' Phylactery they would be unable to use it, but they would be able to target the Princess through an unbreakable Intimacy link with a strength equivalent to love. Fortunately any technique that would cut the connection Princesses use to summon her Phylactery would, by definition, destroy it.

\section*{Practical Magic}

In addition to the immense power each Princess wields in her Transformed identity, the Nobility can also wield Practical Magic. A subtle magic that she can call upon in both her Identities. Which abilities a Princess possesses depends upon which Queen she follows and the details can be found under the relevant Queens. 

\subsection*{Countless Practical Magic}

Courtless Princesses draw upon their own perfected self rather than their Queen. While in their mundane form they can spend a Wisp to one raise one of their Attributes or Skills to the level of it's Transformed equivalent for a single turn. They may spend extra Wisps to affect additional traits.

High Belief allows the first Wisp spent per turn to affect multiple traits. At Belief 8 it affects two traits, at Belief 9 it's three traits, and four traits at Belief 10.

\section*{Modified Merits}

\subsection*{Mentor (\textbullet - \textbullet\textbullet\textbullet\textbullet\textbullet)}

The Mentor Merit detailed in the World of Darkness Rulebook focuses on relations within mortal or supernatural society. While both of those can be of great help to a Princess, a further option is available to a lucky few Princesses: Personal mentorship from their Queen. Even though a Queen cannot leave the Dreamlands, she still has such a wealth of power and experience that she would be far beyond a five dot Mentor. However the Queens have many obligations that demand their time besides tutoring a Princess. Therefore when applied to a Queen the Mentor Merit represents not her skill (rather than three skills, Queens can be assumed to have every skill. Even the Queen of Clubs has the raw intellect and magic to master computer programming in an hour or so if she was ever given a reason), but how much of her attention she will bestow upon the character.

As a general rule you may assume that for each Dot in Mentor you get at least one chance to talk with your Queen per Session. A chat can be just a few moments before the throne, but at high dots it can be significantly longer. After a consulting with your Queen you either gain the Advised condition or more direct clues about what you should be doing next. 

When portraying the Queens the Storyteller should always remember that they have had no contact with earth for millennia and are consequently out of touch. Therefore no matter how many dots a Princess has in Mentor and no matter how important it is; the Queen of Hearts cannot reveal to her followers the innermost secrets of the Chinese political system. Instead she can teach the Princess how to discover such secrets herself.

A Princess must follow a Queen before she can place dots in Mentor in a Queen. Neither Storms nor Mirrors will serve as Mentors. A follower of The Queen of Tears cannot place more than three dots of Mentor into her Queen. The Queen of Tear's kingdom is under siege and conforms to the normal rules of time, she just does not have enough time to spare.

Zero dots: As a Princess you are always welcome to attend court, but unless you have important business your Queen will focus her attentions on those who do. When the players have an emergency they can usually get a chance to explain and some advice. The amount of time received depends on how serious the emergency is, and whether the Princess should be able to handle it or needs significant help. Remember that both of these are opinions and two Queens might see the same situation differently. The Queen of Swords considers loosing a boyfriend as roughly equivalent to a small crisis. Even her own followers often think that's taking things too far.

With one dot a Princess can usually get the occasional snatch of time whenever there is a lull in court proceedings. Enough time to talk about recent events or ask questions and get a brief bit of advice.

At three dots the Queen often has your name in the royal itinerary for time with you alone, or perhaps group sessions with your Nakama. You have the opportunity to talk at length about your progress in the war of hope and receive private tutoring. You also know what your queen is like when she has an opportunity to take off her crown, so to speak. Generally speaking a Princess with three dots of Mentor has something special about her that caught her Queen's eye. Something the Queen is especially keen to nurture. She may be the only Onceborn in the Court or have the largest following among the Queen's court. Perhaps she was someone the Queen respected in a past life or maybe the Princess works full time as one of the Queen's agents upon Earth and must report in often (This can be especially helpful for beginner players as it both justifies clear goals for the character and advice from the Storyteller).

At five dots the Princess is spending at least an hour or so with the Queen most nights, and if they don't show up the Queen may even get worried and send one of her other followers to check on the Princess. This level of attention is exceptionally rare and Characters who have five dots are either vital to the Queen's agenda or have an exceptionally strong personal connection. Perhaps the Queen believes the Princess might become a Queen herself and has dedicated herself to making sure it happens. The Princess may be the first Ambassador to a concept the Queen cares for greatly. Alternatively the Queen and Princess might have an immense personal bond of friendship, or maybe the character is the Queen's consort (though this is usually only an option for followers of Swords).

\subsection*{Retainer \textbullet+}

While Princesses have as much benefit from a normal human retainer as anyone else they may also seek out Beacons, accept the fealty of Sworn, or travel with Shikigami. 

For a Beacon or Sworn, their magical abilities are basic add a single additional Dot to their effectiveness, and merit cost, as a Retainer, this remains true even when one person wields both the magic of a Beacon and a Sworn. 

Even though Shikigami typically have a mentor-student relationship with the Nobility their lack of connections or influence in the waking world and their loyalty means that they are better represented by the Retainer merit. Since the typical Shikigami is a person of note in the Dreaming Kingdoms and has access to magic they're rarely worth less than four dots as a retainer. As a special rule a Nakama can split the cost of a Shikigami between them, after all one of a Shikigami's most useful abilities is serve as a magical relay between all the Princesses it is bonded with. 

\subsection*{Sympathetic \textbullet}

Princesses are good, perhaps too good, at letting others get close. The Sympathetic Merit can be brought by Princesses for only one dot. 

\subsection*{Taste \textbullet}

A Princess' Transformed self, and the Regalia she wears are the innermost expression of who she wishes to be. This expression is influenced by her culture, this is why Princesses in Europe who wish to be \textquotedblleft pure\textquotedblright often have white as a prominent motif in their Regalia, while Princesses in much of Asia often wear white if they wish to work with ghosts. When used to study Regalia the usual questions answered the Taste Merit can be asked about the Princess herself. On an Exceptional Success gain the Informed Condition, applying to the Princess' self identity. 

\textbf{Drawback:} Studying a person isn't quite the same as studying an object, the Princess can contest the roll with Manipulation + Subterfuge to cloud the issue. If the Princess disguises her regalia with magic the benefits of Taste are no greater than when studying the fashion of any other disguise.

\subsection*{Vice-Ridden}

Princesses cannot take the Vice-Ridden merit. The worst examples of humanity simply don't Blossom.

\subsection*{Virtuous}

All Princesses have two Virtues, therefore a Princess may not take the Virtuous Merit.


\section*{Noble Merits} 
The Hopeful may buy Merits with Attribute or Skill prerequisites that they only meet when transformed. If they do so, they only gain the benefit of the Merit in question while in their transformed identity. You may convert transformed dots to mundane dots unlocks Merits with prerequisites in the mundane identity if the character's new mundane traits are high enough to support the Merit.

Below are new Merits related to the Princesses. Unless otherwise noted, all these Merits are reserved to the Hopeful. 

\myframe{\subsection*{Transformed Merits}

Sometimes a Princess has a merit which only applies in her Transformed identity. Her perfected self may be significantly prettier than her mundane self (that's a common one), she may transform into a tougher person. Alternatively a Princess may live off the grid in her mundane identity but have achieved fame for her exploits in her Transformed identity. Every time a player buys a Merit she can declare it only applies to one identity and take a Beat. Transformed Attributes and Skills count towards any perquisites, but only in the Transformed identity of course. 

\vspace{6pt}

If the Princess puts in some effort most merits can be expanded to cover both identities. A Princess who is Fleet of Foot in her Transformed body could train herself at running in her mundane body. This costs nothing more than repaying any Beats given for taking a Transformed Merit. 

\vspace{6pt}

This only applies to merits that are part of the character. Resources, Contacts, and any merit that represents something external to the Princess do not provide Beats. They are assumed to belong to one identity by default, unless the Princess wants her Contacts to know about both her identities.

}

\subsection*{Circle (\textbullet\nobreak\hspace{.16667em}-\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet\textbullet\textbullet)}

The human mind was not designed for large numbers. When the suffering of millions feels incomprehensible, you can turn to the small every day problems and triumphs of friends and family to remind yourself what you are fighting for. The Circle Merit represents healthy relationships between a Princess and her family, close friends, or mentors, who are ordinary mortals (not supernatural in any way.) The more dots a Princess has, the more or the stronger these relationships are and the healthier her social life is. Describe the people your character is intimate with when you buy dots in Circle.

Once per day a Princess with this Merit can spends an hour socialising with her Circle and regain up to (Circle * 2) - Shadows Wisps. She doesn’t have to speak to every friend she has in an hour, like most people she probably different friends or family members at different times. 

Friends and family are good for more than Wisps, they also provide a support network which provides pervasive modifiers to Compromise rolls. A Princess with two dots of Circle gets +1 to all Compromise rolls, at four dots the bonus increases to +2, however a Princess with no Circle has a -1 penalty to all Compromise rolls.

\textbf{Drawback:} Friendships require investment, family is more forgiving but even a family relationship can grow distant. If a Princess goes a significant amount of time without socialising with her Circle she may loose dots. 

\subsection*{Emotional Intuition (\textbullet\textbullet\textbullet)}

People are always being told to follow their heart, and when your emotions are the source of magical powers following your heart can lead you right. Once per chapter you may ask the storyteller one of the following questions. Roll Belief, on a Success the storyteller answers truthfully. On a failure you get no answer. An Exceptional Success lets you ask a second question. If a character has been attempting to deceive the Princess they get a roll to contest any questions asked about them. Even if they are not present they can contest, the defensive roll represents any false impressions the Princess retains from past deceptions. The Storyteller should roll the target's Manipulation + Subterfuge in secret. If the target wins the answer is what they would want the Princess to think.

\begin{itemize}
 \item How will this character react to this action?
 \item How does this character feel about this thing?
 \item How does this character feel about that person?
 \item What is this character hoping to achieve? 
 \item Can I trust this character? 
\end{itemize}


\subsection*{Entwined Destiny (\textbullet\textbullet\textbullet)}

Prerequisite: Hopeful or not supernatural. Gaining another supernatural template does not break the bond from this Merit, but the benefit and drawback from it cease to apply. (Note that supernaturals of other types can be the subject of an Entwined Destiny.)

You were bound to another before you were born, and both events and your inmost will urge you towards a specific role in his life. When you take this Merit, choose the nature of your relationship with its subject -- true love, rivalry, protection, loyalty, and enmity are all possible, and if none of these fit you may define your own, with the ST's approval. You may also choose the subject's name and general nature, or leave that up to the ST to decide. Once a scene, whenever you succeed in a significant task that plays into your destined role, you regain 1 point of Willpower.

Entwined Destiny cannot directly influence an person's choices, but when you have this merit Fate will attempt to nudge you in certain ways. For example if you have an Entwined Destiny of love Fate cannot make you feel love. Instead Fate can and will create coincidences where you and your destined bump into each other in circumstances appropriate for heart to heart talks. If the destiny is natural it can also be assumed that your destined true love are compatible people, your destined ward will need a protector, or similar.

\textbf{Drawback:} In any scene when you have an opportunity to fulfil your destined role in dramatic action, and deliberately forgo it, you take a -2 penalty on all your actions until the scene ends. For example, if your destined rival challenges you, you must accept; if you discover your destined enemy's plot, you must oppose it; if your destined ward is in peril, you must rescue him.

\subsection*{Iaijutsu Kensai (\textbullet\textbullet)}

You have learned to use Transformation itself as a weapon, manifesting your Regalia mid-motion to catch your foes by surprise. Whenever your Kensai weapon is not manifested and you Transform reflexively you may roll Wits + Brawl or Weaponry vs Wits + Brawl or Weaponry. If you win you may make an attack using your Kensai weapon that bypasses your opponent's Defence. 

A character who witnesses you using Iaijutsu Kensai is immune to it for the remainder of the scene. 

\subsection*{Onceborn (\textbullet\textbullet\textbullet)}

Available at character creation only.

You are one of the rare people who Blossomed, and became one of the Hopeful, without any memory of a past life as a Princess; your soul was never trapped in the Dreamlands, and the bitter memory of the Fall is not yours. This unshadowed innocence grants an unusual level of moral clarity. Your Belief begins at 8, not 7.\\

\noindent\textbf{Drawback:} You have no experience from past lives to call upon. 

\subsection*{Palace (\textbullet)}

There is a difference between a house and a home. A Palace is not a place to live, though a Princess may live in one. A Palace is a place with such an intimate emotional connection to a Princess that her magic works better there than anywhere else. A Palace automatically has the Consecrated Condition, which lasts indefinitely just so long as the Princess' emotional connection remains strong. Any additional benefits of a Palace may be represented by Merits such as Safe Place or Gallery, or as Equipment. 

\subsubsection*{Palace Veiling (\textbullet\,\nobreak\hspace{.16667em}to\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet)}

Something odd happens to some Palaces, when its mistress deliberately associates her domicile with her mundane self and avoids associating it with her Transformed self. The effects of her Dual Identity seeps into her home, preventing others from connecting it to her Transformed Identity. Each dot assigned to Palace Veiling provides a -1 penalty to any attempt to find the location of the Palace when searching for the home of it's mistresses' Transformed Identity. Searching for her Mundane Identity's home has no penalty. Anyone inside the home suffers the same penalty to notice any evidence of the Princess' identity. This is not infallible, a -3 penalty is not enough for her to greet guests in full Regalia and though she might get away with leaving her magic wand on her desk, don't risk it. 

Finally a Veiling also serves to protect those inside from hostile scrying. This does not stack with any other Merits that penalize scrying \textendash\, apply the larger penalty if a character with such a Merit scrys upon a veiled Palace.


\subsection*{Royal Tongue (\textbullet)}

Prerequisite: Sworn or Hopeful. It might be possible for other supernatural creatures to find a way to mimic its effects, but that would require the active use of powers (such as the Mind Arcanum or a Majesty Devotion), and so they cannot learn the Merit.\\

\noindent You know how to produce the Royal Tongue. You can use it to enhance your Charms.

As languages go the Royal Tongue is unique, it is quite possibly the densest language there is. Meaning is conveyed not just by words but also tone and the placement of stresses, two different words could be completely identical except for where it's grammatically acceptable to use them. A monosyllabic prefix or suffix can completely change a word within it's conceptual space; the Royal Tongue has over a thousand words for friend, (and just as many for lover or sister or brother) each defines the exact details of the relationship and not only do they all come from the same root word, they all sound like that root word.

The hardest thing to do with the Royal Tongue is speak a straight sentence. Between the grammatical rules and the enormous amount of information in every word a simple sentence like \textquotedblleft thank you for helping\textquotedblright\, would, if translated into English, look like two paragraphs of flowery purple prose about the inherent virtue of teamwork. When asked how such a language came about the Queen of Hearts implied that it was deliberate, the Queen of Spades burst into laughter and the Queen of Diamonds (who's fluent in, and prefers, most Earthly languages) gave a put upon sigh.

Mortals can hear the the Royal Tongue but they cannot understand it. Many Princesses swear blind that the Royal Tongue uses magic as well as sound waves as a carrier to pack even more information into each word. The cost of this is that only Princesses, Sworn and Beacons can learn to understand the Royal Tongue. Beacons can't even speak it. To anyone else it sounds like someone singing in an unknown melodic language, the emotional intent comes across clearly but the words are incomprehensible. The Royal Tongue can't be recorded either, a Princess who hears a recording of the Royal Tongue catches at best the occasional word, it sounds as though someone has removed 40\% of the syllables and all the grammar. This is considerably more confusing than it would be in a normal language.

The most useful aspect of the Royal Tongue is to enhance a Princess' Charms (Though some Troubadours insist it's use in lyrics and poetry is more useful... Deep purple prose is an acquired taste). If you spend a turn speaking the Royal Tongue, declaring that you will use a Charm on a target, and forcing the qualia, the experience and feeling of what you are about to do, into the musical speech, your activation roll for the power gains the 9-again quality. 

Use of the Royal Tongue is a supernatural ability, and triggers the sense of individuals with Unseen Senses related to Princesses or the Light.

\subsection*{Second Calling (\textbullet\textbullet)}
Your character feels two Callings in her Heart. Choose a second Calling for her; she may recover Wisps from that Calling just as well as first, and she may follow Draems from either Calling. 

She does not gain an extra transformed Attribute dot or affinity to any Charms from her second Calling.\\

\noindent \textbf{Drawback:} Your character is bound by the Oaths of her second Calling, just as much as those of her first - both sets of Oaths are breaking points for her.

\subsection*{Tomoyo's Touch (\textbullet)}

Your character is unusually adept at manipulating her Regalia, as well as her Phylactery. While she is transformed she may Reflexively modify her Regalia as per a Transformation action as without needing to roll or spend a Wsip. She may do this once a turn. 

\subsection*{Troupe Magic (\textbullet)}

\textbf{Perquisites:} A Commonality of Dedicated. 

Your character belongs to a performing Nakama who've learned to reinforce each other’s magic, as well as their vocals. You may perform Inspire Charms as a Teamwork action even with secondary actors who do not know the Charm. 

\subsection*{Unfinished Business (\textbullet\nobreak\hspace{.16667em}-\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet)}

Something in your character's past life still haunts her, and when an opportunity to address the issue arises (which usually means tracking down the reincarnation of someone else involved) your character's past self may replace her current personality for a short while. Once per Session, while you are Transformed, you may elect to have your character's past self take over and peruse her goal. You get two experience points per dot of this Merit to represent the skills your presumably older and more experienced incarnation knew at the moment she died, you do not have to spend the experience the same way each time. If your past self causes a significant hardship for your present self, take a Beat.

Princesses who manifest their past self this way don't manifest all of their former self. In behaviour and attitude they are identical, but they are clearly people outside their own time. They have trouble forming emotional connections to present people or situations, which is extremely unusual for a Noble, and relate to the world as though they were just reading about it in a particularly dry history text book. They show a similar lack of concern about the fact they are dead. Only something which relates to her unfinished business or her own time can form an strong emotional reaction.

Not every Princess agrees with her past self and others simply don't have the time. Some find closure through therapy rather than a quest, and others seek inner peace through meditation or in their Crawlspace.

It is recommended that Characters with Unfinished Business also take the White Rabbits Merit as that ability makes a great way to provide clues to her Unfinished Business and find sitautions where you can bring out your character's past self.

If you resolve your unfinished business remove the Merit and refund it's cost. 

\subsection*{Veiling (\textbullet\nobreak\hspace{.16667em}-\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet)}

Some Hopeful's perfected selves differ so much from their mundane selves that they are excessively difficult to identify, even beyond the norm. A Princess with Veiling is one such; whenever an observer tries to connect her two identities, she adds her dots in the Merit to her dice pool in the contest. Also, supernatural attempts to discover her status as a Princess while she is not transformed suffer a penalty equal to her dots in the Merit.

If a Princess has Veiling and Anonymity the two merits have distinct roles. Anonymity makes it hard to find information about the Princess (or one of her identities). Once you have that information Veiling makes it hard to connect it to her second identity, or even realise she has two identities. 


\section*{Common Merits}
The following merits are available to both Princesses and mortals. 

\subsection*{Bequest (\textbullet +)}

Your character possesses an object, within which has been bound a Charm. This might have come from within your own soul, to be granted to another or used to boost your own powers, or might have been obtained on a quest to the Dreamlands. Some senior members of the Nobility (such that there are) make a habit of gifting trusted friends with them for, despite the cost, they can give a Princess access to powers that she might not otherwise be able to reach.

Every Bequest, like the Princesses, has two appearances: a mundane one from the vessel, and a glorious one from the Charm. And, like the Princesses, a Bequest's power can be used only when the Bequest is transformed. Transforming a Bequest is somewhat more difficult than transforming yourself; you can spend a Willpower point to do it reflexively (not a Wisp) or make a transformation roll of your Inner Light (not Belief + Inner Light.) A Bequest, once transformed, remains so for 1 scene. You need not be transformed to transform or use a Bequest, and you do not have to transform a Bequest yourself to use it.

Many permanent Charms grant bonuses to tasks falling within a Skill speciality; when one of these Charms is Bequeathed, the tasks it assists are fixed as the Bequest is made, and the character making it must have any speciality she puts into the Bequest. Anyone using the transformed Bequest as a tool gains the Charm's benefit within the speciality (or specialities) encoded in the Bequest, not on any speciality of his own. He does not get the +1 speciality bonus on actions the Bequest enhances, unless he has a relevant speciality himself.

Any of the Hopeful, whether transformed or not, may recognize a Bequest as such; she rolls her Inner Light the first time she touches it in a scene. Bequests also show up on an Unseen Sense for the Light.

Bequests based on permanent Charms apply their Charm's effect to the person holding them as long as they are transformed. Bequests based on activated Charms require the person holding them to pay the Charm's cost, and then release the Charm's effect. If a Bequest is based on an upgraded Charm, every upgrade included in the Charm applies every time the Bequest is used, and you must pay the upgrades' cost in full \textendash\, a Bequest, unlike a Charm, is not flexible. If you have an Invocation that's compatible with the Bequest's Charm, you may apply it when using the Bequest, with the same effect as it would have on the Charm.

Some Bequests simply cannot be used by anyone without an Inner Light of their own (that is, Princesses and Queens); This includes Bequests that contain the Charms: Bequeath, Accept Fealty or Long May She Reign. Bequests containing an Avatar Charm cannot be used by anyone who does not have four dots in the related Invocation.

Many Bequests carry a pool of Wisps within themselves, which their holders can spend to activate them (but not for any other purpose.) The capacity of the pool is 10 Wisps. To add Wisps to the pool, the Bequest’s owner has to carry out a duty while the Bequest is on her person, roughly equivalent to a duty of a Calling (and using the rules for them); the specific duty, and the dice pool the owner rolls, are fixed at the Bequest’s making.

A Bequest's base Merit dot cost is equal to the level of the Charm (so, for example, Charge, a Govern 2 Charm, costs two dots), plus one dot per upgrade, plus one dot if the Bequest has a Wisp pool. For more details on Bequest creation, see the rules for the Bequeath charm.

\subsubsection*{Gallery (\textbullet\nobreak\hspace{.16667em}-\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet)}

Humans are social creatures and Princesses even more so. A Gallery is a set up designed to help with anything from dinner parties to theatre shows. Each Gallery covers one Speciality. When performing any Expression, Persuasion or Socialise action which fits under a Gallery's speciality the Princess gets a bonus equal to the dots, so long as she inside the Gallery at the time. 

\textit{Example. Princess Gwendolyn of Hearts wants the mayor to invest more in the town's cultural heritage. Gwendolyn has Gallery (\textbullet\textbullet\, Dinner Parties) and has invited the mayor to discuss her proposals over a meal. She gains +2 to all Persuasion rolls during the evening.}


\subsubsection*{Lucid Dreamer (\textbullet\textbullet)}

Your character is aware of when she is dreaming and has the ability to act consciously within her own dreams. This is especially useful if someone else is inside your dreams, as it gives you the ability to interact with and oppose intruders. While in their own Dreams a mortal can roll an appropriate Mental Attribute + Integrity to perform any physical action imaginable. Whether that's imagining a gun and shooting an intruder with it or imagining the entire dream flooded with lava. A success is a success, dream guns and lava are equally powerful barring special circumstances. 

Lucid Dreaming is common among Nobility, and even more frequent among their Transformed Selves. Maintaining awareness in the Dreamlands, a universal ability for Princesses, is not much different from remaining aware in a regular dream. When only the Transformed self is a lucid dreamer it is the Princess' Transformation within the dream, not her physical body, which applies. This means that a Princess who is attacked in her dream and instinctively transforms achieves lucidity. 

While asleep a lucid dreaming Nobel uses Belief instead of Integrity, though most use their Charms instead as they are often significantly more powerful.

\subsection*{Mandate (\textbullet\nobreak\hspace{.16667em}-\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet\textbullet\textbullet)}

\textbf{Perquisite:} Princess or possession of a Bequest with a duty. \\

\noindent Every Calling has it's Sacred Oaths, the means by which a Princess feels is her duty to help the world. The Mandate Merit represents not an emotional connection to one's Calling, but a practical ability to fulfil it. Any Grace could take it upon herself to help the local bully apologise and make amends but she'll only come across so many bullies in a month. A Grace who works as a relationship councillor, she'll be seeing clients every day. 

A Mandate, therefore, represents opportunities to help people that come along as part of a Princess' day without her having to go looking for them. A Champion could work on the police force, a Troubadour could have a popular blog where she posts poetry. 

When a Princess buys the Mandate Merit, the player states how their character is in an advantaged position to make a difference. During downtime the Princess can fulfil her mandate, rolling an appropriate choice of Attribute + Skill - Shadows. Each success grants one Wisp and if the Princess' mandate is appropriate to her Queen's Philosophies she gains a bonus Wisp providing she scored at least one Success. She may do this a number of times each day equal to her Mandate dots, each roll requires at least an hour or of work. 

\textbf{Drawback:} A lot of Mandates are responsibilities as well as opportunities. A Mender who's parents own an animal rescue centre can leave the animals in her parent's hands while she goes of to deal with some Darkspawn. A Mender working as a Doctor at the local hospital will be in trouble if she doesn’t put in her hours. Generally Mandates without responsibilities tend to be worth few dots. 

The Storyteller is encouraged to see a Mandate as a way to start interesting plots, not just a time sink that keeps players from the adventure. Darkspawn victims could come into the hospital emergency ward. A police officer could assigned and interesting case, mundane or supernatural. A blogger might meet a fellow blogger who reports on supernatural events. 

\subsection*{Poplulist Rhetoric (\textbullet\nobreak\hspace{.16667em}to\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet\textbullet\textbullet,\nobreak\hspace{.16667em}Style)}

\textbf{Perquisites:} Presence 3 Manipulation 3.

Your character has been trained in making friends and influencing people. She might be a politician or a cult leader, even if she is not she sees words as tools to make people do what she wills. Such power can be used for both good or ill.

\textbf{Anecdote (\textbullet)} Your character brings up a heartwrenching story. Arguing against her is like arguing against little orphan Annie. Roll Presence + Expression vs Composure + Expression, on a Success your target has a -2 to social rolls against you on this topic for the rest of the scene.

\textbf{Polispeek (\textbullet\textbullet)} Your character can talk at length while saying nothing. By spouting a never ending stream of ambiguous statements and platitudes you can dodge questions while appearing to give answers. When someone is debating against you, you may reflexively forgo your action for a turn to subtract twice your manipulation from your opponents Persuasion or Expression rolls. This works best at stalling for time or when you can't win a debate and hope to simply minimise the scale of your loss.

\textbf{Catch phrases (\textbullet\textbullet\textbullet)} People are naturally tribal and like a social chameleon your character can fit in anywhere by spouting catchphrases and speaking with the correct lingo. Once per scene you may spend a point of Willpower and gain a bonus equal to half her Subterfuge to all social rolls with a certain group. This cannot be done if the target group has perquisites your character does not meet, an adult could not join a teenager only group for example. Using this technique is not declaring loyalty to a group, in fact it's probably best to avoid doing so, but if she's good people will naturally feel more comfortable around her.

\textbf{Drawback:} By getting in with a group your character is placing herself outside other groups. She gains an equal penalty to those who dislike the group, for example if she creates a bonus with Republicans she'll take a penalty while talking to Democrats for the rest of the scene. 

\textbf{Encouragement (\textbullet\textbullet\textbullet\textbullet)} Your character can convince people to associate what they like about themselves with herself. You try to treat all people politely, that's not because you're a good person. That's because you're a Christian/Liberal/Humanist/Feminist/Conservative. You can apply a variant of the Inspired Condition to your listeners, it may only be Resolved on actions in line with their Virtue but when it is resolved you open a door.

\textbf{Rally (\textbullet\textbullet\textbullet\textbullet\textbullet)} Your character can call play the crowd like a fiddle, alienating and isolating her opponent. Both your character and her opponent pick a social merit that gives you influence over people (Usually: Allies, Fame, Mystery Cult Initiation, or Status though others may be aloud. The people represented by that merit must be present, be they in the audience, waving placards outside or posting comments on the blog with the debate). Roll Presence + Persuasion + Merit Dots. For every (Targets Composure + Merit dots - your successes) rolls the target must spend one point of Willpower to keep going in the face of such hostility. This does not count as the target's one willpower per turn.

\textit{Example: Gwena\"{e}lle is a columnist having a public debate about obesity with Desmond, the director of public relations in a greedy fast food chain. Gwena\"{e}lle rolls Presence + Persuasion + her Status in the newspaper to fill her next column with catch phrases that sound a call to arms. She gains four successes. Desmond has a Composure of 3 and chooses to play his Status 4 in the corporation, getting subordinates to ghost write and give him some emotional distance. Every third roll Desmond looses a willpower as his corporate blog is hammered with aggressive comments by Gwena\"{e}lle's supporters. }

\subsection*{Scientific Rhetoric (\textbullet\nobreak\hspace{.16667em}to\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet\textbullet\textbullet,\nobreak\hspace{.16667em}Style)}

\textbf{Perquisites:} Intelligence 2, Academics or Science at 3 or at 2 with a speciality in academic methodology or practices.

For your character a debate isn't about winning or convincing others, it's about spreading the truth. Scientific Rhetoric works best against the open minded, even if your character looses the debate she learns something.

\textbf{First Principles} (\textbullet): Quantum nonsense, pyramid power, \textquotedblleft I'm not a doctor but I play one on TV". People have been using scientific lingo to promote rubbish for years, to a real scientist it usually sounds ridiculous. As a reflexive action you may inflict a -1 penalty on anyone making an argument based on science or academics (the fields, not the skills). This does not work if their science is sound, assume that a speciality or three dots in a relevant skill confers immunity. Less for basic topics.

\textbf{Citation} (\textbullet\textbullet): You don't need to prove your point, just point to someone else who has already proved it for you. You may apply the Library merit to social rolls, provided you have access to your Library and your conversation partner lets you fetch books. Internet access is worth +1, unless you have a Library of bookmarks to hand.

\textbf{Just the Facts} (\textbullet\textbullet\textbullet): A quick tongue doesn't matter, for the facts speak for themselves. You may fall back to established facts, allowing you reroll one failed social roll per scene providing it is on a scientific or academic topic.

\textbf{Burden of Proof} (\textbullet\textbullet\textbullet\textbullet): You stand your ground and insist debate will be decided on the facts. Make a contested Manipulation + Persuasion roll (or a Presence + Expression roll when debating in front of an audience). If you win you and your opponent must use an appropriate mental skill (such as science or medicine for a debate on evolution) in place of social skills.

\textbf{Scepticism} (\textbullet\textbullet\textbullet\textbullet\textbullet): There is a reason reproducibility is one of the principles of the scientific method. After a social encounter has opened one of your Doors you can take the time to double check the other guy's claims. Is that salesman's product really the best in it's field? Make an extended research roll with a target equal to the dicepool used to the door. If you succeed that door closes again. You may only ever use this maneuver once for any door and it fails automatically if the claim you are investigating turns out to be true.


\subsection*{Spiritual Temperance (\textbullet\nobreak\hspace{.16667em}to\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet\textbullet\textbullet,\nobreak\hspace{.16667em}Style)}

\textbf{Perquisites:} Composure 3, Academics 2 or with a speciality in an appropriate school of thought.

Your character is attuned to the spiritual side of the world. She may be a Buddhist monk, a Christian monk, or simply read a lot of paperback philosophy. Her spiritual attunement helps him above the temptations of everyday life. Spiritual Temperance excels at resisting persuasion, it is least effective when directness is a virtue and against those who cannot understand it's hidden meanings.


\textbf{Unclouded Eyes (\textbullet):} Like the fool your character favours the simple explanation. She plays little attention to distractions or complex word games. Ironically this makes her exceptionally hard to fool, all subterfuge rolls against your character take a -1 penalty.

\textbf{Cessation of desire (\textbullet\textbullet):} By focusing on the spiritual your character has freed herself from temptations. Mundane social rolls gain no benefit from tempting her with her vice.

\textbf{Drawback:} No vice means no Willpower. They player may choose for their character to indulge in their Vice but then the provider gains the usual bonuses. 

\textbf{Mediation (\textbullet\textbullet\textbullet):} Your character speaks peace to the world. So long as she gives her full attention to mediating a conversation all characters treat their impression as one level higher. As soon as your character stops the impressions return to their usual level. \textit{Example: two people with an average impression can roll to open doors once per day, providing that each roll was made while your character is mediating.}

\textbf{Drawback:} Your character cannot use mediation when she wants to open a door herself.

\textbf{Koan (\textbullet\textbullet\textbullet\textbullet):} Your charter tells a short story or gives a riddle with layers upon layers of hidden meaning and a kernel of wisdom hidden at it's core. Roll Expression + the target's Wits. On a Success the target gains the Informed Condition, however when they resolve the Condition open a door. Understanding and following your koan is another step along your path.

\textbf{Inner Peace (\textbullet\textbullet\textbullet\textbullet\textbullet):} Your character has risen above desire, she could live comfortably on nothing but rice and water. This lack of desire makes it incredibly hard to push her into anything. In any social roll where your character's only goal is to resist she may roll Composure + Integrity (or Belief) instead of the usual dice pool.

\subsection*{Taint Awareness (\textbullet\textbullet)}
\textbf{Perquisites:} Beacon, Sworn, Shikigami or Hopeful.\\

\noindent Your character's sensitivity to corruption from the Darkness is so finely tuned that she can perceive it from miles away. Whenever a creature of the Darkness enters our world from the Dark World, or the size or Severity of a Tainted area increases within Inner Light miles of your character (1 mile for a Beacon or Sworn) she is instantly and unambiguously aware of it. She may roll Wits + Sensitivity to acquire a sense of the direction and rough distance to the Tainted area or the place where the creature crossed over.

Some character's are especially sensitive, however these lucky or unlucky people have senses so refined that it is painful to feel an intrusion. You may, for the same Merit Dots, opt to have your character sense Taint or intrusions within Inner Light * 3 miles and gain a +3 bonus to determining the location and distance. If you do so you take the moderate version of the Sick Condition for one scene as you sense the Taint through a medium of nasuia, headaches, uncomfortable periods, cramps or some other painful medium. The exception is if you are currently in your Transformed Identity, a Princess' magical body is better able to regulate supernatural senses.

\subsection*{White Rabbits (\textbullet\nobreak\hspace{.16667em}-\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet\textbullet\textbullet)}

\textbf{Perquisites:} The ability to travel to the Dreamlands.\\

\noindent Your Character has an especially strong connection to the Dreamlands; when she sleeps she is called to witness prophecies and portents applicable to her life and her goals. To consult the White Rabbits, the Princess must go to sleep for long enough to reach REM sleep. The Princess may not look for White Rabbits more often than once per session. The Princess rolls Wits + Empathy - Shadows; if she has not found a Crawlspace entrance near her current resting place the roll is at -2.
\begin{myindentpar}{10pt}
    \emph{Dramatic Failure:} The Princess is called to the Dreamlands by a March Hare, or perhaps even a Black Rabbit, that she mistakes for a Prophecy Rabbit.
    
    \emph{Failure:} No Rabbits appear that night.
    
    \emph{Success:} The Princess is called to the Dreamlands by a Prophecy Rabbit or Memory Rabbit and learns information on a question or topic chosen by the player. The Princess will receive at least one clue per dot of White Rabbits, though the clue may be hidden behind signs or portents.
    
    \emph{Exceptional Success:} In addition to the regular benefits the Princess also gains the Floating Blessing Condition with a pool equal to her dots in White Rabbits. The Condition lasts for the remainder of the Session. At any point during the Session the player can declare that the Princess knows the what to do because of her dream and cash in dice from her pool: The affected trait is \textquotedblleft things related to my dream\textquotedblright. 
\end{myindentpar}

The Storyteller is free to introduce White Rabbits without players using this Merit. Even a Princess without any dots in White Rabbits can experience the occasional prophecy if it's important enough. See the Dreamlands appendix for more details on the White Rabbits.


\section*{Mortal Merits}

The following merits are only available to Mortals. 

\subsection*{Dedication (\textbullet\nobreak\hspace{.16667em}-\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet\textbullet\textbullet)}

Prerequisite: Sworn \\

\noindent A Princess' Light shines forth into the world and those Sworn to her service reflect that light becoming brighter themselves. Dedication represents one Princess who the Sworn respects and follows. The Merit's rating reflects the scale of that respect. 

When the Sworn spends time with the Princess (or a Queen), either socialising or assisting with her duties, he may roll Empathy + Dedication once per scene or once per hour during downtime. Each success grants one Wisp, no more than Dedication Wisps can be gained in one day. If the Sworn is Dedicated to a Princess of the same court and assists her in a task that fits the court's philosophies then providing he got a single success on the roll he gains a bonus Wisp, this can take him to a maximum of Dedication + 1 Wisps per day.

A Sworn may buy this merit multiple times for Dedication to multiple Princesses. The daily limit applies to each Princess independently, however only one roll may be made per scene or hour. 

\subsection*{Dream Travel (\textbullet\nobreak\hspace{.16667em}or\nobreak\hspace{.16667em}\textbullet\textbullet\textbullet)}

Prerequisite: Not supernatural\\

\noindent Your character has psychic powers, specifically he can project his mind into the Dreamlands. For the most part this uses the same rules as Princesses, spending Willpower instead of Wisps where appropriate. See the dreamlands appendix for more details. 

There may be some small differences, some psychics might prefer to use meditation or concentration instead of REM sleep and so gain different situational bonuses to reaching the Dreamlands. The only significant difference is that psychics are not targeted by The Trap and so must discover their abilities unaided. A strong desire to escape regular life or a coincidence where someone with the gift decides to train themselves in lucid dreaming are the most common method. 

The three dot merit allows the psychic to create a shield against the gales using the power of their mind, this provides the same protection as Regalia. The shield can take any form, from nothing at all to transforming into an astral avatar. However it looks the psychic may spend a point of Willpower to manifest their shield for the duration of a trip to the Dreamlands. 

Dream travelling psychics may buy the White Rabbits merit. It is also not unknown for them to have additional psychic gifts, such gifts usually work in both Earth and the dreamlands but at the Storyteller's discretion an exp discount may be applied if gifts that typically work in both worlds are modified to only in the Dreamlands. \\

\textbf{Drawback:} Doors allow travel both ways, your character is especially \textit{accessible} to astral threats like Amanojaku. Hopefully he has the training or gifts to defend himself.

\subsection*{Secret Keeper (\textbullet\textbullet)}

Prerequisite: Player character\\

You know of a Princess' secret identity, and you've sworn above all else to honour her trust in you. When rolling to protect against any attempt to pry the secret from you, be it mundane or supernatural, you apply the Rote Action rule. This Merit may be taken multiple times to protect multiple Princesses. 

Players who wish for their character to have a NPC secret keeper should invest in the True Friend Merit. 



\section*{Blessed Places}

\begin{quote}
HERE MEN FROM THE PLANET EARTH FIRST SET FOOT UPON THE MOON
JULY 1969, A.D.
WE CAME IN PEACE FOR ALL MANKIND
 \end{quote}
 
The classroom of an inspirational teacher. A humble yet gifted artist's studio. The best, hardest working hospital in town and the underfunded free clinic opening against the odds in the most deprived area. A truly welcoming and tolerant church. The laboratory tirelessly working on the latest disease to evolve and the library that preserves wisdom of ages gone by. These are the Blessed places, they stand on a legacy of the very best of humanity.
 
Anyone touched by the Light - any Beacon, Sworn or Noble - feels her heart lift when she arrives in a Blessed area, though she may not realize why. The Storyteller makes a Perception check, rolling Wits + Composure + Sensitivity - Shadows; if it succeeds the character notices the Light-touched quality of the place she enters.
 
\subsection*{Creating a Blessed Place}
Blessed places are formed when attempts to improve the world are performed with true passion and great skill. This can be as general as making something beautiful simply for the sake of beauty or as specific as helping one single person. A single but extraordinary act can create a Blessed place all by itself while others are formed by gradual accumulation.

Blessed places have two attributes, their Size and the Beauty of their Blessings. The Size of a Blessed place is measured on the scale as of zero to five. \\

\noindent 0 dots - Around the size of a person, a closet, bathtub or tiny bedroom.\\
\noindent 1 dot - A small apartment or a cabin in the woods; 1-2 rooms\\
\noindent 2 dots - A large apartment or small remote house; 3-4 rooms\\
\noindent 3 dots - A converted church, warehouse or large house; 5-8 rooms\\
\noindent 4 dots - A mansion, a clinic or a small region; 9-15 rooms\\
\noindent 5 dots - A hospital, a neighbourhood, a large office complex; countless rooms\\

\noindent The Beauty of a Blessed place measures how powerful and numerous its effects are; each dot in Beauty supports one Blessing. Larger Blessed places are also more resilient; a Blessed place has a Hold track with a number of boxes equal to their Size +1. Most methods to damage the Beauty of a Blessed place marks Hold boxes. When the rightmost box is marked reduce the Beauty by one, remove one Blessing and clear the Hold track. Blessed places recover from damage if left alone; clear 1 Hold box on each day that no Hold box is marked.

When creating a Blessed place the Storyteller should first imagine the person or people responsible. An artist motived by his love of art? A scientist dedicated to discovery? A good Samaritan? See where their actions fall on this rough guide to how much Beauty may be created. A dot of Beauty costs 1 point; a dot of Size costs points equal to the new value of Size (1 point to raise Size from 0 to 1, 2 points to raise from 1 to 2, and so on.)

\begin{table}[H]
    \begin{tabular}{|l|l|l|l|l|l|}
        \hline
        ~                                                                                         & ~   & ~   & ~     & ~     & ~   \\ \hline
        Action                                                                                    & 0-4 & 5-9 & 10-14 & 15-19 & 20+ \\ \hline
        Selfless and genuine attempt to help others.                                   & 0*  & 0   & 0     & 0     & 0   \\ \hline
        ... that inspires witnesses.   & 1   & 0*  & 0     & 0     & 0   \\ \hline
        ... that directly improves a small town or village, or a small institution.                                                                                          & 	2  & 1   & 0*    & 0     & 0   \\ \hline
       ... that directly improves a city, or a large institution.                   & 3   & 	2  & 1     & 0*    & 0   \\ \hline
        ... that directly improves a country.                     & 4   & 3   & 	2    & 1     & 0*  \\ \hline
        ... that directly improves the entire world.                             & 5   & 4   & 3     & 	2    & 1   \\
        \hline
    \end{tabular}
\end{table}

0* means that a single act at that level gives no points, but repeating it many times can build up to a point eventually.

Actions that involve significant personal sacrifice count as one step downward in this table.\\

\noindent A Blessing can produce any one of the following list of effects. A Blessed place can grant most Blessings any number of times, within the limit of its Beauty.

\begin{itemize}    \item Attribute: Dice pools that include one Attribute have a +1 bonus.
 \item    Skills: Rolls of two Skills take a +1 bonus; or, rolls of one Skill have a +2 bonus. An Attribute + Attribute dice pool, such as Perception, may be treated as one Skill.
\item     Specialities: Three types of tasks, each of the scope of a speciality, take a +1 bonus. These can be stacked, with one type taking +2 or +3.
\item     Pacifism: Characters with evil general intentions are find themselves unable to commit evil, reduce their combat dicepools by -1.
\item     Resistance: Characters with good general intentions are protected from supernatural powers. Increase either Resolve or Composure by (not both - pick one) when the Attribute is used to resist a power.
 \item    Health: The Blessing aids recovery and bolsters the will to recover. Halve all healing times; this does not stack with supernatural powers that increase the rate of healing unless they are an innate ability for a supernatural creature. A Blessed place cannot have more than one of this Blessing.
\item     Willpower: The blessing bolsters the will to act. Characters acting with general noble intentions gain a free point of Willpower when entering the blessed place. This Willpower is spent first and vanishes upon leaving the Blessed Place. Blessed Places can only grant Willpower once per day to any person.
 \item    Moral Fibre: Breaking Point and Compromise checks within the area take a +2 bonus if they were caused by the pursuit of a noble cause. A Blessed place cannot have more than one of this Blessing.
\item     Blessed Virtue: The blessing reinforces human nobility. Each time you take this Blessing chose one Virtue. Anyone within the Blessed place may fulfil that Virtue in addition to their own, but only if fulfilling the Virtue comes from a genuine goodness of heart: A judge who refuses to be threatened could fulfil blessed Righteous, but vigilante killer driven by hatred could not. As always you may only regain Willpower through Virtue once per Chapter. A Blessed place cannot have more than one Blessing of this type for each Virtue.
\end{itemize} 

\subsection*{Sanctification}

Mortals staying in a Blessed Place find good deeds easier and more rewarding. Over time this may lead to them learning to be a better person. Every time a mortal sleeps within a Blessed Place roll Beauty.

    \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Mortal somehow disrupts the blessing. Mark off one of the Blessed place’s Hold boxes.
    
    \emph{Failure:} Nothing happens. 
    
    \emph{Success:} The character gains the Uplifted Condition with one point of Lux. If the character already has the Uplifted Condition increase it's Lux by one, up to a maximum of half Beauty (rounding up) or 5, whichever is higher. 
    
    \emph{Exceptional Success:} The character gains two points of Lux, up to the normal maximum. \end{myindentpar}

\noindent Beacons, Sworn and Princesses are effected in a slightly different manner.

    \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Hopeful looses connection to the Blessing. For the next day they do not benefit from this Blessed Place. 
    
    \emph{Failure:} Nothing happens. 
    
    \emph{Success:} The player chooses to either gain Lux (as per a success for mortals) or remove Shadows: The player may immediately spend Beats to remove Shadows with a discount equal to the successes rolled. It costs a minimum of 1 Beat or Luminous Beat per dot of Shadows removed. 
    
    \emph{Exceptional Success:} The player chooses to either gain two Lux or remove Shadows with a particularly large discount. \end{myindentpar}
	
	
%\subsection*{Foci}

%Within each Blessed area is at least one focus: Something related to the original cause of the Blessed Place that still gives structure and focus to it's beauty. As the Size and Beauty of Blessed Place grow it's strength creates multiple foci - a good rule of thumb is to have as many foci, and types of Blessing, as the lower of Size and Beauty/5. 

%If a Blessed Place has multiple foci, the Storyteller distributes its Beauty among the foci and decides which Blessings emanate from each focus. Destroying one focus removes those Blessings however it does not reduce the Beauty of the Blessed place. For each focus that was destroyed, one point of Blessings is restored per day. These restored curses forming around new foci.
	
\subsection*{Dreamguard}

Deep within the Dreamlands servants of the Darkness built built a trap, a shining lure to lead Light away from the world but within a Blessed place that lure doesn’t seem quite as tempting. The nightly roll for a Character with Shadows to be lured into the Dreamlands is penalised by the Blessed Place's Beauty. 	

\subsection*{Protecting Blessed Places}

Every Blessed place is a treasure, any Nakama with knowledge of one is sure to do their best to protect it. So what do they need to protect it from? 

\subsubsection*{Taintings}
Tainting and Blessed places cancel each other out weakening or even destroying the Beauty of a Blessed Place forever. When a Tainting is committed within Blessed Places roll Beauty - the amount of Taint created (as per the rules for Tainted Places) on a failure the Beauty decreases by the amount of Taint created; if there is any excess taint it forms a Tainted Place. 
\subsubsection*{Symbolic Opposition}
Every Blessed Place has cause, something beautiful people did that has left it's mark on the area. Actions which directly oppose this cause can cause the beauty to decay.

\textit{Example: Harriet is a true artist who's only motivation is to make the world a better place by creating things of beauty. Her dedication turns her studio into a small Blessed Place. If her studio passed on to another artist who saw art merely as a way to get money and prestige – going against everything Harriet believed in – then this could degrade and ultimately destroy the Beauty of her studio.}

As a general rule assume that every successful roll, or successful extended action, which is directly opposed to the origin of the Beauty marks of one Hold box, but turnabout is fair play: every successful action which reinforces the ideals of the Blessed Place can clear one hold box providing it was specifically marked by Symbolic Opposition. 
\subsubsection*{Physical Destruction}
The power of a Blessed Place is held in the physical from: It is in the ancient stonework of a university who's scholars have added to mankind as a whole. It is in the trees of a forest where generations have found peace and strength. Destroying such things can damage a Blessed Place. If the physical place is changed enough that it is no longer recognisable as the same place, the blessings are destroyed. 

\section*{Invocations}

Invocations are Beliefs of the Queens. A Queen's light shines out onto the world and Princesses reflect that light to shine ever brighter. A Princess may buy up to 5 dots in an Invocation. Normally, when she activates a Charm, the Princess spends 1 Wisp on top of the Charm's usual cost to apply one of the Invocations she knows - this adds her dots in the Invocation to the dice pool for activating the Charm. Charms that don't require a roll to activate gain power from Invocations in other ways; for example, several permanent Charms allow a Princess to apply an Invocation to some mundane Skill rolls. It is never possible to apply two Invocations to a single dice pool, or to stack Invocations in any other way. Some Charms, called Invoked Charms, are linked to one specific invocation. These are denoted by having dots in an Invocation, as well as a Charm family. A Princess may not learn an Invoked Charm unless she has sufficient dots in the relevant Invocation, and when using an Invoked Charm only the linked 
Invocation may be used to increase the Charm's potency. 

Each Queen favours one Invocation, and the Hopeful sworn to her find that Invocation easier to learn than any other. Due to this intimate tie to the Queens, the Invocations are described under the Queen who favours them. An Invocation can be applied for free (without paying the extra Wisp) under certain conditions, generally when her actions are consonant with the principles of the Queen favouring that Invocation. There is also, for each Invocation, a prohibition that a Princess should not break; if she does, she loses the right to apply that Invocation for a period of time, she may still use Charms that depend upon that Invocation as a perquisite.

\subsection*{Invoking For Willpower}

Aside from adding power to Charms, an Invocation can inspire Nobles who strive to live up to its principles. What could be more encouraging than knowing a person of almost divine wisdom supports of your actions? If the Storyteller agrees that a Princess’ actions during a scene reflect the ideals of an Invocation the Princess has learned, and she hasn’t broken its ban, the Princess rolls her dots in that Invocation as a dice pool. (This pool cannot be modified in any way - she may not spend Willpower on it, and no magic or Condition affects it.) She may do this once per session, for each Invocation separately. She need not be transformed to use her Invocations this way.
 
 \begin{myindentpar}{10pt}
    \emph{Dramatic Failure:}  The Princess’ recent actions feel a bit hollow; she doubts the ideals that inspired them. Until the scene ends, she may not spend Willpower on actions that reflect the Invocation.

    \emph{Failure:} The Princess goes on with her life.

    \emph{Success:} The Invocation confirms the Princess’ actions. She regains one spent Willpower point.

    \emph{Exceptional Success:} The Invocation revives the Princess’ flagging will; she regains all spent Willpower.
\end{myindentpar}

\subsection*{Choosing Your Invocations}

The choice if Invocations is an important one, an Invocations shapes empowers a Princess' magic. The easiest trap for a player to fall into is jump to thinking which Charms she wants. Invocations are not a neatly packaged source of power for any Princess' who likes the look of a certain Charm. Rather, an Invocation is the ideals and Beliefs of a Queen given form, resonating in the souls of mankind through the inherent magical nature of a Queen.

When choosing Invocations a player should think about what views and beliefs a Princess shares with a Queen. The more a Princess has in common with a Queen, the more she upholds a Queen's ideals, the brighter the Invocation shines within her. With practice (represented by spending experience) she can draw on that Invocation to enhance her magic. The Queen's philosophies can provide a yard stick. A Princess who only follows one of the Queen's philosophies is unlikely to advance beyond one or two dots in an Invocation. Agreeing with two philosophies can reach three or perhaps even four dots. A Princess who broadly agrees with and lives up to all three philosophies can with time master an invocation. (For Lacrima, a Princess is considered to uphold the philosophies if she applies similar ideals to her own friends, family or some other organisation instead of Alhambra.)

And what of the Twilight Invocations? Not every philosophical ideal of the Twilight Queen's is pure evil to be rejected by any right minded Princess. Protecting those you love or opposing the Outer Dark in all it's forms are ideas commonly found among the Radiant. So what stops a Princess waking up one morning and realising she now has a Dot of Lacrima? The answer is choice. A Princess who believes in protecting those she loves can feel a connection to Lacrima deep within herself and knows she can draw power from it, but she can choose not to. The connection to an Invocation does not shape her beliefs, it is shaped by her beliefs. An Invocation she chooses not to use, or vows to stop using, cannot turn her to the dark side. 






\myframe{

\section*{Dancing in Twilight}

One of the dirtier secrets of the Radiant is the sheer number of Nobles who, at one point in their life or another, dabble in the Invocations of the Twilight Queens. Dabbling in this case can be anything up to buying two or three dots in the Invocations; more requires a strength of commitment to the ideals of the Queen which is largely incompatible with remaining a member of the Radiant (for one, one's own Queen will tend to object). The truth is that, the flaws in the Twilight Queens are ones which are within the hearts of man as a whole, and so most of the Enlightened have felt the same urges at some point in their life. Note that, however, such dabblers still consider themselves part of the Radiant, and, in the case of those who feel affinity for the Queen of Mirrors, often consider the The Child Queen to be Radiant. They still oppose the Darkness, and will fight against the loyalists of Tears and Storms. One of the greatest topic of debate in the multiple, disparate groups of the Enlightened is how to 
respond to people who use Twilight Invocations, and whether or not they're doing anything wrong.

\vspace{4 mm}

The Invocation of Lacrima, tool of the Last Empress, the Queen of Tears, is an object of fear and mistrust to the vast majority of the Radiant. It is apparently evil, in a way that neither Specchio nor Tempesta are, because it's Charms are an inherent Compromise of one's Belief, and to many, it is irrevocably tainted by the fact that it has the Charms used to drain Light from the world or transform oneself into a creature of the Dark. But, nevertheless, there are those Princesses who learn it, and who do not follow the Queen of Tears. One of the fundamental things about Lacrima is that it can always be used to protect those you care about, and to a Princess who wants to do exactly that, the expediency of methods means that Lacrima can look attractive. When a friend died because you pushed your views on someone and so Legno was sealed off, the universal applicability of Lacrima for protecting your own starts to look very tempting. The dabblers are typically more experienced, and more able to justify to 
themselves the 
moral compromises involved, in part because although there are Lacrima Charms which are Belief Compromises, dabblers tend to only have access to the ones which are Compromises against very high Belief or not Compromises at all, and so there are less of an objection. Moreover, there exists a notable sub-faction of the followers of the Queen of Diamonds who specifically learn Lacrima for its use in studying the dead and the Underworld, and, aggravatingly to some others, the Queen has even given her support to the practice. Such dabblers often have a strict moral code restricting their use of the Invocations to only using it to study the dead - never to harm, and they point to the gains in knowledge that they have provided to the Radiant; their detractors point out that once the power is there, it can be hard to resist. 

}\myframe{

The Invocation of Tempesta, tool of the Seraphic General, the Queen of Storms is for most of those who dabble in it, purely a weapon. It is something that is learned as a tool against the Darkness, and it is used for that role. It does not (generally speaking) heal or right wrongs, but it does eliminate the followers of the Darkness and of Alhambra. In Atlanta, in the mid-90s, almost an entire generation of Radiant Princesses knew at least the basics of Tempesta. So hard-pressed were they by the Darkness and a major, well-organised Alhambran Outpost that it became unofficial policy for elder Enlightened to guide each newcomer towards it, because the universal applicability and raw power of the Invocation in such circumstances was too much of a boon. That large numbers of Nobles in the city were driven towards extremism was viewed as an acceptable price, even if by the end, and the arson of the Alhambran Outpost, there were Enlightened just as callous as the worst of Storms, still officially among the Radiant.
 For those Princesses in the know, too, Tempesta can also be seen as the most moral of the Twilight Invocations, because the innate costs to it, the damage it does to the user, is known, and only affects the self. The common consensus is that it is dangerous, and a sign that a Noble is starting to spiral into extremism, but whether the use of it should be enough to ostracise one of the Radiant is a lot more contentious, especially since in areas where it is done, there are frequently not the Enlightened to spare.

\vspace{4 mm}

The Invocation of Specchio, tool of the Crown's Custodian, the Queen of Mirrors, however, is the most subtle and insidious of the Twilight Queens, and the influence it is. In part, it is because of the lack of an overall enemy that the Invocation is linked to; while both the Ravens and the Furies provide a highly visible \textquotedblleft there but for the grace of the Light I go" example which other dabblers can keep away from, the egotism and self-righteousness implicitly promoted by the Queen of Mirrors, and the lack of a solid adversary is hard to fight against, especially since many Princesses have tendencies in that direction naturally. Dabblers can slip into following the Queen of Mirrors much more easily, especially since the Queen does not demand fidelity, which means that some elder Radiant are much more harsh in opposing its use. There are those who argue that, unlike Tempesta and Lacrima, use of this Invocation makes you a de facto follower of Mirror's agenda. And on the other hand, there are 
those who count the Queen of Mirrors as among the Radiant Queens, despite the objections of the other five. Moreover, there us \textit{also} a faction in the Court of Diamonds who study Specchio for the unique sources of information it provides, or even to study the strange achronal or spacewarping Charms unique to Specchio, once again the Queen has given her consent. Even outside the Court of Diamonds there are Radient who find these Charms to be exceptionally useful and irreplaceable with more moral Invocations, not just an improvement over them. In the Court of Diamonds these dabblers protect themselves from the effects of madness by only using Specchio while supervised by a Princess who knows the Reclaim Charm. Of all the Twilight Invocations Specchio might be the easiest to learn, too; all one needs for it is self-belief in ones own cause, and a spark of the brilliance needed to reshape the world. And neither are rare among the Enlightened. 

}



\section*{Charms}
The basic magics of the Hopeful are called Charms. Use of a Charm is, as a rule, an obviously magical event, as obvious as transformation, unless the Princess specifically tries to cloak herself. Generally the Light's force overflows into some visible manifestation -- a flash of light, a snatch of music, the appearance of a solid object -- that leaps from the Princess to her target.

The Charms are divided into 10 trees. Each Calling has an affinity to 3 of them, learning the Charms within them more easily. 

Each Charm has an Action attribute, giving the type of action using it is:

\begin{itemize}
\item Instant: Activating the Charm is an instant action, taking a turn. The dice pool to roll for the action is noted.
\item Full turn: Activating the Charm is an instant action, but it also requires forgoing Defence in the turn you activate it.
\item Reflexive: Activating the Charm is a reflexive action; it doesn't interfere with your normal action and can be done at any point in the initiative cue. A dice pool to roll is noted.
\item Reactive: Activating the Charm can be done at any point in the initiative cue but it consumes your action for the turn. A dice pool to roll is noted.
\item Permanent: The Charm enhances another ability. No action is required to activate it -- if the proper conditions obtain, it just works. A Princess can always disable a permanent Charm if she so chooses. If no other method is presented a Transformation action will activate or deactivate any number of permanent Charms. 
\item (one of the above) and resisted: The Charm has a target, and you must subtract one of his traits from the dice pool.
\item (one of the above) and contested: The Charm has a target, who reflexively rolls an opposed dice pool; you must roll more successes than he does for the Charm to take effect.
\end{itemize}
    
Other than the permanent Charms, each Charm has a duration, ending when the stated time runs out; and a cost, usually in Wisps. Powerful Charms call for Willpower points; many Charms favoured by the Queen of Storms inflict damage on their user, which resists magical healing; and using some Charms favoured by the Queen of Tears transgresses against Belief. 

A Charm with a duration of \textquotedblleft lasting” changes its target permanently in a flash of magic; as a Charm it ends immediately. Charms with an \textquotedblleft indefinite” duration leave a continuing trace of magic on their target (often a Condition or Tilt) which other supernatural powers can detect or influence. A Charm with a duration of \textquotedblleft concentration” needs its user’s active attention, and ends if the user spends her turns action on anything but maintaining the Charm.

If a Charm is used on a person, a Princess can use it on herself Charm specifically states she cannot. 


\subsection*{Learning Charms}

Each Charm has a rating in dots, which sets the price and difficulty of learning its basic effect. While Charms need not be learned in any fixed sequence, the more advanced Charms can't be learned without practice with simpler powers. To learn a Charm at its basic level, a Princess must have a sufficient number of dots in other Charms in the same tree (counting each Upgrade as an additional dot), as defined in this table. 

\begin{table}[H]
    \begin{tabular}{|l|l|}
        \hline
        Charm Rating & Dots Required \\ \hline
        1            & 0             \\ \hline
        2            & 1             \\ \hline
        3            & 3             \\ \hline
        4            & 6             \\ \hline
        5            & 10            \\
        \hline
    \end{tabular}
\end{table}

\textit{Example: Before she can learn a Govern Charm rated at three dots, a Princess would have to know: Three one dot Govern Charms, a one dot and a two dot Govern Charm, two one dot Govern Charms one of which has an Upgrade, or a single Govern charm which has two Upgrades.}

A few Charms have another Charm as a prerequisite; to learn these Charms, a Princess must have learned the prerequisite Charm, as well as meeting the total dots required for its basic effect. Upgrades can also have prerequisites. Finally, your Inner Light limits the dots you can put in a Charm; a Princess cannot learn a Charm with more than Inner Light + 2 dots. A Princess 

Many upgrades change the cost or duration of their Charm, add a modifier to the activation roll, or have a Drawback, or trigger Specchio's drawback. Therefore, you are not required to apply any upgrade when using a Charm \textendash\, the basic effect is always available, at the original cost. 

\subsection*{Invoked and General Charms}

By default a Princess can learn any Charm, providing she knows enough dots in the relevant Charm family. Once she knows a Charm she may apply whichever Invocation is most useful to increase the Charm's potency. 

A fair number of Charms work differently. These Charms, known as Invoked Charms, require dots in an Invocation to purchase. They can be recognised by the presence of Invocation dots along side the Charm's dots. Invoked Charms cannot be learned until the Princess has the listed dots in the linked Invocation and cannot be cast with any Invocation but their prerequisite. When using such a Charm, a Princess can apply the prerequisite Invocation to gain its bonus (if conditions permit) or she can make the activation roll without any bonus, but she may not apply any other Invocation's bonus. 

A Princess who breaks an Invocation's ban may still use that Invocation's Invoked Charms. Naturally she cannot apply any Invocation for bonus dice. 

There are also general Charms with upgrades that require Invocation dots -- applying such an upgrade converts the Charm to an invoked one -- and some invoked Charms with upgrades that require more Invocation dots than the basic Charm does. Upgrades that require different Invocations are not compatible; you may not apply both of them to the same activation of a Charm. 

\subsection*{Charm Modifiers}

\subsubsection*{Intimacy}

Some Charms can be used on distant targets, or on multiple targets, by taking penalties to their activation roll.  If a Charm's dice pool is modified by Intimacy, the strength of the emotional connection between the Princess and her target affects the power of the Charm.  Consult this table for the penalty to the activation roll: 

A Princess does not have to use her own emotional connection. By touching another person she may use their Intimacy instead of her own. This increases the Intimacy modifier by one step (add the intermediary's Composure as an additional penalty if they are unwilling). A Princess can also use the connection between a person and a treasured object, this increases the penalty by two steps. 

If the Princess has a keepsake, a treasured object that symbolises her relationship with another (such as a love letter) this reduces the penalty by one die. If she touches uses somebody else's connection she can reduce the penalty by one die if she touches the that person and one of their keepsakes. The benefit does not stack with multiple keepsakes. 

If a character is targeted via Intimacy and they are aware of it they may respond by using any of their own abilities that work via Intimacy at the same dicepool modifier. If a Princess witnesses someone or something else being targeted via Intimacy they may respond using the original dicepool modifier plus one or two steps as is normal for using a proxy. In essence, the character sends their magic back down the channel someone else created through Intimacy. At the Storyteller's discretion this can work with mechanics that work similarly to Intimacy, such as a Mage's Sympathy. 

\begin{table}[H]
    \begin{tabularx}{\textwidth}{|l|X|}
        \hline
        Penalty & Strength of Connection                                                                            \\ \hline
        0       & Sensory: You can see the target directly.                                                         \\ \hline
        -2      & Love or hate: The target is a longtime friend or enemy, a member of your family, a romantic lover, hurt you badly, or a prized possession.       \\ \hline
        -4      & Friendship or enmity: You know the target well; or the target is something you own and care about.                         \\ \hline
        -6      & Compassion or dislike: You know the target slightly; or the target is an a typical item you own.         \\ \hline
        -8      & Acquaintance: You have met the target briefly; or the target is an item you have held.  \\ \hline
        -10     & Few feelings: You have a verbal description of the target, but nothing more.                         \\  \hline
		-       & Unknown: You cannot affect the target via Intimacy. \\
        \hline
    \end{tabularx}
\end{table}

\subsubsection*{Commonality}

\noindent If a Charm's dice pool is modified by Commonalty, it can affect all the members of a social group at once. Commonality does not increase the range of a Charm and cannot be combined with Intimacy, so all the affected people will have to be present. If such a Charm is resisted, the member of the group with the best resistance trait resists for the whole group; for a contested Charm, each member rolls to contest individually. The difficulty of extending the Charm over a social group depends on the commitment the members have towards each other, or towards the common goal for which the group exists.  Consult this table for the appropriate penalty: 
\begin{table}[H]
    \begin{tabularx}{\textwidth}{|l|X|}
        \hline
        Penalty & Strength of Connection                                                                                                                                                                        \\ \hline
        0       & Individual: one person, the default.                                                                                                                                                          \\ \hline
        -3      & Dedicated: everyone in the group affected is mutually friends, or the group's goal takes up the majority of its members' time and thought; an established nakama, a family.                  \\ \hline
        -6      & Concerned: everyone in the group knows eachother, or all the members make significant sacrifices for the common goal; a new nakama, the long term employees of a small business.  \\ \hline
        -9      & Interested: everyone in the group is mutually acquainted or better, or the members share an interest in the group's goal; a social club, employees of a large corporation.                    \\ \hline
        -12     & Casual: some members of the group have only encountered each other; the group is merely a lot of people gathered in one place, with no common interest.                                       \\
        \hline
    \end{tabularx}
\end{table}

\subsubsection*{Sanctuary}

Several Charms affect large areas, and most of those Charms require more magic and more effort to affect a larger place. When a Charm refers to Sanctuary Size consult this table: 

\begin{table}[H]
    \begin{tabularx}{\textwidth}{|l|X|}
        \hline
        Rating  & Sanctuary Size                                                                                                                                                                        \\ \hline
        X       & Just enough room for one person to stand or lie down (Typically Charms using the Sanctuary keyword can’t affect an area this small) \\ \hline
        \textbullet      & A small apartment or a cabin in the woods; 1-2 rooms                  \\ \hline
        \textbullet\textbullet      & A  large apartment or small remote house; 3-4 rooms   \\ \hline
        \textbullet\textbullet\textbullet     & A converted church, warehouse or large house; 5-8 rooms                     \\ \hline
		\textbullet\textbullet\textbullet\textbullet  &    A mansion or apartment building; 9-15 rooms                    \\ \hline
        \textbullet\textbullet\textbullet\textbullet\textbullet    & A vast palatial estate, a city block, a skyscraper or a small village                             \\        \hline
    \end{tabularx}
\end{table}

Charms that use the Sanctuary keyword are typically easier to activate when the area in question is one the Princess values, and conversely are difficult to use in areas she dislikes or fears. Consult the following suggested modifiers: 

\begin{itemize}
\item +5 Exceptionally strong memories of love and safety, such as a childhood home
\item +3 Strong memories of love and safety, such as a long time friend’s home
\item +1 The Princess, or her Principality, owns the property
\item +1-3 The area is a Safe Place for the Princess (bonus = half the Merit dots, rounding up)
\item -2 General feeling of dislike, such as a school room where the Princess was board.
\item -3 The Princess has never been in the area before
\item -5 Strong memories of fear or horror
\end{itemize}

\subsection*{Extended Actions and Charms}

Charms do not exist in isolation, they are deeply tied into a Princess' hopes and beliefs. Usually a Princess' Charms are influenced by her hopes, but a particularly strenuous act of magic can have a noticeable if fleeting affect upon a Princess' emotions. 

If a Princess performs a Charm or uses an Embassy Privilege as an Extended Action she may gain the following conditions, in addition to any effects of the Charm itself: 

\begin{itemize}
 \item Exceptional Success: Luminous
 \item Failure: Stuck Magic
 \item Dramatic Failure: Shaken
\end{itemize}

\subsection*{Teamwork Actions and Charms}

Princesses are very good at working together and all Charms with an activation roll can be invoked as a Teamwork action, just so long as every participant knows the base Charm. Only the primary actor needs to spend Wisps, Willpower, or take Damage in the case of Tempesta Charms; however when invoking a Lacrima or Specchio Charm (including an Invoked Upgrade) the relevant Drawback applies to all participants. All participants in a teamwork action must apply the same Invocation or no Invocation at all, and secondary actors must still pay the Wisp for Invoking Charms unless they qualify to apply the Invocation without a cost. 

The Merit Troupe Magic removes the need for secondary actors to know the base Charm, but only for Inspire Charms. 

\subsection*{Clash of Wills}

When two Princesses (or anyone with magical powers) attempt to invoke conflicting magics a Clash of Wills occurs. This could be two Hope Engineers fighting to control the same body of water, a Wild trying to magically remove the capability for violence while a Fury tries to whip a crowd to a murderous fury or a group of Jewels each trying to inspire people to believe in their political party. 

When a Clash of Wills occurs each party makes a contesting roll to resolve the clash, the winning party's magic takes precedence. The Dicepools are as follows: 
\begin{itemize} \item Princess (including Ghost Princesses): Inner Light + half Belief (rounding up)
\item Sworn or Beacon (with a Bequest): half Integrity (rounding up)
\item Shikigami: half Integrity (rounding up)
\item Dreamlanders (including Wardens but not the former inhabitants of the Kingdom): Power + Rank
\item Goalenu: Power + Rank (unvesseled) or Attribute + Rank (vessled)
\item Creature of the Darkness: Shadows
\item Dethroned: Inner Darkness
\end{itemize}

\subsection*{Disabling Charms}

Some Charms have Upgrades that provide passive or automatic abilities. When a Princess Transforms the player may choose which Charms are in effect and a further Transformation action may be made at any time to switch which Charms are in play. This also applies to individual Upgrades. 

\subsection*{Regalia}

Some permanent Charms add items to the Princess' transformed self, or give her the ability to add an item. These extra pieces form the Princess' Regalia. When a Charm states that an item is part of the Regalia, it can appear on her person, ready for use, when the Princess transforms, if she wishes it to. If a Charm does not state that it creates Regalia a player may still declare that it does so, but this has no mechanical effect. 

A Princess can switch any number of Regalia pieces into or out of solid existence with a Transformation action; the dice pool for this action is the same as the one for full Transformation. However, if she returns to mundane form she must dismiss all her Regalia as well. Naturally, pieces of Regalia help a Princess with her goals only when they are in existence - any bonuses they confer are lost if she sends them away.

All Regalia has a Structure equal to Belief and a Durability of Inner Light. If a piece of Regalia is destroyed or lost, the Princess can recreate or summon it while transformed; as with a dissolved phylactery, she must spend a Wisp and a Willpower point to recreate a piece of Regalia, which takes a full round and this requires her absolute concentration. 

If another was to steal a Princess' regalia they would be unable to use it, but they would be able to target the Princess through an unbreakable Intimacy link with a strength equivalent to love. Fortunately any technique that would cut the connection Princesses use to summon Regalia would, by definition, destroy the Regalia.  



\subsection*{Appear}

The Appear Charms change your appearance, and produce other illusions. Seekers and Troubadours have affinity for them. 

\subsubsection*{Life of the Party (Appear \textbullet)}
\noindent Action: Permanent \\

\noindent An ornate hat, crown, tiara, hair accessories or some other headdress becomes part of the Princess' Regalia, giving her an air of pleasant elegance. She gets the 9-again quality on mundane Socialize rolls within one of her specialities (fixed when she takes the Charm) and she may apply an Invocation to those rolls.\\

\begin{myindentpar}{10pt}\noindent \textbf{Upgrade: Gregarious}

\noindent Stacks, up to 2 \\ 

\noindent The Princess is at home in any social situation. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for rolls covered by any of the added specialities.\\

\noindent \textbf{Upgrade: Carousing (Aria \textbullet\textbullet)}\\

\noindent The Princess can get drunk, or high on drugs, and never show it \textendash\, she keeps her poise and self-control. Reduce all social penalised for intoxication or drugs by Aria. The Princess isn't actually resistant to drugs, she just doesn’t show the effects.  

\noindent \textbf{Upgrade: Gossiping (Terra \textbullet\textbullet)}\\

\noindent When asking for information from her connections, the Princess nearly always finds what she seeks. She gets the 9-again quality on all rolls to get information from her Contacts (see p. 114 of the core book) if she questions them while transformed, and may apply Terra to those rolls. (Using this ability on a Contact who knows only the Princess' mundane identity is best done over email ...)\end{myindentpar}

\subsubsection*{Light the Way (Appear \textbullet)}

\noindent Action: Instant 

\noindent Cost: 1 Wisp 

\noindent Duration: Inner Light or Invocation hours \\

\noindent The Princess can, at any time, create a soft light that banishes the thickest natural darkness. The light source can take any source the princess wishes, from a torch or a glowing halo to a simple ambient glow, it illuminates the Princess' path and leaves her hands free. She can bring the light up or douse it reflexively, and set it to shine at any intensity short of full sunlight.

\begin{myindentpar}{10pt}\textbf{Upgrade: Dazzling (Fuoco \textbullet)}\\

\noindent The Princess can make her light flash brightly enough to dazzle and blind an opponent. As an instant action, she spends a Wisp and rolls Dexterity + Athletics - the target's Defence. The target takes the Dazzled Tilt for one turn per success.\end{myindentpar}

\subsubsection*{Twenty Faces (Appear \textbullet)}

\noindent Action: Instant, Wits + Subterfuge

\noindent Cost: 1 Wisp 

\noindent Duration: 1 scene \\

\noindent Sometimes, the full glory of the light must be veiled, so that a Princess may walk unnoticed.

\begin{myindentpar}{10pt}
    \emph{Dramatic Failure:} The Princess cannot use Twenty Faces for the rest of the scene.

    \emph{Failure:} The Princess' appearance and raiment are unchanged.

    \emph{Success:} The Princess wraps herself in an illusion that conceals her Regalia; she seems to be dressed in appropriate \textquotedblleft civilian" clothes for the area. The illusion does not alter her features - anyone who has seen her transformed self will recognize her if they meet her - but her status as a Noble is hidden. Any use of Charms dismisses the illusion. Supernatural powers that pierce illusions must beat the Princess' successes to see her true appearance.

    \emph{Exceptional Success:} The illusion blurs the Princess' features. People who have met her transformed before don't recognize her, unless they make a special effort to identify her (succeeding on a Wits + Investigation roll.)
\end{myindentpar}
    
\begin{myindentpar}{10pt}
\textbf{Upgrade: Disguised}

The Princess is able to choose her imaginary clothing's appearance, dress her hair, and add cosmetics to taste. An outfit chosen to support a disguise adds a +1 equipment bonus for each activation success; such changes can extend to anything a mundane make-up artist could accomplish - hair and skin can be dyed, hair lengthened or shortened, figures padded, and so on. Clothing chosen to support other Social tasks in which proper clothing helps grants a flat +1 bonus.

\textbf{Upgrade: Masked}

Requires Disguised

\noindent Cost: +1 Wisp

The Princess changes her features dramatically. She may alter all aspects of her appearance - ethnicity, height, build, voice, even sex - within the limits of her Size trait. (A Princess with the Giant Merit will always be a very tall man or woman, no matter how this Charm is used; a child Princess cannot look like a full-grown adult, and an adult cannot pass herself off as a child.) All attempts to identify her fail automatically. If she chooses her appearance to support a disguise, the Princess gets the equipment bonus from Disguised, and witnesses take a penalty of half her Inner Light (rounding up) to pierce the disguise.

The Princess can even attempt to take on the appearance of a specific person, applying the Intimacy modifier for her connection to the person she wishes to impersonate. The Princess and her target must still have the same Size.

\textbf{Upgrade: Durable}

Use of Charms does not destroy the illusion permanently. Instead, it flickers, revealing the Princess' true appearance for a moment; observers will notice this if they succeed on a reflexive Wits + Composure roll, penalized by her activation successes.
\end{myindentpar}

\subsubsection*{Unseen Traveller (Appear \textbullet)}
\noindent Action: Permanent\\

\noindent A Princess usually wants to be seen, to be noticed, to be the one that holds the lantern of Light that is the beacon to guide others. But sometimes, being seen is exactly what you don't need, as the Darkness flees from the Light it becomes harder to determine its plan and intent. The Princess gets the 9-again quality on mundane Stealth rolls within one of her specialities (chosen when she takes the Charm) and may apply an Invocation to such rolls. 

\begin{myindentpar}{10pt} \textbf{Upgrade: Chameleon}

Stacks, up to 2

The Princess' cloak shifts its appearance to best conceal her wherever she is. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for mundane Stealth rolls covered by any of the added specialities.

\textbf{Upgrade: Quiet (Lacrima \textbullet\textbullet)}

The Princess' movements are almost silent. When she attempts a surprise attack, her target's roll to avoid surprise takes a penalty equal to her Lacrima, and all attempts to locate her by listening take the same penalty. Moreover, she may spend a Wisp to make herself and anything (or anyone) she touches totally silent for a number of turns equal to her Lacrima; she can walk over ground littered with twigs and leaves or open a squeaky door without being heard. Things the Princess touches remain silent only while she is touching them, so she can still make noise indirectly. For example, if she bumps into a table with a vase on it, her impact makes no noise but the table's scrape against the floor might, and if the vase falls over it will make noise.

\end{myindentpar}

\subsubsection*{Mantle of Authority (Appear \textbullet, Terra \textbullet)}
\noindent Action: Instant, Presence + Politics 

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The power given a Princess from the Light appears, for a while, to be a more worldly sort of power.

    \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess may not use the Charm for 1 week.

    \emph{Failure:} The Princess' apparent status does not change.

    \emph{Success:} The Princess' transformed identity gains 1 dot of Status in a mundane organization she knows of. This dot stacks with any Status Merit she has in her transformed identity with that organization, but not with Status in her mundane identity, and it vanishes when the Charm ends.

    \emph{Exceptional Success:} The Princess' transformed identity gains 2 dots of Status in the mundane organization.\end{myindentpar}

\noindent A Princess may not use the Charm if she is already under its effects. \\


\begin{myindentpar}{10pt}\textbf{Upgrade: True}

If the Princess has Status in her mundane identity, she may claim all the privileges of that Status in her transformed identity by activating the Charm, instead of gaining a temporary Status.\end{myindentpar}

\subsubsection*{Face of Lover's Alarm (Appear \textbullet, Specchio \textbullet\textbullet)}

\noindent Action: Reflexive, Manipulation + Empathy

\noindent Cost: 1 Wisp\\

\noindent One would not threaten a loved one, would they? And as the Queen of Mirrors teaches, the True Heir will be beloved by all. This Charm is activated in response to an attack, and the Enlightened's face and appearance blurs into a loved one of the attacker. Successes on the roll cancel successes on the attack, on a one-to-one basis.

Such a delicate flower cannot be seen to fight back against the actions of a monster; a character may not apply their Defence against this attack, for to fight back would break the illusion. In addition, the Charm relies on the empathy and the goodness of the target, and so the number of successes which can be removed cannot exceed the Integrity (or supernatural equivalent) of the attacker. Against a target with no Integrity, such as a Darkspawn or an animal, the Charm fails to activate.

\begin{myindentpar}{10pt}\textbf{Upgrade: Known}

Clinging onto the glamour of the veiled features, the Princess can grasp the memory. She knows whose appearance she took on, and the nature of the emotional connection to the attacker. If she cancels out all the successes on the attack, she also unconsciously impersonates their mannerisms for the rest of the scene, imposing a -1 penalty on all further attacks for the rest of the scene, which explicitly stacks with multiple uses to a maximum of -5. This penalty, like the base Charm, vanishes if the Princess attacks. 

\textbf{Upgrade: Doomed (Specchio \textbullet\textbullet\textbullet\textbullet)}

\noindent Cost: +1 Willpower

Does the mirror reflect the truth, or does it show things how they should be? If the individual whom the Noble mimics is present, and within the attack range of the form of weapon used to attack her, the damage cancelled is transferred to them. In the case of a melee weapon, the target might swing wide and hit their friend; for a ranged weapon, it can be more improbable, as ricochets, arcing electrical conduits, and exploding fire extinguishers all conspire to hurt their ally. Armour cancels transferred damage on a one-for-one basis, but Defence does not apply against it.\end{myindentpar}

\subsubsection*{Phantom (Appear \textbullet\textbullet)}
\noindent Action: Instant, Wits + Expression 

\noindent Cost: 1 Wisp

\noindent Duration: concentration, then activation successes in turns\\

\noindent The Princess forms a Wisp into an illusory object. The illusion affects only sight, and
material objects pass through it without stopping. The Size of the image is limited to 2 + Inner
Light, but within that limit she can show any image she is capable of imagining.

\begin{myindentpar}{10pt}

\emph{Dramatic Failure:} The Charm fails with a burst of light and a loud crack, alerting
anyone nearby who could see or hear to the Princess's presence.

\emph{Failure:} No image appears.

\emph{Success:} The Princess creates the image she desires, somewhere within her sensory
range. The image remains as long as the Princess concentrates on maintaining it (which
prevents her from taking any action unrelated to the image) and for additional turns equal
to her activation successes. While she is concentrating on it, the Princess may move and alter the image with mundane actions, rolling Wits + Expression. The Storyteller may require
a different Skill for some actions (e.g. Subterfuge when an image is meant to deceive.) The
Princess may resume concentrating on the image after releasing it, as long as the Charm’s
duration hasn’t expired; any turn the Princess spends concentrating on the image does not
count against the Charm’s duration. The image freezes in place when the Princess stops
concentrating on it.

\emph{Exceptional Success:} The Princess manipulates her illusion deftly. Her mundane actions to control it gain a +2 bonus.

\textbf{Upgrade: Dancing}

The Princess may create an image that moves without her conscious attention. When
her concentration lapses, the image continues to act on the instructions she last gave it.

\textbf{Upgrade: Glowing}

Requires Light the Way

The Princess can make her illusions give off light, just as her Regalia does with Light
the Way. As long as she is concentrating on an image, she may vary the light coming from it
reflexively, independently of her personal light. If she has upgraded Light the Way, she may
apply all that Charm’s upgrades to the image’s light as if it were her own.

\textbf{Upgrade: Lasting}\\
Cost: +1 Wisp\\
Duration: 1 scene

The image endures to the end of the scene, whether the Princess concentrates on it or
not.

\textbf{Upgrade: Consecrated}\\
Requires Lasting

The Princess may sustain a Lasting illusion with the blessing of a Consecrated area. Doing
so keeps the illusion intact until the Consecrated Condition ends, but limits its movements
to the area covered by the Condition. The Princess must apply Lasting to tie an illusion to a
Consecrated area.

\textbf{Upgrade: Singing}

The Princess may create an illusory sound, or add sound to an illusory image. A sound
without an image seems to come from a point the Princess can see, which she can move while
concentrating.

\textbf{Upgrade: Solid}

The image becomes substantial. As long as it lasts it has a degree of solidity, as well as
a firmness and texture appropriate to what it depicts. However, just because it projects an
image of solidity does not mean it is solid; the image shatters if force is applied to it (by kicking
an illusionary wall, for example) or with it (an illusionary wrench won't tighten or loosen a
bolt).

\textbf{Upgrade: Thinking (Acqua ••)}\\
Requires Dancing

When the Princess releases her concentration, in addition to providing the illusion with
further instructions she may grant it a measure of adaptability. For each dot of Acqua she may
instruct the image to react to one condition, altering its behavior in response. For conditions
that require senses to recognize, the illusion has a Perception dice pool equal to the Charm’s
activation successes.

\textbf{Upgrade: Multiplied (Aria ••)}\\
Requires Dancing

The Princess may create multiple distinct images with a single Charm activation. She can
make one image for each dot of her Aria; for each image beyond the first, the maximum Size
of all the images is reduced by 1. The Princess can try to control more than one image at once but takes a -2 penalty to her dice pool for each image beyond the first. If she applies Singing,
each image may have its own sound and images can be replaced with sounds, but the number
of distinct illusions remains limited to her Aria.

\textbf{Upgrade: Scented (Legno •)}

The Princess may create an illusory scent, or add scent to an illusory image or sound.
If the image is Solid, she can give it a taste as well. A scent without an image seems to come
from a point the Princess can see, which she can move while concentrating.

\textbf{Upgrade: Painted (Terra •)}

The Princess may create an illusory surface which covers and disguises an existing object. Applying this upgrade adds 1 to the image’s maximum Size, raising it to 3 + Inner Light;
however, the image’s shape must be fairly close to that of the object it disguises. The Princess
may disguise part of an object if she wishes, or the whole exceeds her Size limit. The image is
bound to the object and moves with it, though the Princess can still change it while concentrating on it.

\end{myindentpar}
\subsubsection*{Dim (Appear \textbullet\textbullet)}
\noindent Action: Instant and contested, Manipulation + Stealth vs. Wits + Composure + supernatural advantage

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The Princess becomes very difficult to notice or remember. An onlooker might see her, but he ignores her the same way he might ignore any completely inconsequential thing that he expects to be present. When someone first perceives the Princess, or when she does something that draws someone's attention (casting a Charm invariably does so) he must beat her successes on his perception roll to notice her presence or recall it afterwards. Anyone the Princess speaks to, touches or otherwise interacts with is immune to the Charm as long as they keep her in view; but if they look away, they must win the contest again to find her.

\begin{myindentpar}{10pt}\textbf{Upgrade: Traceless}

The concealment extends to recording devices -- video cameras show only a human-sized distortion in the air where the Princess is, and microphones record meaningless noises (like the adults' voices in \textquotedblleft Peanuts") instead of her voice, unless she deliberately speaks into them.

\textbf{Upgrade: Veiled}

Using another Charm does not automatically attract attention to the Princess, though again the direct effects of the Charm are not concealed.\end{myindentpar}

\subsubsection*{Speaking Eyes (Appear \textbullet\textbullet, Acqua \textbullet)}
\noindent Action: Instant, Wits + Persuasion

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene\\

\noindent The movements of the Princess' body are saturated by meaning. On a successful activation roll, she can convey the most complicated of thoughts with a turn of the head, a twist of the hand, or a facial expression, as quickly as with normal speech; others will understand her intent even if they share no languages with her, as long as they can see her. The Charm does not help the Princess understand other people, and it is not selective - everyone who sees her knows what she means, when she chooses to communicate in a gesture.

\begin{myindentpar}{10pt}\textbf{Upgrade: Intimate (Acqua \textbullet\textbullet)}

The language of the Princess' movements becomes private. When she activates the Charm, she chooses one person for each success rolled, up to her Acqua. Until the Charm ends, she can convey her thoughts to those people without words if they can see her, as with the basic Charm, but nobody else looking at her will understand her meaning. Indeed, unless onlookers examine her carefully (succeeding on an Intelligence + Investigation roll) they won't realize that she is \textquotedblleft saying" anything at all.\end{myindentpar}  


\subsubsection*{Summon Backup Dancers (Appear \textbullet\textbullet\textbullet)}
\noindent Action: Instant, Dexterity + Expression

\noindent Cost 3 Wisps

\noindent Duration: 1 scene \\

\noindent Sometimes a Princess just needs to wow a crowd. With this Charm a Princess can summon her own support team with a maximum of Inner Light members.

Before casting Summon Backup Dancers the Princess must declare what kind of action they're going to support. The Princess could declare singing in which case they'd be able to perform dance routines or backup vocals. The Princess could declare painting and summon a model to paint.

Backup dancers are solid but only when it relates to their assigned task, an actor would be able to interact with props, and wear costumes, but would not be able to fetch a cup of coffee. A cunning Princess might still be able to use them for other roles, she might ask her trope to dance around waving their arms in front of her enemies face while she hides, or to attack foes who don't realise the backup dancers cannot hurt them. (Assume a 1 die pool on any social actions, mental and physical tasks fail automatically). If attacked a single point of Damage, even Bashing, causes a Backup dancer to vanish into a puff of ephemera appropriate to the Princess.

A Princess can only have one instance of Summon Backup Dancers active at a time.

\begin{myindentpar}{10pt}     \emph{Dramatic Failure:} You summon Inner Light performers but have no control over them. They immediately run riot, while not actually harmful they can be very very annoying and are certainly inappropriate to the Princesses wishes. Think clowns, not monsters.

    \emph{Failure:} No Dancers appear.

    Successes: The Princess summons up to Inner Light backup dancers. Their assistance allows her to add Inner Light to any mundane rolls in a chosen Crafts or Expression Speciality (The Princess does not need to have that Speciality herself). If the Charm was Invoked the Princess add her Invocation instead of Inner Light.

    \emph{Exceptional Success:} As per Success but with an additional +1.\end{myindentpar}

\subsubsection*{Goccia Astrale (\textbullet\textbullet\textbullet)}
\noindent Action: Instant, Intelligence + Crafts 

\noindent Cost: 2+ Wisps

\noindent Duration: Variable\\ 

\noindent \textquotedblleft I can't be in two places at once!\textquotedblright\, is an all-too-common complaint from just about anyone; the Hopeful especially find it necessary to be two people at once, when mundane obligations interfere with fighting a supernatural incursion. With this Charm a Princess can partly resolve such dilemmas, by making a facsimile of her mundane self that moves and speaks, and can pass as herself if not examined too closely.

To use the Charm, the Princess must have a mass of material that she can shape barehanded, or else a quantity of fluid, of roughly Size 2. Infusing this material with Wisps, she transforms it into an Astral Droplet: an exact physical copy of herself just before her last transformation, wearing identical clothing. The Droplet has the same mundane Attributes and Skills as its creator, and access to all her memories as of the time of its creation. However, it lacks energy and imagination; it does not get 10-again on any dice pool, or any other quality that allows rerolling dice, cannot spend Willpower, and has neither Virtue nor Vice. The Droplet is also fragile - a single point of damage of any type is enough to dissolve it into the stuff it was made of and glimmers of light. Finally, the Droplet has none of the Princess' Light-derived powers, not even Practical Magic.

The Droplet's basic duration is 30 minutes for each activation success. The Princess may choose to extend the duration by spending more Wisps than the minimum of 2 - each extra Wisp doubles the time before the Droplet disintegrates, cumulatively. She cannot, however, spend more Wisps for this purpose than half her Inner Light, rounded up. She may choose the total number of Wisps spent after the activation roll, though she must spend at least 2. She may end the Charm prematurely by touching the Droplet and concentrating for a turn. A Princess cannot create a second Droplet before the first Droplet dissolves - the Charm just fails if she tries.

By default the Droplet is an automaton which follows any instruction given to it which does not pose a threat of physical harm, and otherwise stays wherever it is put; it takes no action on its own. If the material used to make it resonates with an Invocation the Princess may apply that Invocation to the Charm (Aria uses thick mist or smoke, or a strong breeze, Lacrima can use total darkness or dark shadow.) Droplets so formed have some initiative and the rudiments of a personality; in the absence of clear instructions they follow the tenets of the applied Invocation, to the extent allowed by the knowledge and abilities the Princess possesses.

\begin{myindentpar}{10pt} \textbf{Upgrade: Integrated}

It's often useful to know what your double has been doing during your absence. If the Princess dissolves her Droplet prematurely by touching it and concentrating, she can recall to memory a description of the actions the Droplet took and the events it saw and heard. A roll to recall any detail of the account is at -2 in addition to any other penalties.

\textbf{Upgrade: Lifelike (Specchio \textbullet\textbullet\textbullet)}

A Lightbringer can use that indescribable quality that makes her reflection \textquotedblleft her reflection\textquotedblright instead of a simple image and use it to place mind and will into the Droplets they make. To apply Lifelike the Princess needs a reflecting surface large enough to hold an image of her upper body; she takes the hands of her image and pulls it out of the surface. The resulting Droplet is flipped left-to-right, and with the opposite dominant hand. The real difference though, is that the Droplet gains a nearly-human initiative and will; it has the Belief dots, Virtue and Vice of its creator, gets 10-again on its dice pools, can benefit from other qualities that permit rerolls, and may spend and regain Willpower (though it begins with none.) The only supernatural ability the Droplet possesses is the ability to Transform and benefit from Transformed skills and attributes, created by Specchio it possesses the Queen of Mirror's Practical Magic. The first time the Princess creates this 
Droplet, its personality exactly matches her own (including any forms of madness) and aside from the physical inversion they can't be told apart.

\textbf{Drawback:} By invoking a Lifelike a Princess is summoning an independent being. The Droplet's personality does not vanish when its body dissolves; it returns to being her reflection, until she makes another Lifelike Droplet. At that moment it returns and inhabits the new-made body. Every time the Princess invokes Lifelike there is a chance that Specchio's madness will infect her Droplet. Each time it inhabits a new body the Droplet rolls Resolve + Composure, with a -2 penalty if the Princess is suffering from Specchio induced madness. If she fails, the Droplet's falls to Specchio's arrogance; she is convinced of her excellence and her right to rule, and resents the Princess taking her rightful limelight. The Droplet will do what it can to avoid returning to behind the mirror. It can lengthen the Charm's duration by spending its own Willpower; it may spend 1 point each day for this, which adds 24 hours of continued embodiment. (The Droplet cannot do this if the Resolve + Composure check succeeds.) 
Just what the Droplet does is up to the Storyteller, but it should avoid Compromising it's own beliefs.

If the Princess applies Integrated and Lifelike, all her memories since the Droplet's first creation become available to it on the same terms as its are available to her after she dissolves it. Other than that, neither personality can remember what the other has done.\end{myindentpar}

\subsubsection*{Masquerade (Appear \textbullet\textbullet\textbullet, Aria \textbullet)}
\noindent Action: Instant and resisted, Manipulation + Empathy vs Composure + Supernatural Advantage

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent Instead of changing herself, the Princess changes how another perceives her. If she succeeds, the target cannot see through any disguise that she assumes or role that she enacts; in all contests of Wits + Subterfuge for this purpose between them, the target automatically gets a dramatic failure. The Princess cannot use Masquerade to impersonate a specific person the target knows or has met -- she is limited to a generic role. Masquerade ends if the Princess uses any other Charm.

\begin{myindentpar}{10pt}\textbf{Upgrade: Familiar}

\noindent Cost: +1 Wisp

The Princess can try to impersonate someone her target knows. The target does not automatically fail this contest, but the Princess takes no penalty from the target's familiarity with the person she imitates, and she adds her successes on the activation roll as a bonus to her side of the contest.

\textbf{Upgrade: Social (Aria \textbullet\textbullet)}

\noindent Cost: +1 Wisp

The Princess may use Masquerade on a social group, applying the Commonalty modifier. The member with the highest Composure resists for the whole group.

\textbf{Upgrade: Veiled}

The Princess may use other Charms without ending Masquerade, and the target will not notice their manifestations -- he perceives the direct effects of the Charms, but will not trace them back to her.\end{myindentpar}

\subsubsection*{A Flight of Furious Fancies (Appear \textbullet\textbullet\textbullet, Aria \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Wits + Subterfuge - Composure

\noindent Cost: 1 Wisp

\noindent Duration: 1 Turn\\

\noindent The princess conjures an host of illusionary attacks on any target she can see clearly. These attacks can do no damage but the target may waste their attention defending against non-existent foes. Each success reduces the target's defence by one until the next turn, if the target chooses to Dodge then apply the penalty after doubling Defence.


\subsubsection*{Doppelgänger Defence (Appear \textbullet\textbullet\textbullet, Aria \textbullet\textbullet\textbullet)}
\noindent Action: Reflexive, Wits + Subterfuge vs Wits + Composure

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: 1 Turn\\

\noindent At the perfect moment the princess creates an illusionary double of her ally, or herself, just as her enemy prepares to strike. If the Princess wins the contested roll her opponent targets the illusion, if she fails her enemy sees through the ruse or gets lucky.

The effects of this Charm depend on what the target was planning to do. A sword stroke is entirely wasted but throwing a grenade at the illusion might still catch the real person in the blast. If the target is using a gun capable of automatic fire she could easily shoot at both to be on the safe side.


\subsubsection*{Know My Pain (Appear \textbullet\textbullet\textbullet, Tempesta \textbullet\textbullet)}
\noindent Action: Full turn and resisted, Resolve + Intimidation - target's Composure

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene\\ 

\noindent There are those who would tell you that pain is bad, and to be avoided at all costs. They are weak. Pain is a tool, just like any other. It is not only useful, but even necessary, to use it against those who would try to stop you.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess gives pain only to herself. For the rest of the scene she suffers a -1 penalty to all her actions.

    \emph{Failure:} The target ignores the Princess' pain.

    \emph{Success:} The target suffers phantom bashing damage, equal to the number of boxes with damage of any type on the Princess' Health track or his unmarked Health boxes, whichever is less. The target suffers wound penalties from this damage if it goes into the last three boxes, and must check their Stamina to remain conscious if it fills the last box, as normal. However, the damage is not real; it vanishes when the Charm ends as if it were healed, and if the target takes real bashing damage when the track is full, that damage replaces the phantom damage instead of wrapping into lethal damage. Phantom damage also has no effect if the target has no empty Health Boxes to fill. The phantom damage can also be healed magically, or mitigated as it's inflicted by targets who have that ability.

    \emph{Exceptional Success:} The phantom damage from the Charm is lethal. The target does not bleed out if the phantom damage incapacitates him, and real lethal damage replaces it instead of wrapping into aggravated damage. 

\textbf{Upgrade: Intimate}

A part of the injury the Princess suffers from her target returns to him. Whenever a target of the Charm damages the Princess further, she may spend a Wisp reflexively to inflict 1 damage on that target, of the same type as what he inflicted. Unlike the initial damage, this is fully real, and remains after the Charm ends.

\textbf{Upgrade: Shared (Tempesta \textbullet\textbullet\textbullet)}

\noindent Cost: +1 Wisp

The Princess may use Know My Pain on a social group, applying the Commonalty modifier; every member of the group takes phantom damage. The member with the highest Composure resists for the whole group.

\end{myindentpar}

\subsubsection*{Drawn From Within The Mirror (Appear \textbullet\textbullet\textbullet, Specchio \textbullet\textbullet)}

\noindent Action: Instant, Manipulation + Crafts

\noindent Cost: 1 Wisp

\noindent Duration: 1 Scene\\ 

\noindent The Princess can reshape mirrors and reflective surfaces into tools for her use.

    \emph{Dramatic Failure:} The princess begins to reshape the mirror, but a misplaced gesture makes it shatter, lacerating her hands. She takes one level of lethal damage, and a -1 to all rolls involving her hands for the rest of the scene.

    \emph{Failure:} The reflective surface will not flow into shape, even if it twists and warps subtly.

    \emph{Success:} The princess touches a reflective surface, and the surface of the mirror flows like liquid metal into her grasp, forming an object with Size less than or equal to the size of the reflective surface. The object, apparently made of light and reflections and quicksilver, provides a number of bonus dice equal to the successes rolled to any skill which it could aid. The Storyteller is to use their discretion for this; while a beautiful dress can be used with many social skills, a knife is pretty much limited to Weaponry, and possibly Intimidate, rolls. The equipment bonus is capped at +5.

    The tool is fragile and brittle - it has 0 Durability and just 1 Structure. If it takes damage, it is destroyed. It must be a single item with no moving or electronic parts, with the exception of clothing, which may provide an entire set of clothing. The item lasts for a scene, and at the end of it, it falls into dust. Since it is made of the reflective surface of the mirror or metal, the item is defaced, and must be repaired or repolished before it will reflect again.

    \emph{Exceptional Success:} The tool is crafted with such skill that it is more resilient to damage, and has 3 Structure rather than 1.
    
\noindent Suggested modifiers:

\begin{itemize}\item -2 : Surface of water, reflection is weak and inconstant
\item -1 : Tin foil
\item 0: Modern mirror
\item +2 : Reflection is especially clear, mirror is highly valued (Resources 3+) or of great sentimental value to someone.\end{itemize}
    


\subsubsection*{Cloaks of Mist (Appear \textbullet\textbullet\textbullet\textbullet, Acqua \textbullet\textbullet\textbullet)}

\noindent Requires: Dim

\noindent Action: Instant and contested, Manipulation + Stealth vs. Wits + Composure + supernatural advantage

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene \\

\noindent The Princess summons a dew that falls on targets whose total Size does not exceed 5 times her successes. For the duration, the targets fade from the notice and memory of all save the Princess and each other; each benefits from the effects of Dim.

\begin{myindentpar}{10pt} \textbf{Upgrade: Traceless}

The targets are concealed from recording devices as well.

\textbf{Upgrade: Veiled}

The targets may activate Charms (or other obviously supernatural powers) without automatically attracting the attention of observers.\end{myindentpar}

\subsubsection*{Imaginary Friend (Appear \textbullet\textbullet\textbullet\textbullet, Aria \textbullet\textbullet\textbullet)}

\noindent Action: Instant and contested, Manipulation + Subterfuge vs. Wits + Subterfuge + supernatural advantage

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene\\

\noindent The Princess creates the illusion of a man or woman, especially crafted for a single person. She chooses a role for the illusion; if she gains any successes, the target perceives a person who behaves appropriately for that role in the present situation, according to the target's beliefs. However, if she doesn't beat the target's successes, he realizes that this person is an illusion within moments. If she doed get more successes, the target will treat the imaginary person as fully real, and respond to it as to a person of the role you chose. No one else -- including the Princess -- will see or hear the illusion; she has no control over its behavior.

\subsubsection*{Garden of Bright Images (Appear \textbullet\textbullet\textbullet\textbullet)}
\noindent Requires: Phantom

\noindent Action: Extended, Presence + Expression (1 minute/roll, threshold = Sanctuary + duration in hour). 

\noindent Cost: (Sanctuary rating) Wisps

\noindent Duration: 1 or more hours \\

\noindent The Princess decorates her surroundings with a beautiful glamour. She chooses an area to affect and a time for the glamour to last when she starts working on the Charm.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess deceives only herself; she sees the area transformed according to her intentions, but everyone else sees it as it really is

\emph{Failure:} The Princess makes no progress towards the Threshold.

\emph{Success:} When the Princess reaches the threshold, the appearance of every nonliving thing in the targeted area is transformed to match a theme the Princess chooses. (For instance, \textquotedblleft formal ballroom", \textquotedblleft open bazaar", \textquotedblleft African jungle" and \textquotedblleft undersea grotto" are all valid themes.) Permanent fixtures are always changed; she can choose whether to change people’s possessions, but cannot affect some possessions and not others. As long as the Charm lasts, the changed objects look, sound, feel and even smell like what they appear to be; observers may make Perception rolls to spot something wrong with the illusion, but they take a penalty equal to the Princess’ successes.

\emph{Exceptional Success:} If the Princess scores an Exceptional Success on her extended roll then mundane senses cannot penetrate the illusion. 

\textbf{Upgrade: Palatine} 

The Princess may take advantage of a Consecrated Condition. When she does so, the illusion covers all the Consecrated ground and lasts until the Condition expires or she dismisses the Charm; treat the duration as 0 when calculating the threshold\end{myindentpar}

\subsection*{Bless}
The Bless Charm enhances people, pushing their abilities to a peak and bringing their actions to perfection. Champions and Graces have affinity for it.

Several Bless Charms add dots to Attributes or bonus dice. Unless otherwise noted, dots from these Charms don't contribute to Charm activation rolls, or any roll to activate a supernatural power.

\subsubsection*{Small Providence (Bless \textbullet)}

\noindent Action: Instant, Manipulation + Streetwise

\noindent Cost: 1 Wisp

\noindent Duration: 1 day \\

\noindent The Princess (or one she helps) finds, and obtains, that one thing she was looking for, at a surprisingly low price. The target gains the Bargain condition: The applicable purchases are everything and the discount is one dot. On an exceptional success the discount is two dots.  

\subsubsection*{Sea-Foam's Touch (Bless \textbullet, Acqua \textbullet)}

\noindent Action: Instant, Wits + Academics

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent Truth is an ocean, from which the Princess draws a few drops. Success grants the target the Floating Blessing Condition: The affected traits are Mental Skills and the pool starts with two dice per success. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Splashing}

The affected traits are now Mental Attributes and Mental Skills.\end{myindentpar}

\subsubsection*{Bejewelled Visage (Bless \textbullet, Terra \textbullet)}

\noindent Action: Instant, Manipulation + Empathy

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent An odor of trust enfolds the one the Princess blesses, smoothing his path in society. Success grants the target the Floating Blessing Condition: The affected traits are Social Skills and the pool starts with two dice per success. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Profuse}

The affected traits are now Social Attributes and Social Skills.\end{myindentpar}

\subsubsection*{Count No Cost (Bless \textbullet, Tempesta \textbullet)}

\noindent Action: Instant, Stamina + Athletics

\noindent Cost: 1 Wisp, 1 resistant bashing damage

\noindent Duration: 1 Scene \\

\noindent The Princess blesses the target with a small part of the storm's fury. Success grants the target the Floating Blessing Condition: The affected traits are combat rolls (including tricks like Wits + Brawl to read a fighter's combat experience) and the pool starts with two dice per success. 

\subsubsection*{I'm the Best! (Bless \textbullet, Specchio \textbullet)}

\noindent Action: Reflexive and Contested, Presence + Wits vs Composure + supernatural advantage

\noindent Cost: 1 Wisp

\noindent Duration: 1 extended action\\

\noindent Others might say that they are the masters of their fields. But, simply, the Enlightened of the Queen of Mirrors know this to be false. They can't be better. This Charm can be used to enhance any contested extended action against an opponent who has a higher dice pool than they do. Each success removes one dice from the target's pool, and adds one dice to the Noble's pool. The number of dice transferred is capped by the Specchio rating of the Noble; such glorious victory comes from one's own strength, after all. This may not reduce the target's pool to less than zero. This Charm only applies to a single roll; it must be re-invoked to apply to other rolls in the extended action.

\begin{myindentpar}{10pt}\textbf{Upgrade: Truly}

Stacks, up to 3

On actions where this Charm is used, once the dice transfer has been applied, the Noble may then add +1 to their own pool, as if it were coming from a Speciality in \textquotedblleft Defeating (opponent's name)".
\textbf{Upgrade: Triumphantly} (Specchio 4)

The limitation that the target must have a higher initial dice pool than the Noble is now waived. In addition, if the foe is reduced to a dice pool of zero, the Noble may reflexively spend a Willpower point to force a Dramatic Failure.\end{myindentpar}

\subsubsection*{Intuitive Flash (Bless \textbullet\textbullet)}

\noindent Action: Instant, Intelligence + Academics

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The Princess grants knowledge and ability to someone within sight. For each success, the target gains one additional speciality, provided by a stack of the Blessing Condition. The Princess chooses which specialities are bestowed. 

Intuitive Flash does not stack with other supernatural powers that provide specialties. The target chooses which blessing they wish to benefit from and discards any others.

\subsubsection*{Touch of Fortune (Bless \textbullet\textbullet)}

\noindent Action: Reflexive, Wits + Occult

\noindent Cost: 1 Wisp

\noindent Duration: Duration: 1 scene \\

\noindent The Princess grants a blessing of good fortune to a person she can see. The next rolls made by the target, up to a number equal to the activation successes, gain the 9-again quality. A Princess may cast Touch of Fortune at the same moment another person acts to bless that roll. If there are blessings unused when the scene ends, they are lost. The Charm may not be used on anyone currently affected by it. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Well-timed}

The target's good fortune comes when most needed. Before the target makes a roll, he declares whether the Charm will affect it. The number of rolls affected does not change. 

\textbf{Upgrade: Strong}

\noindent Cost: +1 Wisp

The Princess grants a stronger blessing; the rolls affected by the Charm gain the 8-again quality.

\textbf{Upgrade: Perfected}

Requires Strong

\noindent Cost: +3 Wisps

The blessed actions become deceptively easy; instead of gaining 9-again the rolls affected by the Charm gain the rote quality. Strong and Perfected cannot both be applied to the same activation.\end{myindentpar}

\subsubsection*{Engine Heart (Bless \textbullet\textbullet, Fuoco \textbullet)}

\noindent Action: Instant, Presence + Persuasion 

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent Passion blazes in the Princess' heart, and with it she can ignite any heart. Success grants the target the Floating Blessing Condition: The affected traits are Power Attributes and the pool starts with two dice per success. 

\subsubsection*{Steady Resolve (Bless \textbullet\textbullet, Legno \textbullet)}

\noindent Action: Instant, Composure + Persuasion 

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent With a reassuring word, the Princess hardens her or another's spirit. Success grants the target the Floating Blessing Condition: The affected traits are Resistance Attributes and the pool starts with two dice per success. 

\subsubsection*{Wits of Wind (Bless \textbullet\textbullet, Aria \textbullet)}

\noindent Action: Instant, Wits + Persuasion 

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The Princess moves on wild winds, she moves faster, thinks sharper and for a time she can even carry another with her. Success grants the target the Floating Blessing Condition: The affected traits are Finesse Attributes and the pool starts with two dice per success. 

\subsubsection*{Burden of Rule (Bless \textbullet\textbullet, Lacrima \textbullet)}

\noindent Action: Instant, Manipulation + Empathy

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The Princess calls up cold despair and unending resolve. Success grants the target the Floating Blessing Condition: The affected traits are Anything that protects my kingdom and the pool starts with two dice per success. 

When used in defence of Alhambra, anything that protects the city's supply of Wisps explicitly qualifies for the blessing. 

\subsubsection*{Light’s Aegis (Bless \textbullet\textbullet\textbullet)}

Action: Instant, Presence + Resolve

Cost: 2 Wisps

Duration: 1 scene \\

\noindent The Princess extends a portion of her mantle over another person, granting him the power to ward off injuries. The Charm may not be used on anyone currently affected by it or anyone who has been affected by it in the current scene. 

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess mishandles her power and injures herself. She takes 1 resistant lethal damage.

\emph{Failure:} The target is unprotected by the Charm. 

\emph{Success:} The target has limited access to the Princess’ Holy Shield. He takes the Aegis Tilt: each activation success each creates one shield-point which is equivalent to one Wisp spent on Holy Shield: A shield-point can be spent to downgrade Aggravated to Lethal damage, downgrade Lethal damage to Bashing damage, or negate all but the first point of Bashing damage. The Aegis may spend the same number of shield-points per turn as the caster's Wisps per turn. The Tilt stacks with the innate Holy Shield if used on a Noble; both may be used against an attack. 

\emph{Exceptional Success:} Extra successes are their own reward. \end{myindentpar}




\subsubsection*{What's That Sound (Bless \textbullet\textbullet\textbullet, Aria \textbullet\textbullet)}

\noindent Action: Instant and resisted, Wits + Composure

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent With a breath of excited air the Princess sends her target into a state of extraordinary alertness. The target gains the condition Alert. 

\begin{myindentpar}{10pt}Upgrade: Collective

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group that can see or hear her, using the Commonalty modifier. 
\end{myindentpar}

\subsubsection*{Oaken Fortitude (Bless \textbullet\textbullet\textbullet, Legno \textbullet)}

\noindent Action: Instant, Strength + Medicine

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The Princess' presence fortifies, allowing the one she blesses to endure and throw off wounds. The target gains the Temporary Health condition with one Health box per Success, this condition comes with the Healing modifier. 

If the target already has Temporary Health this charm can \textit{not} be used. 

\subsubsection*{Jade Palm Strike (Bless \textbullet\textbullet\textbullet, Terra \textbullet\textbullet)}

\noindent Action: Instant, Presence + Expression

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene \\

The Princess wraps a friend's hands in a magical aura that cuts the flesh of servants of Darkness.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The target's arm turns into solid Jade. Take the Arm Wreck Tilt for the scene. 

    \emph{Failure:} For a moment, the target feels spiritually cleansed.

    \emph{Success:} The target acquires the mystical purity of jade. His flesh has the same effects on creatures of Darkness that jade does until the Charm ends and he gains a bonus die to resist Dark magic. Jade Palm Strike cannot stack bonuses with physical jade. 
    
    \emph{Exceptional Success:} The target also treats Creatures of the Darkness as purely mundane humans for determining if interaction with a Darkspawn causes a Breaking Point. 


\textbf{Upgrade: Armed}

The target's enchanted aura spreads to his weapons. A weapon in his hands acts on Dark creatures as if made of jade. The aura comes from the target, not the weapon, so it fades from a weapon when he releases it; however, it lingers long enough for a thrown object or a bullet to hit its target.

\textbf{Upgrade: Multiple}

Cost: +1 Willpower

The Princess may give a jade aura to all the members of an organization in her presence, applying the Commonalty modifier.\end{myindentpar}


\subsubsection*{Drawn by the Moon (Bless \textbullet\textbullet\textbullet\textbullet, Acqua \textbullet\textbullet)}

\noindent Action: Instant, Intelligence + Science

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene \\

\noindent  As the tide rises to follow the moon, the mind rises to follow the light. The Princess applies the Blessing Condition to the target. The affected trait is a Mental Attribute of her choice, and the increase is her activation successes, up to her Acqua. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Grand (Acqua \textbullet\textbullet\textbullet)}

The Princess may split her activation successes, creating multiple Blessing Conditions each affecting one Mental Attribute. She still cannot add more than her Acqua to any one Attribute.\end{myindentpar}

\subsubsection*{Wind-Borne Grace (Bless \textbullet\textbullet\textbullet\textbullet, Aria \textbullet\textbullet)}

\noindent Action: Instant, Presence + Expression

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene \\

\noindent The wind grants both speed and subtlety. The Princess applies the Blessing Condition to the target. The affected trait is a Finesse Attribute of her choice, and the increase is her activation successes, up to her Aria. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Grand (Aria \textbullet\textbullet\textbullet)}

The Princess may split her activation successes, creating multiple Blessing Conditions each affecting one Finesse Attribute. She still cannot add more than her Aria to any one Attribute.\end{myindentpar}

\subsubsection*{Stoke the Furnace (Bless \textbullet\textbullet\textbullet\textbullet, Fuoco \textbullet\textbullet)}

\noindent Action: Instant, Strength + Persuasion

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene \\

\noindent The Princess brings fuel the body, mind or character. The Princess applies the Blessing Condition to the target. The affected trait is a Power Attribute of her choice, and the increase is her activation successes, up to her Fouco. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Grand (Fuoco \textbullet\textbullet\textbullet)}

The Princess may split her activation successes, creating multiple Blessing Conditions each affecting one Power Attribute. She still cannot add more than her Fouco to any one Attribute.\end{myindentpar}

\subsubsection*{Forest Sanctuary (Bless \textbullet\textbullet\textbullet\textbullet, Legno \textbullet\textbullet)}

\noindent Action: Instant, Stamina + Survival

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene \\

\noindent A tall tree shelters those beneath its branches. The Princess applies the Blessing Condition to the target. The affected trait is a Resistance Attribute of her choice, and the increase is her activation successes, up to her Legno. 

\begin{myindentpar}{10pt}Upgrade: Grand (Legno \textbullet\textbullet\textbullet)

The Princess may split her activation successes, creating multiple Blessing Conditions each affecting one Resistance Attribute. She still cannot add more than her Legno to any one Attribute.\end{myindentpar}

\subsubsection*{Crown Jewels (Bless \textbullet\textbullet\textbullet\textbullet, Terra \textbullet\textbullet)}

\noindent Action: Instant, Manipulation + Persuasion

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene \\

\noindent Courtesy is the most beautiful jewelry. The Princess applies the Blessing Condition to the target. The affected trait is a Social Attribute of her choice, and the increase is her activation successes, up to her Terra.

\begin{myindentpar}{10pt}\textbf{Upgrade: Grand (Terra \textbullet\textbullet\textbullet)}

The Princess may split her activation successes, creating multiple Blessing Conditions each affecting one Social Attribute. She still cannot add more than her Terra to any one Attribute.\end{myindentpar}

\subsubsection*{Tendril of Nothing (Bless \textbullet\textbullet\textbullet\textbullet, Lacrima \textbullet\textbullet\textbullet)}

\noindent Action: Instant and resisted, Presence + Intimidation - target's Composure

\noindent Cost: 2 Wisps, 1 Willpower, Compromise at Belief 4+ with a -3 modifier

\noindent Duration: 1 scene \\

\noindent The void can seep into every mind. Give in, it says. Do not resist. Give up, and let your sorrows drown you.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess lets the void only into your own mind. She suffers from the Depression condition, it cannot be Resolved but fades on the next full moon.

    \emph{Failure:} The power does not activate.

    \emph{Success:} The stillness of the void settles into the heart and mind of a foe. The target gains the Condition Cursed, the affected trait is a Resistance Attribute of the Princess' choice, the decrease is the activation successes. This Charm cannot reduce an attribute to zero dots. 
    
    If the last box on the target's Health track fills with aggravated damage, the Charm ends and the Condition is removed. When the Charm does end, the target's Attributes return to their normal values; all restored Health boxes are empty.

    \emph{Exceptional Success:} Such a show of force terrifies the foe, showing them the foolishness of standing up to the Princess. In addition to the other effects, he suffers from the Depression Condition until the next time he sees the sun.\end{myindentpar}

\subsubsection*{Avenger's Might (Bless \textbullet\textbullet\textbullet\textbullet, Tempesta \textbullet\textbullet)}

\noindent Action: Instant, Resolve + Brawl

\noindent Cost: 2 Wisps, 1 resistant lethal damage

\noindent Duration: 1 scene\\

\noindent The Princess binds fury into flesh. The Princess applies the Blessing Tilt to the target. The affected trait is a attack rolls, and the increase is the activation successes, up to her Tempesta.


\subsubsection*{Peaceable Kingdom (Bless \textbullet\textbullet\textbullet\textbullet\textbullet, Legno \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Intelligence + Animal Ken

\noindent Cost: 3 Wisps, 1 Willpower

\noindent Duration: 1 scene \\

\noindent The Queen of Clubs' avatar is guardian and teacher of the beasts. The Princess undergoes a second transformation on activating the Charm, assuming traits that suggest a large and powerful animal \textendash\, typically a lion, though bear-like and eagle-like miens are known, and there are rumors of one Hopeful who evokes a dragon. The change always suggests a king or queen of beasts, and the peril and majesty of the natural world; any mortal seeing the Princess is somewhat shaken, and she gains +1 on all Intimidation rolls against them until the Charm ends.

However, the main effect of the Charm is on beasts who see it. Any natural animal that can perceive the Princess when she activates the Charm has its Intelligence raised by 1 dot, becoming sapient. Further, the animals affected gain instant fluency in her native language, and the Charm grants them the ability to speak it comprehensibly if they have any ability to vocalize at all. The Princess may use Social Skills on the animals as she would with mortals, and gains a bonus on such rolls equal to her activation successes. When the Charm ends, the animals return to their former non-sapient state. If the Princess use the Charm twice on the same animal, it remembers everything that happened during the first use.

Until the Charm ends, the Princess gains the Invocation Lock condition keyed to Legno.

\subsubsection*{Sheltered by Her Hand (Bless \textbullet\textbullet\textbullet\textbullet\textbullet, Lacrima \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Resolve + Empathy, modified by Commonalty

\noindent Cost: 1 Wisp, 1 Willpower, Compromise at Belief 4+ with a -3 modifier

\noindent Duration: 1 scene \\

\noindent To preserve her city and her subjects is the first principle of the Queen of Tears, and those who incarnate her are able to guard their allies from all harm. A Princess uses this Charm to protect citizens of Alhambra (no other Commonality group may be used; Lacrima may not be magically linked to Alhambra, but the avatar of Alhambra's Lady certainly is).

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess fails utterly to protect her allies, and is crushed. She looses a point of Willpower and cannot spend or regain Willpower for the rest of the scene. In other words, she gains the Depression Condition but automatically suffers it's full effects without needing to fail in her goals first. 

    \emph{Failure:} The Princess cannot protect her allies. The Charm fails.

    \emph{Success:} The Princess undergoes a second transformation that drains all the colour from her body and Regalia. All members of the target group who can see this transformation feel a breath of cold pass over them, penetrating through all clothing for a moment. 
    
    Until the Charm ends, the transformation expands and substantially modifies the Princess' Holy Shield; creating the Sheltering Hand Tilt: When anyone affected takes damage the Princess automatically protects them by spending Wisps at her usual rate for Holy Shield. If she does not have sufficient Wisps she drains the land around her, for each Wisp drained roll one die and create a point of Taint per Success. 
    

    \emph{Exceptional Success:} The Princess touches the determination that has sustained the Queen of Tears in her mission. She also gains the Blessing Condition. The affected trait is Inner Strength rolls and the increase is 2. The Blessing ends when the Sheltering Hand Tilt does so.\end{myindentpar}

\noindent \textbf{Drawback:} The Queen of Tears perpetually mourns for the lost Kingdom, and the sacrifices that must be made to sustain its remnant; her avatar bears the burden of her grief, and so also gains the Queen's Grief Tilt. At the end of every turn where she protected someone with this Charm roll Resolve + Composure: 

   \begin{myindentpar}{10pt}   \emph{Dramatic Failure:} The princess collapses into a hysterical mess for the scene, and suffers all accumulated Depression.
    
    \emph{Failure:} The Princess takes a -1 penalty to all future Resolve + Composure rolls to maintain Sheltered by Her Hand for this scene. In addition she adds one day of Depression to her accumulated total. 

    \emph{Success:} The Princess takes a -1 penalty to all future Resolve + Composure rolls to maintain Sheltered by Her Hand for this scene.

    \emph{Exceptional Success:} Nothing happens. \end{myindentpar}

When the Charm ends the Princess mediately falls into Depression for the number of days accumulated during this Charm. 
    
Until the Charm ends, the Princess gains the Invocation Lock condition keyed to Lacrima.

\subsection*{Connect}
Connect Charms trace and use the connections between people, or make and break such connections. Only Graces have affinity for them.

\subsubsection*{Fair Welcome (Connect \textbullet)}

\noindent Action: Instant, Manipulation + Socialize

\noindent Cost: 1 Wisp

\noindent Duration: 1 day or 1 week \\

\noindent The Princess can strike up a conversation with nearly anyone she meets, and learn many things from an hour of polite talk. On using this Charm the Princess gains the Blessing Condition. The affected trait is her Contact merit and the Blessing adds one dot. In all respects she follows the normal rules for interacting with Contacts.

The Blessing lasts for a day, or a week with an exceptional success.

\subsubsection*{Illuminatus (Connect \textbullet)}

\noindent Action: Permanent \\

When the Princess transforms, the secrets of the wealthy and powerful in her community cannot be hidden from her. She gets the 9-again quality on mundane Politics rolls within one of her specialities (fixed when she takes this Charm) and may apply an Invocation to those rolls.

\begin{myindentpar}{10pt}\textbf{Upgrade: Connected}

Stacks, up to 2

Other communities' inward lives become known to the Princess. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for mundane Politics rolls covered by any of the added specialities.

\textbf{Upgrade: Influential (Terra \textbullet\textbullet)}

Organizations shift their policies when the Princess drops a word in the right ear. She may spend 1 Wisp to reduce the number of successes she needs to convince a social group to move a Policy dot by her Terra. If this lowers the threshold to 0 successes, the Princess does not roll; the group changes its Policy after a scene or hour of conversation. If the group she is influencing is covered by an enhanced speciality, her extended action to persuade it also gains the 9-again quality, even if she isn't using her Politics Skill.\end{myindentpar}

\subsubsection*{The Stare (Connect \textbullet)}

\noindent Action: Permanent\\

\noindent To her opponents, the Princess’s eyes feel like the stare of a thousand predators, and the aura she exhudes is like a great beast stalking her prey. No wonder they become more... cooperative. She gets the 9-again quality on mundane Intimidation rolls within one of her specialities (fixed when she takes the Charm) and she may apply an Invocation to those rolls. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Versatile}

Stackable 2 times

The Princess makes herself more generally fearsome. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for rolls covered by any of the added specialities.\end{myindentpar}

\subsubsection*{Laying Down The Line (Connect \textbullet)}

\noindent Action: Instant, Resolve + Streetwise

\noindent Cost: 1 Wisp

\noindent Duration: One scene (Consecrated)\\

\noindent A Noble is a creature of divides; between Light and Dark, Transformed and mundane, Hope and despair. Drawing a line on the ground, she separates one area from another, and so becomes aware of anyone that crosses that line. Before this Charm can be used, the Noble must first make some kind of line or divide to empower, such as a chalk line drawn on tarmac, a rope thrown down, or even putting up a picket fence around a house. This is a mundane activity, unrelated to the actual use of the Charm, and these divides can be linear, or enclose an area. It can also empower pre-existing divides, such as a doorway, or a river. These divides must either measure no more than (Inner Light x 20) yards in any direction, or be in an area affected by the Consecrated Condition.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess's clumsy magic temporarily manages to scramble her memories. She gains the Lost Condition, she is no longer able to remember how place connects to place. 

    \emph{Failure:} The Charm fails to activate, with a slightly pathetic spluttering noise.

    \emph{Success:} The divide is empowered, gaining the Line in the Sand Condition. She nominates certain targets and instantly knows if they cross the line (and which line, if she has more than one active). The Princess can nominate everyone, a single individual, or she may nominate a social group by adding Commonality to her roll. By default, the duration one scene. If used on a single natural divide, such as a doorway or across a bridge, the duration is increased to one day. If used on Consecrated ground the duration is until the area is no longer Consecrated.

    \emph{Exceptional Success:} The magic flows easily, the divide feeling natural, and so the Princess is refunded the Wisp cost for the Charm.

    Suggested Modifiers: Naturally secure building (+ Safe Place). Exceptionally strong memories of love and safety, such as a childhood home or childhood holiday home (+5). Strong memories of love and safety, such as a long time friend's home (+3). The character does not have position of the owner of the land to do this (-2).

\textbf{Upgrade: Illuminated}

\noindent Cost: +1 Wisp

Reaching out, the Princess sketches the bounded area in her mind, painting the delineation in liquid light. She is not required to make a mundane divide, and so may encompass any area up to the limit as part of the activation Instant action, and the line may not be removed by the destruction of the mundane component. 

\textbf{Upgrade: Unnatural}

The Princess has additional options when deciding who the lines should target. She may now choose anyone Supernatural, Princesses and Sworn, or Creatures of the Darkness. For the purpose of this Charm \textquotedblleft supernatural\textquotedblright\, has a minimum threshold of a Minor Template such as Sworn.

\textbf{Upgrade: Sheltered (Lacrima \textbullet)}

The Princess has additional options when deciding who the lines should target. She may now choose the Court of Storms, including Princesses, Stormwracked and Goalenu. She does not need to add Commonality to her roll. 

\textbf{Upgrade: Righteous (Tempesta \textbullet)}

The Princess has additional options when deciding who the lines should target. She may now choose Creatures of the Dark or the Court of Tears, including Princesses, Ghost Princesses (if they are part of the Court of Tears) and Sworn. She does not need to add Commonality to her roll. 

\end{myindentpar}

\subsubsection*{First Impressions (Connect \textbullet)}

\noindent Action: Instant, Manipulation + Empathy

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

Surrounded with fresh faces and unfamiliar places, the Princes adorns herself in an radiant aura of trust. 

\begin{myindentpar}{10pt} \emph{Dramatic Failure:} The Charm works in reverse, making the Princess naive and awestruck by new people. She applies the Fresh Impression condition to herself, increasing her impressions of anyone she hasn't already formed an opinion about by one step. 

    \emph{Failure:} Nothing happens. 

    \emph{Success:} Until the Charm ends she automatically applies the Fresh Impressions Condition to anyone she interacts with for the first time as well as anyone who has spoken to the Princess before but has no opinion about her. Essentually, if the phrase \textquotedblleft first impressions \textquotedblright\, fits then the Charm functions. The Condition increases the target's impression by one step. 

    \emph{Exceptional Success:} The Princess also gains the Blessing Condition, she has a +1 to all social rolls with the affected people. 
    
    \textbf{Upgrade: Second Chances}

Instead of an all-emcompassing aura the Princess may instead focus this Charm on one single person, even one who has met the Princess before. The activation roll is Contested by the target's Composure + Supernatural Advantage. 

    \textbf{Upgrade: Introductions}
    
    The Princess may invoke First Impressions on someone other than herself. 

\end{myindentpar}

\subsubsection*{Open Heart (Connect \textbullet)}

\noindent Action: Permanent \\

\noindent When the Princess transforms, she radiates kindliness and trustworthiness; those she meets take her as a natural confidant. She may apply an Invocation to mundane Empathy rolls.

\begin{myindentpar}{10pt}\textbf{Upgrade: Curious}

The Princess draws secrets out of people, not by terrifying them but with a pleasant manner and an air of sympathy. She may use Empathy to interrogate people (see p. 81 of the core book) instead of Intimidation. All other rules for that task are the same; only the required Skill changes.

\textbf{Upgrade: Distant (Acqua \textbullet\textbullet)}

The Princess' knowledge of people allows her to predict their actions while they are absent. She may use Empathy to extrapolate what someone known to her is doing or has done while out of her sight, as an instant action. She takes an Intimacy penalty on this roll, and may apply Acqua to it. The Storyteller gives the Princess' player one clue to her target's behavior for each success.

\textbf{Upgrade: Startling (Aria \textbullet\textbullet)}

The Princess easily sees when people are on the edge of violence. She may use Empathy to read the emotions of all the people around her as an instant action, and may apply Aria to the roll; if she succeeds, and anyone present starts a fight, she adds her successes to her Initiative. The Princess can't do this after a fight starts - she needs a few moments of calm to look for signs.

\textbf{Upgrade: Deep (Terra \textbullet\textbullet)}

The Princess can read people's desires, hopes and fears as easily as most people can read faces. When she uses Empathy to understand a person, she may apply Terra and spend a Wisp to turn her successes on the roll into bonus dice for all Persuasion attempts on that person for the rest of the scene.\end{myindentpar}

\subsubsection*{Sweet Fragrance (Connect \textbullet, Legno \textbullet)}

\noindent Action: Instant and contested, Composure + Socialize

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene

The Princess releases a subtle scent into the air around her, that relaxes those who breathe it and inclines them to be friendly. She affects a circular area with a radius up to (Inner Light + Legno) yards, centred on
herself.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The scent the Princess releases is mildly offensive. She takes a -1 penalty on all Social rolls for the rest of the scene, or until she cleans herself with soap or magic.

    \emph{Failure:} The Princess releases no scent. 

    \emph{Success:} Anyone within (Inner Light + Legno) yards of the Princess who cannot match her activation Successes with a  Composure + Supernatural Tolerance roll gains the Trusting Condition. The Princess must roll to avoid gaining the Condition herself.

    \emph{Exceptional Success:} The Princess is immune to her own scent.\end{myindentpar}

\subsubsection*{The Naked City (Connect \textbullet)}

\noindent Action: Permanent \\

\noindent When the Princess transforms, she easily evades the nets and snares laid by the authorities, and those who live outside the law know her for a friend. She gets the 9-again quality on mundane Streetwise rolls within one of her specialities (chosen when she takes the Charm) and may apply an Invocation to such rolls.

\begin{myindentpar}{10pt}\textbf{Upgrade: Connected}

Stacks, up to 2

The Princess' knowledge of her city's underside grows broader. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for mundane Streetwise rolls covered by any of the added specialities.

\textbf{Upgrade: Seeking (Aria \textbullet\textbullet)}

If the Princess needs something that is a little hard to find, from a rare book to some stronger \textquotedblleft social lubricant\textquotedblright\,,a touch of magic leads her to the right dealer. When trying to acquire equipment or services, the Princess' Streetwise is treated as though it was Aria dots when measuring against Availability. 

\textbf{Upgrade: Listening (Aria \textbullet\textbullet)}

There are eight million stories in the naked city, and the Princess can hear them all. When listening to rumors in a city (using Streetwise to find information) she may spend 1 Wisp to reduce the number of successes she needs to learn what she wants to know by her Aria. If this lowers the threshold to or below 0 successes, the Princess hears exactly the right rumor in a single interval.\end{myindentpar}

\subsubsection*{Razzle Dazzle (Connect \textbullet)}

\noindent Action: Permanent \\

\noindent When the Princess transforms, she has a honeyed tongue; people readily listen to anything she chooses to say. She gets the 9-again quality on mundane Persuasion rolls within one of her specialities (fixed when she takes the Charm) and she may apply an Invocation to those rolls.

\begin{myindentpar}{10pt}\textbf{Upgrade: Versatile}

Stacks, up to 2

The range of the Princess' persuasive talents expands. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for rolls covered by any of the added specialities.

\textbf{Upgrade: Skeptical (Acqua \textbullet\textbullet)}

The Princess keeps her head when others try to confuse her. When someone is trying to confuse her (not any suberfuge counts) she may apply Acqua as a penalty to the perpetrator's roll.

\textbf{Upgrade: Blathering (Aria \textbullet\textbullet)}

The Princess can talk a mile a minute, and leave another person's mind spinning in bewilderment. When making a subterfuge roll she can spend a Wisp to inflict the Confused condition on her target(s) on an ordinary rather than an Exceptional Success; providing she rolled more successes than her target.

This is not affecting her target with magic, the Princess is just that good at confusing people. 

\textbf{Upgrade: Preaching (Fuoco \textbullet\textbullet)}

The Princess' words blaze with passion and can inflame the audience. When she attempts oratory she may spend 1 Wisp, if she does so every member of the audience who agrees with her takes the Inspired condition. If she already has the Inspiring Merit they take the Inspired Condition twice and so apply the benefit on two rolls. 

\textbf{Upgrade: Bargaining (Terra \textbullet\textbullet)}

The Princess perceives the natural flow of a negotiation, and steers ably past all obstacles to a deal. During an extended negotiation she may spend 1 Wisp when she opens the first Door, if she does so she will open a second Door as though she had rolled an Exceptional Successes (on an actual Exceptional Success she opens three Doors). If the Princess has four dots in Terra she may do so again when opens Doors for the second time. 

This is not affecting her target with magic, the Princess is just that good at cutting a deal. 

\textbf{Upgrade: Seductive (Specchio \textbullet\textbullet)}

Requires: Striking Looks

The Princess has a gift for flirtation, and for tempting people into indiscretion. At the start of a seduction attempt, she may reflexively spend 1 Wisp when she opens the first Door, if she does so she will open a second Door as though she had rolled an Exceptional Successes (on an actual Exceptional Success she opens three Doors). If the Princess has two dots in Striking Looks she may do so again when opens Doors for the second time. 

This is not affecting her target with magic, the Princess is just that good at flirting. \end{myindentpar}

\subsubsection*{Animal Magnetism (Connect \textbullet Legno \textbullet)}

\noindent Action: Permanent\\

\noindent The Princess becomes a friend to birds and beasts when she transforms; through a combination of smell, sound, or visual cues, some animals take her for one of their own. She gets the 9-again quality on mundane Animal Ken rolls within one of her specialities (fixed when she takes the Charm) and may apply an Invocation to those rolls.

\begin{myindentpar}{10pt}\textbf{Upgrade: Multispecies}

Stacks, up to 2 times.

The Princess grows attractive to more kinds of beasts. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for mundane Animal Ken rolls covered by any of the added specialities.

\textbf{Upgrade: Trusted (Legno \textbullet\textbullet)}

No matter how strange, exotic or frightened the animal, a Princess knows how to deal with it safely. She can reduce penalties to an Animal Ken roll by up to her dots in Legno. \end{myindentpar}

\subsubsection*{Mercury's Blessing (Connect \textbullet, Acqua \textbullet)}

\noindent Action: Instant, Intelligence + Expression

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent With a touch of the hand and a look in the eye, the Princess may converse with anyone in the world. She touches someone to activate the Charm. With an ordinary success, she acquires a basic understanding of the target's native language until the Charm ends. She gains the Blessing Condition, the affected trait is a dot in the multilingual merit applied to a single language the target knows. On an Exceptional Success the Princess gets the Language Merit instead. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Lasting}

\noindent Cost: +1 Wisp

\noindent Duration: 1 day

The Princess' magical fluency persists for a full day from the moment she gained it.

\textbf{Upgrade: Overflowing (Acqua \textbullet\textbullet)}

If a person speaks more than one language, the Princess can learn them all. The effects apply to one language for each success rolled, up to her Acqua.\end{myindentpar}

\subsubsection*{Better Together (Connect \textbullet\textbullet)}

\noindent Action: Instant, Manipulation + Socialise vs Composure + Supernatural Advantage

\noindent Cost: 1 Wisp

\noindent Duration: Until the condition is resolved \\

\noindent With deft fingers the Princess weaves two people together, using each as support for the other so that they may reach greater heights. The Princess may be one of the two people. The is contested by the higher dice pool of the targets, but if everyone consents the Charm is unopposed. 

\begin{myindentpar}{10pt}
    \emph{Dramatic Failure:} Both parties take the Fresh Impressions condition, setting their impressions one stage lower for a day. 
    
    \emph{Failure:} Nothing happens. 
    
    \emph{Success:} The charm takes effect, one or both of the targets, the Princess' choice, gain the Guided Condition connecting them to the other target.
    
    \emph{Exceptional Success:} In addition both parties take the Fresh Impressions condition, setting their impressions one stage higher for a day. 
\end{myindentpar}

\subsubsection*{Shared Interests (Connect \textbullet\textbullet)}

\noindent Action: Instant, Presence + Socialise 

\noindent Cost: 1 Wisp

\noindent Duration: One scene or one day \\

\noindent The Princess turns common knowledge and training into a bond among the people near her. The Princess may use this Charm on a person she can touch, when the target is in the company of at least four other people, and he and the others all have at least 2 dots in the same Skill. The Princess may not use the Charm on anyone already under its effects.

\begin{myindentpar}{10pt}
    \emph{Dramatic Failure:} The Princess becomes flustered and distracted when the target can see her. She takes the Nervous Condition, which resolves when she has left the target’s presence for at least one scene.
    
    \emph{Failure:} Nothing happens. 
    
    \emph{Success:} For the rest of the scene, the target has the benefits of the Hobbyist Clique Merit, related to the Skill he shares with the others who are present. The benefit
is limited to one Skill at a time; if more than one clique can be formed around the target for different Skills, the Princess chooses a Skill as she activates the Charm. The target needs the help of at least four clique members to get the benefit; the Charm does not end if the clique disperses, but it has no effect unless five members including the target are working together.
    
    \emph{Exceptional Success:} The Charm grants its benefits to the target until the next sunrise.
\end{myindentpar}

\subsubsection*{The Right Word (Connect \textbullet\textbullet)}

\noindent Action: Instant and contested

\noindent Dice pool: Manipulation + Persuasion vs. Composure + Supernatural Tolerance

\noindent Cost: 1 Wisp

\noindent Duration: instant\\

The Princess can read the hearts of those she meets, discovering what they most desire and what she can do to help them reach it. At the start of a social maneuver with a person, the Princess may activate this Charm.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:}  The Princess is led to believe the target has an Aspiration which is, in fact, repugnant to him. If she offers to help him achieve the spurious goal, add one Door to her social maneuver and lower the impression by one step.
 
\emph{Failure:} The Princess learns nothing of her target’s desires. The social maneuver proceeds normally.

\emph{Success:} The Princess learns one of the target’s current Aspirations in the course of her first attempt to open a Door. She may appeal to that Aspiration after the first attempt resolves, whether it succeeds or fails. If the target has a Dream, or any other trait similar to Aspirations, the Princess can discover it instead of an Aspiration.

\emph{Exceptional Success:} The Princess learns two of the target’s Aspirations (or Vocations, or similar traits) as she tries to open her first Door.

\textbf{Upgrade: Convincing}

\noindent Cost: +1 Wisp

The Princess knows just how to appeal to her target’s wishes. When she appeals to an Aspiration revealed by the Charm during the social maneuver she used it, she opens two Doors instead of one.
\end{myindentpar}

\subsubsection*{Beast Speaker (Connect \textbullet\textbullet, Legno \textbullet)}

\noindent Action: Instant, Intelligence + Animal Ken\\

\noindent Cost: 1 Wisp\\

\noindent Duration: 1 scene \\

\noindent Beast Speaker allows a Princess to speak to any animal, and understand its replies.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The targeted animal, and any other animal of the same species, turns hostile and will attack the Princess if it can until the Charm ends.

    \emph{Failure:} The animal does not understand the Princess, and behaves as it normally would.

    \emph{Success:} The Princess acquires the Blessing Condition, the affected trait is the Language Merit, applied to the species of animal targeted. 

    \emph{Exceptional Success:} The Princess acquires a second Blessing Condition. The trait is social rolls with any member of the species targeted and the bonus is +2 dice. \end{myindentpar}
    
\subsubsection*{You Didn't Earn My Love (Connect \textbullet\textbullet, Specchio \textbullet\textbullet\textbullet)}

\noindent Requires: Razzle Dazzle, Seductive

\noindent Action: Reflexive, Manipulation + Persuasion vs Composure + supernatural advantage

\noindent Cost: 1 Wisp \\

\noindent Duration: Specchio days \\

\noindent When the Princess attempts to seduce someone she may inflict the Suitor condition upon her target. The Princess chooses the token of affection that will grant willpower. The token must be related to romance with the Princess using this Charm, something along the lines of: Agreeing to go out on a date, a kiss, marriage. It cannot involve direct harm to oneself, not even something minor along the lines of \textquotedblleft get humiliated by me\textquotedblright. While she may refuse to give the winning kiss until her target does her a favour, the favour cannot be the goal itself.

\subsubsection*{You're Only in Trouble if you Get Caught (Connect \textbullet\textbullet, Aria \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Intelligence + Composure 

\noindent Cost: 1 Willpower

\noindent Duration: Indefinate \\

\noindent Sometimes, one must learn to lose, to give up, and, to put it bluntly, to run away. By using magic taught by the Queen of Thieves a Knave may escape from her past, and those who would use it to track her down with magic.

Each success on the activation roll reduces your Intimacy to a chosen subject by one degree per success. If this reduces the connection below Few Feelings, it breaks altogether. 

The effects last indefinitely, but the connection can be reformed if the Princess does not avoid contact with whoever she has left behind. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Partners in Crime (Aria \textbullet\textbullet\textbullet\textbullet)}

\noindent Cost: + 1 Wisp

You can use the Charm on another person you can speak to. The target must give their consent for such a thing to occur.

\textbf{Upgrade: Band of Thieves (Aria \textbullet\textbullet\textbullet\textbullet\textbullet)}

\noindent Requires: Partners in Crime

\noindent Cost: + 2 Wisps

You can use the Charm on a social group you can speak to, extracting yourself from a Commonalty group. If combined with Partners in Crime the Princess can extract multiple people at no additional cost.\end{myindentpar}

\subsubsection*{Meet Cute (Connect \textbullet\textbullet, Specchio \textbullet\textbullet\textbullet)}

\noindent Action: Instant and contested, Presence + Expression vs Composure + Supernatural Advantage; Requires one minute of performing.

\noindent Cost: 2 Wisps 

\noindent Duration: One scene\\

\noindent The True Heir the pinnacle of grace and beauty, and what better accessory to go with an elegant crown than a matching handsome prince? 

First, The Princess describes a person by describing a set of criteria, these can refer to traits on the character sheet, \textquotedblleft he must have five dots of Resources \textquotedblright\, or to something less defined \textquotedblleft he must have perfect teeth\textquotedblright. She may define at most one criteria for every dot she has in Specchio. Then she charges herself up with magic. When she first sees somebody who fits the criteria roll their Composure + Supernatural Advantage against the Princess' original success.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure by the Princess:} The madness of Specchio fills the Princess's mind with cracks. She gains the Yandere Condition, they are unaffected.

\emph{The Princess scores no successes or looses the roll:} Nothing happens.

\emph{The Princess wins the roll:} The Princess gains the First Impressions condition, and through confidence and Specchio she reflects her \textquotedblleft love\textquotedblright\, onto her target. Both take the First Impressions condition, setting each other to perfect impressions. 

\textbf{Upgrade: Girls out Hunting}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group whose members can see her, applying the Commonalty modifier. Each member of the group may choose their own criteria. 

\end{myindentpar}

\subsubsection*{Cherish (Connect \textbullet\textbullet\textbullet)}

\noindent Action: Instant and resisted, Wits + Empathy - target's Composure

\noindent Cost: 1 Wisp

\noindent Duration: Inner Light days \\

\noindent A person she's met, a place she's been \textendash\, these fix themselves in a Princess' heart. The Princess uses this Charm on a target within sight, to grant herself temporary Intimacy to it.

   \begin{myindentpar}{10pt} \emph{Dramatic Failure:} The Princess cannot use any Charm through an Intimate connection to the target until she sees it again.
   
    \emph{Failure:} The Charm has no effect.
	
    \emph{Success:} The Princess and her target gain the Entwined condition, linked to each other. For every Success the Link Strength is one step stronger than her natural Intimacy, to a minimum of Love. The Condition ends when a Charm is invoked across the new connection. 
	
    \emph{Exceptional Success:} The connection lasts for several Charms, though it frays each time the Princess uses it. The first Charm she uses has an Intimacy modifier of 0, the second has one of -2, the third -4, and so forth until she returns to the original level of Intimacy.\end{myindentpar}

\noindent Note that the Intimacy made by Cherish works both ways; if the target has a power that exploits Intimacy, he can send that power through the connection the Princess made.

\begin{myindentpar}{10pt}\textbf{Upgrade: Durable}

\noindent Cost: +1 Wisp

\noindent Using Charms no longer ends the Entwined condition, it lasts for Inner Light days and no longer. \end{myindentpar}

\subsubsection*{Leading the Way (Connect \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Presence + Persuasion

\noindent Cost: 1 Wisp

\noindent Duration: Until the condition is resolved \\

\noindent We put a lot of ourselves into our leaders. We trust them, we follow them, we even base parts of our identity on which leader we follow. A Princesses can work with the connections between people and their leaders, bringing herself closer to the people she serves. 

\begin{myindentpar}{10pt}
    \emph{Dramatic Failure:} The Princess shakes her confidence in her goals. Take the Self-Doubt Condition. 
    
    \emph{Failure:} Nothing happens. 
    
    \emph{Success or Exceptional Success:} Choose one Dream of Aspiration and mark it with the Guiding Light Condition. When you fulfil it everyone who helped you do so in the current Session takes a Beat, Princesses who help you fufil a Dream also gain a Luminous Beat. 
    
\end{myindentpar}

\subsubsection*{An Introduction (Connect \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Manipulation + Empathy

\noindent Cost: 2 Wisps

\noindent A Princess' true power comes from the lives she has touched, so sometimes it's important to touch the right person. The Princess activates this Charm to meet someone who is predisposed to like her. She may take penalties to the roll to narrow the search, specifying that the person she will meet has certain qualities. A quality represented as a trait (e.g. an Attribute, Skill or Merit) adds a penalty equal to the desired dots in the trait; a less quantifiable trait adds a -1 penalty. She may not use the Charm while she is affected by a previous activation.

\begin{myindentpar}{10pt}
    \emph{Dramatic Failure:} The Princess learns how to find someone who satisfies all her requirements; however, if she meets him, the storyteller should inflict some hardship upon her.
    
    \emph{Failure:} Nothing happens. 
    
    \emph{Success:} The Princess learns how to find someone who satisfies all her requirements. If she follows the indicated plan (the Storyteller must provide a plan) she meets the person in question.
    
    \emph{Exceptional Success:} In addition, she will meet the person in favorable circumstances and create an initial impression one step higher than she naturally would have.
    
    \textbf{Upgrade: Proxy}
    
    Cost: +1 Wisp 
    
    The Princess can act as an intermediary. She may use the Charm on a person she can touch, though not on anyone under its effects. The Charm affects the target exactly as it would if he activated it himself, except that the Princess learns the plan and must tell it to the target.    
\end{myindentpar}

\subsubsection*{Whispers from Afar (Connect \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Wits + Socialize, modified by Intimacy

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene \\

\noindent What need is there of speech between you and those you love? A Princess uses this Charm to communicate with another person; if he is not present, the Intimacy modifier applies. If the target has Wisps, he can share the activation cost; both the Princess and the target spend 1 Wisp, and the target does so reflexively. \\


\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} For the duration, the Princess imagines the voice of her target is speaking to her; what it says is what she generally expects him to say, but it chooses the most distracting moments to speak. She takes a -2 penalty on all Wits-based rolls.
    
	\emph{Failure:} The Charm has no effect.
    
	\emph{Success:} The Princess can speak directly to the mind of her target, without using her voice, and the target can reply the same way. The Charm conveys only sounds that the Princess and the target could actually speak; so, for example, if one thinks in a language the other doesn't know, he hears the words but cannot understand them. On the other hand, anything said is heard as clearly as if the two of them stood together in a quiet room. The first time someone is the target of this Charm, he must roll Resolve + Composure to learn how to speak through the link (and, possibly, to persuade himself that he isn't imagining the voice in his head.)
    
	\emph{Exceptional Success:} In addition, by concentrating the Princess and the target can share a memory. The one who has the memory makes a memory roll (see p. 44 of the nWoD core book) to recall it; whatever she recalls passes over the link, and the other makes a memory roll to retain the information. This takes an instant action from both characters.

\textbf{Upgrade: Party}

\noindent Cost: +1 Wisp

The Princess adds the Commonality modifier to create a channel of voiceless speech among several people. She can speak to any or all of the targets' minds, and they can speak to her and each other in the same way. 

\textbf{Upgrade: Borrowing (Aria \textbullet\textbullet)}

The Charm's link between minds carries sensations. Anyone in the link can make a Perception roll at a -2 penalty to borrow the senses of another person in the link for a brief moment, seeing what the other sees and hearing what she hears in that moment.\end{myindentpar}

\subsubsection*{Ivory Gate (Connect \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Manipulation + Socialize

\noindent Cost: 2 Wisps

\noindent Duration: 1 night \\

\noindent The Princess binds her mind to another; when they next fall asleep they will share their dreams. The Charm grants both the gift of lucid dreaming for the night and clear memories the morning after. To open an Ivory Gate a Princess needs permission from the target, and the pair must sleep close enough to touch.

A lesser known use of this Charm is that it interacts with Crawlspaces. Normally the only way into another person's Crawlspace is to travel through the Dreamlands, but while two people are connected by an Invocation of Ivory Gate they may see the entrance to each others Crawlspace. Only the owner of the Crwalspace may unlock it, but they may lead others. Every traveller must pay 1 Wisp or one Willpower.  

The other, even more obscure, use of Ivory Gates is to invoke it on oneself. This seems to be a waste of good Wisps, but while she is within her own Crawlspace and under the effects of a self-applied Invocation of this Charm, she will be able to navigate from her Crawlspace into a regular dream (and yes, she can bring others too but they don't benefit from lucidity or clear memories unless Ivory Gate is invoked upon them). An expensive but effective cure for insomnia or a fun night of lucid dreaming. 

\begin{myindentpar}{10pt} \textbf{Upgrade: Distant}

\noindent Modify the roll by Intimacy

The Princess can enter a dream from any distance. She still requires permission, but a simple phonecall or arangeing in advance is sufficient. 

\textbf{Upgrade: Dream of Me (Specchio \textbullet\textbullet)}

The Princess no longer needs permission to enter another's dreams, and can even open an Ivory Gate without giving the gift of lucid dreaming to the other party. This Upgrade can also be used to invade somebody's dream from the Dreamlands and even allow a full invasion of another person's dreamscape (see Amanojaku in Chapter four for more details on how to access a person's dream from the Dreamlands, and how to invade a dreamscape), doing so requires that the Princess navigates through the Crawlspace into the target's dream. They may not detour or use the Crawlspace in any way except as a path into the Dreams, this Charm simply doesn’t have the power. 

\end{myindentpar}

\subsubsection*{Up in Smoke (Connect \textbullet\textbullet\textbullet, Aria \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Dexterity + Larceny, modified by Intimacy

\noindent Cost: 1 Wisp

\noindent Duration: instant \\

\noindent The Princess summons and banishs objects in puffs of coloured smoke. She can move an object of Size up to her Aria between her current location and a place she knows of; the Intimacy modifier applies to the other place, not to the object, so she can't summon an object that's been moved since she last saw it. Also, to send an object somewhere the Princess has to be carrying it, and when she takes an object it ends up in her hands; the Charm can't be used on anything the Princess can't lift.

\begin{myindentpar}{10pt} \textbf{Upgrade: Shuffled}

\noindent Cost: +1 Wisp

The Princess can take an object from one distant place and send it to another with one activation. Apply the worse of the Intimacy modifiers for the two locations.

\textbf{Upgrade: Treasured (Aria \textbullet\textbullet\textbullet\textbullet)}

The Princess can summon an object to herself, no matter where it has been moved; apply the Intimacy modifier for the object itself. She still cannot send objects to another place without a connection to the place.\end{myindentpar} 

\subsubsection*{Hymn to Orpheus (Connect \textbullet\textbullet\textbullet, Legno \textbullet\textbullet)}

\noindent Action: Instant and resisted, Presence + Expression - targets' Composure

\noindent Cost: 2 Wisps

\noindent Duration: concentration \\

In the myths, the songs of Orpheus were so beautiful that all the natural world came to hear them. The Princess can, in a small way, emulate him. When she has a natural animal within sight, she sings or plays music pleasing to it, and all the animals of the same species who hear the song gather together to listen. The Charm ensures that the music can be heard anywhere within 100 times her successes in yards; natural acoustics may carry the song further, at the Storyteller's discretion. (Note that while only animals of the same kind as the target are certain to come, anyone and anything with ears can follow the music if they like.) Once they arrive, the summoned animals will stand or lie near the Princess, quietly listening, as long as she performs; when she stops, the Charm ends and the beasts revert to their normal behavior in the following turn.

\begin{myindentpar}{10pt}\textbf{Upgrade: Calling (Legno  \textbullet\textbullet\textbullet)}

The Princess may perform for an animal that is not within sight, provided she knows it well. Apply the Intimacy modifier to the chosen target; animals of that species will come to hear her.\end{myindentpar}

\subsubsection*{Ferryman's Shroud (Connect \textbullet\textbullet\textbullet, Lacrima \textbullet)}

\noindent Action: Instant, Composure + Athletics

\noindent Cost: 2 Wisps, Compromise at Belief 7+ with no modifer

\noindent Duration: instant \\

\noindent The Queen of Tears has deemed that all Princesses are entitled to the freedom of her city. To use this Charm, the Princess must be in complete darkness; light bright enough to see by, from any source, makes the Charm fail. When she activates it, the darkness she stands in thickens to an utter negation of light for an instant; then the ground vanishes and she falls, splashing into the black salt lake of Alhambra. The Charm is generally considerate enough to drop her near a shore, where she can reach dry land in a single turn. It doesn't, however, have to leave her in a specific place within the city; with a single success she may have to walk an hour or two to reach the district she wanted, and an exceptional success brings her straight to the nearest shore. The Charm will not take anyone back from Alhambra \textendash\, the Queen of Tears does not wish anyone to leave her who has not proven their fidelity to the true Kingdom.

As an incidental benefit, those who learn this Charm can light lamps in Alhambra as its citizens do... it's not clear why. 

\begin{myindentpar}{10pt} \textbf{Upgrade: Driven}

\noindent Cost: +1 Wisp/every 5 points of Size above 5

The Princess can drive a vehicle into Alhambra, carrying along all its contents. She takes a penalty on the activation roll of -2 for 5 points of the vehicle's Size exceeding 5; that is, a Size 10 vehicle takes a -2 penalty, a Size 15 vehicle takes -4, and so on. As with the basic effect, the vehicle must be in darkness to travel, and will arrive over water; most Hopeful using this Charm travel in boats.

If she rolls a dramatic failure, the Princess cannot use the Charm for one full day.

\textbf{Upgrade: Returning (Lacrima \textbullet\textbullet\textbullet)}

The Princess may use the Charm to travel from Alhambra to a place she knows well; apply the Intimacy modifier for the destination. As with the basic Charm, the upgrade only works in complete darkness (and in Alhambra that carries risk; see the rules in that section.) On the other hand, activating the Charm to leave Alhambra is not a sin against Belief at any level.

The followers of Tears only teach this Charm to people who have proven their loyalty to Alhambra, but nothing other than the Lacrima perquisite and the risk of retaliation prevents anyone else from learning the Charm.\end{myindentpar}

\subsubsection*{Mirror Walk (Connect \textbullet\textbullet\textbullet\textbullet, Specchio \textbullet\textbullet)}

\noindent Action: Instant, Dexterity + Athletics, modified by Intimacy

\noindent Cost: 3 Wisps

\noindent Duration: Instant \\

A simple trick but a very useful one. The Princess targets two mirrors before stepping into one and out the other. Both mirrors must be large enough for her to fit through. Intimacy is measured to place the Princess wishes to arrive at, if it has no Mirrors large enough to squeeze out of the Charm automatically fails and the Princess knows why. If it has more than one suitable mirror than the Princess can choose to rive at any mirror she knows about.

The Charm cannot cross between realms. This may not be used to gain either egress or entrance to Alhambra, nor may it be used to exit or leave the hisil of the shapeshifters, the twisted thorn-world of the fae-folk, or any other such hidden place. However, should a Princess find herself in any of these alternate worlds, it may be used for transit within them if such a thing is possible within the alien dimension.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess enters the mirror, but gets lost. She rolls Wits + Composure each turn after using the Charm; when she succeeds, she emerges from the mirror she left. If the mirror is shatters in the interim she emerges somewhere nearby. 
    
	\emph{Failure:} Nothing happens.
    
	\emph{Success:} The Princess transports herself to the target mirror.
    
	\emph{Exceptional Success:} When the Princess emerges, she may immediately move up to her Speed, even if she had to move to reach the mirror she left.

\textbf{Upgrade: Leading}

\noindent Cost: +1 Wisp per additional person

With this Upgrade the Princess can now lead others through mirrors. Each extra person or 5 Size points of equipment beyond what she can carry costs an additional Wisp.

\textbf{Upgrade: Seeking (Specchio \textbullet\textbullet\textbullet)}

With this Upgrade the Princess can use her Intimacy modifier to a person instead of a place. She will arrive at the nearest appropriate mirror, assuming their is one in an area about the size of a modest family home. 

If she prefers the Princess can also use her Intimacy modifier to a physical mirror, which can come in handy if you can get your bedroom mirror posted somewhere useful (you can reach through the mirror to remove obstructions like packaging, just be careful not to damage a mirror while you are half way through.) 

\textbf{Upgrade: Writ of Passage}

The Princess learns how to combine her magical mirrors with complementary magic to travel beyond the world. If she knows a Charm, Edict or Privilege that allows access to another world, or she works with someone who does, then she may use Mirror Walk and travel to a mirror in that world, Intimacy permitting. Doing so requires that the activation cost of the other power be paid in full. She may also use Writ of Passage to return from other worlds \textendash though some worlds are infamous for being easier to enter than to escape. 

The ability Enter Darkness, known to all creatures of the Darkness can be used to walk to a Mirror in the Dark World. Ferryman's Shroud cannot be used to enter Alhambra, the city's defences are strict about what may enter. Realms without physical substance, such as the Dreamlands, are never valid destinations for Mirror Walk.

\end{myindentpar}

\subsubsection*{Charms of Entwined Destiny (Connect \textbullet\textbullet\textbullet\textbullet, Invocation \textbullet\textbullet\textbullet)}

\noindent Action: Extended, Manipulation + Empathy (30 minutes/roll, threshold = Princess' Willpower), modified by Intimacy

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: 1 month \\

\noindent In a lengthy ceremony, invoking all she knows of him, the Princess weaves the thread of her fate into another's, becoming an exemplar in his life of one of the Queens. Each Queen teaches a different version of this Charm, with her favored Invocation as a prerequisite; these versions must be learned as separate Charms.

Unlike natural Entwined Destinies there is no guarantee that the people involved are suited for new connection with eachother. Even if the target actively resists the destiny selfish or incompetent uses of this Charm can be seriously unethical, harmful and just all round messy. 

       \begin{myindentpar}{10pt}  \emph{Dramatic Failure:} The Princess cannot use the Charm on the target for 1 month, and suffers a -2 penalty to all Social rolls involving him during that period.

        \emph{Failure:} The Princess makes no progress. If she does not reach the threshold, she cannot use the Charm on the target again for 1 week.

        \emph{Success:} The Princess makes progress. When she reaches the threshold, the target gains the Blessing Condition. The Blessing creates the Entwined Destiny Merit, with the appropraite relationship and the target of the Princess' choice. 

        \emph{Exceptional Success:} The Princess makes great progress tying her destiny to the target's.\end{myindentpar}

The five versions of the Charm each confer a different form of Entwined Destiny:
\begin{itemize}
\item    Better Living Through Education (Acqua) - Mentor. The Princess gains Willpower when she has taught the target something important, and takes penalties if she passes up an opportunity to educate.

\item    Manic Pixie Dust (Aria) - Gadfly. The Princess gains Willpower when she exposes the target to unusual situations (for him) or alters the pattern of his life in a benign fashion, and takes penalties if she ignores a chance to do so. Doing the target permanent or serious harm does not fall under the Destiny.

\item    Red String of Fate (Fouco) - Lover. The Princess gains Willpower when she has furthered the target's love for her, and takes penalties if she misses a chance to do so. The love in question need not be erotic or marital, but it must involve mutual affection and trust.

\item    Under Ursa's Star (Legno) - Guardian. The Princess gains Willpower when she rescues the target from harm, and takes penalties if he is harmed when she is present.

\item    Great Expectations (Terra) - Sponsor. The Princess gains Willpower when her target's social standing improves, and takes penaltes if she lets a chance to help him rise go by. 
 \end{itemize}

\begin{myindentpar}{10pt}\textbf{Upgrade: Proxy (Invocation \textbullet\textbullet\textbullet\textbullet)}

The Princess can weave the thread of another person's life. The threshold for doing so is the Willpower of the person being given an Entwined Destiny, and the Intimacy modifier is either the Princess' connection to that person, or to the Destiny's subject, whichever is worse. If either person being given a Destiny is not willing to accept the role the Charm gives him, the Princess suffers the effects of a dramatic failure towards him.

\textbf{Upgrade: Mutual (Fouco \textbullet\textbullet\textbullet\textbullet)}
\noindent Requires Red String of Fate

\noindent Cost: +1 Willpower

When the Princess casts Red String of Fate both herself and her beloved gain an Entwined Destiny of lovers to each other. The two destinies are the natural compliment such as motherly love to daughterly love, or romantic love to romantic love. If the target does not give informed consent the Princess suffers a Dramatic Failure.

\textbf{Upgrade: Taut}

\noindent Cost: +1 Wisp

The thread that ties the Princess to her target pulls them together. The Princess and her target gain the Entwined condition. The strenght of the link is equivalent to an Intimate connection of Love, regardless of the connection they had before. When the Charm ends their Intimacy returns to it's natural level.
\end{myindentpar}


\subsubsection*{The Old Allegiance (Connect \textbullet\textbullet\textbullet\textbullet, Lacrima \textbullet\textbullet\textbullet)}

\noindent Action: Extended, Presence + Intimidation (30 minutes/roll, threshold = target's Willpower), modified by Sympathy

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: 1 month\\

\noindent It is right and proper, the Last Empress teaches, for the Nobility to reward those who serve the Light, and punish those who refuse to serve. In a lengthy ceremony, invoking all she knows of him, the Princess weaves the thread of another person's fate, calling him to assist her in her labors.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess cannot use the Charm on the target for 1 month, and suffers a -2 penalty to all Social rolls involving him during that period.

\emph{Failure:} The Princess makes no progress. If she does not reach the threshold, she cannot use the Charm on the target again for 1 week.

\emph{Success:} The Princess makes progress. When she reaches the threshold, the target's fate makes him a loyal servant of an organisation of the Princess' choice, until the Charm ends. The target gains Willpower when his actions serve the organisation's goals, and suffers penalties when he flouts them, or ignores them to serve another goal. Most Ravens use this Charm to instill loyalty to Alhambra. 

\emph{Exceptional Success:} The Princess makes great progress weaving the target's destiny.\end{myindentpar}

\noindent Unlike the Radiant Queens' Charms of Entwined Destiny, it is perfectly possible to use The Old Allegiance on an unwilling target. It is however a Belief compromise to do so, the modifier is at -3 (note that this isn't Lacrima's Drawback, it's just very unethical). Further degeneration checks may be called for if the Princess takes advantage of people she has woven a destiny for. As a general rule, it doesn't count as consent if they're only saying it as a result of an artificial destiny.

\begin{myindentpar}{10pt}\textbf{Upgrade: Collective (Lacrima \textbullet\textbullet\textbullet\textbullet)}

Cost: +1 Willpower

The Princess may bind all of a social group to her goals at once. When she reaches the threshold, all the members of the target group who see her are affected. The Charm is modified by Commonalty of the target group, instead of by Sympathy.\end{myindentpar}

\subsubsection*{Ultimate Fidelity (Connect \textbullet\textbullet\textbullet\textbullet, Tempesta \textbullet\textbullet\textbullet)}

\noindent Action: Extended, Resolve + Composure (1 minute/roll, threshold = 11 - Belief)

\noindent Cost: 1 Willpower dot

\noindent Duration: indefinite \\

\noindent The original Sworn Guard and the One-Who-Became-Storms swore this oath when they stood before the gates of the last city of the Kingdom, alone against the hordes of the Darkness. And they retain it. The Alhambrans know nothing of it; why would those treacherous curs know anything about loyalty or devotion? This was an oath of the Army of the Kingdom, not the soft weaklings who betrayed it from within. 

When using the Charm, the Princess declares a Cause. This may be anything that can be described in a sentence or so, consisting of an end-goal that is important to her. For example, \textquotedblleft Kill the six-fingered man who killed my father\textquotedblright\, is a valid target, while \textquotedblright Buy some milk from the shops \textquotedblright\, is almost certainly not. The Princess repeats these words over and over again, drumming them until they become all-consuming. The Charm is complete when the scars blossom across her chest, spelling out the Cause for all who would see. Whenever the Princess advances the Cause; finding a list of men with six fingers, finding which one he is, finding where he lives, watching his routines, breaking into his house, she gains one Willpower. At most one Willpower per scene. 

In addition, the Princess cannot be dissuaded; she doubles her appropriate Resistance Attribute against any attempts, whether mundane or supernatural, to prevent her from fulfilling the Cause. This covers things like torture, which would double Stamina, just as much as Composure might be used against magical mind-control or mundane persuasions. However, the Cause consumes those who have willingly sworn it. When faced with a choice between advancing or fulfilling the Cause, or taking another action, the Princess rolls Resolve + Composure. If she succeeds , she may perform the other action; otherwise she must continue with the Cause, and ignore the other situation, even if it would seem to be more important to an objective observer. 

Once the Cause has been accomplished, the Princess regains the Willpower dot lost when swearing to it. If it becomes impossible to attain the Cause for any reason (say, the six-fingered man dies before they can get their revenge), not only does she not regain the Willpower dot, she must roll Resolve + Composure, with each success inflicting one point of resistant aggravated damage, as her soul seeks redemption in coruscating flames that erupt from her mouth and burn at the tongue that swore an oath it could not uphold. 

\begin{myindentpar}{10pt}Upgrade: Proxy (Tempesta 4)

\noindent Cost: 2 Wisps from you, 1 Willpower dot from the target

The Princess may use the Charm to seal another person to a Cause they willingly swore to. The target is affected as if he had cast it himself.\end{myindentpar}

\subsubsection*{Standing on a Pedestal (Connect \textbullet\textbullet\textbullet\textbullet, Specchio \textbullet\textbullet\textbullet)}

\noindent Action: Extended, Presence + Persuasion (30 minutes/roll, threshold = target's Willpower), modified by Intimacy

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: 1 month \\

\noindent In a lengthy ceremony, invoking all she knows of him, the Princess weaves the thread of another person's fate into hers, giving him opportunities to prove himself worthy of her.

\begin{myindentpar}{10pt}        \emph{Dramatic Failure:} The Princess gains the Yandere Condition focused on the target.

        \emph{Failure:} The Princess makes no progress. If she does not reach the threshold, she cannot use the Charm on the target again for 1 week.

        \emph{Success:} The Princess makes progress. the target gains the Blessing Condition. The affected trait is the Entwined Destiny Merit.

        \emph{Exceptional Success:} The Princess makes great progress tying her destiny to the target's.\end{myindentpar}

The target's Entwined Destiny makes him a seeker for the Princess' approval; she can choose what kind of favor he is destined to seek. He may be a romantic suitor, and fulfil the destiny when he earns a sign of her affections. He may seek her social favor, and fulfil the destiny when she compliments him on his apparel, or invites him to a party. He may even seek her intellectual favor, and fulfil the destiny when she publicly approves of an idea he had. The general rule is that the target gains Willpower when the Princess chooses to bestow a sign of her approval upon him, and suffers penalties when he refuses an opportunity to seek the Princess' favor. He does not suffer penalties when he makes a genuine attempt to win her favour, regardless of how the Princess reacts.

Unlike the Radiant Queens' Charms of Entwined Destiny, it is perfectly possible to use Standing on a Pedestal on an unwilling target. It is however a Belief 4 compromise to do so (it is not a compromise to use it against targets who give informed consent). Further degeneration checks may be called for if the Princess takes advantage of people she has woven a destiny for. As a general rule, it doesn't count as consent if they're only saying it as a result of an artificial destiny.

\begin{myindentpar}{10pt} \textbf{Upgrade: Collective (Specchio \textbullet\textbullet\textbullet\textbullet)}

\noindent Cost: +1 Willpower

The Princess may bind many favor-seekers to herself at once, if they are all present. The Charm is modified by Commonalty of the target group, which must include the Princess, instead of by Intimacy.

\textbf{Upgrade: Taut}

\noindent Cost: +1 Wisp

The thread that ties the Princess to her target pulls them together. The Princess and her target gain the Entwined condition. The strenght of the link is equivalent to an Intimate connection of Love, regardless of the connection they had before. When the Charm ends their Intimacy returns to it's natural level.

If the Princess applies Collective and Taut, she gains the Interwoven condition becomes a member of the target group for the purposes of Commonalty Charms, instead of improving her Intimacy with any of them. The link strength is whatever the group members have with eachother.\end{myindentpar}


\subsubsection*{Becoming the Fulcrum (Connect \textbullet\textbullet\textbullet\textbullet\textbullet, Aria \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Wits + Investigation

\noindent Cost: 3 Wisps, 1 Willpower

\noindent Duration: 1 scene \\

\noindent With a gust of air the Princess' eyes see open to strange sights. As Spades' avatar she see how everything fits together and how those connections can be exploited with the slightest touch to make great change. She gains the Living Fulcrum Condition. The Princess may make mundane instant actions (they must use a Finesse Attribute) and record the Successes. At any time she may reflexively apply the recorded successes as a bonus or penalty to any roll for someone she can see - the sticky cake she threw onto the ceiling falls of and lands on the Brat just as she was starting to brag. 

The Princess may store a one roll per activation success and she may modify any number of rolls per turn, but she may only apply one modifier to any given roll. 

While the Princess wears the mantle of Spades she is permanently surrounded by gusts of wind. It smells of exotic lands and is as elegant and chaotic as the Queen herself. The Princess also gains the Invocation Lock Condition keyed to Aria.

\subsection*{Fight}
The Fight Charms enhance a Princess' ability to fight. Only Champions have affinity for them.

\subsubsection*{Empty Hands (Fight \textbullet)}

\noindent Action: Permanent \\

\noindent Many of the Hopeful have weapons in their Regalia, but some prefer to master control over the ability to inflict harm. She may apply an Invocation to rolls to start grappling, to her manuevers within a grapple, and to rolls to touch an opponent without hurting him.

\begin{myindentpar}{10pt}\textbf{Upgrade: Crushing}

While grappling, the Princess delivers immense force in her grasp. She may do either lethal or bashing damage to her opponent, once she has a hold on him.

\textbf{Upgrade: Grasping}

Stacks, up to 3

Whenever the Princess may apply an Invocation because of the Charm, she always adds a +1 equipment bonus for each time she takes this upgrade.

\textbf{Upgrade: Penetrating (Acqua \textbullet\textbullet)}

The Princess knows how to put opponents out of action quickly. When she applies Acqua to a grappling roll, and does damage to her opponent, she rolls dice equal to the damage done. If she gets any successes, her opponent must roll his Stamina; if he fails this roll, he is frozen for turns equal to the damage done.

\textbf{Upgrade: Disarming (Aria \textbullet\textbullet)}

While grappling, the Princess can manuever objects on her person or her opponent's with startling speed. When she applies Aria, she draws and attacks with a weapon on her person with a single roll; if her opponent holds a weapon, she may take it from him and attack with a single roll, or take it and throw it away, or pocket it.

\textbf{Upgrade: Blistering (Fuoco \textbullet\textbullet)}

During a grapple, the Princess' skin and clothes grow hot to the touch. In each turn that she applies Fuoco, her opponent automatically takes 1 bashing damage, in addition to any results of manuevers that turn.

\textbf{Upgrade: Entrancing (Legno \textbullet\textbullet)}

The Princess' opponents, if once they touch her, find it strangely hard to do anything that would really injure her. During a grapple, in any turn the Princess applies Legno, any roll her opponent makes that would damage her, either barehanded or with a weapon, is penalized by her Legno.

\textbf{Upgrade: Unbroken (Terra \textbullet\textbullet)}

The Princess stands unmoved, and her hold is almost impossible to escape. During a grapple, in any turn that she applies Terra, any roll her opponent makes to break the grapple or to render her prone is penalized by her Terra.

\textbf{Upgrade: Draining (Lacrima \textbullet\textbullet)}

The Princess' mein unsettles anyone who comes too close. During a grapple, in any turn that she applies Lacrima, her opponent must roll Resolve + Composure. If he fails, he cannot do anything that turn but try to break the grapple, unless he spends 1 Willpower.\end{myindentpar}

\subsubsection*{Kensai (Fight \textbullet)}

\noindent Action: Permanent \\

\noindent A melee weapon becomes part of the Princess’ Regalia, manifesting her courage and belief. Initially the weapon's Damage is 1 but when she attacks the Princess may apply an Invocation to add Damage or additional dice to her pool, this stacks with any damage or bonus dice from Upgrades but in either case the maximum is 5. The damage can be either Bashing or Lethal and the Princess can swap between them with a Transformation action. The princess may not apply the same Invocation to both Damage and Accuracy in a single turn, she may apply two different Invocations to gain both benefits unless she is using an Invoked Upgrade. 

The Princess chooses either Brawl or Weaponry as the Skill for using her weapon when she learns the Charm. The weapon always has a Size between 1 and 4. For anyone but the Princess, the Initiative penalty and the minimum Strength needed to use the weapon equals 3 + the Princess' Inner Light. For the Princess herself, both are 0 \textendash\, as an extension of her will, the weapon obeys her desires as well as her own hands.

\begin{myindentpar}{10pt}\textbf{Upgrade: Accurate}

Stacks, up to 3

The Princess wields her weapon with supernatural skill. Each time the Princess takes this upgrade, she gains 1 bonus die when attacking with her weapon.

\textbf{Upgrade: Damaging}

Stacks, up to 3

Each time the Princess takes this upgrade, she adds 1 to her weapon’s Damage. 

\textbf{Upgrade: Durable}

The Princess' weapon becomes nearly impossible to break. Add her Inner Light to the weapon's Durability.

\textbf{Upgrade: Precise (Acqua \textbullet\textbullet)}

The Princess places her strokes with marvelous accuracy. If she applies Acqua, she may ignore up to her Acqua in penalties from aiming at a specified target (see pp. 203 in the GMC) on top of the Invocation bonus.

\textbf{Upgrade: Swift (Aria \textbullet\textbullet)}

The Princess strikes quick as a flash, her weapon seems to disappear and reappear inside her opponent's flesh. If the Princess applies Aria to an attack, she gains Armour Piercing equal to her weapon's Damage + Aria, however this significantly reduces her weapon's power reducing her weapon's damage to zero. She does gain one bonus die for any point of Armour Piercing above her opponents Armour rating. 

\textbf{Upgrade: Burning (Fuoco \textbullet\textbullet)}

The Princess' weapon erupts into flame. If she applies Fuoco to an attack, it gains the 9-again quality and if the target is as flammable as dry wood it will likely catch fire. 

\textbf{Upgrade: Clinging (Legno \textbullet\textbullet)}
The Princess' weapon wraps around her opponent's flesh, as tree roots burrow into the earth. She can apply an Invocation to boost Grappling rolls and benefits from any purchases of the Accuracy Upgrade. If her weapon uses the  the Weaponry skill, rather than Brawl, she uses that Skill to Grapple. If the Princess does damage in a grapple her weapon's Damage applies as normal.


\textbf{Upgrade: Knockout (Terra \textbullet\textbullet)}

Strikes with the Princess' weapon have the force of avalanches. If the Princess applies Terra to an attack, the attack gains the Stun quality: the target's Size is halved for the purpose of applying the Stunned Tilt (GMC 212)

\textbf{Upgrade: Draining (Lacrima \textbullet\textbullet)}

The Princess' weapon draws shadows to itself, unsettling anyone with the bad luck to touch it. If she applies Lacrima to an attack, and the target takes damage from the attack, he must roll Resolve + Composure, and loses 1 point of Willpower if he fails. Using this upgrade is a Compromise at Belief 6+ with a -1 modifer.

\textbf{Upgrade: Berserk (Tempesta \textbullet\textbullet)}

The Princess' weapon's blows come so furiously that they catch their targets by surprise. If she makes an all-out attack with the weapon and applies Tempesta to the attack, she doesn't get the normal +2 bonus; instead the target loses his Defense against the attack.\end{myindentpar}


\myframe{
 
 \textbf{Fighting Styles} \\
 
 Just because a Princess is firing rainbows from a cheerleading baton doesn’t mean she can't benefit from a few days training down at the firing range. Princesses can use fighting styles just like anyone else. 
 
  \vspace{4 mm}
  
 A Princess may pick one type of mundane melee weapon for Kensai, mundane ranged weapon for Levinbolt (including those which use Athletics), and one mundane defensive armament for Shining Shield. She may use her magical weapon for any fighting style where that mundane weapon is appropriate, even if this means she's using the Light Weapons style with an enormous hammer. The Princess may not use her weapon for any fighting styles that are inappropriate for her chosen mundane weapon.
 }


\subsubsection*{Levinbolt (Fight \textbullet)}

\noindent Action: Permanent\\

\noindent A ranged weapon becomes part of the Princess’ Regalia, delivering the force of her will from afar. It can appear as nearly anything; wizards’ staffs, futuristic pistols, wands of ice, and daggers that fly back to the hand are all known examples. Regardless of the weapon's form, the Princess uses the Firearms Skill to attack with the weapon. Initially the weapon's Damage is 1 but when she attacks the Princess may apply an Invocation to add Damage or additional dice to her pool, this stacks with any damage or bonus dice from Upgrades but in either case the maximum is 5. The princess may not apply an Invocation to both Damage and Accuracy in a single turn, she may apply two different Invocations to gain both benefits unless she is using an Invoked Upgrade.  

The weapon’s range is (10/20/40) * Inner Light in yards, its clip holds 3 shots and it allows autofire. The damage can be either Bashing or Lethal and the Princess can swap between them with a Transformation action. The weapon always has a Size between 1 and 4. For anyone but the Princess, the Initiative penalty and the minimum Strength needed to use the weapon both equal three + the Princess' Inner Light For the Princess herself, both are 0 - as an extension of her will, the weapon obeys her desires as well as her own hands.

The weapon is unloaded when the Princess summons it, unless she spends a Wisp as she does so; at any time as an instant action, she may spend 1 Wisp to reload it, conjuring shots directly into the clip.

\begin{myindentpar}{10pt}\textbf{Upgrade: Accurate}

Stacks, up to 3

The Princess wields her weapon with supernatural skill. Each time the Princess takes this upgrade, she gains 1 bonus die when attacking with her weapon.

\textbf{Upgrade: Damaging}

Stacks, up to 3

Each time the Princess takes this upgrade, she adds 1 to her weapon’s Damage. 

\textbf{Upgrade: Multiple}

Stacks, up to 2 times

The first time a character takes this upgrade, the weapon's clip grows to 10 shots, allowing a medium burst of autofire. On the second purchase, the clip grows to 30 shots, allowing a long burst. No matter how large the clip, 1 Wisp is enough to reload the weapon completely.

\textbf{Upgrade: Long}

The weapon's range doubles, to (20/40/80) * Inner Light in yards.

\textbf{Upgrade: Boiling (Acqua \textbullet\textbullet)}

In addition to taking damage from the weapon's shot, a target is pushed away. If the Princess applies Acqua to an attack, for each success, the target moves half the Princess' Speed away from her, unless pushed into an obstacle. Targets that hit an obstacle are crushed against it, and take extra bashing damage. Roll 1 die for each success, minus 1 for each step of Speed/2 the target moved before impact (rounding up); the target takes 1 bashing damage for each success on this roll.

\textbf{Upgrade: Freezing (Aria \textbullet\textbullet)}

The weapon's shot guides itself around obstacles and penetrates protective clothing. If the Princess applies Aria to an attack, she gains Armour Piercing equal to her weapon's Damage + Aria, however this significantly reduces her weapon's power reducing her weapon's damage to zero. She does gain one bonus die for any point of Armour Piercing above her opponents Armour rating. 

\textbf{Upgrade: Burning (Fuoco \textbullet\textbullet)}

The Princess' weapon erupts into flame. If she applies Fuoco to an attack, it gains the 9-again quality and if the target is as flammable as dry wood it will likely catch fire. 

\textbf{Upgrade: Soothing (Legno \textbullet\textbullet)}

If the Princess applies Legno to an attack, and a target takes damage from it, a dose of an opiate enters his bloodstream, and he must roll his Stamina + Resolve - the Princess' Legno. If he fails, he suffers the effects of a dose of morphine (see page 177 in the nWoD core book for details.)

\textbf{Upgrade: Quaking (Terra \textbullet\textbullet)}

It the Princess applies Terra to an attack, the earth bucks under the target's feet as the weapon's shot strikes him. In addition to taking damage, the target must succeed on a reflexive roll of Dexterity + Athletics, penalized by -1 per success, or be knocked down.

\textbf{Upgrade: Draining (Lacrima \textbullet\textbullet)}

The weapon's shot assaults the will of the target if it strikes home. If the Princess applies Lacrima to an attack, and the target takes damage, he also loses 1 point of Willpower. Using this upgrade is a Compromise at Belief 5+ with a -2 modifier.

\textbf{Upgrade: Irradiating (Tempesta \textbullet\textbullet)}

The Princess may increase the Damage of the weapon's shot by inflicting resistant damage on herself. 1 level of bashing damage gives a +1 bonus, and 1 level of lethal damage gives a +3 bonus. The Princess chooses whether to take bashing or lethal damage for each attack.

\textbf{Upgrade: Trickshot (Specchio \textbullet\textbullet)}

The Princess's weapon fires a bolt of pure light in an impossible shot. She might aim over her shoulder with a mirror, ricochet the bolt several times to her target or shoot a target 100 foot away from the hip. She ignores up to her Specchio in penalties for long range, called shots, concealment and other similar modifiers.\end{myindentpar}

\myframe{
 
 \textbf{It's Magic} \\
 
 \noindent Regardless of their form weapons created by Kensai, Levinbolt and even the weaponless combat of Empty Hand are treated as magical damage. They are the Princess' willingness to hurt another, or to defend another, made manifest. 
 
 \vspace{4 mm}
 
 This means that a Princess' may create a sword of the purest silver, but it will not be of any extra help when fighting a Werewolf (though the Werewolf might not know that), but contrawise it will not be stopped by that anti-silver forcefield the Werewolf brought off a Mad Scientist. 
 
 \vspace{4 mm}
 
 Invoked upgrades can change this rule, for example after applying the Fuoco Upgrade Burning a Princess' attack consists of both magic and fire. Apply the greatest defence against either magic or fire, but any damage that gets through is counted as the more effective of the two. 
 
}

\subsubsection*{Flash Step (Fight \textbullet, Aria \textbullet)}

\noindent Action: Reflexive, Wits + Athletics

\noindent Cost: 1 Wisp

\noindent Duration: instant\\

\noindent The Princess dodges her foe's attack so swiftly that, by the time it lands, she's somewhere else. She may activate Flash Step when a foe attacks her in close combat; if she succeeds, she moves up to her Speed times her activation successes in yards. She loses her Defense against the attack, but each activation success subtracts one success from the attacker's roll.

\subsubsection*{Courteous Parry (Fight \textbullet, Terra \textbullet)}

\noindent Action: Permanent\\

\noindent A smile and pleasant voice disarms a Princess' attackers, or a calculated remark at the right moment throws them off-balance. When the Princess takes a Dodge action, she may add her Manipulation + Persuasion to her Defense instead of doubling it, if the attackers have a roughly human mindset. Afer doing so she uses Defence as a dicepool to dodge attacks as normal. Unfortunately, social acumen doesn't do anything to inhuman foes; against an animal, a spirit and similar beings the Princess' Defense remains at its base value, even when she dodges.

\begin{myindentpar}{10pt}\textbf{Upgrade: Instinctive}

Using social talent to evade injury becomes almost a reflex. When the Princess transforms, she may choose to use her Manipulation + Persuasion instead of Wits, Dexterity and Athletics when calculating Defence, again this only applies against attackers with a basically human mind. When Dodging add her Athletics + the lower of her Wits + Dexterity rather than doubling Defence. The drawback, as before, is that against inhuman attackers she has no Defence without dodging. She may return to normal Defence with a transformation action.\end{myindentpar}

\subsubsection*{Shield Wall (Fight \textbullet, Terra \textbullet\textbullet)}

\noindent Action: Reflexive, Presence + Brawl or Weaponry 

\noindent Cost: 1 Wisp

\noindent Duration: 1 Turn\\

\noindent The Princess stands firm like a rock, and holds the line together. When one of her companions is attacked she may shout a warning, direct a fighter to their ally's aid or parry the blow herself. For every Success rolled the Princesses subtracts one Successes from every attack that is penalised by defence targeted at an ally in Inner Light yards. The Princess also benefits from this Charm, but she has to have at least one ally within Inner Light yards.

Any given individual can only benefit from Shield Wall once per turn, even if, especially if, multiple Princesses are trying to direct the defensive line.

\subsubsection*{Lighting Charge (Fight \textbullet, Aria \textbullet)}

\noindent Action: Reflexive, unrolled

\noindent Cost: 1 Wisp

\noindent Duration: 1 Turn\\

\noindent The Princess charges into battle with the speed of lightning, she may spend a Wisp to make a charge action (WoD Core, p164) without sacrificing her Defense.

\subsubsection*{Strike False (Fight \textbullet\textbullet)}

\noindent Requires: Kensai or Levinbolt

\noindent Action: Instant, Dexterity + Brawl, Firearms or Weaponry.

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The Princess' weapon becomes a phantom, creating the appearance of danger without inflicting actual harm.

\begin{myindentpar}{10pt} 
\emph{Dramatic Failure:} The Princess' attacks are real, but she is convinced they are not, and does not realise otherwise until the Charm ends

\emph{Failure:} The Princess' attacks remain unchanged.

\emph{Success:} The Princess' Regalia weaponry inflicts phantom damage The target suffers wound penalties from this damage and risks unconsciousness if it fills the last box, as normal. However, the damage is not real; it vanishes when the Charm ends as if it were healed, and if the target takes real damage when the track is full, that damage replaces the phantom damage instead of wrapping over. Phantom damage also has no effect if the target has no empty Health Boxes to fill. The phantom damage can also be healed magically, or mitigated as it's inflicted by targets who have that ability. Phantom damages is removed at the end of the charm's duration, and the Princess may reflexively end the Charm; restoring the lethal capacity of her weaponry and removing any phantom damage she has caused. 

\emph{Exceptional Success:} The Princess may choose whether to inflict normal or phantom damage for each attack.

\textbf{Upgrade: Suggestive}

Cost: +2 Wisps

Any Charm the Princess casts that inflicts damage inflicts phantom damage instead of normal damage. 

\end{myindentpar}
\subsubsection*{You Might Hurt Yourself (Fight \textbullet\textbullet)}

\noindent Requires: Kensai 

\noindent Action: Reactive and Contested, Dexterity + Brawl or Weaponry.

\noindent Cost: 1 Wisp

\noindent Duration: instant \\

\noindent When an armed foe attacks the Princess in close combat, she strikes at his weapon. The Princess gains no Defence against any attack countered with this Charm but every success rolled subtracts one from the attacker's successes. If the Princess rolls more successes then her opponent he is disarmed, and his weapon goes flying Strength yards in a random direction.

\begin{myindentpar}{10pt}\textbf{Upgrade: Confiscating (Acqua \textbullet\textbullet\textbullet)}

In a fluid movement, the Princess pulls her enemy's weapon into her grasp. When she disarms someone with this Charm (and she has a spare hand), she may keep hold of the weapon instead of knocking it away; she may use it on her next action.\end{myindentpar}

\subsubsection*{Fluid Defence (Fight \textbullet\textbullet, Acqua \textbullet)}

\noindent Action: Unrolled

\noindent Cost: 1 Wisp

\noindent Duration: 1 turn\\

Like flowing water the Princess redirects energy instead of opposing it. She may give up her turn to turn her Defence into Soak at a 1:1 ratio. Soak downgrades Aggravated damage to Lethal, and Lethal to Bashing, apply Armour before Soak and apply Soak before Holy Shield. Bashing damage is not affected by Soak. 

Soak only applies when Defence would apply, a Princess can no more position her body fast enough to diffuse the energy of an oncoming bullet than she could move it fast enough to dodge a bullet. At least, not without Celestial Dance and Danmaku Dance.

\subsubsection*{Safety in Stillness (Fight \textbullet\textbullet, Legno \textbullet)}

\noindent Action: Instant, Composure + Brawl

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene\\

\noindent The Princess stands unperturbed by the assaults of many foes. After activating the Charm, her Defense is not reduced until she has taken (1 + her successes) attacks in a turn.

\subsubsection*{Seraphic Fury (Fight \textbullet\textbullet, Tempesta \textbullet\textbullet)}

\noindent Action: Reflexive

\noindent Cost: 1 resistant lethal damage

\noindent Duration: 1 turn\\

The Princess channels fire and fury through her veins into the flesh of an enemy of the Light. Her weapon seeks the heart and severs arteries. She may activate the Charm when she attacks a creature of the Darkness or a follower of Tears, before making the roll. If the attack hits the creature, it does aggravated damage. Seraphic Fury may enhance Kensai, Levinbolt, Empty Hand or any mundane weapon.

\begin{myindentpar}{10pt}\textbf{Upgrade: Discretionary (Tempesta \textbullet\textbullet\textbullet\textbullet)}

The Princess judges for herself who the Light’s enemies are. She may use the Charm when attacking anyone - her enemy need not be a creature of the Darkness.\end{myindentpar}

\subsubsection*{Guardian Angel (Fight \textbullet\textbullet, Fuoco \textbullet)}
\noindent Action: Instant, Strength + Presence\\

\noindent Cost: 1 Wisp\\

\noindent Duration: successes in turns or 1 scene\\


A true Heroine gladly risks her life to save another from harm. The Princess uses this Charm on someone she can see; she cannot use it on herself or anyone with a Supernatural Advantage equal or greater to her Inner Light - 2.

\begin{myindentpar}{10pt} 

\emph{Dramatic Failure:} The Princess is struck by dizziness and loses strength, as if suffering a high fever. She takes the moderate form of the Sick Tilt (GMC p. 212). The fever fades if the Princess rests long enough to reduce the penalty to 0.

\emph{Failure:} Nothing happens. 

\emph{Success:} Everyone who can see both the Princess and the target realizes that she has put him under her protection; those who wish to harm him must first defeat her. For turns equal to the activation successes, any character who attacks the target cannot apply Defense against an attack from the Princess until their next action.

\emph{Exceptional Success:} The Princess' protection lasts for the rest of the scene.

\textbf{Upgrade: Everyone's Angel (Fuoco 2)} 

Cost: +1 Wisp

The Princess offers her protection to members of a group that she can see, applying the Commonalty modifier for that group; while the Charm lasts, anyone who attacks a member of that group loses his Defense against the Princess until his next action.\end{myindentpar}


\subsubsection*{Contest of Champions (Fight \textbullet\textbullet, Fuoco \textbullet\textbullet)}

Action: Reflexive, Presence + Intimidation vs Composure + Supernatural Advantage\\

\noindent Cost: 1 Wisp\\

\noindent Duration: One fight\\

\noindent In the midst of battle the Champion challenges her counterpart to single combat, drawing her foe away from weaker targets.

\begin{myindentpar}{10pt} 
\emph{Dramatic Failure:} The Princess looses all Defense against the target for one turn.

\emph{Failure:} or the Princess looses the roll: Nothing happens.

\emph{Success:} and the Princess wins the roll: The Princess and her target both gain +1 Defence against all attackers other than each other. In addition, if either chooses to do anything other than attack the other in single combat, or perform some other action suited for single combat, she loses all defence against her opponent for the turn and ends the charm.

\emph{Exceptional Success:} and the Princess wins the roll: As above, and the Princess immediately gains a point of Willpower. If she chooses she may reflexively spend this point to make an Inner Strength roll.

\textbf{Upgrade: Arena of the Gods}

Cost: +1 Wisp

When the Princess and her opponent close into melee range a ring of fire springs up around them. This ring has a radius of 10 feet, and though the flames are only three foot tall they will burn anyone up to ten feet in the air. If there is insufficient space the arena will shrink to accommodate it's limitations, and it will never form if anyone but the Princess and her opponent would be inside the ring. It may, however, start small and grow out, pushing others away to give the champions room.

The flames have the size of a bonfire and the heat of a bunson burner (WoD core p180), and can be treated as normal flames except that they never ignite anything else and cannot be extinguished by non-magical means.

\textbf{Drawback:} Obviously enough, by invoking this Charm the Princess has cut off her escape with a big wall of fire. This can by bypassed with charms like Barrier Jacket, but in a formal dual it is considered cheating to exit the arena.

\textbf{Upgrade: Radiant Victory}
Cost: +1 Wisp

With the enemy's champion defeated and their own claiming a heroic victory the fighters are rallied and ready to turn the tide. They can add the winner's Presence to their next roll. This requires some storyteller judgement, as defeating an obviously inferior foe will not inspire anyone. 

\textbf{Drawback:} If your opponent wins they gain the bonus.\end{myindentpar}

\subsubsection*{Spite Strike (Fight \textbullet\textbullet, Tempesta \textbullet)}

\noindent Action: Reflexive, Dexterity + Intimidation

\noindent Cost: 1 Wisp

\noindent Duration: Reflexive\\

\noindent None may strike a Fury without reprisal. The Princess is attacked, she may forgo her Defence and activate Spite Strike. If she takes damage from the attack, she may retaliate against her attacker by rolling her normal dicepool + the amount of damage received, the type of damage done is the type of damage the Princess recieves. The Princess must actually take damage -- if she mitigates any of it by spending Wisps, or if the attacker fails to inflict any damage, the Charm fails.

\subsubsection*{Befriending (Fight \textbullet\textbullet, Specchio \textbullet\textbullet)}

\noindent Action: Reflexive, no roll is required

\noindent Cost: None

\noindent The Queen of Mirrors wants everyone to get along, in service to the True Queen. Isn't that nice? Sadly, violence is sometimes necessary, but violence should always serve a higher cause, and bind people together. If a character is defeated in combat by the Princess this Charm can be used to apply the Fresh Impressions Condition to the target. For one week the Condition sets their Impressions to Good. Some storyteller discretion may be needed to define defeated.

This power does not work upon Creatures of the Darkness, not even Darkened. At the Storyteller's discretion other fundamentally evil beings may also be immune. 

\subsubsection*{Cauterising (Fight \textbullet\textbullet, Tempesta \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, unrolled

\noindent Cost: 2 Wisps 1 Willpower

\noindent Duration: 1 scene\\

For the remainder of the scene any damage the Princess inflicts upon a Creature of the Darkness is Resistant. Despite what the Furies believe about the Court of Tears, this Charm only affects monsters that actually are of the Darkness (though that would include a Princess who temporarily transformed herself into one through Lacrima magic). 

The exception to this Charm is that it cannot enhance attacks caused by or reinforced by other Invocations. If the Princess applies any Invocation but Tempesta or uses a non-Tempesta Invoked Charm the damage can be healed like normal. 

\subsubsection*{One Woman Warband (Fight \textbullet\textbullet, Specchio \textbullet\textbullet\textbullet)}

\noindent Action: Reactive, unrolled

\noindent Cost: 1 Wisp

\noindent Duration: 1 turn\\

\noindent What's more impressive than flamboyantly taking down an opponent without a scratch? Flamboyantly taking down ten opponents. When the Princess activates One Woman Warband she makes a dodge action during which susequent attacks will not decrease her Defence. Instead each attack within a turn adds +1 to her dice pool for dodging. She may never increase her dicepool above three times Specchio or double her Defence. Whichever one is higher. 

\textbf{Upgrade: Countered}

At the end of the turn the Princess may make one counter attack with a dicepool equal to the number of people who attacked her this turn. If her target attacked her and missed this turn she gains a bonus die.


\subsubsection*{Load Cartridge (Fight \textbullet\textbullet\textbullet)}
\noindent Requires Kensai or Levinbolt

\noindent Action: Instant, Unrolled

\noindent Cost: 2 Wisps

\noindent Duration: 1 Scene \\

The World of Darkness is full of strange and weird monsters, and sometimes a Princess' magic isn't the right tool for the job. By taking a sample, at least the size of a finger, of any mundane physical material the Princess may load it into her Levinbolt or Kensai weapon. For the remainder of the scene attacks with the enhanced weapon count as both the loaded material and magic and should be treated appropriately when compared to a supernatural (or natural) weakness and when up against defences that protect against specific materials. If Princess applies an Invoked Upgrade to her attack, the attack counts as magical, the loaded material, and the Invocation's element all at once. 

Any Transformation action that modifies the Princess' weapon will end this charm early. 

\subsubsection*{Backstab (Fight \textbullet\textbullet\textbullet, Aria \textbullet\textbullet\textbullet)}

\noindent Action: Reflexive, unrolled

\noindent Cost: 2 Wisps

\noindent Duration: 1 Turn\\

\noindent Seizing the opportune moment the Princess repositions herself to strike with stealth and surprise. She may make a flanking attack (WoD Core, p165) during established combat providing that her target is not currently aware of her, and of course she is behind or to the side of her target. 

The Princess may use Backstab multiple times in the same combat, even against the same target, providing that her target has not noticed her for a number of turns equal to his Wits + Composure. 

\subsubsection*{Refutation in Arms (Fight \textbullet\textbullet\textbullet, Acqua \textbullet\textbullet)}

\noindent Action: Instant and resisted, Wits + Brawl, Weaponry or Firearms - target's Wits

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene\\

The attacks of a fighter fall into patterns, and the Princess can read those patterns. The Princess may activate this Charm against any opponent she has attacked or who has attacked her in the last turn. 

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess misreads her foe. For the rest of the scene, all her attacks on this opponent take a -1 penalty, and she cannot use Refutation in Arms again.

\emph{Failure:} The Princess learns nothing from her foe's movements.

\emph{Success:} The Princess gets the Blessing Tilt; all her attacks on this opponent gain a +1 bonus until the Charm ends. In addition every turn she spends fighting that opponent increases the bonus by one die, up to a maximum of Acqua times two. 

\emph{Exceptional Success:} As above but the bonus starts at +2.\end{myindentpar}

\noindent For the purposes of this Charm \textquotedblleft fighting an opponent\textquotedblright\, is defined as attacking that opponent, using a Charm upon that opponent, taking an action designed to prevent the opponent's action from succeeding, or assisting one of her allies in doing any of the aforementioned actions.

The designated opponent must be the primary target of the Princesses action. If one Darkspawn plans to use a trick which removes Defence so that the Princesses designated target can attack a defenceless foe; then preventing the first Darkspawn's action will not qualify. The Princess can still do so but it will not change her calculative bonus. 

A Princess can gain a bonus from this Charm against only one target at a time; if she uses it again before the scene ends, the first use of the Charm ends immediately.

\subsubsection*{Tangling Vine (Fight \textbullet\textbullet\textbullet, Legno \textbullet\textbullet)}

\noindent Requires: Kensai

\noindent Action: Instant and resisted, Strength + Brawl - target's Defense

\noindent Cost: 1 Wisp

\noindent Duration: concentration\\

\noindent A net of brambles grows in the Noble's hands, and she throws it at a target at a range of (10/20/40) * Inner Light yards. Despite the unusual idea of fighting with living plants it functions identically to a mundane grapple, except for the fact the Princess may do so at range. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Thorny}

The net grows sharp thorns; it may inflict lethal damage in the grapple.

\textbf{Upgrade: Wide}

\noindent Stacks, up to 3 times

\noindent Cost: +0-2 Wisps

The net is broad enough to ensnare more than one person. Use the autofire rules. The first purchase gives the net the bonus of a short burst. The second purchase adds 1 Wisp to the cost, and allows the equivalent of a medium burst. The third purchase adds 2 Wisps to the cost, and allows the equivalent of a long burst.\end{myindentpar}

\subsubsection*{Salted Wounds (Fight \textbullet\textbullet\textbullet, Lacrima \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Resolve + Medicine

\noindent Cost: 2 Wisps, Compromise at Belief 5+ with a -2 modifier

\noindent Duration: See text\\

\noindent The Raven imbues her weapon with salty despair and resignation, when she next attacks the curse sinks into the wounds and takes hold. When the Princess next strikes a target she gains the Inverse Curse Tilt, which penalises any attempts to heal the victim (by herself or others). The penalty is equal to the amount of Lethal or Aggravated damage the Princess inflicts, after reductions, and lasts for one scene. Healing the damage does not end the Curse, though specialised Charms such as Unweaving can do so.

\subsubsection*{Demilitirzation (Fight \textbullet\textbullet\textbullet\textbullet, Legno \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Composure + Expression

\noindent Cost: 3 Wisps, 1 Willpower

\noindent Duration: 1 scene\\

\noindent The greatest victory is the battle won without violence, and magic is good at sharing victory with all. By calling upon the Matron of the Forests a Princess can snatch the weapons from her foes hands, but she cannot do it without taking violence from her friends as well. 

This Charm spreads the Anti-War Zone tilt to the surounding environment. The penalty is equal to the successes rolled. 

\subsubsection*{Towering Inferno (Fight \textbullet\textbullet\textbullet\textbullet\textbullet, Fuoco \textbullet\textbullet\textbullet\textbullet)}

\noindent Requires: Levinbolt

\noindent Action: Instant, Strength + Firearms

\noindent Cost: 2 Wisps

\noindent Duration: instant\\

\noindent The Princess conjures a ball that explodes in a gout of consuming fire. The ball is an aerodynamic object of Size 1, and is thrown normally for such objects; when it hits, it explodes with a blast area equal to the Princess' Inner Light and a Damage equal to her successes. The explosive is also an incendiary -- anything damaged by it ignites, and while the direct explosive damage is bashing, damage from fires set by it is lethal. All such fires are mundane, though the explosive is not. The Princess may hold the ball up to her Fuoco in turns, after which it explodes wherever it is.

\subsubsection*{Strength of Ten (Fight \textbullet\textbullet\textbullet\textbullet\textbullet, Terra \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Presence + Expression

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: 1 turn\\

\noindent Blows delivered by the Princess' friends become steps in a great dance, and her strike against a foe is its culmination. The Charm may be activated only during combat. For each activation success, add the successes rolled for a mundane action by one character on the Noble's side of the fight as a bonus to her dice pool in the next turn, provided that her action that turn is a mundane attack (an attack using Kensai or Levinbolt counts as mundane). If the Princess does anything other than attack a foe as her next action, she gains no benefit from the Charm. She must choose whether an eligible action is part of the attack before the player for that character rolls. If a character rolls a dramatic failure on an action that's part of the attack, the Princess takes a -4 penalty to her dice pool.

\subsubsection*{The Finest Hour (Fight \textbullet\textbullet\textbullet\textbullet\textbullet, Tempesta \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Resolve + Composure

\noindent Cost: 3 Wisps, 1 Willpower, 1 Resistant Aggravated Damage

\noindent Duration: 1 scene \\

\noindent The Princess draws upon the dedication and resolve the Seraphic General displayed during the fall, and recreates her own lesser version of that courage to become Storms' avatar. 

    \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess is overcome with a feeling of utter futility and defeatism. She loses all Willpower and must flee all combat for the scene. She is considered to have broken Tempesta's ban.

    \emph{Failure:} The Princess cannot focus.

    \emph{Success:} The Princess enters a combat trance, a tranquil fury or even a screaming hysteria. In this state she is one of the most powerful and terrible combatants known to the Radiant. She gains the Seraphic Fury Tilt: Any damage she inflicts is Aggravated, she gains temporary health equal to her Inner Light + Resolve and every time she kills someone she believes to be in league with either the Darkness or Tears she completely refreshes her Willpower.

    \emph{Exceptional Success:} The Princess develops such as strong aura of violence and power that her foes flee at the very sight of her. She also gains the Terrifying tilt, the people affected are Mortals (including minor templates like Sworn and Darkened) and Darkspawn.\end{myindentpar}

\textbf{Drawback:} Once this Charm is active the Princess must fight to the death - she simply cannot conceive of not fighting for as long as one foe remains standing. The Princess also gains the Invocation Lock condition keyed to Tempesta.

\subsection*{Govern}
The Govern Charms control supernatural powers and those who possess them. Graces and Seekers have affinity for them.

\subsubsection*{Consecrate (Govern \textbullet)}

\noindent Action: Extended - teamwork, Presence + Expression (10 minutes/roll, threshold = variable)

\noindent Cost: 3 Wisps

\noindent Duration: special\\

\noindent The Princess blesses the ground she stands on, and dedicates it temporarily to her Queen and the Light. By using this Charm a Princess applies the Consecrated condition to the area until the Charm ends. Many Charms, distinguished as such in their description are more durable or effective when invoked upon consecrated groups. The Princess needs to cleanse and purify every part of the area she wishes to sanctify; this can be as simple as giving it a thorough spring cleaning, or it can be an elaborate rite for casting out evil spirits, depending on the Princess' cultural background. However, if she applies an Invocation, the method of purification invokes the relevant Queen and must use symbols appropriate for her. 

Consecrating a large area is naturally harder than a small one, Consecrate is a Sanctuary based Charm. 

    \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess ruins the area's blessing - all her accumulated successes are lost, and if the area has the Consecrated  condition immediately loses it. No one can use Consecrate there for a full month.

    \emph{Failure:} The Princess makes no progress, but may continue her efforts.

    \emph{Success:} The Princess progresses in her work. When she reaches the threshold, the area gains the Consecrated condition and retains it for 1 day. The Princess may continue working to extend the Charm's duration:

    2 * Sanctuary Size = 1 day
    
    4 * Sanctuary Size = 1 week
    
    6 * Sanctuary Size = 1 month
    
    8 * Sanctuary Size = 1 year
    
    10 * Sanctuary Size = indefinite 

    \emph{Exceptional Success:} The Princess makes great progress.\end{myindentpar}

\noindent  If an area is already Consecrated, Consecrate will not take effect until the Princess reaches enough successes to exceed the remaining duration of the previous Consecration. (For instance, if an area will be Consecrated for five days, the Princess must reach enough successes for a week's duration, after which the area will be Consecrated for a week.) If any part of an area is Tainted, the Charm automatically fails. Consecrate ends if the area suffers major alterations or damage, or someone manages to bring Taint into it.

If the Princess has access to gems created by the Charm Enduring Beauty she can use them to empower Consecrated ground, extending the duration of the protection. A gem worth Resources three increases the duration by one step (so 2 * the area's size successes creates a duration of 1 week). A gem worth Resources five increases the duration by two steps. It takes five gems worth Resources one to increase the duration by one step. Multiple gems may be combined for a greater effect but the required successes can can never drop below 2 * the area's size. Obviously the duration cannot be increased past indefinite. 

Gems used to empower Consecrated Ground must be reworked into part of the ground, becoming beautiful statues, windows or other features. This happens as part of the Charm. They must be displayed prominently but can be protected by any anti-theft measure that doesn’t spoil their beauty. If even one of these reworked gems is removed from the Consecrated ground the Charm ends. Once this happens they can never again be used to enhance magic, however they are still beautiful and worth money, and they can still be used to return beauty to whomever it was taken from.

Making use of Consecrated ground that is built on stolen beauty is a Belief Compromise, unless there is good evidence to suggest that the beauty was taken consensually. There is no modifier for the Compromise roll.

\begin{myindentpar}{10pt} \textbf{Upgrade: Purifying}

The Princess may apply the Consecrated condition on top of Taint. The Taint will always overcome this Charm given enough time, but it can allow the Princess some vital breathing space. Invoke Consecrate like normal, when the Princess accumulates a number of Successes equal to the Taint's Severity then:

   \begin{itemize} \item The Taints' Curses go dormant.
    \item The Taint will not attempt to Corrupt nor will it cause Hauntings for characters with sensitivity.
    \item The Taint no longer provides access to and from the Dark World\end{itemize}

However once per day reduce the Princesses Successes by the Taint's Severity. When her Successes are reduced to zero or when the duration expires, as measured by her unmodified Successes, the Consecrated condition ends and the normal effects of Taint return. The Princess may invoke Consecrate again to add additional Successes, but this only delays the inevitable.

Purifying does not protect against new Taint, only the existing Taint.

\textbf{Upgrade: Bastion}

Several charms have special benefits when cast upon Consecrated ground. When Consecrate is invoked with Bastion another benefit is added: Charms that benefit from the Consecrated condition are immune to being dispelled (such as by the Charm Unweaving) for as long as the condition remains.

It is important to note that Consecrate itself can be dispelled and this Upgrade offers no protection against that.

\end{myindentpar}

\subsubsection*{Reflected Light (Govern \textbullet)}

\noindent Action: Permanent\\ 

\noindent The Princess gains the benefits of the Unseen Sense merit for any use of a supernatural ability within 10 x Inner Light yards. The simple presence of a being with magical powers does not register to her new sense, but she will notice any power such beings use.

The Princess may roll Wits + Occult reflexively on sensing a power in use to identify it, and may apply an Invocation to this roll. If it springs from the Light or the Darkness, success identifies the power as of the Light or the Darkness. For other powers  the Princess must learn about the nature of the power through research or investigation. 

So if a Princess felt a power belonging to a Vampire she could tell that it was the same kind of power as every other use of a Vampire's power she previously felt. But she would not know that all these powers belonged to vampires without investigating. 

If the character using the power has the ability to conceal itself from supernatural detection, then the Princess must overcome that concealment as per the usual rules.  

\begin{myindentpar}{10pt} \textbf{Upgrade: Sensitive}

Double the range of the Princess' Unseen Sense, to 20 x Inner Light yards.

\textbf{Upgrade: Light-attuned}

The Princess recognizes individual powers springing directly from the Light; when she rolls to identify a Charm, she learns the exact Charm along with any Upgrades and which Invocation, if any, was applied. 

\textbf{Upgrade: Dark-attuned (Tempesta \textbullet)}

The Princess recognizes individual powers springing directly from the Darkness; when she rolls to identify an Umbra or Caligo, she learns the specific power, not just \textquotedblleft power from the Darkness". If the Storyteller rules that other supernatural entities draw powers from the Darkness; the Princess can identify any such powers.\end{myindentpar}


\subsubsection*{Dreaming Sight (Govern \textbullet)}

\noindent Action: Reflexive\\ 

\noindent Cost: 1 Wisp\\ 

\noindent Duration: 1 Scene\\ 

\noindent The Princess can see into Twilight to perceive natives of the Dreamlands who have escaped to the waking world, along with similar phenomina like astrally projecting psychics. With a Successfull Perception roll she can notice Manifestation Conditions related to a Dreamlanders in her vicinity. Physical objects still block her sight, so a Dreamlander can hide behind - or inside - such objects to evade her.	

\begin{myindentpar}{10pt} \textbf{Upgrade: Touching}
 
By spending an additional Wisp, the Princess shifts her flesh partly into Twilight, allowing her to touch or attack Dreamlanders, and they her, until the Charm ends. All of her regalia (including weapons and armor) are carried into this state with her, as are the effects of Charms.

\textbf{Upgrade: Spirit Sight (Legno \textbullet)}
One of the Wilds may attune herself to the presence of spirits. If she applies Legno instead of spending a Wisp, the Princess sees spirits in Twilight Form, and can make Perception rolls to notice Manifestation Conditions related to a spirit, or the presence of a locus [GMC 220]. She cannot see Dreamlanders and spirits at the same time. Applying Touching makes the Princess tangible to spirits, not Dreamlanders.

\textbf{Upgrade: Second Sight (Lacrima \textbullet)}

A follower of Tears can part the veil and see into the great beyond. If she applies Lacrima instead of spending a Wisp, the Princess sees ghosts in Twilight Form and structures made of ghostly ephemera, and can make Perception rolls to notice Manifestation Conditions related to a ghost, a ghost’s Anchor or an Avernian Gate [GMC 226]. She cannot see Dreamlanders and ghosts at the same time. Applying Touching makes the Princess tangible to ghosts, not Dreamlanders.

\end{myindentpar}

\subsubsection*{Study Inheritance (Govern \textbullet)}

\noindent Action: Extended, Intelligence + Empathy (5 minutes/roll, threshold = Bequest's Merit rating)

The mysteries of the Kingdom's relics can be unveiled. The Princess uses this Charm on a transformed Bequest; when she reaches the threshold, she discovers what Charm the Bequest is based on, the cost of activating it, whether it carries a pool of Wisps, if it is empowered, and the duty one must carry out to refill the pool.

\subsubsection*{Charge (Govern \textbullet\textbullet)}

\noindent Action: Instant, Stamina + Empathy

\noindent Cost: none

\noindent Duration: instant \\

\noindent By touching someone (or something) with a pool of Wisps, the Princess transfers some of her own Wisps to the other pool. She may give up to 1 Wisp for each success, capped by her normal Wisps/turn limit. She cannot give more Wisps than the target can hold.

\begin{myindentpar}{10pt} \textbf{Upgrade: Accepted}

The Princess may take Wisps from other people, if they are willing to give them. If the target consents, the Princess may take 1 Wisp for each success, capped by her normal Wisps/turn limit. As inanimate objects, Bequests cannot consent to relinquish their Wisps. 

\textbf{Upgrade: Distant}

\noindent Cost: +1 Wisp

The Princess may use the Charm on people who are not present, applying the Intimacy modifier. With Accepted, she can take Wisps from those she can't see as well. 

\textbf{Upgrade: Stolen (Lacrima \textbullet\textbullet)}

Requires Accepted

\noindent Cost: Compromise at Belief 4+ with a -3 modifer

The Princess can take Wisps from unconsenting people. Subtract the target's Resolve from the activation roll. Moreover, unless she applies Distant, the Princess must already have a hand on her target; if she needs an instant action to touch him, the Charm does not work.

\textbf{Upgrade: In Memoriam (Lacrima \textbullet\textbullet)}

The Princess can convert between Wisps and Ghostly Essence at a 2:1 ratio, in either direction, she may also use Charge and all it's Upgrades on a Ghost. Princesses cannot store Essence - she must give converted Wisps to a ghost, and transform any Essence received into Wisps.\end{myindentpar}

\subsubsection*{Gold Abhors Ebon (Govern \textbullet\textbullet)}

\noindent Action: Instant and contested, Presence + Intimidation vs. Resolve + supernatural advantage

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene

\noindent Invoking the Light's authority, the Princess drives off a being of the Darkness. If the Princess wins the contest, the target becomes irrationally afraid of her for the duration; gaining the Terrified Tilt.

\begin{myindentpar}{10pt}

\textbf{Upgrade: Ruling}

Inhuman monsters must acknowledge the Princess' authority. She may use the Charm on non-human supernatural beings, such as ghosts and spirits.

\textbf{Upgrade: Majestic}

Requires Ruling

\noindent Cost: +1 Willpower

All those with power bow to the Light. The Princess may use the Charm on humans with supernatural powers that aren't derived from the Light. This includes anyone with a major or minor template, and anyone with powers they would lose if they gained a template, except for Beacons, Sworn and Hopeful.

\textbf{Upgrade: Fearsome (Lacrima \textbullet\textbullet)}

\noindent Cost: Compromise at Belief 6+ with a -1 modifier

The Queen of Tears claims the right to rule all the world, mortals, Nobles and supernaturals alike. The Princess may use the Charm on humans without supernatural powers, and on Beacons, Sworn and other Princesses.\end{myindentpar}



\subsubsection*{Light over All (Govern \textbullet\textbullet)}

\noindent Action: Permanent \\

\noindent Mortals may not be magical, but they can use magic. Some forms of magic used by mortals are impossible for a Princess to perform, others are rendered obsolete, and then there are some types of magic that Princesses find come even easier after they Blossom. 

On the whole Princesses aren't that great at working with or against Ephemeral Beings (Dreamlanders excepted). The noble magic that affects such beings tends to be basic, with only obscure Embassies mastering anything substantial. Ghosts are easier but to learn Charms that affect Ghosts she would have to first become a practitioner of Lacrima, even though Lacrima's Ghost Charms do not compromise Belief few among the Radiant are willing to take that step.

So if Princesses want to deal with an Ephemeral Being they'll either call the Embassy, or they'll turn to the same tricks that mortals use (see GMC p230). It is fortunate then, that a Princess' own magic can reinforce mortal techniques, with Light over All she can apply an Invocation to the rolls. 

In addition, the following dice bonuses and penalties apply, based on the entity:

\begin{itemize} \item    +3: The entity was never human, and is anathema to reality (Some creatures of the Darkness)
\item    +1: The entity was never human, but is not anathema to humanity; or was human, but thinks nothing like a human (most Spirits and Dreamlanders, some ancient Ghosts)
\item    +1: The Princess is cleansing a Tainted Place
\item    -1: The entity was once human, and still thinks in somewhat human ways (Ghosts, some Dreamlanders)
\item    -3: The entity is human, and thinks like a human
\end{itemize}

\begin{myindentpar}{10pt}\textbf{Upgrade: Blood Magic (Tempesta \textbullet)}

During any roll where Light over All applies, the Princess may take a point of resistant bashing damage to add +3 to one roll.\end{myindentpar}


\subsubsection*{Seed of Light (Govern \textbullet\textbullet)}

\noindent Action: Extended, Dexterity + Expression ((20 - Willpower) minutes/roll, threshold = 3 * seeds made)

\noindent Cost: 1 Willpower, 1+ Wisps (special)\\

\noindent The Light exists within the world, within the hearts of all men. However, with will and effort, the Hopeful may calcify Wisps into gem-sized, imperishable Seeds, proof against the ravages of chance. Each Wisp spent on the Charm forms a separate Seed. The Princess does not have to decide how many Seeds to calcify beforehand; after spending the Willpower, she starts to concentrate on her pool of Wisps. Each three successes accumulated allows the Princess to transform one Wisp into a Seed, and she may roll a number of times equal to her dice pool, or until she runs out of Wisps. Extra successes are wasted

The shape of a Seed is a profound expression of its creator's soul, and is heavily influenced by the Invocation (if any) applied in its making. (Applying Legno, for instance, often creates Seeds in the form of living, unchanging flowers.) Any character examining a Seed, if they make a Wits + Occult roll, can recognize a Seed as coming from the same hand as one they've seen before (Invocations are usually clear without a roll). 

To recover the Wisp from a Seed, a character must bring it into contact with their phylactery, and spend a minute in concentration. No actions may be performed while doing this, and the character is at -3 to all Wits-based rolls, so deep is their focus. The Seed glows, and becomes incohesive, melting into their soul, and adding the Wisp to their pool. If the character's Wisp pool is full, the Seed vaporizes and releases the Wisp into the air, where it dissipates.

As tiny fragments of solidified Light, Seeds are incredibly alluring to creatures of the Darkness. Any character with the Darkened template can consume Seeds to regain Willpower, gaining one point of Willpower per Seed eaten. The Darkened can smell out Seeds kept in quantity - they gain a cumulative +1 bonus to all Perception rolls to notice a person carrying Seeds for each Seed above the carrier's Composure, and tend to aim first at opponents carrying the most Seeds. Moreover, any location where large numbers of Seeds are stored can be noticed for miles. For this reason, Alhambran outposts, where they store their misbegotten gains, tend to either be very heavily protected, or to try to move them back to their rain-soaked city as fast as possible. And for the same reason, servants of the Queen of Storms have been known to use captured Seeds as Darkspawn bait.

\begin{myindentpar}{10pt}\textbf{Upgrade: Bereaved (Lacrima \textbullet\textbullet\textbullet)}

The production of Seeds by Alhambrans occurs on an industrial scale. Reduce the time per roll to once per turn. 

As a side effect of applying this Upgrade, the character removes the unique traces of their identity from the Seeds they make. Instead, the Seed forms as one of the seals of the Kingdom, the crown of the Queen of Tears prominent on it. The production of such a Seed is frequently used as a test of identity by an Alhambran outpost sent a new Noble, and documents and packages sent between groups are sealed with wax imprinted with this mark. This leaves unmistakable magical traces, which a character with Lacrima 1 or higher, or the ability to see auras, can detect with a Wits + Occult roll, making forging the seal harder.

\textbf{Upgrade: Militant (Tempesta \textbullet\textbullet or Fuoco \textbullet\textbullet\textbullet)}

One cannot simply wait for the Light to diffuse into one's soul! All of existence is a war against the Darkness, and no soldier of the Seraphic General should be caught without her arms! When creating the Seed, the Noble may choose to make it release its energy quickly. If Tempesta was applied, the Wisp can be recovered from the Seed as a reflexive action, at a cost of 1 resistant Bashing  damage, with no more than skin contact with the Seed. There is no limit to how many Seeds can be tapped in this way per round, beyond the limits of one's well-being.

The followers of the Queen of Swords are less rash, but no less aware of the dangers of the world. By applying Fuoco, they create Seeds that release their Wisp as an instant action.\end{myindentpar}

\subsubsection*{Safety in Mortality (Govern \textbullet\textbullet)}

\noindent Action: Full turn, Resolve + Intimidation

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene, (Consecrated) \\

\noindent A Princess is as much a being of mortality as she is of the Light. Just as the Transformation allows her to switch between these worlds she may push these changes outwards, creating a safe space through which magic cannot enter. The Charm is used on an enclosed space, such as a building or a fenced park - if the Princess needs to protect an area that isn't enclosed, she must mark its border somehow, by (for instance) drawing a chalk line or throwing down a rope. The area must not extend more than (Inner Light x 20) yards in any direction, unless the area is Consecrated.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess makes herself vulnerable to others' magic. Any supernatural power that is normally resisted, when used on her, gets a +1 bonus on its activation roll for 1 day.

    \emph{Failure:} The area gains no protection.

    \emph{Success:} The Princess applies the Warded condition to the target area for one scene; any attempt to direct magic from outside to inside the protected space triggers a Clash of Wills against the Princess' Clash of Wills dicepool at the point this Charm was invoked, and the Princess is aware of any such attempts. If this Charm was invoked as a teamwork action the Primary Actor's Clash of Wills dicepool is used, but all participants are aware of any attempts to breach the Wards. If the enclosed space has the Consecrated Condition, the Charm lasts until the area is no longer Consecrated and the Warded Condition extends to cover the complete Consecrated are.

    \emph{Exceptional Success:} The Charm's protection lasts for a full day.\end{myindentpar}



\subsubsection*{Light's Riposte (Govern \textbullet\textbullet, Fuoco \textbullet)}

\noindent Action: Reflexive and resisted, Wits + Occult - target's Stamina

\noindent Cost: 1 Wisp

\noindent Duration: instant\\

\noindent Those who cast hostile magics at the Princess shall suffer for their temerity. When she is the target of a supernatural effect that she recognizes as such, she may activate the Charm. For each success rolled, the magic's user takes 1 bashing damage. This may be done only once per effect. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Lethal (Fuoco \textbullet\textbullet)}

\noindent Cost: +1 Wisp

The Princess' rebuke grows harsher; for each success rolled, the target takes 1 lethal damage.\end{myindentpar}

\subsubsection*{A Magical Girl's Eyes (Govern \textbullet\textbullet\textbullet)}

\noindent Requires: Reflected Light\\

\noindent Cost: 1 Wisp\\

\noindent Action: Reflexive, Unrolled\\

\noindent Duration: 1 Scene\\

\noindent In her Transformed identity a Princess is an inherently magical being. Her shining heart is comprised of both muscle tissue and solid magic, her fingers are made of flesh and clever little enchantments, her eyes, those are magic too. By spending a Wisp the Princess can see (or smell, or taste or somehow sense) magic. This includes both magical beings, magical items or places, and the presence of lasting magical enchantments. This sense extends as far as she can see with her eyes and can be enhanced with binoculars, a telescope or remote vision Charms, but not over a television or camera.

By rolling Intelligence + Empathy (for a Princess' magic), Science (for a mad scientist's work) or Occult (for anything else) the Princess can also determine what kind of magic she is looking at. She may apply an Invocation to this roll. However the Princess cannot see in any detail. At best she might get something like \textquotedblleft it looks angry" when looking at a werewolf or a werewolf's spell. If the Princess sees the same kind of magic again she can recognise the similarity; to the normal limits of her memory. If the Princess learns that the angry looking person is a werewolf she can conclude that all the other people with the same angry look are also werewolves or their creations.

If she is looking at an active magic effect or magical item she can determine its purpose to a similar level of detail, such as \textquotedblleft protect this building". If the Princess has the Reflected Light upgrades Light Attuned or Dark Attuned she gains their benefits when using Magical Girl's Eyes, if she has Study Inheritance then she only needs to look at a Bequest to learn it's particulars. As with all uses of vision this power is less effective over distance, as a rule of thumb the Princess's ability to analyse magic fades with distance at the same rate as her ability to recognise faces.

This Charm provides no ability to see into Twilight, though if the Princess has some other means of seeing into Twilight it will apply to it's full extent upon the residents of that plane. 

Magical concealment has it's usual effect against Magical Girl's Eyes. The Princess' dicepool for seeing though magical concealment is Wits + Composure, an Invocation may be applied. This roll is Resisted, Contested or otherwise affected by the concealment as per it's usual rules. The usual things that affect perception modify the roll as normal, and if the Princess has reason to be suspicious and intentionally examines a seemingly mundane object for magic she may be given a bonus.

\subsubsection*{Astral Companion (Govern \textbullet\textbullet\textbullet)}

\noindent Action: Extended, Inner Light + Presence (10 minutes/roll, threshold = 3x Dreamlander's Rank or Inner Light)

\noindent Cost: 1 Wisp

\noindent Duration: 1 day or Presence days.

Every Princess can bind herself to a Shikigami, but some Princesses know other ways to invite Dreamlanders to Earth. A Princess with this Charm travels to the Dreamlands and brings a willing Dreamlander back to the threshold of waking, where it can be activated - a task quite similar to binding one's Shikigami, though the Charm does not require a vessel (or allow for one).

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess wakes without bringing the Dreamlander with her; she cannot use the Charm on him again.

    \emph{Failure:} The Princess makes no progress. If she stops rolling before reaching the threshold number, she wakes without bringing the Dreamlander with her.

    \emph{Success:} The Princess makes progress. When she reaches the threshold number, she wakes, and brings the Dreamlander with her in an immaterial state. The Dreamlander gains the Fettered Condition, it is tied to the Princess. When the Charm expires the Dreamlander does not have to worry about Influences or Manifestations, lingering magic means that it can spend one Essence to renew the Condition for another day or travel through the Princess' Crawlspace to return home. 

    \emph{Exceptional Success:} The Princess makes great progress. The Dreamlander's stay in the waking world is prolonged; the Charm lasts for Princess' Presence in days.\end{myindentpar}

When summoned to waking life by this Charm, Dreamlanders' powers are somewhat limited. See the Appendix on the Dreamlands for full rules governing Dreamlanders. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Vesseled}

\noindent Cost: +1 Willpower

The Princess can bind Dreamlanders into physical vessels, allowing them to affect the physical world without worrying about Manifestations for the duration of the Charm. Mechanically this can be treated as a Shikigami without a bond to any Princess (unless they acquire one later of course).

\end{myindentpar}

\subsubsection*{Bequeath (Govern \textbullet\textbullet\textbullet)}

\noindent Action: Extended, Inner Light + Crafts (10 minutes/roll, threshold = 3x Bequest's Merit rating)

\noindent Cost: 1 Wisp/roll, 1 Willpower point or 1 Willpower Dot

\noindent Duration: Session or Indefinite \\

\noindent The Princess binds the form of a Charm into a physical vessel, creating a new Bequest. Acquiring a Charm's form is a quest through her Crawlspace (for a Charm the Princess knows) or the Dreamlands (for one she doesn't). When she has found the form in the Dreamlands, and has a suitable vessel with her sleeping body, she carries the form into her Crawlspace, and standing at the threshold between wakefulness and dreams begins casting Bequeath.

If the Princess spends a Willpower point the Bequest will last for a Session, however if she spends a full Willpower Dot then Bequest lasts Indefinitely. 

Bequeath cannot be used by Sworn or Beacons even if it itself is crafted into a Bequest. The production of new tools for the Radiant is limited by the Willpower of it's Nobility. 

    \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess wakes without transforming the vessel. She can never make the target Charm into a Bequest.

    \emph{Failure:} The Princess makes no progress.

    \emph{Success:} The Princess makes progress. If she reaches the threshold, the Charm merges with and transforms the vessel, becoming a new Bequest.

    \emph{Exceptional Success:} The Princess makes great progress.

Suggested modifiers: vessel resembles the Charm's form (+1 to +3), vessel significantly unlike the Charm's form (-1 to -3)

\textbf{Empowered}

When creating a Bequest a Chosen can embed a gem created by Enduring Beauty as a source of power. If she does so the Bequest has an equipment bonus to its activation roll equal to the Resources value of the gem she used. She may trade two points of the equipment bonus to allow the Bequest to generate 1 Wisp per day into it's own pool. The Charm Study Inheritance will reveal the details of a Bequest's Empowerment but anyone with experience of Bequests will have little trouble figuring it out.

By pressing an Empowered Bequest to the forehead of the gem's original owner, the owner's beauty may be restored; doing this destroys the Bequest beyond repair.

The question that haunts many Nobles is whether using such tools is an endorsement of their creation. Knowingly using an Empowered Bequest, unless the Princess has reason to believe the Gem at its heart was created consensually, is a Belief compromise. There is no modifier to the roll. 

\textbf{Upgrade: Charged}

The new Bequest carries a pool of 10 Wisps, which is initially empty. The Princess must define a duty the Bequest's owner can fulfill to fill its pool. Note that this adds a dot to the Bequest's Merit rating, raising the threshold.

\end{myindentpar} 

\subsubsection*{Ofuda (Govern \textbullet\textbullet\textbullet)}

\noindent Action: 10 minutes of full concentration, Presence + Expression

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The Princess imbues an object with the power to repel a type of supernatural beings, bestowing the Ofuda Condition. Ofuda tend to be small symbolic objects, a short scroll of text or a picture. 

The area affected is a circle surrounding the Ofuda with a radius of 2x Inner Light Yards. The Princess may choose any type of supernatural being she has encountered before, she may also create a blanket prohibition against all Creatures of the Darkness.

If there is already an Ofuda in place the Princess may cast additional invocations of this Charm into the same object to expand the Charm's affects to more kinds of supernatural beings; if she does so the Successes on the origonal invocation apply for every protection. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Exemption}

The Princess may allow a number of trusted individuals, up to her Inner Light, to bypass her protections. Alternately, by adding Commonalty to the roll she may allow a social group to enter unbarred. The Princess may change who is permitted and who is not after the Ofuda is created by casting Ofuda again while touching the imbued Item. This will not change the strength of the defences.

\textbf{Upgrade: Sanctuary}

The Princess may intertwine an Ofuda with Consecrated ground. This both extends its range to cover the entire Consecrated area and extends the duration until the area no longer possesses the Consecrated Condition or until the imbued object is destroyed.

An Ofuda invoked with Sanctuary must be built into the physical structure of the Consecrated ground it protects, even if only by nailing it to the wall. If it is removed from the Consecrated ground the Charm ends.

\textbf{Upgrade: Lasting (Legno 2)}

Cost: +2 Wisps; Duration: 4 x Inner Light hours

The Princess' Ofuda wards lasts for longer, instead of one scene they last for 4 x Inner Light hours.\end{myindentpar}

\subsubsection*{Spirit's Friend (Govern \textbullet\textbullet\textbullet, Legno \textbullet\textbullet)}

\noindent Requires: Light over All

\noindent Action: Instant and contested, Manipulation + Persuasion vs. Resistance + Rank

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

Spirits are dangerous, but they need not be hostile. Mankind is part of the spiritual world too, and the Wilds know well how to move in harmony with their environment. If the Princess wins the contest, the target is irrationally attracted to her for the duration; treat this as the Swooning Condition. 


\subsubsection*{Capitation (Govern \textbullet\textbullet\textbullet, Lacrima \textbullet\textbullet)}

\noindent Requires: Charge

\noindent Action: Instant and resisted, Resolve + Politics - Sanctuary Size

\noindent Cost: 2 to 6 Wisps, Compromise at Belief 4+ with a -3 modifier

\noindent Duration: instant \\

\noindent All humanity ultimately owes allegiance to the Kingdom-which-is-Alhambra. Though they may not follow their oaths, it is still possible to extract the taxes rightfully owed. Like most feudal kingdoms, in Alhambra land is the defining symbol of wealth and the basic tax is on property rather than income. Capitation allows Alhambra to drain Wisps out of the very soil, but at a terrible cost. 

Before casting Capitation the user must choose the Size of the estate they wish to tax, as per the Sanctuary Size scale. A success inflicts the Property Tax condition, draining Wisps from the land. At first the process is slow, but as Wisps come loose it becomes significantly faster. Every week the land produces (Size * weeks active) Wisps. On a Blessed place double the Wisps produced.

The cost in Wisps is 1 + Sanctuary Size of the area affected, so it requires at least two weeks for Capitation to turn a profit. Alhambrans nearly always scout extensively and prepare an enclave to monitor and protect their efforts; Capitation requires daily maintenance, this costs nothing but requires fifteen minutes of work by someone who knows the Charm (or has a Bequest). The Unweaving Charm can also stop Capitation in it's tracks. 

Anyone who knows the Capitation Charm can also gather the Wisps it creates, they must stand inside the affected area and may gain up to Lacrima wisps every five minutes. Bequests containing Capitation can refill their own pool or their user's Wisp pool. \\

\noindent \textbf{Drawback} Draining the Light from the land ruins it. At the end of each week roll the Wisps produced. A success inflicts one point of Taint, what is left behind after Alhambra steals all which is good. On a Blessed place, only roll for Taint after the Beauty is gone. Once there is at least 10 points of Taint there is little left to gain, the Condition ends 24 hours later and any ungathered Wisps are lost. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Supply Line}

Requires: Seed of Light, Bereived 

When the Princess gathers Wisps exposed by Capitation she does not add them to her pool, instead each Wisp becomes a Seed of Light.\end{myindentpar}

\subsubsection*{Purgation (Govern \textbullet\textbullet\textbullet, Tempesta \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Extended, Resolve + Intimidation (5 minutes/roll, threshold: 7 Successes)

\noindent Cost: 1 resistant Aggravated damage, 2 Wisps

\noindent Duration: Lasting \\

\noindent The Princess invokes the power of the Queen of Storms to scour away the Darkness with blood. To use Purgation, the character cuts herself and drips blood from the cut onto a Tainted area. As she continues to invoke Purgation the blood writhes and boils, channelling the endless fury of the Queen of Storms. When she reaches the Threshold the her blood immediately catches alight with green fire. 

The green fire that is created by this Charm is mostly mundane. It spreads or dies like an ordinary fire, it does however burn in both the Tainted Place and the Dark World beneath it. The fire created by Purgation has the heat of a Bunsen burner, it has no supernatural effect on most things but against creatures of the Dark or the physical structure of the Tainted place it has the heat of a chemical fire. What's more the physical substance of the Tainted Place goes up like paper, no matter what it's made from it is completely flammable and has no Durability against the fire. The flame can be put out with mundane or magical means, though it's abundant fuel and effective heat against the Tainted Place make this difficult. It is rare for anything but ash to remain after Purgation is unleashed upon a Tainted Place.

The initial Size of the flame is Torched sized, however given it's supernatural properties it is likely quickly become much bigger. The short of is that once a Princess has burned down a large Tainted Place what is left behind is a large fire which can easily spread elsewhere. If the fire reaches the border of the Tainted place, any flames that cross the border will be completely mundane orange fire.

If the Princess is interrupted she must begin the Charm from scratch; her spilt blood bubbles and boils, evaporating in seconds.


\subsubsection*{Catch a Falling Star (Govern \textbullet\textbullet\textbullet)}
\begin{table}[H]
    \begin{tabular}{|l|l|l|l|l|}
        \hline
        \multicolumn{5}{|c|}{Duration of Suspension}                                         \\ \hline
        Successes                                                & At will    & Improbable & Infrequent & Common  \\ \hline
        1                                                        & 10 minutes & 30 minutes & 1 hour     & 1 day   \\ \hline
        2                                                        & 30 minutes & 1 hour     & 1 day      & 2 days  \\ \hline
        3                                                        & 1 hour     & 1 day      & 2 days     & 4 days  \\ \hline
        4                                                        & 1 day      & 2 days     & 4 days     & 6 days  \\ \hline
        5                                                        & 2 days     & 4 days     & 6 days     & 8 days  \\ \hline
        \multicolumn{5}{|c|}{Each success beyond 5 adds 2 more days to the duration.}        \\
        \hline
    \end{tabular}
\end{table}

\noindent Action: Instant, Wits + Empathy

\noindent Cost: 1 Wisp

\noindent Duration: varies \\

\noindent The Princess delays a Charm's effects. She must touch the intended target, then use another Charm on him; the second Charm does not take effect immediately, instead the target gets the Held Charm condition for a time depending on her successes. She may choose to release the delayed Charm, allowing it to take effect, as an instant action at any time; if she doesn't release it when this Charm expires, the delayed Charm dissipates without effect. Alternately, instead of creating a delayed Charm that she may release herself, the Princess may set a condition that, if met, releases it automatically, to lengthen the time that Charm remains suspended; the more likely the condition is to occur, the longer the suspension lasts.

The Princess must tell the target what will happen when the suspended Charm takes effect, and if she sets a condition, she must tell the target what it is; but she can be as cryptic (\textquotedblleft\, When all eyes turn toward you, you'll find the strength to carry on") or as direct (\textquotedblleft\, Hey, jackass! Try stealing someone's purse again, and you're going to get set on fire!") as she wishes. She can keep up to her Inner Light in Charms suspended at once -- once she reaches that limit, she must release a Charm before she may use this Charm again.

In addition to either method of triggering the Charm the Princess may also set a condition in which the Charm vanishes without activating (\textquotedblleft\, Turn yourself in to the police by midnight or you'll be set on fire!\textquotedblright). 

\begin{myindentpar}{10pt}\textbf{Upgrade: Inanimate}

The Princess can place Held Charms on things other than living beings. She could for example enchant a corrupt lawyer's bag to teleport to her hands with Up In Smoke as soon as someone puts a laptop in it.\end{myindentpar}

\subsubsection*{Resting Place (Govern \textbullet\textbullet\textbullet, Lacrima \textbullet\textbullet\textbullet)}

\noindent Action: Full turn, Presence + Occult (vs Composure + Supernatural Advantage)

\noindent Cost: 2 Wisps

\noindent Duration: Inner Light in days

With access to both a ghost and any object a Raven can bind a new anchor for the ghost, applying the Anchor Condition to a target of her choice. This is temporary and only with great and constant effort can a Princess keep a loved one on this plane, more commonly it is used by the Followers of Tears to position their ghostly retainers where they can be of greatest service to the Last Empress. When used on an existing Anchor Resting Place can apply the Open condition. 

If the target is a living being he may resist the charm by rolling Composure + Supernatural Advantage, inanimate objects have no roll to resist. 

It should be noted that while ghosts can normally teleport to an anchor, the defences around Alhambra prevent them from crossing the boundary of the fortress city.

\subsubsection*{Unweaving (Govern \textbullet\textbullet\textbullet\textbullet)}

\myframe{\textbf{Disciplines, Gifts and Contracts. Oh My!}

\vspace*{6pt}

Can a Princess unravel a Gift, or unpick a Contract? Well no. By default a Princess can only use Unweaving on magic created by Princesses, the Dark and other things found in the Princess books. Even when a Gift is mechanically similar to a Charm they are metaphysically different enough that a Princess cannot unpick the threads and end the magic.

\vspace*{6pt}

This is true, unless you, the Storyteller, decides it is not. Allowing Princesses to undo the magic of other's is certainly an advantage over other creatures, but if all the players are Princesses or the other creatures are given an equivalent ability to undo Charms this might not be a problem. You might choose to allow Unweaving to work against all forms of magic. She rolls Occult (or Science against Geniuses), not Empathy, at say a -2 penalty for targets unrelated to Princesses (waive the Penalty if the Princess belongs to an appropriate Embassy, or make Embassy membership a prerequisite if you prefer).}

\noindent Action: Reactive,

\noindent Instant or Extended

\noindent Dexterity + Empathy (5 minutes/roll, Threshold = Special )

\noindent Cost 2 Wisps\\

To unravel magical defences, to unpick a curse upon a beloved little sister, to tear apart a hostile Charm flying at you. There are many reasons why a Princess might need to unweave the Charms and magic of another. This Charm allows her to do so. The Princess may choose to Invoke this Charm as an Reactive or as an Extended action depending on the difficulty of the task ahead. 

If invoked reactively the Princess grabs hold of the unfinished magic and tries to rip it apart while her opponent tries to hold the magic together. In short, Unweaving lets the Princess trigger a Clash of Wills at any time she wishes.

An enchantment that has been completed and taken hold is tougher. Instead of a Contested Action the Princess must score more Successes than her opponent's Clash of Wills dicepool. She can attempt to grab the magic magic and rip it apart as an instant action, or she can delicately unweave it thread by thread as an extended action. 

Unweaving can only be used against \textquotedblleft magic power\textquotedblright\, abilities with a duration that lasts longer than a Turn. Innate abilities such as Transformation or Hauntings are unaffected. The Princess also needs to be able to touch the magic, usually this means being within the affected area or within arms reach of the target. 

When used against Ephemeral Beings, such as Dreamlanders, Unweaving can be used to undo the effects of Influences and Numina. Unweaving cannot be used to undo Manifestations, it can remove Manifestatinon Conditions if they were created by an appropriate method. For example, Unweaving can remove the Anchor condition if was created with the Charm Resting Place, an Infleunce or a Numina. 

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess gets her magic into a horrible tangle, and is at -2 to perform Unweaving for the rest of the scene.

    \emph{Failure:} The Princess makes no progress.
    
    \emph{Success:} Progress is made, when enough Successes are reached the target magic fall apart.
    
    \emph{Exceptional Success:} In addition to making great Progress, the Princess also learns some detail about the magic's origin, or why this thing was enchanted. Take the Informed Condition.
    
    Suggested Modifiers: The target magic is cast on a human (including Sworn and Princesses) (+2); The target magic is cast on something other than a living being (-2); the target magic is a Charm (+1), the target magic is a Charm and the Princess knows a Charm from the same family (+2), the target magic is a Charm and the Princess knows it (+3); the Princess applies an emotionally appropriate Invocation, such as Fuoco to unpick magic that turns love to loathing or Acqua to remove a curse of ignorance (+2), the Princess applies an emotionally inappropriate Invocation (-2), the Princess applies an elementally appropriate Invocation, such as Acqua or Fuoco to extinguish a magical fire (+2), the Princess applies an elementally inappropriate Invocation (-2).\end{myindentpar}

\subsubsection*{Accept Fealty (Govern \textbullet\textbullet\textbullet\textbullet, Invocation \textbullet\textbullet\textbullet)}

\noindent Action: Extended, Presence + Persuasion (10 minutes/roll, threshold = target's Willpower)

\noindent Cost: 1 Wisp/roll, 1 Willpower dot.

\noindent Duration: Lasting \\

\noindent Through a Ceremonial induction the Princess can invite mortals to join her Court, becoming Sworn. The ceremony is typically held in a relatively quiet and isolated location. This is for pragmatic reasons, as the process of the Charm creates a rather impressive light show. For the Sworn, the ceremony is an enlightening experience, no pun intended. They see the image of the Queen they have chosen to serve, and they feel her magic flowing through them. For a brief moment, they are allowed to touch the Light itself, which leaves behind the smallest spark.

Many Princesses will gladly swear a mortal into their Court as a favour to Princesses who don't know this Charm or belong to another court, in exchange for a Bequest or a favour worth a dot of Willpower. 

\subsubsection*{I am Become Light (Govern \textbullet\textbullet\textbullet\textbullet\textbullet, Fuoco \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Resolve + Intimidation

\noindent Cost: 3 Wisps, 1 Willpower

\noindent Duration: 1 scene \\

\noindent A Blazing crimson light shines forth from the Princess' heart, glowing through her body and Regalia. The Queen of Swords' avatar may walk among things not of the light, and know that they are the ones at the disadvantage.

   \begin{myindentpar}{10pt} \emph{Dramatic Failure:} The Princess' phylactery shatters, and she reverts to mundane form. The normal procedures for obtaining a new phylactery must be followed.

    \emph{Failure:} White light scintillates from the Princess' clothes, but there is no further effect.

    \emph{Success:} The Princess goes through a second transformation, her normal Regalia replaced with ones of even greater purity and a golden light shines out from her heart. The shift releases a burst of the Light that burns away magics alien to it; all supernatural powers not of the Light with fewer successes than the Princess' roll within a radius of Inner Light + successes yards immediately end, if the successes for their activation were less than her successes. Powers that did not require activation remain intact. In addition the Princess gets both the Shining Heart Tilt, with the same activation successes and radius, which bathes the affected area in true sunlight as well as applying her activation successes as a penalty to all supernatural powers not of the Light. Finally Swords' avatar gains the Terrifying Tilt which affects all Creature's of the Dark except the Dethroned.  

    \emph{Exceptional Success:} The extra successes are their own reward.\end{myindentpar} 
    
\subsubsection*{Martyr (Govern \textbullet\textbullet\textbullet\textbullet\textbullet, Tempesta \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Presence + Intimidation + the number of Health Boxes without Aggravated Damage - Inner Darkness + the number of Health Boxes without Aggravated Damage.

\noindent Cost: 2 Wisps, 1 Willpower. Using this Charm is suicide. \\

\noindent The Seraphic General is Hate, and what she hates is The Darkness and the Nobility who betrayed mankind to the Darkness. Most such filth can be found hiding in Alhambra like the cowards they are, but others fell deeper into despair. Their crowns were shattered, their titles stripped from them, they were Dethroned. 

The sad truth is that, much like Princesses, you can't really kill a Dethroned. They reincarnate. Driving a Dethroned away or killing will normally keep it away for a very long time but for a truly permanent solution you have to redeem the Princess it once was. 

This doesn’t sit right with the Court of Storms, they don't believe the fallen deserve redemption, and so they have their own method. Reaching deep into the Dethroned they grab hold of their soul, they incinerate their body and drag the Dethroned's rotten soul into the afterlife.

To use this Charm the Princess must touch their target. Note that after the Dethroned is killed it's body remains for around ten minutes or so, during this time Martyr can be cast and the Dethroned cannot resist the Charm. 

\begin{myindentpar}{10pt} \emph{Dramatic Failure:} The Princess dies for nothing, the Dethroned remains at large. 

    \emph{Failure:} The Princess takes Resistant Lethal Damage equal to the Dethroned's Inner Darkness, and the Dethroned takes Resistant Lethal Damage equal to the Princess' Inner Light. If this kills either of them the Charm dosn't affect what happens next. 

    \emph{Success:} The Princess grabs the Dethroned and both ignite with green fire. In seconds only ash remains. 

    \emph{Exceptional Success:} No additional effect.\end{myindentpar} 

The furies claim that the Dethroned's rotten soul will be burnt to nothing by the Queen's righteous fury while they will remain as a part of the Queen of Storms and lend their strength to her crusade. While there is some evidence that the Furies do join with their Queen, what happens to the Dethroned is unknown. Since no one has kept a record of which Dethroned were killed in this manner they can't even prove it permanently kills Dethroned. 

\subsection*{Inspire}
The Inspire Charm lifts people's hearts, sparks their passions, and exhorts them to action. Only Troubadours have affinity for it.

\subsubsection*{Beginner's Luck (Inspire \textbullet)}

\noindent Action: Instant, Intelligence + Dexterity

\noindent Cost: 1 Wisp

\noindent Duration: instant\\

\noindent  If a thing is worth doing, it's worth doing badly. When the Princess assists in an instant teamwork action, she may activate this Charm instead of rolling the relevant dice pool. Each success on the activation roll becomes a bonus die for the primary actor. In an extended teamwork action The Princess can use Beginner's Luck multiple times, once for each roll. Any bonuses or penalties on the teamwork dice pool also apply to the charm roll, and a dramatic failure penalizes the primary actor's roll as usual.

\begin{myindentpar}{10pt}\textbf{Upgrade: Enduring}

\noindent Cost: +1 Wisp

When assisting in an extended teamwork action, all the Princess' rolls are Intelligence + Dexterity instead of the relevant dice pool.

\textbf{Upgrade: Guided}

Do not apply penalties on the teamwork dice pool to the activation roll.

\textbf{Upgrade: Twinned}

\noindent Cost: +1 Wisp

When the Princess activates the Charm, she also rolls the relevant dice pool, and adds successes from both that roll and the Charm. The pools are separate; any bonuses and penalties apply to both.\end{myindentpar}

\subsubsection*{Hear Me, O Muse (Inspire \textbullet)}

\noindent Action: Instant, Intelligence + Expression

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The Princess calls on the Light for inspiration. If she is Successful she grants the target (which may be herself) the Blessing Condition. The affected trait is \textquotedblleft creating art\textquotedblright. The increase is equal to the Princess' activation successes. 

The blessing also has an end trigger, it vanishes after one applicable action. If the action in question is extended, the bonus applies to all rolls until the task is complete, or the Princess turns her attention to something else; she loses the bonus if she stops the job partway, and doesn't get it back if she resumes it.

\begin{myindentpar}{10pt}\textbf{Upgrade: Cooperative}

\noindent Cost: +1 Wisp

When others assist the Princess (she is primary in a teamwork action) they gain the same bonus on their rolls as she does.\end{myindentpar}


\subsubsection*{Living Image (Inspire \textbullet)}

\noindent Requires: 2 dots in Crafts or Expression, and a speciality in creating art

\noindent Action: Instant, Inner Light + Presence 

\noindent Cost: 1 Wisp, 1 Willpower

\noindent Duration: Indefinite\\

\noindent Artists among the Hopeful have can infuse the Light into their art, and make it bring forth magic. This Charm enchants artwork, turning into a vessel to hold and invoke another Charm. The art to be enchanted may be created through mundane, technological or magical means but it must be a product of the Princess' creativity and it must be designed specifically to carry the chosen Charm. The art is about, means, the Charm it holds, so a wholly or partly finished work on another subject cannot carry the intended Charm.

The Princess first chooses the Charm, Upgrades, and  the precise effects (for example, which emotion the Charm Feel So Close will enhance) she desires. The Princess then creates her art to express the ideas and emotions of the chosen charm, using the normal rules for that. When the artwork is ready the Princess casts Living Image upon it to turn her art into a vessel. 

Once the art is enchanted the Princess may touch it and invoke the appropriate charm to fill the vessel at any time. Record the Princess' activation successes when she charges her artwork, note that Charms that don't require a roll are not compatible with Living Image, also note that Inspire Charms do not require a performance to be placed into a work of art.

When someone takes the time to appreciate her artwork, by viewing it, reading it, or even eating it if that's what is appropriate then the Charm is invoked using the same Successes as the Princess originally rolled. 

\begin{itemize}\item    A Charm that affects the Princess activating it, instead affects the artwork.
\item    When the artwork's Charm requires touching a target, its target becomes someone touching the artwork. This usually means a tactile or taste artistic medium (such as a story written in braille).
\item    When the artwork's Charm affects a target within sight or a specified distance, its target is the closet person currently appreciating the artwork.
\item    When the artwork's Charm affects an area, its target is the artwork's immediate neighbourhood and it affects everyone appreciating the art at the moment of invocation.
\item    When the artwork's Charm is modified by Intimacy, the target is fixed as part of making the artwork, and the art will only invoke it's effects when the targeted person appreciates it.
\item    When the artwork's Charm is modified by Commonalty, the minimum Commonality is chosen when creating the artwork. When the art invokes it's effects when the first person to appreciate it and a group they belong to that meets the minimum Commonality, chosen to affect the maximum number targets. With a Commonality of Casual it will reliably affect everyone appreciating the art at the time the Charm is activated.
\end{itemize}

Living Image lasts until the magical artwork is damaged in such a way as that it no longer provides the desired experience (a painting is visually disfigured, a dress gets torn, etc) or the Princess wishes it; it does not end when the Princess returns to mundane form. Living Image does not end when the artwork's effect is triggered. The Charm contained within the artwork is expended but the artwork itself is still a vessel and the Princesses can simply walk up to her artwork and cast the same Charm again to refill it.

At any one time a Princess may have Inner Light + Belief different works of art enhanced with Living Image. Artwork that has used up it's Charm still counts towards this limit. 

Gems created by the Specchio Charm Enduring Beauty can be used to empower art created by Living Image, doing so requires that the art revolve around a deception of the human form. As these are Brats, it's often a depiction of the Princess creating the Art. 

The gems embedded in the artwork cause it to constantly produce Wisps allowing the art to replenish it's own Charm again and again. A gem worth Resources 3 produces 1 Wisp a day and always rolls two successes on it's internal Charm. A gem worth Resources 5 produces 2 Wisps a day and rolls three success. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Duplicated}

While some methods of creating artwork do not lend themselves to duplication, others are the exact opposite. A story can be photocopied without loosing any of it's artistic value. 

With this upgrade a Princess can convert her artwork into vessels en mass. She could invoke Living Image on a computer document and start printing out copies or she could invoke Living Image on a bowl of cake mixture and start pouring it into individual cupcakes. Each instance of her artwork beyond the first costs one Wisp and all enchanted works must be created within the same scene. In addition each one must be filled with charms independently, though at the Storyteller's discretion the player may be permitted to roll only once to keep the game moving quickly.

Duplicated artwork only counts as a single work towards the Princess' maximum uses of Living Image.

\textbf{Upgrade: Gallery}

Stacks, up to 4

The Princess can now sustain magic in more artwork. Each time she takes this upgrade, she adds two to the number of Living Image activations she may have up at once.

\textbf{Upgrade: Light Attuned}

The Princess may specify that her artwork will only invoke Charms upon Beacons, Princesses, Shikigami, Sworn, or any combination of those three groups. Alternatively, she may specify that her artwork won't affect the Light touched. 

\textbf{Upgrade: Remote}

The Princess may refill her artwork with fresh Charms without being in it's physical presence. She must modify her Charm activation roll by her Intimacy to the artwork itself. 

Remote can be combined with Duplicated, but not easily. Unless a Princess feels different emotions about the various copies of her artwork she will be unable to choose which copy she refills.

\textbf{Upgrade: Dark Attuned (Tempesta \textbullet)}

The Princess may specify that her artwork will only invoke Charms upon Creatures of the Darkness. She may not specify which kinds of creates. 

And yes, with the right Charm it is indeed possible to create artwork that makes Darkspawn feel so bad they explode. After all, emotions are magic. 
\end{myindentpar}


\subsubsection*{Fire on the Mountain (Inspire \textbullet)}

A musical instrument, a microphone, dancing shoes, a pen or some other artistic tool becomes part of the Princess' Regalia. The tool is of excellent make, giving the 9-again quality to mundane Expression rolls within one of her Specialities (fixed when she takes the Charm) when using it, and the Princess may apply an Invocation to increase this bonus. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Quality}

Stacks, up to 3

The Princess' tool becomes superlative. Each time she takes this upgrade, the instrument confers a +1 equipment bonus to mundane Expression rolls within her Speciality.

\textbf{Upgrade: Magical}

The Princess weaves her magic into her chosen art. She can add her instrument's equipment bonus to her Inspire Charms to offset a Commonalty penalty, if she incorporates playing the instrument into the Charm activation. The instrument's bonus will not reduce the Commonalty penalty to less than -0; if a Charm doesn't take the Commonalty modifier, the instrument provides no benefit.

\textbf{Upgrade: Written (Acqua \textbullet\textbullet)}

The Princess performs as well backstage as she does on the stage. She may apply Fire on the Mountain to a second Speciality related to preparing art for Fire on the Mountain's first Speciality: composition for a singer, chirography for a dancer, or something similar. Alternatively she may take a Speciality related to publishing her art, a chef may take a Speciality in cook books and start publishing her recopies. This upgrade may be brought twice for both benefits, given a suitable field of art. 

Often this Upgrade adds a second piece of regalia. A Shakespearian quill pen to go with an Actor's costume. 

\textbf{Upgrade: Entrancing (Fuoco \textbullet\textbullet)}

The Princess' music sways the emotions of all who hear it; she can use this to influence what they do. When she applies Fuoco to a roll to perform, she may grant herself the Blessing Condition. The affected trait is \textquotedblleft Persuasion, on people in her audience\textquotedblright\, and the increase is equal to successes on the roll. The blessing lasts until the current scene ends. 

The Princess can get the bonus from her performance any number of times during the scene, but only once for persuading any specific person. If she makes a speech, she adds the bonus to her Persuasion roll against the whole audience, losing the chance to persuade the members personally.

\textbf{Upgrade: Heartthrob (Specchio \textbullet\textbullet)}

The Princess' performance leaves all who hear it cowed by her manifest superiority, and ready to obey her. When she applies Specchio to a roll to play her instrument, all members of the audience with a composure lower than the Princess' Successes gain the Swooning Condition focused on the Princess.\end{myindentpar}


\subsubsection*{Cooking By the Book (Inspire \textbullet, Acqua \textbullet)}

\noindent Action: Instant, Intelligence + Expression; requires a performance with a variable length. \\

\noindent Cost: 1 Wisps\\

\noindent Duration: One Extended Action or one day.\\

\noindent You gotta do the cooking by the book. You know you cant be lazy.

If something is worth doing, it's worth planning it out first. Before beginning an Extended Action the Princess may invoke Cooking By the Book, doing so takes the same duration as a single roll on the affected Extended Action. 

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess inspires confusion in her targets, for the rest of the Extended Action discard the first Success of every roll (after rerolling). If it is a teamwork action this only applies to the primary actor. 
 
 \emph{Failure:} Nothing happens
 
 \emph{Success or Exceptional Success:} The Princess inspires clarity and confidence, the target knows exactly what they need to do. Halve the duration between rolls for the affected extended action. This does not stack with other effects that reduce the time between rolls.
 
 \textbf{Upgrade: Collective}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group that can see or hear her. \end{myindentpar}


\subsubsection*{Feel So Close (Inspire \textbullet\textbullet)}

\noindent Action: Instant and Contested, Manipulation + Expression vs Composure + Supernatural Advantage; requires 1 minute of performing. 

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The Princess puts on a performance that inspires an emotion of her choice in its hearer. If the Princess applies an Invocation to the Charm, the emotion inspired must be appropriate for that Invocation.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess inspires the wrong emotion, the storyteller chooses something likely to cause the Princess problems. The target gains a +2 bonus to all actions in line with it their emotion, and taking a -2 penalty to actions opposed to it.
 
 \emph{Failure:} Nothing happens
 
 \emph{Success:} The target feels the desired emotion, gaining a +2 bonus to all actions in line with it their emotion, and taking a -2 penalty to actions opposed to it.
 
 \emph{Exceptional Success:} The bonus and penalty increase to +3. 
 
 \textbf{Upgrade: Collective}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group, applying the Commonalty modifier. The member with the highest Composure + Supernatural Advantage contests for the group.\end{myindentpar}

\subsubsection*{Carry On (Inspire \textbullet\textbullet)}

\noindent Action: Instant, Presence + Expression, 1 minute/roll; requires 1 minute of performing. 

\noindent Cost: 1 Wisp

\noindent Duration: Lasting \\

\noindent With all our love we cant go wrong

The Princess performs for a target who can see or hear her, and her performance bolsters the target's will. The Princess cannot use the Charm on herself.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The target's apathy or fatigue infects the Princess, loose a point of Willpower. 
 
 \emph{Failure:} Nothing happens
 
 \emph{Success or Exceptional Success:} The target gains a point of Willpower, each Princess can only give any person one point of Willpower a day with this charm. 
 
 \textbf{Upgrade: Collective}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group that can see or hear her, using the Commonalty modifier. \end{myindentpar}

\subsubsection*{Fighting Evil by Moonlight (Inspire \textbullet\textbullet)}

\noindent Action: Instant, Stamina + Expression; requires 1 minute of performing. \\

\noindent Cost: 1 Wisp\\

\noindent Duration: 1 scene\\

Winning love by daylight.

School, friends, royal duties, sleep, choose three. If the Princess has chosen to skip on sleep then a Troubadour can inspire her to keep going through the night, or day as the case may be.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The target takes an addtional -1 peanlty to all actions. 
 
 \emph{Failure:} Nothing happens
 
 \emph{Success:} The Princess removes all the effects of fatigue from her target for one scene. It doesn’t remove the fatigue itself, and when the Charm ends the target must contend with all the usual effects of tiredness as though she had never been reinforced by magic.
 
 \emph{Exceptional Success:} The effects last two scenes. 
 
\textbf{Upgrade: Collective}

Cost: +1 Wisp

The Princess may use the Charm on a social group, applying the Commonalty modifier. \end{myindentpar}

\subsubsection*{For the First Time (Inspire \textbullet\textbullet)}

\noindent Action: Instant, Composure + Expression; requires one minuet perf\\

\noindent Cost: 1 Wisp\\

\noindent Duration: 1 scene\\

At least I've got a chance.

Doing something for the first time can be scary, but with a stirring performance the Princess banishes those fears. 

\begin{myindentpar}{10pt}
\emph{Dramatic Failure:} The Princess becomes convinced that she can handle any challenge the world might throw at her. She takes the Overconfident Condition.

\emph{Failure:} The Princess doesn’t give any confidence to her target.

\emph{Success:} For each activation success, the target may ignore unskilled penalties on actions using one Skill for the rest of the scene. The Princess chooses which Skills are affected. Some actions (e.g. flying an airplane) impose an unskilled penalty on anyone lacking an appropriate speciality; the Charm removes that penalty too, so if a young Princess has a pressing need to fly an airplane this is the Charm to know.

\emph{Exceptional Success:} Extra successes are their own reward.

\textbf{Upgrade: Collective}

Cost: +1 Wisp

The Princess may use the Charm on a social group, applying the Commonalty modifier.\end{myindentpar}

\subsubsection*{You Must Remember This (Inspire \textbullet\textbullet, Acqua \textbullet)}

\noindent Action: Reflexive and resisted, Intelligence + Expression - target's Composure; requires 1 minute of performing. 

\noindent Cost: 1 Wisp

\noindent Duration: Lasting\\ 

\noindent The fundamental things apply as time goes by.

Words the Princess speaks long remain in the memory. When she is speaking to the target, or guiding his attempt to learn something, she may use the Charm to help him remember what she's saying. The target gains the Blessing condition, the affected trait is \textquotedblleft remembering what the Princess is saying\textquotedblright\, and the increase is equal to her Successes. The Blessing also has an ending trigger, it only applies for one roll.

The Princess may use the Charm to help her own memorization rolls, but to do so she must still repeat the facts she's memorizing aloud.

\begin{myindentpar}{10pt}\textbf{Upgrade: Collective}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group that can see or hear her, using the Commonalty modifier. The member with the highest Composure resists for the group.\end{myindentpar}

\subsubsection*{Giggle at the Ghostly (Inspire \textbullet\textbullet, Aria \textbullet)}

\noindent Action: Instant, Wits + Empathy; requires 1 minute of performing. 

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent Bullies, tyrants, even the horrors of the Dark \textendash\, all these lose their terrors if you can just show them their absurdity. The Princess may use this Charm on a single person within sight.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess frightened of the target, taking two Cursed conditions. The first inflicts a -2 penalty on all social actions with the target for the rest of the scene, the second makes it impossible to use this Charm on the target for the rest of the day. 

    \emph{Failure:} The target retains his ability to frighten.

    \emph{Success:} The target laughs at his fears, he gains the Protective Blessing Condition, the affected trait is \textquotedblleft causing fear\textquotedblright\, and the decrease is equal to the Princess' successes.

    \emph{Exceptional Success:} Laughing at his fears completely robs them of their power, the target also gains the Steadfast Condition. 

\textbf{Upgrade: Collective}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group whose members can see her, applying the Commonalty modifier. If the Charm succeeds, all the members take the bonus; on a dramatic failure, the Princess is penalized when opposing any member of the group.

\textbf{Upgrade: Swift (Aria \textbullet\textbullet)}

The Charm becomes Reflexive; the Princess may use it when a target tries to frighten or overawe, and imposes the penalty on that attempt if she succeeds. Subtract the Presence of whoever is trying to cause fear from the roll.\end{myindentpar}


\subsubsection*{Queen's Sorrow (Inspire \textbullet\textbullet, Lacrima \textbullet\textbullet)}

\noindent Action: Instant and contested, Manipulation + Intimidation vs. target's Composure + supernatural advantage

\noindent Cost: 1 Wisp, Compromise at Belief 6+ with a -1 modifier

\noindent Duration: 1 scene \\ 

\noindent The Princess speaks to another, and drains his strength of conviction. If she wins the contest, the target gains the Willpower Blocked Condition. He can't spend Willpower to add a bonus to his rolls until the scene ends. He can still spend Willpower for any other purpose the rules and his abilities allow. The Condition has an ending trigger: If the target gains a Willpower point, he rerolls his Composure + supernatural advantage, and defeats the Charm if he gets more than the activation successes.

\begin{myindentpar}{10pt}\textbf{Upgrade: Heavy (Lacrima \textbullet\textbullet\textbullet)}

The target also loses the ability to bolster his Defense or Resistance Attributes by spending Willpower.\end{myindentpar}

\subsubsection*{Look Into the Future (Inspire \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Presence + Pursuasion; requires 5 minute of performing. \\

\noindent Cost: 3 Wisps 1 Willpower\\

\noindent Duration: Lasting \\

\noindent Tell me what you see.\\ 

\noindent I really need to know now, is there a place for me?

The Princess makes a stirring performance about the future she wants to build, and the audience's place in it. Through her art she inspires people to help build that future. 

   \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess shakes her confidence in her goals. She takes the Cursed tilt, the next roll she makes using Belief as a dicepool takes a -2 penalty. 

    \emph{Failure:} The Charm does not activate.

    \emph{Success or Exceptional Success:} The target may choose to take an additional Aspiration (other Nobles may choose a Dream instead). This Aspiration must reflect the Beliefs of the Princess invoking this Charm. The player, the target's player and the storyteller should work together to choose an Aspiration. 
    
    Aspirations and Dreams created by this Charm last until they are fulfilled or until the target chooses to stop perusing them. Under no circumstances can anyone gain more than one Aspiration or Dream from Look Into the Future. Nor can a Princess acquire both an Aspiration and a Dream.   

\textbf{Upgrade: Collective}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group that can see or hear her, applying the Commonalty modifier. Each member may take a different Aspiration, providing it is appropriate.\end{myindentpar}

\subsubsection*{Rousing Song of Heroism (Inspire \textbullet\textbullet\textbullet, Fuoco \textbullet\textbullet)}

\noindent Action: Instant, Presence + Persuasion; requires 5 minute of performing. \\

\noindent Cost: 2 Wisps\\

\noindent Duration: 1 scene \\

\noindent Who are you? \\

\noindent Just a man or a super-man?

The will of a person the Princess can see becomes nearly insurmountable. If successful the target gains the Inflamed Will Condition, with one flame per success. When spending a Willpower they may spend a flame for an additional +2 (for a total of +5 per Willpower) or +1 when defending (for a total of +3)

\begin{myindentpar}{10pt}\textbf{Upgrade: Intense}

The target gains a further +1 when spending Willpower, for a total of +6 dice, or +4 to Defense or a Resistance Attribute.

\textbf{Upgrade: Do it for us}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a distant target, applying the Intimacy modifier.\end{myindentpar}

\subsubsection*{Give Me Love (Inspire \textbullet\textbullet\textbullet, Legno \textbullet\textbullet)}

\noindent Action: Instant, Resolve + Persuasion vs Composure + Supernatural Advantage

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent Give me peace on Earth. With their focus on harmony and understanding the Wilds are never entirely comfortable with controlling another's opinions. Rather than making another want peace a Princess of Clubs might use this Charm to prevent violence, allowing her to pursue peace in more traditional ways: with hearts and voices.

This Charm cannot be used if the Princess has attacked anyone or used a combat Charm within the Scene.

   \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess somehow manages to revert the Charm on herself and takes the Peace on Earth Tilt. She also gains the Curse Tilt which inflicts -1 Defence from slightly constricting plant life. What's more any enemies in the area know it.

    \emph{Failure:} The Charm does not activate.

    \emph{Success:} Ghostly flowers appear on the target, vines wrapping around their limbs. The target gains the Tilt Peace on Earth. 

    \emph{Exceptional Success:} The Princess also gets a flash of insight into why her target wishes to fight. She gains the Blessing Condition, it grants +1 on any social rolls with the target for the rest of the scene.

\textbf{Upgrade: Collective}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group that can see or hear her, applying the Commonalty modifier. Each member contests the effect independently.\end{myindentpar}

\subsubsection*{Name Your Poison (Inspire \textbullet\textbullet\textbullet, Tempesta \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Presence + Expression vs Resolve + Supernatural Advantage; requires 5 minute of performing. \\

\noindent Cost: 3 Wisps, 1 Willpower\\

\noindent Duration: Six hours.\\

If you don't name your poison; I'll have to get the boys in.

The magic of Tempesta unerringly seeks out the weaknesses of the Outer Darkness, the Furies tend to favour the obvious weaknesses of unarmoured joints and vital organs but properly used Tempesta can be more diverse than that.

To perform this Charm the Princess must have some object or person and name a way Creatures of the Darkness might fulfil their Vice using that thing. For example she could use herself and the possibility of eating her flesh. The Princess makes a performance mocking the Darkness for the perverted Vice she's targeting and then rolls Presence + Expression, if she's using an unwilling living being as the focus he may roll Resolve + Supernatural Advantage to Contest the Princess' magic.

If the Princess wins any contest then every Darkspawn in Inner Light miles with a Composure lower than her successes instantly gains the Depraved condition; the only way they can get their fix is by indulging their vice on the Charm's focus. The Darkspawn don't gain the ability to sense the location of the Charm's focus but they'll know it when they see it. What's more the focus' location is revealed to them for an instant at the moment the Charm is cast.

The Princess then sits down with a big gun and waits for the monsters to come to her. 

\subsubsection*{Notice Me (Inspire \textbullet\textbullet\textbullet, Aria \textbullet\textbullet)}
\noindent Action: Instant, Presence + Subterfuge, modified by Commonalty\\

\noindent Cost: 1 Wisp\\

\noindent Duration: successes in turns\\

\noindent I'm drawn to you and I can't look away

Sometimes it's necessary to provide a spectacle to draw people's attention away, while an accomplice does the real work. The Princess uses this Charm on the members of an organization who can see her, applying the Commonalty modifier for them.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess can't get attention from her targets to save her life. For the rest of the scene, her Social actions aimed at the targets take a penalty equal to her Aria.

\textbf{Failure:} The Princess fails to distract her targets.

\textbf{Success:} For one turn per activation success, and as long as the targets can see the Princess, their eyes remain fixed on her and everything else slips from their notice. Outside of combat, the targets must succeed on a Perception roll to notice the presence of any other person or object beyond the most generic description (e.g. "man", "woman" or "child"; "car" or "truck"; "chair, "desk" or "table") and anyone who actively conceals themselves will succeed automatically. The Charm is less effective during a fight, when people are keyed up and attentive, but even then the targets take -1 to their Defense against anyone but the Princess, and fail to notice anyone who doesn't attack them. However, the Princess herself can't avoid attention - any use of Stealth immediately ends the Charm.

\textbf{Exceptional Success:} The targets perceive nothing but the Princess. Their Perception rolls are penalized by her dots in Aria.\end{myindentpar}

\subsubsection*{Tame the Savage Beast (Inspire \textbullet\textbullet\textbullet, Legno \textbullet\textbullet)}

\noindent Action: Instant and resisted, Presence + Animal Ken - target's Resolve

\noindent Cost: 1 Wisp

\noindent Duration: successes in turns \\

\noindent With soft persuasion or a sharp command, the Princess makes a beast heed her.

    \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The target animal turns hostile, and will attack the Princess if it can.

    \emph{Failure:} The Charm has no effect.

    \emph{Success:} The animal carries out one order for each success. Each order may specify a single action, that involves at most one object; \textquotedblleft bite that man" and \textquotedblleft bring me the keyring" are each one order, \textquotedblleft bite those two men" and \textquotedblleft bring me the keyring and the gun" are each two orders. Descriptions of things in your orders are limited by the animal's understanding. Finally, no animal will obey a suicidal order, and making a domesticated animal break its training is much more difficult than commanding a wild animal; the Storyteller should impose penalties on the activation roll for such orders. (On the other hand, making a domesticated animal follow its training gives bonuses.)

    \emph{Exceptional Success:} After following multiple orders, the animal acquires a habit of obedience. For the next day it gains the Inverse Blessing Condition, the affected trait covers further use of this Charm as well as mundane efforts to tame or train it. The modifier is +1 dice.

\textbf{Upgrade: Swarming}

\noindent Cost: +1 Wisp

The Princess can give orders to a whole swarm of creatures, if none of them exceed Size 2: insects, small birds, or rats. All the animals in the swarm must belong to the same species.\end{myindentpar}

\subsubsection*{Don't Stop Believing (Inspire \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Extended, Presence + Persuasion; requires 10 minute of performing. 

\noindent Cost: 1 Wisp, 1 Willpower

\noindent Duration: 1 day \\

\noindent The Princess’ song revive in her target memories of lost innocence. 

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The target takes the Blocked Willpower Condition.

    \emph{Failure:} The Charm has no effect.

    \emph{Success or Exceptional Success:} If she succeeds the target's gains the Blessing Condition. The affected trait is either Belief or Integrity and it is increased to a number chosen by the Princess before she begins her performance, to a maximum of the Princess' own Belief. The Storyteller has discretion on whether this Charm affects alternative Integrity traits other than Belief.  

It should be noted that magically enhanced Integrity or Belief does not protect against Breaking Points or Compromises (the modifier to the roll for high or low Belief is affected). If Princess with Belief five that is magically enhanced to 7 fails a Compromise roll the result is Belief four magically enhanced to six. 

\textbf{Upgrade: Collective}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group that can see or hear her, applying the Commonalty modifier. Each member contests the effect independently.\end{myindentpar}

\subsubsection*{No Choice, No Hope (Inspire \textbullet\textbullet\textbullet\textbullet, Lacrima \textbullet\textbullet\textbullet)}

\noindent Requires Queen's Sorrow

\noindent Action: Instant, Manipulation + Intimidation - target's Resolve

\noindent Cost: 2 Wisps, 1 Willpower, Compromise at Belief 3+ with a -4 modifer

\noindent Duration: 1 scene \\

\noindent The Princess' voice acquires the blighting and consuming quality of the Darkness, sapping the wills of those who hear it and bringing them under her sway for a time. For each activation success, the target loses a point of Willpower, feeling drowned in apathy. If the target still has Willpower left when the Princess stops casting, he rolls Wits + Composure at -5 to realize that the despair they felt was not natural. If the target runs out of Willpower during the casting, he gains the Suggestible Condition; until he regains Willpower or the Charm ends.

On a dramatic failure, the target instantly realizes the Princess is responsible for the moment of despair and reacts with outrage. The Charm immediately ends (though lost Willpower is not restored) and she cannot cast it on that target for a full 24 hours.

\begin{myindentpar}{10pt}\textbf{Upgrade: Collective (Lacrima \textbullet\textbullet\textbullet\textbullet)}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group, applying the Commonalty modifier. The member with the highest Resolve resists for the group. On a dramatic failure, all those in the group, and any group they belong to, are immune to the Charm for 24 hours.\end{myindentpar}

\subsubsection*{Consumed With Hate (Inspire \textbullet\textbullet\textbullet\textbullet, Tempesta \textbullet\textbullet\textbullet)}

\noindent Action: Instant and resisted, Manipulation + Persuasion

\noindent Cost: 2 Wisps, 1 resistant lethal damage

\noindent Duration: Tempesta turns \\

\begin{myindentpar}{10pt}\noindent With only a few words, the Princess can cause a person's rage to boil over, driving him uncontrollably to lash out. On reaching the threshold, the target gains the Blessing Tilt which grants +2 on all rolls to inflict violent harm on another, and suffers the Cursed Tilt which inflicts -1 penalty to all other rolls. 

What's more, once the threshold is reached the target flies into a rage. The Princess has no control over who is attacked but someone will be.

    \emph{Dramatic Failure:} The Princess goes too far in her rhetoric; the target sees her as a crazy person he needs to get away from. None of the Charm's effects take hold.

    \emph{Failure:} The Princess gets nowhere with inciting the target's rage, but may continue.

    \emph{Success:} The Princess makes progress inciting the target.

    \emph{Exceptional Success:} The Princess makes great progress inciting the target.

\textbf{Upgrade: Collective (Tempesta \textbullet\textbullet\textbullet\textbullet)}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group, applying the Commonalty modifier. The member with the highest Composure resists for the group, and your threshold is his Composure.\end{myindentpar}

\subsubsection*{Jumping Jack Flash (Inspire \textbullet\textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Presence + Expression, modified by Commonalty

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: concentration\\ 

\noindent You were born in a crossfire hurricane. And you howled at your Ma in the driving' rain. But it's all right now.

The Princess puts on a performance that inspires people to the heights of their abilities -- and beyond. Everyone in the group she uses the Charm on gets the Blessing Condition, it applies to every possible roll, but it has an end trigger: The Blessing only applies for one roll. The Charm is, essentially, a Teamwork roll that applies to everyone. 

The effects only last as long as the Princess continues performing, spending her action for a turn. Every member of the target group gains the bonus once, but if they haven't used it by the time she finishes performing the bonus is used.

\subsubsection*{Everything is Awesome (Inspire \textbullet\textbullet\textbullet\textbullet\textbullet)}

\noindent Requires: Beginner's Luck

\noindent Action: Instant, Wits + Manipulation

\noindent Cost: 2 Wisps

\noindent Duration: Concentration \\ 

\noindent  Everything is cool when you're part of a team!

The Princess brings focus to a group working for a common goal. Activate this Charm before assisting in a teamwork action. For each success, one secondary actor contributes his successes directly to the goal, instead of adding dice to the primary actor's roll. The Princess must be a secondary actor -- the Charm does not work if she is alone, directing the team, or not contributing. The Princess must remain performing for the entire duration of the Extended Action, which limits this Charm to tasks that can be completed in a reasonable time.  

\subsubsection*{Wearing a Heavy Crown (Inspire \textbullet\textbullet\textbullet\textbullet\textbullet, Terra \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Presence + Persuasion, modified by Commonalty; requires a fifteen minuet performance.

\noindent Cost: 1 Wisp, 1 Willpower

\noindent Duration: 1 scene \\

\noindent To be the Queen of Hearts' avatar is to become the leader people need, the leader the people may one day deserve. The Princess assumes that role and leads any who will follow to greatness. This Charm is used on members of a social group who are willing to work at the Princess' direction, or towards a goal that she has set. She can let others come up with plans (what leader doesn’t have advisers?) but the final decision of what the members do must rest on her shoulders alone.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess proves herself unworthy of leadership and may not use Terra again for 11 - Belief days. 

    \emph{Failure:} The Princess cannot claim a crown. The Charm fails.

    \emph{Success:} The Princess undergoes a second transformation; a heavy crown appears upon her brow. All members of the target group gain the Light's Unity condition, the maximum is equal to the Princess' activation successes. When multiple people with Light's Unity from the same Princess perform a Teamwork action together the primary actor gains a bonus equal to the number of secondary actors multiplied by the total number of actors (only counting actors with Light's Unity from the same Princess) or the condition's maximum. Whatever is lower. 
    
    The Princesses leadership also motivates her followers to stand together in the face of adversity, they also get the Blessing Condition. The affected trait is Resolve, when it is used to resist being dissuaded from following the Princess' plan. The increase is the difference between the recipient’s Resolve and the Princess' Presence (if they have a higher Resolve than the Princess' Presence they get no blessing). 

    \emph{Exceptional Success:} Everyone blessed by this Charm also gains a free point of Willpower\end{myindentpar}

\noindent Drawback: The Princess gains the Burden of Leadership Condition: She ains 8again on Sensitivity rolls when the victim or the perpetrator is someone blessed by this Charm. In addition, if anyone blessed by this Charm causees her to face a Belief compromise through setting a Bad Example, she does not halve or double the perpetrator's modifier when making her own Comrpomise roll.

She also gains the Invocation Lock condition keyed to Terra. 

\subsection*{Learn}
The Learn Charm confers knowledge, and reveals what has been hidden. Only Seekers have affinity for it.

\subsubsection*{Data Wizard (Learn \textbullet)}

A portable computer becomes part of the Princess’ Regalia. Any mundane Computer task the Princess performs with this computer within one of her specialities (chosen when she takes the Charm) gets the 9-again quality, and she may apply an Invocation to these tasks. The computer can store data in practically unlimited quantities, has adapters to connect to any computer networks available where the Princess lives, and reads from or writes to all common forms of removable media she can find. The Princess still has to supply passwords to gain access to a network, or else defeat the network’s security. The Princess cannot connect to supernatural networks, unless they were specifically created to be compatible with The Light or mundane networks. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Versatile}

Stacks, up to 2 

The Princess' computer has a greater variety of programs. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for mundane Computer rolls covered by any of the added specialities. 

\textbf{Upgrade: Advanced}

Stacks, up to 3

The Princess' computer is excellectly engineered. It gives her a +1 equipment bonus on mundane Computer rolls each time she takes this upgrade.

\textbf{Upgrade: Remote}

The Princess can connect her computer to any other she wishes over a magical Intimate link. Spend a Wisp and roll Intelligence + Computer - Intimacy, an Invocation may be applied. This does require an Intimacy link directly to a computer, but Hope Engineers do love their gadgets. Once the Princess is connected the link functions as though the Princess was standing next to the target machine and connected to it by wire. She still needs to defeat any relevant security, but might bypass security that's location on a separate machine. Unless the Princess has the Discrete or Traceless Upgrades, system administrators trying to trace the Princess' connection will see something like \textquotedblleft direct magical link" from their administrative tools. They may not believe what they see. 

\textbf{Upgrade: Crawling (Acqua \textbullet\textbullet)}

Since the 1960s humanity has been hard at work making information and knowledge available to all. It is a beautiful act of humanity and it sits at a Princess' fingertips. 

The Princess' computer includes it's own software for searching the web, software that search based on the emotional intent behind the Princess' questions. She may spend a Wisp, roll Acqua + the computer's equipment bonus to gain the Informed Condition For most topics this takes between one and ten minutes to find, read, and digest new information. Exceptionally complicated topics like rocket science might take significantly longer.

The web crawler can only find publicly available information, but this includes information on the deep web. It can normally register itself for websites and even defeat basic tests that check the viewer's humanity. It can't access paid content for free, but it might ask the Princess to buy an article if there's no equivalent information available for free. 

\textbf{Upgrade: Fishing (Acqua \textbullet\textbullet)}

The Princess' computer monitors networks constantly, looking for scraps of data she might need. Once in a scene, the Princess may roll Acqua + the computer's equipment bonus when confronted by something outside her normal experience; success means her computer's trawl for data has found a relevant article or post on the Net, and brings it to her attention. The roll follows the rules for the Encyclopedic Knowledge merit (p. 109) except for the dice pool and it is not limited to one topic.

\textbf{Upgrade: Discrete (Aria \textbullet\textbullet)}

When the Princess is connected to the internet her computer automatically routes her connections through a network of proxies that inflicts a -Aria penalty to all attempts to trace her. Despite it's supernatural origins this is a purely mundane countermeasure.

\textbf{Upgrade: Traceless (Aria \textbullet\textbullet)}

When the Princess' computer is connected to a mundane network it automatically sends pulses of magic along with mundane data, rewriting electronic logs to cover the Princess' tracks. Mundane methods cannot track the Princess, the trail simply isn't there, unless the Princess slips up and posts useful information to a website. Supernatural methods still function, at a -Aria penalty. 

Drawback: By it's very nature this magic is hidden, a Princess using A Magical Girl's Eyes takes a -Aria penalty to spot magic rushing through an internet cable, however such defences can be overcome. If the Princess connects to or her signal passes through a supernaturally defended computer she may trigger all sorts of alarms by inadvertently trying to hack the logs. In short, Traceless trades strong protection from mundane tracing for an increased risk of supernatural tracing. \end{myindentpar}

\subsubsection*{Keen Observation (Learn \textbullet)}

\noindent Action: Permanent \\

\noindent When the Princess transforms, she becomes keen-eyed, missing no detail when she fixes her attention. She gets the 9-again quality on mundane Investigation rolls within one of her specialities (chosen when she takes the Charm) and may apply an Invocation to those rolls.

\begin{myindentpar}{10pt}\textbf{Upgrade: Alert}

The Princess' keen perception becomes a matter of reflex. Whenever an Invocation applies at no cost, the Princess adds it to her Perception rolls based on sight and hearing. If more than one Invocation applies at no cost, the Princess uses the highest of them. She may also apply an Invocation when listening for a target while blind.

\textbf{Upgrade: Versatile}

Stacks, up to 2

The Princess becomes perceptive in more situations. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for mundane Investigation rolls covered by any of the added specialities.

\textbf{Upgrade: Enigmatic (Acqua \textbullet\textbullet)}

Mundane riddles and mysteries pose no obstacle to the Princess. When she applies Acqua to rolls to crack enigmas or solve puzzles halve the time taken for each roll.\end{myindentpar}

\subsubsection*{Know Name (Learn \textbullet)}

\noindent Cost: 1 Wisp\\

\noindent Action: Reflexive, Unrolled\\

\noindent When a Princess looks at someone, she learns their name. Under most circumstances this Charm is unrolled, the Princess looks at someone and one name just feels right or she sees a floating name tag. However some characters have multiple names. They might go by a different name in different languages, most people have at least one screen name on the internet, and some people have a more deceptive reason for dual identities. In these cases the Princess learns what the target personally considers to be their name. Against Princesses this Charm will of course provide the name of the Princess' current identity no matter how strongly she identifies with her other name. 

If somebody uses supernatural veils to hide their name the Princess may need to oppose the roll with Wits + Empathy, an Invocation may be applied, or make a Clash of Wills depending on the effects of the defensive power.

Know Name cannot work on recordings, drawings or photographs. However it works fine over live video or Charms that allow remote viewing. 

\subsubsection*{Liberal Artist (Learn \textbullet)}

\noindent Action: Permanent \\

\noindent When the Princess transforms, she remembers her schooling and reading in her favorite field with a crystalline clarity. She gets 9-again on mundane Academics rolls within one of her specialities (fixed when she learns the Charm) and may apply an Invocation to those rolls.

\begin{myindentpar}{10pt}\textbf{Upgrade: Memorious}

The Princess' memory for general facts grows nearly as sharp as her knowledge of her chosen subject. While transformed, she may apply an Invocation to rolls to memorize or remember.

\textbf{Upgrade: Versatile}

Stacks, up to 2

The Princess' gift for scholarship extends to more fields. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for mundane Academics rolls covered by any of the added specialities.

\textbf{Upgrade: Librarian (Acqua \textbullet\textbullet)}

The Princess finds what she wants in a library as easily as in her own home. When she applies Acqua to Academics research rolls she halves the time taken for each roll. 

\textbf{Upgrade: Autodidact (Fuoco \textbullet\textbullet)}

The Princess burns through books and records at great speed, her usual reading speed is multiplied by Fuoco. \end{myindentpar}

\subsubsection{Natural Philosopher (Learn \textbullet, Acqua \textbullet)}
Action: Permanent\\

\noindent The Light illuminates secrets of the natural world. When the Princess transforms, she gets the 9-again quality on mundane Science rolls within one of her specialities (fixed when she takes this Charm) and may apply an Invocation to those rolls.

\begin{myindentpar}{10pt}\textbf{Upgrade: Versatile}

Stacks, up to 2

The Princess' eye teases out knowledge of various kinds. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for mundane Science rolls covered by any of the added specialities.\end{myindentpar}

\subsubsection*{Passion's Light (Learn \textbullet)}

\noindent Action: Instant, Unrolled

\noindent Cost: 1 Wisp

\noindent Duration: One scene \\

\noindent The Princess perceives the emotional state of the people around her. Most Princesses see a wash of colour around their bodies but others have been known to smell emotions, see floating messages or see floating emoticons. 

While Passion's Light is active the Princess can perfectly perceive the emotional state of anyone around her. At any time the player may ask what emotion a character is feeling most strongly and the Storyteller or that  player must answer truthfully. If the Princess wants to examine closer she may roll Wits + Empathy, an Invocation may be applied, and ask one of the following questions per success: 

\begin{itemize}
 \item How strongly is he feeling an emotion? 
 \item What is causing a particular emotion? 
 \item Have the character’s emotions been chemically or supernaturally manipulated? 
 \item What is the character’s Virtue?
 \item What is the character’s Vice?
\end{itemize}

\begin{myindentpar}{10pt}\textbf{Upgrade: Unmasking}

The Princess can recognize supernatural beings by their aura's unusual appearance. A Princess' aura, for instance, is connected to nearby people that she cares about by ribbons of aura and appears to shed light in her vicinity -- things and people near her reflect her current colour, in addition to any aura they have themselves. \end{myindentpar}

\subsubsection*{Scenes Falsehood (Learn \textbullet)}

\noindent Action: Instant and resisted, Wits + Subterfuge vs Composure + Supernatural Advantage

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The Princess develops an additional sense that can sniff out lies and dishonesty.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Charm fails, but the Princess believes it has worked, and thus will believe the target implicitly, unless and until he says something she knows is not true.

    \emph{Failure:} The Charm fails, but the Princess is aware of the failure.

    \emph{Success:} Whenever the target says something he doesn't believe, the Princess perceives the falsehood automatically. The Charm detects the underlying emotions behind untruths, any attempt at deceit or factual assertions made in conscious ignorance also ping her new sense. Most Princesses who make frequent use of this Charm develop habits of asking people how they know something or how confidant they are to filter out honest mistakes. 

    \emph{Exceptional Success:} The Princess' nose catches subtle misleadings as well as direct falsehood; when the target's statements are true but significantly incomplete, she will know that something has been left unsaid.

\textbf{Upgrade: Collective}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group, using the Commonalty modifier. The member with the highest Composure resists for the group.

\textbf{Upgrade: Unwitting}

When the Princess detects a lie, she rolls Wits + the activation successes on the Charm as a reflexive action. If she succeeds, she gains a hint of the truth the target is concealing; on an exceptional success, she learns exactly what the target knows of the subject of his lie.

\textbf{Upgrade: Alert (Aria \textbullet)}

When the Princess detects a lie, she gains additional insight into the liar's motive for deception. For example, she could smell the difference between a lie told out of envious malice and one told out of fear, or tell the difference between a sleazy propagandist and a dedicated, noble spy.

\textbf{Upgrade: Guilty (Terra \textbullet)}

When the Princess detects a lie, the liar experiences a strong pang of guilt, and finds it far harder to deceive again. He gains the Cursed condition for the scene, this reduces all Subterfuge rolls by the Princess' Activation Successes. Further lies in the scene do not increase the penalty.

\textbf{Upgrade: Remote (Acqua \textbullet)}

The Princess' sense can now function on technological communications, from the humble pen to real time video-conferencing (no Upgrade is required for Charm based magical communications). A Princess cannot detect truth or falsehood from any message over a month old. 

\textbf{Upgrade: Righteous (Tempesta \textbullet)}

When the Princess detects a lie, she may punish the liar with impunity. If she attacks the liar as her next action, he may not apply Defense to resist the attack.\end{myindentpar}

\subsubsection*{Fishing Expedition (Learn \textbullet, Acqua \textbullet)}

\noindent Action: Instant and resisted, Resolve + Empathy - target's Resolve

\noindent Cost: 1 Wisp

\noindent Duration: instant \\

\noindent  Dipping a hand into another's thoughts, you draw out a bit of treasure. On touching your target, you learn one fact he knows and wishes to conceal. Which fact you learn is chosen by the Storyteller.

\subsubsection*{Love's Beacon (Learn \textbullet, Fuoco \textbullet)}

\noindent Action: Instant and resisted, Presence + Empathy - target's Resolve

\noindent Cost: 1 Wisp

\noindent Duration: instant \\ 

\noindent  A true love illuminates the beloved, and you see it by that light. On touching your target, you learn the name and appearance of the person or thing he most cares for.

\subsubsection*{Second Glance Wrongness (Learn \textbullet\textbullet)}

\noindent Requires: Scent Falsehood

\noindent Action: Reflexive, Resolve + Composure - power's activation successes

\noindent Cost: none

\noindent Duration: 1 turn \\

\noindent Sometimes magic gets you good. The Enlightened are all too aware of that. Sometimes your mind can be wrapped in irrational fear by the Dark-Spawn hanging from the ceiling, pale-faced, sometimes the warrior of Storms can drive you into a frenzy, some things can pass by invisible. Princesses learn, though, to listen to the subtle wrongness that they get when their senses are being messed with, and it's possible to stoke the radiance within, to burn away the clouds that fog the mind.

Whenever the Princess' mind is influenced or controlled by a supernatural power, the player may declare this Charm Activates and roll Wits + Composure - the power's activation successes. (Innate abilities of supernatural beings which work by influencing the mind subtract the being's supernatural advantage.) 

This Charm may only be rolled once per scene. 

    \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess is so utterly fooled by the deceit that her mind is rendered susceptible to follow-up blows. She takes the Cursed condition, inflicting a -3 penalty to realise she is under a supernatural compulsion. This lasts for a day. 

    \emph{Failure:} Nothing happens.

    \emph{Success:} A distorted perception wavers for a moment, showing what it conceals; an imposed emotion falters, revealing the Princess’ true feelings; a compulsion falls slack, and is disclosed as instilled by another. The Princess may spend 1 Willpower point to bypass it for that action - penalties don’t apply, compulsions don’t restrict her

    \emph{Exceptional Success:}  The power holding the Princess’ mind slips. During the Princess’ next turn, she ignores its effects on her, without spending Willpower.\end{myindentpar}

\begin{myindentpar}{10pt}

\textbf{Upgrade: Meditative (Legno \textbullet\textbullet\textbullet)}

When the Princess sees through an illusion she may opt to enter a tranquil state instead of breaking free for a turn, the same Willpower cost applies. If the Princess chooses tranquillity she remains still, unmoving and unthinking, for Legno minutes. This is often enough for the Princess to fail at whatever crime she was forced to attempt. 

If the Princess is under an effect with a limited duration, the time she spends tranquil does not count towards the duration.

\textbf{Upgrade: Unbroken (Lacrima \textbullet\textbullet\textbullet\textbullet)}

The Darkness around Alhambra is hungry, eroding substance despite the best efforts of the True Kingdom to tame it. The Hopeful of that city learn to do the same to effects that would control them. When rolling against supernatural influence treat the effect's activation successes as though they were Lacrima successes lower, to a minimum of zero.\end{myindentpar}

\subsubsection*{Weight of Memory (Learn \textbullet\textbullet)}

\noindent Action: Extended, Intelligence + Investigation (10 minutes/roll, threshold = 4) 

\noindent Cost: 1 Wisp 

\noindent Duration: Instant \\

By concentrating on her innate sensitivity, the Princess may analyze the traces of past good deeds that has made a place Blessed. She sits and meditates within a Blessed area, or walks slowly through it, considering what her Light-touched senses tell her; if she should be attacked while concentrating, the Charm fails and she learns nothing. If a Princess uses the Charm again on a Blessed area within a week, she takes a -2 penalty for each past attempt in that period. 

  \begin{myindentpar}{10pt}  \emph{Dramatic Failure:} The Princess either becomes convinced that the area is not Blessed after all, or attributes to it a Blessing it does not really have. 

    \emph{Failure:} The Princess makes no progress analyzing the Blessed area. 

    \emph{Success:} The Princess begins to understand the Blessed area. On reaching the threshold, the Princess learns either the Size and approximate boundaries of the Blessed area, or one of the Blessings it grants to those of good will within it. The Princess may continue rolling after reaching the threshold the first time; each time she reaches a multiple of the threshold, she discovers another Blessing, or else that there is nothing more to learn. 

    \emph{Exceptional Success:} If the Princess next sleeps in the Blessed area, add +2 to the Beauty roll for sleeping there. This bonus is not cumulative. 

    \textbf{Upgrade: Tainted}
    
    The Princess' sensitivity detects the tracks of human sin, as well as those of virtuous acts. She may use the Charm to examine a Tainted area.

    \emph{Dramatic Failure:} The Taint reacts to the Princess' examination. The Princess must make a corruption check. 

    \emph{Failure:} The Princess makes no progress analyzing the Tainted area. 

    \emph{Success:} The Princess begins to understand the Tainted area. On reaching the threshold, she discovers either its Size and approximate boundaries, or one of its Curses as well as the history behind that curse. Each time she reaches a multiple of the threshold she learns another Curse, or that there is no more to be learned. If the Princess learns all the Curses associated with a particular Foci she learns of that Foci.

    \emph{Exceptional Success:} The next time the Princess is Haunted by the Tainted area, her dicepool is reduced by 1. This bonus is not cumulative. 
	
	\textbf{Upgrade: Rapid (Tempesta \textbullet)}
	
	Prerequisite: Tainted
	
	When the Princess is examining a Tainted Place she only requires ten turns (30 seconds) per roll.
	
\end{myindentpar}
\subsubsection*{Watchful Mind (Learn \textbullet\textbullet)}

\noindent Action: Instant, Intelligence + Investigation, modified by Intimacy

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene or 1 day \\

Like a bird to its nest, the Princess finds her way unerringly to another person.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess gets an entirely wrong idea of her target's location. Until the scene ends or she actually sees the target, she is convinced he is somewhere chosen by the Storyteller that is not where he really is.

    \emph{Failure:} The Charm has no effect.

    \emph{Success:} For the rest of the scene, the Princess knows the direction and rough distance from herself to the target.

    \emph{Exceptional Success:} The Princess retains her fix on the target's location for 1 full day.

\textbf{Upgrade: Visionary}

When finding the target, the Princess also gets a moment's glimpse of him and his surroundings.

\textbf{Upgrade: Passionate}

\noindent Cost: +1 Wisp

Requires: Passion's Light

When the Princess first finds the target, she also gets a moment's glimpse of his aura, as if the had used Passion's Light in his presence. \end{myindentpar}

\subsubsection*{Pierian Spring (Learn \textbullet\textbullet, Acqua \textbullet)}

\noindent Action: Instant and resisted, Intelligence + Empathy - target's Composure

\noindent Cost: 1 Wisp

\noindent Duration: Instant \\

\noindent As the Princess touches her target's bare skin, she learns how much he has drunk from the wells of knowledge. The Princess may use the Charm on this target again, but later activations during the scene take a cumulative -1 penalty.


\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Charm misleads the Princess. The Storyteller gives a false rating for one or more of the target's Skills; the Princess will believe the target has the stated ratings unless confronted with clear evidence contradicting them. Further uses of the Charm on the target won't reveal such evidence - the Princess must discover her mistake by other methods. She may not use the Charm on this target for the rest of the scene.

\emph{Failure:} The Princess learns nothing of her target. She may not use the Charm on this target for the rest of the scene.

\emph{Success:} The Princess gains flashes of insight into her target's education and mental training. The Storyteller must answer one question from the following list truthfully for each activation success:

\begin{itemize}
 \item One of the target's Mental Skills or specialities
 \item A Merit representing knowledge (e.g. Encyclopedic Knowledge) or access to knowledge (e.g. Contacts, Library).
 \item A subject which the target teaches. 
 \item The name or description of one person who taught the target something of importance to him. 
 \item The name or description of one person whom the target is currently educating or has educated, significantly forming their mind and character.
 \item The nature of the relationship between teacher and student,(e.g. the advisor for his doctoral thesis).
\end{itemize}

\emph{Exceptional Success:} The Princess gains considerable insight into her target's mental training.

\textbf{Upgrade: Personal (Acqua \textbullet\textbullet)}

The Acqua Invocation favors any exercise of the intellect. The Princess may look for insight into the target's character and abilities, so far as these resonate with the Acqua Invocation or the credo of the Queen of Diamonds, or flaws which impair his reason. Add the following to the list of questions the Princess may ask.\end{myindentpar}

\begin{itemize}
\item The target's Intelligence, Wits or Resolve.
\item Any Mental Merit that reflects an innate ability, such as Good Time Management.
\item A mental disorder or other non-supernatural mind affecting Condition. 
\end{itemize}


\subsubsection*{For Want of a Nail (Learn \textbullet\textbullet, Aria \textbullet)}

\noindent Action: Instant and resisted, Wits + Empathy - target's Resolve

\noindent Cost: 1 Wisp

\noindent Duration: Instant\\

\noindent As the Princess touches her target's bare skin, the moments when his life took strange turns become apparent to her. The Princess may use the Charm on this target again, but later activations during the scene take a cumulative -1 penalty.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Charm misleads the Princess. The Storyteller describes an event involving the target that never happened; the Princess will believe in the vision unless confronted with clear evidence contradicting them. Further uses of the Charm on the target won't reveal such evidence - the Princess must discover her mistake by other methods. She may not use the Charm on this target for the rest of the scene.

\emph{Failure:} The Princess learns nothing of her target. She may not use the Charm on this target for the rest of the scene.

\emph{Success:} The Princess gains flashes of insight into the drastic changes her target has undergone. The Storyteller must answer one question from the following list truthfully for each activation success:

\begin{itemize}
\item The time and place of an event that turned the target's life to a course he did not expect
\item One detail of what happened during that event
\item The name or description of one person who was involved in that event
\end{itemize}

\emph{Exceptional Success} The Princess gains considerable insight into events that changed the target.

\textbf{Upgrade: Personal (Aria \textbullet\textbullet)}

The Aria Invocation favors those who can handle surprises, good or bad, with a smile. The Princess may look for insight into the target's character and abilities, so far as these resonate with the Aria Invocation or the credo of the Queen of Spades. Add the following to the list of questions the Princess may ask.
\begin{itemize}
 \item The target's Wits, Dexterity or Manipulation.
 \item A surprise the target is planning to spring upon another. 
 \item How the target is likely to react to a given surprise.
\end{itemize}\end{myindentpar}

\subsubsection*{Love's Beacon (Learn \textbullet\textbullet, Fuoco \textbullet)}

\noindent Action: Instant and resisted, Intelligence + Empathy - target's Resolve

\noindent Cost: 1 Wisp

\noindent Duration: Instant\\

\noindent True love illuminates the beloved. The Princess touches her target's bare skin to learn something of the people he most cares for. The Princess may use the Charm on this target again, but later activations during the scene take a cumulative -1 penalty.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Charm misleads the Princess. The Storyteller describes a vision that gives a quite wrong idea of the target's affections; the Princess will believe in the vision unless confronted with clear evidence contradicting it. Further uses of the Charm on the target won't reveal anything that refutes the vision - the Princess must discover her mistake by other methods. She may not use the Charm on this target for the rest of the scene.


\emph{Failure:} The Princess learns nothing of her target. She may not use the Charm on this target for the rest of the scene.
\emph{Success:} The Princess gains flashes of insight into her target's loves. The Storyteller must answer one question from the following list truthfully for each activation success:

\begin{itemize}
\item The name or description of one person the target loves or has loved
\item The nature of the target's love - marital, romantic, familial, comradely, etc.
\item How the beloved feels about the target, to the best of his knowledge.
\item Where the beloved is most likely to be, again to the target's knowledge.
\end{itemize}

\emph{Exceptional Success:} The Princess gains considerable insight into her target's loves.

\textbf{Upgrade: Personal (Fuoco 2)}

The Fuoco Invocation is brightest in people's loves, but the fire prized by the Queen Errant burns in more than the bonds of affection. The Princess may look for insight into the target's character and abilities, so far as these resonate with the Fuoco Invocation or the credo of the Queen of Swords. Add the following to the list of questions the Princess may ask.

\begin{itemize}
 \item The target's Virtue(s).
 \item The target's current Willpower.
 \item The target's Intelligence, Strength or Presence.
 \item A trait that inspires, or helps inspire, the target to heroics. Anything from a distressed damsel to a code of honour. 
 \item A trait that causes, or helps cause, the target to fall in love. 
 \end{itemize}\end{myindentpar}

\subsubsection*{Scent of Irises (Learn \textbullet\textbullet, Legno \textbullet)}

\noindent Action: Instant and resisted, Intelligence + Empathy - target's Composure

\noindent Cost: 1 Wisp

\noindent Duration: Instant\\

\noindent The Princess learns how much her target is at peace with himself, and what might disturb that peace, by touching his bare skin. The Princess may use the Charm on this target again, but later activations during the scene take a cumulative -1 penalty.


\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Charm misleads the Princess. The Storyteller describes an act the target really has no objection to performing; the Princess will believe the target will refuse to perform that act unless confronted with clear evidence he has done so. Alternately, the act described can be one the target won't do, in which case the Princess believes that he will. Further uses of the Charm on the target won't reveal anything that refutes the delusion - the Princess must discover her mistake by other methods. She may not use the Charm on this target for the rest of the scene.

\emph{Failure:} The Princess learns nothing of her target. She may not use the Charm on this target for the rest of the scene.

\emph{Success:} The Princess gains flashes of insight into her target's moral scruples. The Storyteller must answer one question from the following list truthfully for each activation success

\begin{itemize}
\item The target's Vice.
\item One act which would put the target's Integrity (or equivalent trait) at risk.
\item The name or description of one person or thing for which the target would risk bodily harm or moral degeneration to protect.
\end{itemize}

\emph{Exceptional Success:} The Princess gains considerable insight into her target's moral scruples.

\textbf{Upgrade: Personal (Legno \textbullet\textbullet)}

The Legno Invocation blesses a calm mind, an enduring body, and communion with all living things. The Princess may look for insight into the target's character and abilities, so far as these resonate with the Legno Invocation or the credo of the Queen of Clubs. Add the following to the list of questions the Princess may ask.

\begin{itemize}
 \item  The target's Resolve, Stamina or Composure
\item A Skill or speciality that helps the target live harmoniously in any situation: Crafts, Medicine, Survival, Animal Ken, Empathy or Socialize, or one appropriate speciality of any Skill
\item A Merit representing physical health (any Physical Merit with a Stamina prerequisite) or mental stability (e.g. Common Sense, Meditative Mind)
\item The name or description of one animal the target cares for.\end{itemize}\end{myindentpar}

\subsubsection*{No Man is an Island (Learn \textbullet\textbullet, Terra \textbullet)}

\noindent Action: Instant and resisted, Manipulation + Empathy - target's Composure

\noindent Cost: 1 Wisp

\noindent Duration: Instant\\

\noindent \textit{"No man is an Island, entire of itself; every man is a piece of the Continent, a part of the main ..."}

The Princess sees what links her target to the mass of his society when she touches his bare skin. The Princess may use the Charm on this target again, but later activations during the scene take a cumulative -1 penalty.


\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Charm misleads the Princess. The Storyteller describes a vision that associates the target with a social group he has no connection to; the Princess will believe in the vision unless confronted with clear evidence contradicting it. Further uses of the Charm on the target won't reveal anything that refutes the vision - the Princess must discover her mistake by other methods. She may not use the Charm on this target for the rest of the scene.

\emph{Failure:} The Princess learns nothing of her target. She may not use the Charm on this target for the rest of the scene.

\emph{Success:} The Princess gains flashes of insight into her target's social standing. The Storyteller must answer one question from the following list truthfully for each activation success:

\begin{itemize}
\item An organization in which the target has Status, and the degree of that Status (AKA Merit dots)
\item The name or description of the target's immediate superior in his organization
\item The name or description of the target's Retainer, or a person immediately subordinate to the target in his organization
\item The name or description of one of the target's Allies, and the degree of debt between them (AKA Merit dots)
\end{itemize}


\emph{Exceptional Success:} The Princess gains considerable insight into her target's social standing.

\textbf{Upgrade: Personal (Terra \textbullet\textbullet)}

The Terra Invocation favors all aspects of human sociability. The Princess may look for insight into the target's character and abilities, so far as these resonate with the Terra Invocation or the credo of the Queen of Hearts. Add the following to the list of questions the Princess may ask.
\begin{itemize}
\item The name of an organization the target has great respect for. 
\item The target's Presence, Manipulation or Composure.
\item One of the target's Social Skills or specialities.
\item Any of the target's Social Merits.\end{itemize}\end{myindentpar}

\subsubsection*{Tisiphone's Call (Learn \textbullet\textbullet, Tempesta \textbullet)}

\noindent Action: Instant and resisted, Wits + Empathy - target's Composure

\noindent Cost: 1 Wisp

\noindent Duration: Instant\\

Injuries must be discovered and avenged, Taint must be rooted out. When touching the bare skin of her target, the Princess learns how he has suffered, and who to pursue with Furious justice. The Princess may use the Charm on this target again, but later activations during the scene take a cumulative -1 penalty.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Charm misleads the Princess. The Storyteller describes a false vision of the target being injured, by people who are actually innocent; the Princess will believe in the vision unless confronted with clear evidence contradicting it. Further uses of the Charm on the target won't reveal anything that refutes the vision - the Princess must discover her mistake by other methods. She may not use the Charm on this target for the rest of the scene.

\emph{Failure:} The Princess learns nothing of her target. She may not use the Charm on this target for the rest of the scene.

\emph{Success:} The Princess gains flashes of insight into her target's enemies and tormentors. The Storyteller must answer one question from the following list truthfully for each activation success:

\begin{itemize}
\item The name or description of someone who has harmed the target - physically, mentally or socially
\item The nature of one harm harm done to the target
\item Where a person who harmed the target is most likely to be, to the target's best knowledge
\item The name or description of a creature of Darkness the target has encountered.
\end{itemize}

\emph{Exceptional Success:} The Princess gains considerable insight into her target's enemies.

\textbf{Upgrade: Personal (Tempesta \textbullet\textbullet)}

The Tempesta Invocation encourages all attempts to fight injustice. The Princess may look for insight into the target's character and abilities, so far as these resonate with the Tempesta Invocation or the credo of the Queen of Storms. Add the following to the list of questions the Princess may ask.
\begin{itemize}
\item A description of one of the target's favourite weapons, or the full stats for the target's Empty Hand, Kensai or Levinbolt Charm. 
\item The target's Brawl, Firearms or Weaponry Skill, or one appropriate speciality of those Skills. 
\item A Merit that helps the target on the field of battle (e.g. a Fighting Style)\end{itemize}
\end{myindentpar}
                                         

\subsubsection*{Mirror Mirror (Learn \textbullet\textbullet, Specchio \textbullet\textbullet)}

\noindent Action: Instant, Inner Light + Investigation - Intimacy.

\noindent Cost: 1 Wisp or 2 Wisps

\noindent Duration: 1 Scene\\

\noindent With this trick a Princess of Mirrors can look into one mirror and see out another. Choose one person, the Princess will see out of whichever mirror gives the best viewpoint of that person. If she spends a second Wisp then both mirrors will show each other (this is usually used with the Upgrade I hear you to create magical phones). The Intimacy modifier is of course measured to the person, not the mirror. 

The Princess is limited by the quality of the two mirrors used, a low quality mirror that gives a bad reflection gives a low quality image.

\begin{myindentpar}{10pt}\textbf{Upgrade: I Hear You}

The Princess can also hear through mirrors. If a mirror gives a bad picture it also gives bad audio.

\textbf{Upgrade: On The Wall (Specchio \textbullet\textbullet\textbullet)}

The Princess does not have to look for a specific person, she can see out of any mirror she wishes. Perhaps a mirror she secretly placed overlooking that Darkspawn's lair. The Intimacy modifier applies to the place she wishes to see, or the mirror she's looking out of. Whichever gives the lower penalty.

\textbf{Upgrade: Who's the Fairest in the Land? (Specchio \textbullet\textbullet\textbullet\textbullet\textbullet)}

Cost +1 Wisp.

The Princes asks a mirror a question to which the answer must be a person and cannot require precognition to determine. \textquotedblleft Who murdered Miss Daisy?", \textquotedblleft Who snitched on me to the teachers?" are good examples. \textquotedblleft How do I break into the Alhambran stronghold?", \textquotedblleft Who will win the student election?" are bad examples.

The Storyteller should answer in good faith to the best of her ability by presenting a glimpse of a scene that answers the question. Creative interpretation of the question and other low tricks should only be used on a Dramatic Failure.

Unlike other uses of Mirror Mirror, this upgrade does not make use of the Princess' connection to her target, but draws answers directly from the tapestry of fate. This means you do not apply an Intimacy modifier. On the other hand you only get to watch for 1 turn per success. 

\end{myindentpar}

\subsubsection*{Moving Finger (Learn \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Inner Light + Investigation

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The Princess mentally describes an object. She becomes aware of the location of the nearest object matching the description within 25 yards and may increase the range by taking a penalty to the dice roll at a rate of 25 yards per die. Mundane concealment cannot defend against this Charm. The description must be phrased in terms of the object's composition and form, not its significance or intended use. For example, \textquotedblleft audiotapes", \textquotedblleft letters in my father's handwriting", and \textquotedblleft weak places in the wall" all work; \textquotedblleft incriminating evidence", \textquotedblleft letters about my father", and \textquotedblleft something that will help me escape" do not. A Princess can find only one object at a time; if she activates Moving Finger when she already has it active, the first use ends immediately.

\begin{myindentpar}{10pt}\textbf{Upgrade: General}

\noindent Cost: +1 Wisp

The Princess becomes aware of every object matching the description within range. She can find objects matching only one description at a time.

\textbf{Upgrade: Significant (Acqua \textbullet\textbullet)}

The Princess may describe an object by its meaning. For example, she can find documents about a specific subject in a wall of file cabinets, or search the scene of a murder for clues to the killer's identity.

Note: The presence of Taint, and the property of being a focus of Taint, is considered part of an object's meaning, so applying Significant allows the Charm to find a Tainted area's focus.\end{myindentpar}


\subsubsection*{Genius Loci (Learn \textbullet\textbullet\textbullet, Legno \textbullet\textbullet)} 

\noindent Extended, Manipulation + Occult - Gauntlet Strength (5 minutes/roll, threshold = twice Sanctuary Size)

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent Places, especially buildings, have their own sort of life; as they age and people care for them, they acquire a distinctive Spirit and a voice that speaks in creaking boards or rustling leaves. With careful attention and a touch of magic, the Princess can rouse a place’s spirit and listen to its voice. When activating the Charm, the Noble meditates inside the place she wants to listen and speak to. 

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess rouses the place’s spirit, but offends it. Until she leaves it, a curse of ill luck dogs her; all her actions suffer a -1 penalty. If she returns at any time during the next day, she suffers the same penalty until she leaves again. 

\emph{Failure:} The Princess cannot hear the place’s spirit yet. 

\emph{Success:} The Princess makes progress in waking the place’s Spirit. When she reaches the threshold, the Spirit is fully roused and communicates with her in a fashion only she
understands (patterns of creaks, flickering in the lights, etc.) In essence the Princess applies a the Reaching Manifestation Condition onto the Spirit of the local area and temporally grants it a Numina that allows it to hear the and understand the Princess' voice and to send messages which the Princess alone will understand. However magical abilities may allow others to eavesdrop on the conversation and translate. 

\emph{Exceptional Success:} The place’s spirit finds the Princess agreeable. Her she presents a First Impression one level higher than she otherwise would have. \end{myindentpar}

\subsubsection*{Unearth the Foundations (Learn \textbullet\textbullet\textbullet, Terra \textbullet)}

\noindent Requires: Passion's Light

\noindent Action: Extended and resisted (1 turn/roll, threshold = 4), Composure + Empathy modified by Commonality.

\noindent Cost: 1 Wisp

\noindent Duration: instant \\

\noindent The Princess watches a social group from afar, seeing how they fit together. When she reaches the threshold she asks the Storyteller one of the following questions. 

    \begin{itemize}\item What is one of the group's common causes.
    \item How the group is organised (mailing lists, phone tree, weekly meetings, etc).
    \item Who leads the group. 
    \item How the group is led (democracy, autocracy, do-ocracy, etc).
    \item Why people join the group, if there are common reasons.
    \item Does the group work well together.
    \end{itemize}

\subsubsection*{Psychic Impression (Learn \textbullet\textbullet\textbullet, Terra \textbullet)}

\noindent Action: Instant, Intelligence + Crafts

\noindent Cost: 1 Wisp

\noindent Duration: 1 turn \\

\noindent By holding an object in her hands, the Princess is able to catch a glimpse of the emotional impressions left behind on it, by significant events it was used in. With one success, this Charm grants her a fleeting vision of the most emotionally significant event the object was involved in within the past week; each additional success doubles the range of time she can see into. Especially important events, such as the marriage proposal a ring was used for, may be able to be seen years after they occurred at the Storyteller's discretion. Using this Charm on a bullet might show a vision of the shooting it was used for, a painting may show the emotional state of the artist who created it, etcetera. The vision lasts between three and thirty seconds, and appears to the Princess' eyes as if she were at the event in question -- it's up to her to interpret what she sees.

\begin{myindentpar}{10pt}\textbf{Upgrade: Lasting}

\noindent Cost: +1 Wisp

\noindent Duration: 1 scene 

The vision the Princess receives includes the context of the significant event. She sees a full scene of events, to which the key event serves as a climax. The time it takes her to experience this scene is the same as the time it originally took, and while the vision lasts she enters a meditative trance, only vaguely aware of your immediate surroundings; she forgoes Defense until the Charm ends. If something happens near her, the Princess rolls Wits + Composure - 3 to end the Charm prematurely; if she takes damage, the Charm ends immediately.

\textbf{Upgrade: Specific (Terra \textbullet\textbullet)}

The Princess can look for events other than the most significant one. In a repeated use of the Charm, she takes a penalty equal to the number of events she has already seen from the target object to see visions of an event she hasn't seen before (-1 for the second event, -2 for the third, and so on.) Repeating a vision she has seen already is at no penalty, though it may require more successes if enough time has passed by.\end{myindentpar}

\subsubsection*{Reflected Portents (Learn \textbullet\textbullet\textbullet, Specchio \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Composure + Investigation

\noindent Cost: 1 Wisp, 1 Willpower \\

\noindent How does the Queen of Mirrors know who is the true heir? Simple, she can see the future. Or maybe not, since none of her many True Hairs fulfilled their supposed destiny. Regardless of the truth surrounding the Lightbringer's mysterious Queen, it is a fact that the Invocation of Specchio unlocks powers of precognition beyond the dreams common to all Enlightened.

To perceive the mysteries of time and space the Princess decides which question she wishes to ask, she has to ask about a single person's future. \textquotedblleft Will I be crowned the prom queen?\textquotedblright\, or \textquotedblleft when will I next be attacked is ok?\textquotedblright. The princess could even ask \textquotedblleft who will next attack me\textquotedblright\, because that is part of her personal timeline but she could not ask \textquotedblleft who will be the next Miss America\textquotedblright.

The Princess doesn't have to ask about herself, she could ask who will next attack anyone. All she needs is a mirror positioned so she can see the subject of her question within. 

There is a modifier to the roll based on it's temporal proximity, because of this the Storyteller should always roll for Reflected Portents. A smart player can learn much from just the modifer.

\myframe{ \textbf{Temporal Flux}

    Within a day: 0
    Within a week: -1
    Within a month: -2
    Within a year: -3
    Within five years: -4
    Within 10 years: -5
    Every additional ten years: an additional -1} 

   \begin{myindentpar}{10pt} \emph{Dramatic Failure:} Guided by Fate, or perhaps an unwelcome hint from her own subconscious the Princess sees a horrifying vision. Such as the brutal murder of a close friend. Like all prophecies it's not guaranteed to come true, but she still needs to make a Sensitivity roll.

    \emph{Failure:} The future remains unclear, either nothing happens or the Princess gets a completely accurate vision of a clear blue sky sometime in the future. Or the depths of space, or tv static.

    \emph{Success:} After a few moments the mirror fades to reveal a vision of the future. The player asks one question per Success which the vision will answer. Both sight and sound are provided by the mirror, though both are limited by the quality of the mirror. Anyone looking at the mirror (which doesn't have to be the Princess, if she turns the mirror away after the Charm takes effect) can see the vision. Visions revealed in Reflected Portents are entirely true and accurate, but may nevertheless change for the future remains in flux. Strange beings move outside of Fate, time travellers occasionally change history, even the Princess' vision of the future may introduce new variables into the timeline; perhaps allowing her to escape a horrible fate.

    \emph{Exceptional Success:} Extra Successes are their own reward.\end{myindentpar}

The Princess can only invoke this Charm on the same event once per day. Additionally she cannot learn anything from the past or the present (defined as the current scene). If the Princess asks about a past or present event roll as normal. On a Success reveal that it has already happened but give no further details. If the question has multiple answers; such as asking who will I marry, for someone likely to marry many times, choose the soonest event as defined by the dicepool modifier. If there are multiple events within the same time period favour big and \textquotedblleft noticeable\textquotedblright\, events.

\begin{myindentpar}{10pt}\textbf{Upgrade: Distant (Specchio \textbullet\textbullet\textbullet\textbullet)}

The Princess can prophecies about a distant target by adding Intimacy to the roll. She must name who she is targeting before rolling.

\textbf{Upgrade: What will be? ( Specchio \textbullet\textbullet\textbullet\textbullet\textbullet)}

The Princess no longer needs to name a specific person to scry against. She can instead ask a freeform question like \textquotedblleft where will the next Tainted Place in this town appear?\textquotedblright If more than one person, place or other fits the question then the Charm favours the lowest dicepool modifier from temporal distance. If there are multiple possibilities at the same modifier, the Charm favours big and \textquotedblleft noticeable\textquotedblright\, events. \end{myindentpar}

\subsubsection*{Dire Warning (Learn \textbullet\textbullet\textbullet\textbullet, Fuoco \textbullet\textbullet\textbullet)}

\noindent Action: Reflexive, Wits + Composure

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: instant \\

\noindent The Princess sees a vision of immediate catastrophe, with barely enough time to stop it. The last actions taken by other characters in the current scene, up to the activation successes or the Princess' last action (whichever is less) did not really happen; they occurred only in a prophetic vision. A shouted warning allows a character whose action was \textquotedblleft undone" to choose a different action when their turn comes. If an action is not affected by the Princess' foreknowledge, because all the relevant circumstances are unchanged, its result is the same as the \textquotedblleft vision" of it; do not reroll the dice. If the Princess' last action was undone, the Charm's use replaces that action in the real order of events; if not, the Charm's use is her action in the current turn.

\subsubsection*{Zone of Truth (Learn \textbullet\textbullet\textbullet\textbullet, Terra \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Presence + Investigation

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: 1 scene \\

\noindent The Princess enchants her immediate area, making deception impossible. This Charm creates the Zone of Truth Condition, with an area with a radius of Inner Light x 10 feet. On an exceptional success the Condition is forceful. 

\subsubsection*{Books in Running Brooks (Learn \textbullet\textbullet\textbullet\textbullet\textbullet, Acqua \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Intelligence + Academics

\noindent Cost: 3 Wisps, 1 Willpower

\noindent Duration: 1 scene \\

\noindent ... finds tongues in trees, books in the running brooks, sermons in stones, and good in everything.

The Queen of Diamonds is a scholar without peer, and her avatar has all knowledge at her fingertips. The Princess' memory instantly fills with information on the things, people and places she encounters, arranged in the fashion she finds easiest to understand. Until the Charm ends, the Princess gains the Living Library Condition. She gains the equivalent of a 3 dot Libary on one topic per success and may make research rolls on the covered topics at a rate of 1 roll a turn. The only limitation is that the topics chosen must be knowledge that is \textit{available} to all of humanity. The Princess is of course free to discover new knowladge but her starting point, her libary, is common knowladge. 

In practice this covers just about any topic the Princess is likely to be interested in, except for inner details of the supernatural and uncharted jungles, the far reaches of space or deep ocean trenches. 

When the Princess activates the Charm, her eyes appear to become depthless azure pools (without affecting her vision in any way) and the immediate area is dimly illuminated, as if by moonlight reflected on water. She also gets the Invocation Lock Condition keyed to Acqua until the Charm ends.

\subsection*{Perfect}
The Perfect Charms grant new personal abilities. Champions and Menders have affinity for them.

\subsubsection*{Barrier Jacket (Perfect \textbullet)}

\noindent Action: Permanent \\

\noindent  Weather a shining suit of plate mail or a sailor fuku. The Princess' Regalia and body becomes iron hard, this grants her one Armour covering her whole body. The Princess may reflexively apply an Invocation at any time to add her Invocation dots to her general armour for a turn, to maximum of 5. 

Barrier Jacket cannot be stacked with mundane armour.

\textbf{Upgrade: Adamant}\\

\noindent Stacks, up to 5 \\

\noindent The Princess's armour becomes harder to penetrate. Each time she takes this upgrade, she gains 1 more point of general Armour from her Jacket. This cannot increase the maximum armour above five when combined with an Invocation. 

\subsubsection*{Celestial Dance (Perfect \textbullet)}

\noindent Action: Permanent \\

\noindent When the Princess transforms, she moves with the grace and speed of an Olympian gymnast. She may apply an Invocation to mundane Athletics rolls. She may also Reflexively apply an Invocation to her Defence trait, increasing it by her Invocation dots, for an entire turn. 

A Princess may not use Celestial Dance to boost her Defence during the same turn where she benefits from the Defensive Combat merit. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Shining Shield}

The Princess may now boost her Defence during the same turn as she benefits from the Defensive Combat merit. 

\textbf{Upgrade: Swift}

Stacks, up to 3

The Princess moves a little faster than any normal human can. She adds +1 to her Defence, Speed and Initiative while Transformed each time she takes this upgrade. The Princess may never increase her defence by more than five points with Celestial Dance. 

\textbf{Upgrade: Danmaku Dance}

The Princess moves faster than a speeding bullet, and may apply her Defence to ranged attacks.

Common sense still applies. The Princess cannot avoid bullets unless she has room to dodge into and going prone is a bad idea when your defence depends on maximising your mobility. 

\textbf{Upgrade: Skating (Acqua \textbullet)}

Ice, wet floors and oily slicks and other liquids pose little risk to the Princess' balance; indeed, her movements across them are uncommonly deft. When the Princess would take a negative modifier due to their presence she reduces all such penalties by her Acqua. Moreover, she may spend 1 Wisp to add her Acqua to her Speed and Initiative for a single turn, as long as she stays within the affected area.

\textbf{Upgrade: Whirling (Aria \textbullet)}

The Princess' sharpens her reflexes, and enhances her ability to evade attacks. When she applies Aria to her defence she uses the higher of Wits and Dexterity, not the lower, as part of her Defence trait. 

\textbf{Upgrade: Weightless (Aria \textbullet\textbullet)}

The very air bears the Princess up whenever she leaves the ground. When she jumps and applies Aria to the roll, she may spend 1 Wisp before rolling to double the distance she travels. When she falls, she may spend 1 Wisp reflexively to slow her fall; she then takes 1 bashing damage for each 6 feet she falls, and reaches terminal velocity after falling 30 yards.

\textbf{Upgrade: Heaving (Fuoco \textbullet\textbullet)}

The Princess can lift and throw objects of great weight. She may apply Fuoco to her rolls to lift an object that exceeds her Strength limit (see p. 47 of the core book), and adds her Fuoco in yards to the distance she can throw an object (see p. 67.) Moreover, she can spend 1 Wisp to throw an object with a Size equal or greater than her Strength, but less than her Strength + Fuoco.

\textbf{Upgrade: Gripping (Legno \textbullet\textbullet)}

In high places, the Princess cannot put a hand or foot in the wrong place. When she is climbing and applies Legno, she does not lose her grip on a dramatic failure; she only loses her next action recovering from her mistake. Moreover, she may spend 1 Wisp when she applies Legno to a climbing roll to double the distance she travels on that attempt, moving 20 feet for each success.\end{myindentpar}

\subsubsection*{Valiant Mind (Perfect \textbullet)}

\noindent Action: Permanent \\

\noindent The Princess penalises all unwanted attempts to supernaturally influence or read her mind or emotions by her Inner Light. She may reflexively apply an Invocation to reduce an attempt by her dots in that Invocation instead. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Glacier Mind (Acqua \textbullet)}

All unwanted attempts at influence  are reduced by Acqua, rather than Inner Light. 

\textbf{Upgrade: Tranquil Mind (Legno \textbullet)}

All unwanted attempts at influence  are reduced by Legno, rather than Inner Light. 

\textbf{Upgrade: A Terrible Thing (Tempesta \textbullet\textbullet\textbullet)}

When somebody reads the Fury's mind, everything they touch is burning acidic hate. The Princess may roll Presence + Intimidation, and may apply Tempesta, vs Resolve + Supernatural Advantage to inflict the Shaken Condition. On an exceptional success she inflicts the Terrified Tilt instead as memories of the Fury's battles reveal just whom they have provoked. 

A Terrible Thing takes place before the effect it is retaliating against. 

\textbf{Upgrade: I've Known Worse (Lacrima \textbullet\textbullet\textbullet\textbullet)}

When the Raven falls under unnatural influence she may drown it out with the grief of Lacrima. Immediately after a mental power is used on her, and so long as she has not applied any Invocation but Lacrima to defend against it, the player may declare they are using I've Known Worse and take the Depression condition. This automatically undoes the mental influence.

\end{myindentpar}


\subsubsection*{Fireproof (Perfect \textbullet, Fuoco \textbullet)}

The heat of the natural world does not trouble the Princess. She reduces penalties inflicted by appropriate natural environments by her Fuoco, to a minimum of -0 or adds her Fuoco as a bonus to resist the effects of natural environments. If the environment imposes a time based penalty, such as damage extreme cold, she adds a number of hours equal to her Fuoco to the time she spends in extreme temperatures before taking damage.

Against supernatural environments Fireproof triggers a Clash of Wills.

\subsubsection*{Trains of Thought (Perfect \textbullet, Acqua \textbullet)}

\noindent Action: Instant, unrolled

\noindent Cost: 1 Wisp

\noindent Duration: length of extended action\\

\noindent The Princess can think about two things at once. At the same time she is carrying out normal actions, she may also perform an extended action to accomplish a purely mental task -- one that requires no physical exertion, or physical tools. (For example, composing a speech, doing calculations, or solving a tactical problem.) She may apply Acqua to the mental task, if she has an appropriate Charm. The Charm ends when the Princess has either succeeded or failed in the mental task.

\subsubsection*{Read the Waves (Perfect \textbullet, Acqua \textbullet)}

\noindent Action: Instant, Wits + Composure

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The water touches all things. Flowing and all-encompassing, it feels the shapes of objects by where it is not. By using Read the Waves, the Princess enjoys a reflexive knowledge of her surroundings, up to a range of 5x her successes in yards. This applies to 360 degrees around her. This ability is not sight, but an additional sense. The slight drawback, is that she can only sense her surroundings underwater or when submerged in some other liquid. 

The additional sense has a resolution of about 1/2" (2 centimeters) and the Princess knows the shapes, sizes, textures and positions of all objects in the area within that level of detail. It does not provide colour; a book appears identical whether filled with profane words or chick-lit, although in the former case, a Wits + Crafts roll may be permitted to identify the characteristic texture of human skin binding the book. The sense only works if water currents can flow between the Princess and an object; she can't use it to perceive what is in an water-tight box. 

Her rolls to avoid being surprised by people in range of the additional sense ignore penalties from lack of vision -- darkness, silt clouds, or just having her back turned.

\subsubsection*{Read the Wind (Perfect \textbullet, Aria \textbullet)}

\noindent Action: Instant, Wits + Composure

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent The air touches all things. Flowing and all-encompassing, it feels the shapes of objects by where it is not. By using Read the Wind, the Princess enjoys a reflexive knowledge of her surroundings, up to a range of 5x her successes in yards. This applies to 360 degrees around her. This ability is not sight, but an additional sense that is identical to the one provided by Read the Waves, except that it works when the princess is immersed in some form of gas (most commonly air). 

\subsubsection*{Long Fast (Perfect \textbullet, Legno \textbullet)}

\noindent Action: Instant, unrolled

\noindent Cost: 1 Wisp

\noindent Duration: 1 day \\

\noindent The Light sustains the Princess when she can find no other food. She does not require food or water until the Charm ends, and does not take damage from deprivation or progress towards taking such damage. If she applies Legno, she adds 12 hours to the Charm's duration for each dot in Legno she has.

\begin{myindentpar}{10pt}\textbf{Upgrade: Airless}

Until the Charm ends, the Princess sinks into a trance, in which she does not need to breathe. She also does not require food or water while entranced. She cannot move or act, but is aware of what happens around her, and may awaken from the trance as a reflexive action, which ends the Charm.

\textbf{Upgrade: Immune (Legno \textbullet\textbullet)}

The Light within the Princess' flesh expels alien substances from it. If she applies Legno, for the duration of the Charm, she adds her Legno to all rolls to resist the effects of drugs, poisons and diseases.\end{myindentpar}

\subsubsection*{Waterproof (Perfect \textbullet, Acqua \textbullet)}

The cold and depths of the natural world does not trouble the Princess. She reduces penalties inflicted by appropriate natural environments by her Acqua, to a minimum of -0 or adds her Acqua as a bonus to resist the effects of natural environments. If the environment imposes a time based penalty, such as damage extreme cold, she adds a number of hours equal to her Acqua to the time she spends in extreme temperatures before taking damage.

Against supernatural environments Waterproof triggers a Clash of Wills.

\subsubsection*{Weatherproof (Perfect \textbullet, Legno \textbullet)}

The natural world does not trouble the Princess. She reduces penalties inflicted by natural environments by her Legno, to a minimum of -0 or adds her Legno as a bonus to resist the effects of natural environments. If the environment imposes a time based penalty, such as damage from extreme heat or cold, she adds a number of hours equal to her Legno to the time she spends in extreme temperatures before taking damage.

Against supernatural environments Weatherproof triggers a Clash of Wills.

\subsubsection*{Woodland's Bounty (Perfect \textbullet, Legno \textbullet)}

\noindent Action: Permanent

When the Princess transforms, she walks through a wilderness as if it were her own home. She gets the 9-again quality on mundane Survival rolls within one of her specialities (chosen when she takes the Charm) and may apply Legno to such rolls.

\begin{myindentpar}{10pt}\textbf{Upgrade: Far-flung}

Stacks, up to 2

The Princess is at home in stranger climes. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for mundane Survival rolls covered by any of the added specialities.

\textbf{Upgrade: Tracking}

The Princess' nose grows sensitive, nearly as much as a dog's. She may always add her Legno to Perception rolls based on smell and taste, and to rolls to smell out a target while blind. Also, she is able to track things by scent - she can follow trails over hard ground, that most people can't even see, and she can take scents from people's clothing, giving her a equipment bonus to track them.\end{myindentpar}

\subsubsection*{Quicker Than the Eye (Perfect \textbullet, Aria \textbullet)}

\noindent Action: Permanent\\

\noindent Proof of a criminal or a handsome don in distress, often a Princess has to get past locks without a proper key. She may apply Aria to mundane Larceny rolls within one of her specialities (fixed when she takes this Charm). She may also add bugler’s tools to her regalia, if the speciality requires them.

\begin{myindentpar}{10pt}\textbf{Upgrade: Advanced}

Stacks, up to 3

The Princess' tools are the finest money can(not) buy. When she applies an Invocation to a Larceny roll she gains an equipment bonus equal to the number of times she has taken this upgrade. This only applies if the speciality can make use of equipment.

\textbf{Upgrade: Multipurpose}

Stacks, up to 2

The toolkit on the Princess’ Regalia becomes more extensive. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for Larceny rolls covered by any of the added specialities. 

\textbf{Upgrade: Concealed (Aria \textbullet\textbullet)}
A Princess may not want to attract undue attention when the situation calls for it. When she applies the Invocation to a Larceny roll, attempts to notice her action take a penalty equal to her Aria. \end{myindentpar}

\subsubsection*{Beauty is Talented (Perfect \textbullet, Specchio \textbullet)}

\noindent Action: Instant, Presence + Composure

\noindent Cost: 1 Wisp

\noindent Duration: successes in turns \\

\noindent Don't you know that beautiful people are just better than you? Pretty people are stronger, faster, smarter, more talented than regular people. Until the Charm ends the Princess can add her Striking Looks bonus to any roll. In situations where Striking Looks usually applies this Charm does not stack the bonus with itself.

\subsubsection*{Last Breath (Perfect \textbullet\textbullet, Legno \textbullet\textbullet)}

\noindent Action: Reflexive, unrolled

\noindent Cost: 1 Willpower 

Once per scene, when her last health box is filled with either Lethal or Aggravated damage, the Princess may spend a point of Willpower to clear it. This applies after calculating damage. 

\subsubsection*{Wreathed in Flame (Perfect \textbullet\textbullet, Fuoco \textbullet)}

\noindent Action: Instant, Presence + Athletics

\noindent Cost: 1 Wisp

\noindent Duration: successes in turns \\

\noindent Passion for her beloved ignites in a fiery nimbus, burning anyone who interferes with the Princess. She chooses someone she holds in affection. For 1 turn per success, her flesh and anything she wears or carries is a source of flame, of a colour and Intensity set by the affection's nature and strength (see table in the Fuoco Invocation.) This grants the Wreathed in Flame Tilt.  Anyone and anything that touches the Princess is burnt as by a Torch-sized fire of the given Intensity, as is anyone or anything she touches that was not on her person when she used the Charm. The Princess may try to touch an opponent in combat to burn them, instead of attacking them, but an attack does not burn her target even if she damages him.

\begin{myindentpar}{10pt}\textbf{Upgrade: Banked}

The Princess can temporarily suppress the flames, allowing her to handle things without burning them. 

\textbf{Upgrade: Granted}

The Princess can turn someone else's passion into an aura of flame. She must know of someone the target holds in affection; when she touches him, he gains a fiery nimbus exactly as if he had activated the Charm himself.

\textbf{Upgrade: Wild}

\noindent Cost: +1 Wisp

The fires leap with the Princess' strikes; each time she successfully damages an opponent in close combat, he is burnt as if she had only touched him.\end{myindentpar}

\subsubsection*{Empty Heart (Perfect \textbullet\textbullet, Lacrima \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Full turn, Stamina + Persuasion

\noindent Cost: 1 Wisp, Compromise at Belief 4+ with a -3 modifier

\noindent Duration: 1 scene \\

\noindent The Princess becomes a being of Darkness, a manifestation of the Void. Her skin becomes sallow, her hair either whitens or darkens, depending on how light it was to begin with, and her pupils expand to fill the entire eye, making her look unhealthy but undeniably human. She has all the benefits and drawbacks of the Darkened template, except that she keeps her normal Sensitivity and suffers Hauntings when it is triggered.

\begin{myindentpar}{10pt}\textbf{Upgrade: Umbral}

Stacks, up to 7 - Belief

If the Princess has dots in Shadows when she uses the Charm, she may assume Umbrae up to her current dots. Each time she takes this upgrade, the Princess learns a new Umbra; she may choose freely among the Umbrae she knows when using the Charm. \end{myindentpar}

\subsubsection*{Composed Come What May (Perfect \textbullet\textbullet, Terra \textbullet\textbullet)}

\noindent Action: Permanent \\

\noindent Elegance is not a pretty gown and tasteful jewellery; it's a state of mind and the Princess knows how to be elegant when up to her elbows in mud. Any sensory effect that would grant her a negative situational modifier to social rolls is reduced by her Composure. A Princess who is covered in blood (-5) and has Composure 2 will only take a -3 penalty.

Drawback: This power does not prevent a Princess from looking bad, it merely allows her to overcome its effects with grace and poise. Additionally because elegance is a state of mind a Princess must be in the right state of mind to use this power. If she cannot justify her appearance then she cannot benefit from this Charm. Being covered in mud because you were searching for a missing child and didn't have time to change is fine; turning up in dirty clothes because you'd rather sleep in than wash isn't.

\subsubsection*{Best Defense (Perfect \textbullet\textbullet, Tempesta \textbullet)}

\noindent Action: Permanent \\

\noindent The best defense is a good offense. When the Princess transforms, she may add power to her muscles, striking harder and moving more swiftly; she applies Tempesta to add her dots in it to her Strength, and recalculates all derived traits. Best Defense is not compatible with Barrier Jacket, or any other supernatural effect that gives Armour; it is also not compatible with any other supernatural effect that increases Strength.

If the Princess wants access to her armour, or has some other reason she may choose whether to activate Best Defence when Transforming, or remove it with a Transformation action.

\subsubsection*{Persistently Peachy Pretty Perfect (Perfect \textbullet\textbullet Specchio \textbullet)}

\noindent Action: Permanent \\

\noindent A Princess is so stunning the universe itself cannot bear to mar her exquisite form. Any sensory effect that would grant her a negative situational modifier to social rolls, if her Specchio is equal to or greater than the modifier, is automatically nullified. For example a Princess with Specchio 2 is sprayed with mud by a passing car. Since this only gives a -2 penalty it is magically prevented, not a drop of mud sticks to the Princess. This effect protects the Princess from humiliation on all five senses, she wont smell of mud, nor will her skin feel muddy to the touch.

Drawback: Only the effects on appearance are protected. A Princess with Specchio 5 might be able to walk through miles of raw sewage and still look and smell fresh as a daisy afterwords but she is not protected from catching horrible diseases.
\subsubsection*{Outrace the Sun (Perfect \textbullet\textbullet\textbullet)}

\noindent Requires: Celestial Dance (1x Swift)

\noindent Action: Instant, Dexterity + Athletics

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene \\

\noindent The Princess can reach the speeds of a car on the open road. Until the Charm ends, she follows the rules for vehicles when running (see pp. 142-146 of the nWoD core book.) Her Acceleration is the higher of Inner Light or the applied Invocation in MPH. Her safe speed is 30MPH * Inner Light or the applied Invocation, whichever is higher. Her maximum speed is 75MPH * Inner Light or the applied Invocation, whichever is higher. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Royal Chariot}

While running the Princess may carry others with supernatural ease, to her they become weightless. While they are being carried by the Princess other characters also share her protection against air resistance.

Theoretically the Princess can carry one person per dot of Inner Light or her applied Invocation at any one time. In practice it's really hard to carry more than two people of your size at a time without their feet dragging the ground (which is not recommended at these speeds). However there are solutions, like growing massive with Royal Stature, turning into an animal better suited for carrying others through Skinchange, or creating a very large Bequest. 


\end{myindentpar}


\subsubsection*{Naiad's Paths (Perfect \textbullet\textbullet\textbullet, Acqua \textbullet\textbullet)}
\noindent Requires Celestial Dance with Skating\\

\noindent Action: Instant, Resolve + Athletics

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene\\

\noindent In all its forms, water will support the Princess wherever she might wish to go.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Charm stops working when the Princess is standing on a particularly deep pool, dropping her into the water (or somewhere as inconvenient as that, at the Storyteller's discretion.) The Princess cannot use the Charm again for the rest of the scene.
 
\emph{Failure:} The Princess gains no ability to walk on liquids or atop snow.

\emph{Success:} As long as the Charm lasts, the Princess walks on the surface of any liquid, or along the top of a snowbank, as if it were solid ground, without sinking in. Running water can throw the Princess off balance or carry her with it; the Storyteller may call for Athletics actions to stay upright in white water, for example, though Skating reduces these penalties like normal and she may use Skating to travel faster while travelling upon water. The Princess may end the Charm prematurely if she wants to get under water. If she uses the Charm while submerged, the Princess will rise to the surface at her maximum running Speed.

\emph{Exceptional Success:} The Princess can turn the Charm on and off during the scene without ending it, walking on water or swimming in it as she pleases.\end{myindentpar}

\subsubsection*{Crawling the Walls (Perfect \textbullet\textbullet\textbullet, Legno \textbullet\textbullet)}

\noindent Requires: Celestial Dance (Gripping)

\noindent Action: Instant, Strength + Athletics

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene \\

\noindent The Princess clings to walls as easily as she walks on floors. Until the Charm ends, she can climb objects at her Speed in yards per turn as her movement action, and may take any instant action that can be performed one-handed. She can also double her climbing Speed for one turn by forgoing an instant action that turn.

\subsubsection*{Royal Stature (Perfect \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Stamina + Athletics\\

\noindent Cost: (change in Size + 1) Wisps\\

\noindent Duration: 1 scene \\

\noindent The Princess can assume titanic sizes, or shrink herself until she is no bigger than a mouse. A Princess cannot change her Size by more than the higher of Inner Light and any applied Invocation, nor may she shrink below Size 1. Multiple invocations of Royal Stature do not stack; measure the maximum or minimum size and the Wisp cost from a starting point of the Princess natural Size. Finally the Princess may return to her natural size at any time with a Transformation action.  \refstepcounter{dummy}\label{SizeTable}

\begin{table}[H]
    \begin{tabularx}{\textwidth}{|l|X|}
    \hline
    Size & Effects                                                                                                                                      \\ \hline
    1    & -4 Health, -3 Strength, -3 weapon damage, -3 Speed, +2 Dexterity, +4 Defence, +4 when hiding or avoiding notice, +2 when jumping or climbing \\ \hline
    2    & -3 Health, -2 Strength, -2 weapon damage, -2 Speed, +2 Dexterity, +2 Defence, +3 when hiding or avoiding notice, +2 when jumping or climbing \\ \hline
    3    & -2 Health, -1 Strength, -1 weapon damage, -1 Speed, +1 Dexterity, +1 Defence, +2 when hiding or avoiding notice, +2 when jumping or climbing \\ \hline
    4    & -1 Health                                                                                                                                    \\ \hline
    5    & None                                                                                                                                         \\ \hline
    6    & +1 Health                                                                                                                                    \\ \hline
    7    & +2 Health, +1 Strength, Iron Skin \textbullet\textbullet, -1 Defence                                                       \\ \hline
    8    & +3 Health, +2 Strength, Iron Skin \textbullet\textbullet, -1 Defence                                                       \\ \hline
    9    & +4 Health, +2 Strength, Iron Skin \textbullet\textbullet, -2 Defense                                                       \\ \hline
    10   & +5 Health, +3 Strength, Iron Skin \textbullet\textbullet, -2 Defense               \\ \hline
    11   & +6 Health, +3 Strength, Iron Skin \textbullet\textbullet\textbullet\textbullet, -4 Defense               \\ \hline
    12   & +7 Health, +3 Strength, Iron Skin \textbullet\textbullet\textbullet\textbullet, -4 Defense               \\ \hline
    13   & +8 Health, +4 Strength, Iron Skin \textbullet\textbullet\textbullet\textbullet, -6 Defense               \\ \hline
    14   & +9 Health, +4 Strength, Iron Skin \textbullet\textbullet\textbullet\textbullet, -6 Defense               \\ \hline
    15   & +10 Health, +4 Strength, Iron Skin \textbullet\textbullet\textbullet\textbullet, -6 Defense              \\ \hline
	16   & +11 Health, +4 Strength, Iron Skin \textbullet\textbullet\textbullet\textbullet, -6 Defense              \\ \hline
    \end{tabularx}
\end{table}

A change of size cannot decrease any trait below zero. 

\subsubsection*{Wings of Air (Perfect \textbullet\textbullet\textbullet\textbullet, Aria \textbullet\textbullet\textbullet)}

\noindent Requires: Celestial Dance (Weightless)

\noindent Action: Instant, Wits + Athletics

\noindent Cost: 2 Wisps

\noindent Duration: Inner Light hours \\

\noindent The Princess is wrapped in the air's gusty embrace, and takes to the skies as a leaf on the breeze. Her Speed in the air equals 5 + Strength + Dexterity + (Aria * 2). If the Princess is airborne when the Charm expires, she gently drifts downward until she touches a surface, and takes no damage from the fall.

If the Princess' Transformation ends while she's flying she falls.

\begin{myindentpar}{10pt}\textbf{Upgrade: Airline}

While flying the Princess may carry others with supernatural ease, at her touch they become as weightless as the air. While they are being carried by the Princess other characters also share her protection against air resistance, cold, and low oxygen levels at high altitude, this applies whether the princess has those abilities from Upgrades to Wings of Air or from unrelated Charms.

The Princess can use Airline on up to the higher of Aria and Inner Light people at a time, she must be physically carrying them, though forming a human chain or having them hold onto the edge of her sceptre is sufficient. 

If somebody is falling the Princess may use Airline to catch them. If she can match their speed and slowly decelerate they're fine (and would be with an unUpgraded Wings of Air) but if the Princess has not the time or the knowledge of basic physics she may roll Dexterity + Athletics + Aria. Each success prevents one point of falling damage. 

\textbf{Upgrade: Sonic Rainbow}

While flying the Princess may spend a Wisp to massively increase her speed, at the cost of precision. If she does so use the rules for Outrace the Sun while she flies. Returning to her regular flying speed costs nothing but the time it takes to decelerate.

As with Outrace the Sun, the Princess is protected from the effects of air resistance. She is also protected from the Heavy Winds Tilt while flying at Sonic Rainbow speeds. 

\textbf{Upgrade: Stratospheric}

The Princess can safely ascend to great altitudes. As long as she is outdoors and flying she can breath as easily as she would do at sea level is immune to temperature extremes. 

\end{myindentpar}

\subsubsection*{Skinchange (Perfect \textbullet\textbullet\textbullet\textbullet, Legno  \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Dexterity + Animal Ken - difference in Sizes

\noindent Cost: 2 Wisps

\noindent Duration: until detransformation \\

\noindent The Princess assumes the shape of a beast. The new shape is of one particular species of animal; her mundane Physical Attributes become equal to those of a normal animal of that species, while her Mental and Social Attributes, and her Skills, remain unchanged. The Princess' transformed dots still apply, and she gains the animal's natural abilities and attacks, and the ability to communicate with other animals of the species. She may also activate Charms in animal form.

The Princess cannot, however, speak any human language except the Royal Tongue unless the animal is able to mimic human speech (like a parrot); she takes penalties on any task that calls for hands, unless the animal has them (like a monkey) or capable manipulators (an octopus' tentacles); and her Regalia are transformed away and unavailable. Finally, any object she picked up after transforming out of mundane form does not change with her.

The Princess subtracts the difference between her normal Size and the animal's Size from the activation roll when using the Charm. She may remain in beast form as long as she can remain transformed normally, and may end the Charm at any time with a standard transformation roll or by returning to mundane form.

\subsubsection*{Dryad's Child (Perfect \textbullet\textbullet\textbullet\textbullet\textbullet, Legno \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Stamina + Survival

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: 1 scene \\

\noindent  With a shout, the Princess' flesh and clothes become beautifully-sculpted, flawless wood, and she continues the fight as an animated statue. Despite being wood, she still speaks, thinks, and acts normally, protected by the Living Oak Tilt.

\subsubsection*{Shadowmask (Perfect \textbullet\textbullet\textbullet\textbullet\textbullet, Lacrima \textbullet\textbullet\textbullet)}

\noindent Requires: Empty Heart

\noindent Action: Instant, Resolve + Stealth

\noindent Cost: 2 Wisps, gain 1 Shadow, Compromise at Belief 3+ with a -4 modifier

\noindent Duration: varies \\

\noindent Wrapping herself in the darkness in which the only true remnants of the Kingdom reside, the Princess becomes a true, immaterial figure of shadow. Glowing eyes may glare from the head of the figure, or it may be a featureless mask. Occasionally, long-lost stars twinkle within the cut-out from the universe, before being swiftly extinguished. Certainly, there is no way that she could be mistaken for human.

    \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess only attracts the Darkness. She gains her Inner Light dots in Shadows.

    \emph{Failure:} The power does not activate.

    \emph{Success:} The Princess becomes a living figure of shadow for the rest of the scene. She gains the Cloak of Shadows Condition.

    \emph{Exceptional Success:} The Princess may become a figure of shadow until the next sunrise, changing between that form and any others she possesses with a Transformation action.\end{myindentpar}

\subsubsection*{One Perfect Woman (Perfect \textbullet\textbullet\textbullet\textbullet\textbullet, Specchio \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant and contested, Presence + Persuasion - Commonalty vs. Composure + supernatural advantage

\noindent Cost: 3 Wisps, 1 Willpower

\noindent Duration: 1 scene \\
 
\noindent The true heir to the Kingdom, according to the Queen of Mirrors, is a living personification of the Light itself - her word becomes truth, her actions mighty, her presence a bastion of hope across the land. Mirrors' avatar, who may be that heir someday, can assume the heir's attributes for a time, when her followers need her.

The Princess uses this Charm on members of a social group over whom she has some influence or authority, none of whom are Hopeful; the member with the best Composure rolls to resist. If the Princess gets more successes - even just one - she gains a personal presence and magnetism that sways all who see or hear her; she has the benefits of the Pure Perfection Condition granting the Royal Tongue merit (if she does not already have it) and Striking Looks two, she looks like \textquotedblleft The Best Person Ever!\textquotedblright\, which covers most things. 

The Princess' magnetism is even stronger on the targeted social group; they perceive the Princess as a paragon, the epitome of beauty and charm. They all get the True Follower Condition. Against them the Princess' striking looks counts as five dots, and the Princess may spend their Willpower in place of her own Wisps at a 1:1 ratio. Note that taking Willpower from anyone without permission is a Belief Compromise with a -3 penalty.

\subsection*{Restore}
The Restore Charms repair damaged objects, heal the injured and tend the sick. Only Menders have affinity for them.
\subsubsection*{Friendly Gremlin (Restore \textbullet)}

\noindent Action: Full turn, Dexterity + Crafts

\noindent Cost: 1 Wisp/success

\noindent Duration: variable \\\

\noindent Soon after airplanes were invented, flyers began to speak of gremlins, small spirits who liked to sabotage planes. While no one has ever seen a real gremlin, as far as the Hopeful know, a Princess-mechanic named this Charm after them, as it preserves the delicate mechanisms of aircraft (and other machinery) in perfect working order, keeping the local gremlins friendly. The Princess uses this Charm on any machine with multiple moving parts. For each activation success or Wisp spent (whichever is less), one roll made to operate the target machine gains the 9-again quality. Neither the Princess not the operator chooses which rolls gain the benefit - the \textquotedblleft gremlin" blesses the next set of rolls made, no matter when or by whom, to operate the machine. Friendly Gremlin cannot be used on a machine currently under its effects.

\begin{myindentpar}{10pt}\textbf{Upgrade: Helpful}

\noindent Cost: 2 Wisps/success

The gremlin's help is more effective. For each activation success or 2 Wisps spent (whichever is less), one roll to operate the machine gains the 8-again quality. If the Princess applies Helpful, she cannot give any rolls 9-again with the same activation.

\textbf{Upgrade: Perfected}

Requires Helpful

\noindent Cost: 3 Wisps/success

The gremlin makes it nearly impossible to fail when using the machine. For each activation success or 3 Wisps spent (whichever is less), one roll to operate the machine gains the rote quality. If the Princess applies Perfected, she cannot give rolls 8-again or 9-again with the same activation.\end{myindentpar}

\subsubsection*{Ministering Angel (Restore \textbullet)}

\noindent Action: Permanent

The Princess adds a first aid kit, surgical tools or other medical equipment to her Regalia. She may apply an Invocation to mundane Medicine rolls within one of her specialities (fixed when she takes this Charm) and never suffers penalties from improvised equipment on these rolls.
\begin{myindentpar}{10pt}\textbf{Upgrade: Versatile}

Stacks, up to 2

The Princess' first aid kit holds a larger assortment of medical tools. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for mundane Medicine rolls covered by any of the added specialities.

\textbf{Upgrade: Calming (Acqua \textbullet)}

The Princess remains calm and rational in a crisis, and her calm mind and clear instructions help bring back others from panic. When she applies Acqua to a Medicine roll she may ignore up to her Acqua in situational penalties for stress, panic, loud noises, disgust and other similar distractions. If she is the primary actor in a teamwork Medicine roll, she may spend a Wisp to apply her Calming presence to every secondary actor.

\textbf{Upgrade: Urgent (Fuoco \textbullet)}

The Princess can save people who are dying of their wounds. When someone has a Health track full of lethal damage and is bleeding out, the Princess may make a number of rolls equal to her Fuoco in the time it would normally take to make a single roll. She may do this once a minute.\end{myindentpar}

\subsubsection*{Call Back Yesterday (Restore \textbullet, Terra \textbullet)}

\noindent Action: Extended, Intelligence + Crafts (5 minutes/roll, threshold = 1 per 20 years of object's age)

\noindent Cost: 1 Wisp per 5 Size points of the target

\noindent Duration: Lasting \\

\noindent To the Flowers, nothing that is past is gone forever, and anything can be restored if only a fragment remains. By painstaking inspection of an object that has suffered the ravages of time - wear, rust, corrosion or neglect - and some judicious scrubbing, the Princess can remove every trace of time's passage from it, bringing it back to the condition it was in when newly made. The threshold for the Charm is set by the object's age; an item made less than 20 years ago needs 1 success, one made up to 40 years ago needs 2, one made up to 60 years ago needs 3, and so forth. The Charm does not fix damage to the object, as represented by lost Structure points; if a Princess uses it on a damaged object, the damage is transformed into hidden structural flaws, and the penalty for damage that exceeds the item's Durability remains.

Suggested modifiers: appropriate tools (+equipment bonus), major parts missing (-1 to -3)
\begin{myindentpar}{10pt}\textbf{Upgrade: Selective (Terra \textbullet\textbullet)}

The Princess can restore an object to the state it was in at any time during its existence. The threshold is now set from the number of years between the object's unmodified age and the age the Princess wishes it to be; at the same rate of 1 success per 20 years.\end{myindentpar}
\subsubsection*{Warmed by Hate Alone (Restore \textbullet, Tempesta \textbullet\textbullet)}

\noindent Action: Reflexive, unrolled

\noindent Duration: 12 hours.

\noindent Cost: 1 Wisp, 1 Willpower.

The Princess can call upon her hatred of the Darkness to keep herself warmed against the most bitter and tainted chills. The magnitude of every Taint Curse upon the Princess is reduced by half her Resolve + Tempesta (rounding down). The Fury's Practical Magic adds to this Charm; if the Princess is sufficiently injured add any bonus she gets from practical magic to her Resolve + Tempesta before rounding.

If the Princess has a Resolve + Tempesta of 5 or more, she is immune to any Taint Curses that affect her behaviour directly, such as Tainted Vice. At a Resolve + Tempesta of 10 or more she can comfortably survive in the Dark World, though she gains no protection from the many more active dangers in that physical hell.
\subsubsection*{Balm (Restore \textbullet\textbullet)}

\noindent Action: Instant, Intelligence  + Medicine

\noindent Cost: 1 Wisp

\noindent Duration: Lasting \\

\noindent The Princess lays hands on a person's flesh, and minor injuries fade away. For each activation success, the target heals 1 bashing or lethal damage.

\begin{myindentpar}{10pt}\textbf{Upgrade: Miraculous}

\noindent Cost: +1 Wisp

The Princess' hands bring relief from the most horrible forms of injury. The target heals 1 aggravated damage. If the Princess gets an exceptional success, the target heals 1 aggravated damage and downgrades 1 other aggravated damage to lethal damage.\end{myindentpar}

\subsubsection*{Sure Hands (Restore \textbullet\textbullet)}

\noindent Action: Instant, Dexterity + Crafts

\noindent Cost: 1 Wisp

\noindent Duration: 1 action \\

\noindent Broken things return to their proper form under the Princess' hands. Each activation success grants a +1 bonus on a mundane action to heal or repair something damaged. Eligible actions include (under Crafts) repairing an item, (Medicine) healing wounds, or (Computer) recovering data from a crashed computer. If the action in question is extended, the bonus applies to all rolls until the task is complete, or the Princess turns her attention to something else; the bonus is lost if she leaves the repairs unfinished.
\begin{myindentpar}{10pt}\textbf{Upgrade: Leading}

\noindent Cost: +1 Wisp

When others assist the Princess (she is primary in a teamwork action) they gain the same bonus on their rolls as the Princess does herself.

\textbf{Upgrade: Swift (Aria \textbullet)}

The light-fingered Knaves repair things with deftness and speed. When the Princess uses the Charm for an extended action, she divides the time interval needed for a roll by 2 for each dot of Aria, cumulative (1/2 time for Aria 1, 1/4 for Aria 2, 1/8 for Aria 3, and so on) to a minimum of 1 minute per roll.\end{myindentpar}
\subsubsection*{Bath of Souls (Restore \textbullet\textbullet, Acqua \textbullet)}

\noindent Action: Instant and resisted, Presence + Empathy - target's Composure

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene or 1 day \\

\noindent The Princess brings someone lost in madness back to rationality for a time. Bath of Souls can be used to suppress any Condition which represents a malign mental state, such as Shaken or Fugue. 

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess' intervention makes matters worse. The target immediately has a panic attack, episode or suffers whatever seems appropriate for the Condition. The Princess cannot use Bath of Souls on him for a full week.

    \emph{Failure:} The Condition is not affected.

    \emph{Success:} The Condition is suppressed, it vanishes and reappears at the end of the scene.

    \emph{Exceptional Success:} The Condition is suppressed for a full day.

    \end{myindentpar}
\subsubsection*{Mesmerize (Restore \textbullet\textbullet, Aria \textbullet)}

\noindent Action: Instant and contested, Manipulation + Empathy vs. target's Resolve + supernatural advantage

\noindent Cost: 1 Wisp

\noindent Duration: Lasting \\

\noindent By speaking a few words, the Princess helps a person remember something they have forgotten. The target immediately makes a memory roll (as per the rules on p. 44 of the nWoD core), adding 1 bonus die for each success on the activation roll. If the target contests the Charm, only successes the Princess rolls in excess of his have any effect.
\begin{myindentpar}{10pt}\textbf{Upgrade: Deep}

\noindent Duration: Lasting

The Princess can fix something on the surface of a person's mind. Each activation success gives +1 to all the target's attempts to remember something, until he succeeds.\end{myindentpar}

\subsubsection*{Flame in the Heart (Restore \textbullet\textbullet, Fuoco \textbullet)}

\noindent Action: Full turn, Manipulation + Persuasion

\noindent Cost: 1 Wisp

\noindent Duration: Indefinite \\

\noindent By touching a person, the Princess ignites a flame from the warmth of their affections for another. Taking fire in this way does not affect the target's emotions, just as lighting one candle from another doesn't put the first candle out. The Princess must know the subject of the target's affections when you activate Flame in the Heart; she can't simply take \textquotedblleft the person he feels most strongly for", without knowing just who that is.

The flame created is candle-sized (base damage of 0) and dances on the tip of the Princess' finger; its colour and Intensity depend on the nature and strength of the affection. (See the table in the Fuoco Invocation.) Add 1 to the flame's Intensity if the Princess gets an exceptional success. The flame may be sustained indefinitely if transferred to a flammable substance such as a candle wick. It will continue to burn without consuming its source until it is deliberately extinguished (which is as easy as snuffing out a non-supernatural flame of the same size) or the target dies. A Princess may maintain a number of these flames equal to her Inner Light, if she wants more they must feed on mundane fuel. Extinguishing a flame manually (to allow maintaining a new flame, for example) has no effect on the relationship that originated it.

The Princess can use a flame at any time to set something on fire. However, its proper use is to preserve the relationship that inspired it. If the target's emotions fade they can put the flame back in their heart by holding it against their chest (this is quite safe, don't wear anything flammable) doing so grants the Fresh Impressions Condition: Their Impressions of whomever the flame represents is reset to what it was at the moment the flame was taken. This only lasts for a day, but that can be long enough to rebuild something more durable. Using a flame to reignite a relationship does not consume the flame.

With a lifetime on the road Princesses of Swords can go months or years without seeing their lovers. Distance can dull the strongest emotions and some Princesses like to keep their feelings safe and take them out again for a night of passion. Others are trusted custodians of stable relationships, reigniting the spark after time smothers the flames. 

Finally, as long as the flame exists, it provides an Intimacy connection to both the target of the Charm and whomever the flame Represents. The strength is the strength of the relationship, however like all uses of Intimacy there is a two step penalty when using an inanimate object as a proxy. 

\subsubsection*{Jury Rigger (Restore \textbullet\textbullet, Fuoco \textbullet)}

\noindent Action: Extended, Wits + Crafts (10 seconds/roll, threshold = target's Size)

\noindent Cost: 1 Wisp per 5 Size points of the target.

\noindent Duration: 1 scene or 1 hour using the device

With a few tools and enough duct tape a Princess of Swords can get anything running, at least for a time. To repair a device she requires basic tools and vaguely appropriate replacements for any missing pieces: for a car, for instance, she could use cheap alcohol for missing petrol, several packs of AA batteries to replace a car battery, a circular piece of wood for a missing wheel and lots and lots of duct tape for structural damage.

    \begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess's crude repairs collapse into a pile of junk, damaging the machine further. Remove all Successes and a quarter of the device's Structure.

    \emph{Failure:} The Princess makes no progress.

    \emph{Success:} The Princess makes some repairs. When the Princess reaches the threshold the device is fully functional; the duration is 1 scene or 1 hour, starting from the first turn it is used but there is no negative modifier. 

    \emph{Exceptional Success:} The Princess makes extensive repairs.\end{myindentpar}

Suggested Modifiers: Simple machine (+2), appropriate tools (+equipment bonus), proper replacement parts (+2), very inappropriate parts (-2), complicated problem (-2), exceptionally complicated machine (such as trying to patch up a circuit board) (-4)
\subsubsection*{Purify (Restore \textbullet\textbullet, Legno \textbullet)}

\noindent Action: Extended, Resolve + Medicine (1 turn/roll, threshold = Toxicity + 1)

\noindent Cost: 1 Wisp

\noindent Duration: Lasting \\

\noindent The Princess destroys all poisonous substances within her patient's body with nothing more than a caress. When the Princess reaches the threshold, the continuing effects of the foreign substance end immediately. For a drug (in a dose too weak to cause damage) the threshold is equal to the penalty to resist the drug's effects, plus 1; for a poison, it's the poison's Toxicity + 1. If the Princess reaches the needed threshold before, or in the same turn as, a poison would inflict damage, that damage is prevented.
\begin{myindentpar}{10pt}\textbf{Upgrade: the Plagued}

The Princess can cure mundane diseases. The threshold for this application equals the threshold the infected target must reach to throw off the disease himself, plus 1; if the target has accumulated any successes on his rolls to beat the disease, subtract those successes from the Princess' threahold. The target is cured when the Princess reaches the threshold.

\textbf{Upgrade: the Corrupted (Legno  \textbullet\textbullet\textbullet)}

\noindent Cost: +1 Willpower

Even supernatural illnesses yield to the Princess' ministrations. The Toxicity of these diseases generally equals the Successes rolled to inflict. Unrolled powers generally use the attacker's Supernatural Advantage or Rank. Purify only works on supernatural poisons, drugs and, with the Plauged, diseases. It cannot remove a supernatural template.\end{myindentpar}

\subsubsection*{Memento Mori (Restore \textbullet\textbullet, Lacrima \textbullet)}

\noindent Action: Instant, Composure + Occult

\noindent Cost: 1 Wisp

\noindent Duration: instant \\

\noindent The Princess can call ghosts and give them aid and succor. If she touches a ghost's anchor, she helps it to materialize; her activation successes become bonus dice on the ghost's roll to manifest. She can also heal minor wounds to a manifested ghost's Corpus; for each activation success, the ghost heals 1 bashing damage.
\begin{myindentpar}{10pt}\textbf{Upgrade: Loving}

The Princess can heal more serious damage to a ghost; for each success, the ghost heals 1 lethal damage.

\textbf{Upgrade: Grieving (Lacrima \textbullet\textbullet)}

\noindent Requires: Loving

\noindent Cost: +1 Wisp

The Princess heals the most grevious damage to ghosts; the ghost heals 1 aggravated damage.\end{myindentpar}

\subsubsection*{Their Blood Cries Out (Restore \textbullet\textbullet, Tempesta \textbullet\textbullet\textbullet)}

\noindent Action: Extended and resisted (1 turn/roll), Manipulation + Empathy - target's Composure

\noindent Cost: 1 Wisp, check for Haunting
 
\noindent Duration: 1 scene \\

\noindent The Queen of Storms knows that mortals forget their sufferings in time, and teaches her dedicated followers a way to repair this flaw. The Princess may use this Charm on a target who has recently been injured, physically, mentally or socially. The threshold to reach depends on how long ago the injury was; 1 success reaches an injury in the past week, and each success beyond the first doubles the interval. On reaching the threshold, the target's emotional state returns to where it was when he discovered the injury, and his memories of events since then seem vague and unimportant.

Until the Charm ends, the target get's the Cursed Condition: He has a -2 penalty to resist any suggestion that he revenge himself upon those who injured him and a -2 penalty to recall anything his enemy did in apology, or any penalty he paid -- though if restitution was made to the target's satisfaction, and he remembers this, the Charm ends immediately. In addition the target gets the Blessing Condition which provides a +2 bonus on attempts to take that revenge. The bonus and penalties apply to whoever the target believes injured him, even if he is mistaken.

Bringing back someone's outrage at an injury triggers a Princess' innate sympathy with suffering. On reaching the threshold, the Princess must roll her Sensitivity, and experiences a Haunting if she gets any successes.
\begin{myindentpar}{10pt}\textbf{Upgrade: Collective}

\noindent Cost: +1 Wisp

The Princess may use the Charm on a social group whose members can hear her, applying the Commonalty modifier. The injury done must have been to the group, or to some members as representative of the group, as far as the group believes; that is, the group must believe that their members were injured because of their membership, and not for any other reason. As with the basic Charm, this belief need not be accurate. The member with the highest Composure resists for the group.\end{myindentpar}
\subsubsection*{Stitch (Restore \textbullet\textbullet\textbullet)}

\noindent Action: Instant, Strength + Crafts

\noindent Cost: 1 Wisp

\noindent Duration: Lasting \\

\noindent The Princess swiftly repairs damage done to a single object she can hold or touch. For each success rolled, the item regains one point of Structure, up to its normal maximum.

\subsubsection*{Stain Removal (Restore \textbullet\textbullet\textbullet)}

\noindent Requires: Bath of Souls

\noindent Action: Instant, Resolve + Empathy

\noindent Cost: 2 Wisps

\noindent Duration: Lasting \\

\noindent The Princess may cleanse the first stage of corruption by Tainted areas. For each success rolled, remove 1 point of Corruption.

\begin{myindentpar}{10pt}\textbf{Upgrade: Cleansing}

As an Extended action the Princess may use Stain Removal to cleanse the Darkened of their tainted powers. For this use, the activation roll takes a -1 penalty for each of the target's current Umbrae. The Princess takes this penalty even if the target is cooperating (and if he doesn't, she must subtract his Resolve as well.) Getting 10 successes removes one Umbra. A dramatic failure triggers the Princess' Sensitivity, and adds the number of the target's Umbrae to the pool. A Darkened target with no Umbrae can be returned to full humanity with 20 successes.\end{myindentpar}

\subsubsection*{Choke It Down (Restore \textbullet\textbullet\textbullet, Tempesta \textbullet\textbullet)}

\noindent Action: Instant, unrolled

\noindent Cost: 2 Wisps, 1 resistant lethal damage \\

\noindent Followers of the Queen of Storms don't have time to atone for their actions or aid those in need; there's far too much killing to do. The Shadows of all the pain they see, a great deal of it caused by themselves, haunt their dreams and waking lives, but this only serves to make them angrier. They swallow the pain, armour themselves in rage, and allow their hate to eat at them -- literally -- so long as it takes the guilt with it.

When the Princess is faced with a Sensitivity roll, she may spend 2 Wisps and take a point of resistant lethal damage to automatically score zero Successes. 

\subsubsection*{It Was Necessary (\textbullet\textbullet\textbullet, Lacrima \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Reflexive

\noindent Cost: 1 Wisp, 1 Willpower, Compromise at Belief 4+ with a -3 modifier\\

\noindent To survive Alhambra has done many terrible things and Alhambra must survive. The Queen of Tears teaches her Handmaidens how to cope with the necessity of duty. 

At any time the Princess may spend one Willpower to ignore a single Belief Compromise roll. She may not do this if the Compromise was caused by Lacrima's drawback (doing so would prevent the other Charm from functioning) and invoking this Charm with a Belief of four or more is essentially pointless.\\

\noindent \textbf{Drawback:} Whether a Princess succeeds or fails on a Compromise roll she is dealing with her internal conflicts, denying them simply lets the problem fester. Every time a Princess invokes It Was Necessary she gains the It Wasn't Necessary Condition, or increases her stacks in that condition by one. 

\subsubsection*{Somebody Else's Problem (Restore \textbullet\textbullet\textbullet, Specchio \textbullet\textbullet)}

\noindent Action: Reflexive, Intelligence + Composure - Shadows

\noindent Cost: 1 Wisp

\noindent Duration: Lasting \\

No matter how may of her Heirs fail spectacularly the Queen of Mirrors never shows pause in her tireless endeavours. Some speculate that she wants her chosen to fail, those who know of this Charm often give a different reason. They say that unable to bear the weight of so many failures she has chosen to forget about them and so she crafted a Charm to do just that. Only those Princesses with memories of the Palace of Five Folded Stars itself remember that the Queen of Mirrors was once the Hierophant-Queen. With her magic she could see across time and space and often saw secrets best forgotten; hinting that there was once a more noble purpose to this Charm.

Somebody Else's Problem erases the user's memories. It's as simple as that. This Charm can take the weight of Sensitivity off a Princess' shoulder, for what she does not know cannot hurt her. The most common use of this Charm is to instantly end a Haunting by forgetting all about the action that caused it.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess completely messes up her own mind. Choose one wide ranging topic like \textquotedblleft Academics \textquotedblright , \textquotedblleft my family\textquotedblright\, or \textquotedblleft Connect Charms\textquotedblright . The Princess gains the Amnesia Condition covering that topic, it goes away at the end of the scene.

    \emph{Failure:} Nothing happens.

    \emph{Success:} The Princess erases everything she remembers of the last few minutes, up to at most 3 minutes for each success. The memories are not just suppressed, they are gone as though they had never existed. The Princess knows only that she has erased her own memory. No magic or psychological technique will let the Princess regain her memories; however, she is not prevented from forming new memories about the topic.
    The effects of all Sensitivity rolls during the forgotten time are nullified, including Hauntings and new Shadows. Somebody Else's Problem cannot give free dots of Belief, but erasing all memory of a Belief Compromise will allow a Princess to buy back lost Belief with experience. This is purely an out of character rule rule, but the Storyteller is free to explain the lost experience as valuable life experiences being erased if she wishes.

    \emph{Exceptional Success:} No further benefit.

\textbf{Upgrade: Retroactive}

The Princess may erase her memories up to one day after they have formed. The maximum time erased by a single use remains the same, but she can now use multiple invocations to erase longer periods. Some Princesses use the extra time to write notes to themselves, but knowing what happened is no substitute for experiencing it.\end{myindentpar}

\subsubsection*{Freed By Burning Hate (Restore \textbullet\textbullet\textbullet, Tempesta \textbullet\textbullet\textbullet)}

\noindent Requires: Their Blood Cries Out

\noindent Action: Instant or Reflexive, Presence + Empathy

\noindent Cost: 0 or 1 Wisps, 1 Willpower

\noindent Duration: special \\

\noindent Those who follow in the path of the Queen of Storms know that the world will always seek to hold her in chains, to imprison her so that the misdeeds of the world will be permitted to hold her and others captive. But the Queen of Storms shows her how to break those chains, and how to break them in others. With a snarl, the bonds of the mind are broken.

The Princess may use this Charm on anyone currently affected by a supernatural power that alters their emotional state. If she is affected by an applicable supernatural power she may reflexively use this Charm on herself, she may make one attempt per turn with no penalty for successive attempts and she may do so even if commanded not to.

If the Princess gets more successes than the power's wielder did when they activated it, the power's effect is overridden by a feeling of intense, nauseated rage, and the target suddenly becomes aware that someone has tried to violate his mind. If the power affected dice pools between the target and the perpetrator, the Princess gains the same benefit on any roll to persuade the target to avenge himself on the perpetrator, using the Inverse Curse Condition. The Charm also works on powers that don't require a roll to activate (such as a vampire's blood bonds). To defeat these, the Princess must get more successes than the supernatural advantage of the perpetrator.

The Charm lasts as long as the effect it destroys would have, for it is built on the fragments of that effect. If the perpetrator cancels or removes the effect himself, the target's rage immediately dissipates. The Charm costs 0 Wisps (just the Willpower point) when the Princess uses it on herself, and 1 Wisp plus a Willpower point if used on another person. If a Princess uses the Charm on a target whose emotions are not being influenced, she pays the cost but nothing happens. If she uses it on a target subject to more than one eligible effect, the Charm breaks the least potent, and among effects of equal strength it breaks the one with the shortest remaining duration.

\begin{myindentpar}{10pt} \textbf{Upgrade: Shattering (Tempesta \textbullet\textbullet\textbullet\textbullet)}

\noindent Cost: +1 Wisp \\

\noindent The Princess can break chains forged in deeper layers of the mind. Supernatural powers that alter memories or instill compulsions become vulnerable to the Charm, as does possession by a spirit or ghost. As with emotional influences, the Princess must get more successes than the power's user did when activating it, or than the user's supernatural advantage for unrolled effects.

When used on a compulsion, the Charm transforms the effect into a urge to attack the perpetrator; should the target lack the means to do so, he will act to frustrate the perpetrator's intent as best he knows it. Any rolls the target was entitled to make to resist the original compulsion, he may make to resist this urge as well. 

When used to break a false memory, the Charm sends the target into a bitter fury whenever the implanted memory would have arisen. When an effect simply suppresses a memory, the target is enraged whenever he recalls the memory that it suppressed. The Charm cannot restore a memory that was permanently removed - in this case the target becomes aware that his memory was altered, and feels sick rage at the violation for a few moments, but no longer.

On any successful use of the upgraded Charm, the target experiences a sudden sharp headache, similar to a migraine attack, which inflicts 1 point of bashing damage. Targets who were already wounded have been known to suffer nosebleeds when the Charm took hold.\end{myindentpar}

\subsubsection*{Reclaim (Restore \textbullet\textbullet\textbullet\textbullet, Acqua \textbullet\textbullet\textbullet)}

\noindent Requires: Bath of Souls

\noindent Action: Extended and resisted (10 minutes/roll), Presence + Medicine - target's Resolve

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: Lasting \\

\noindent The Princess restores a shattered mind to sanity. Reclaim can remove any Condition that represents a malign mental effect. The exception is those that are innate to a Supernatural Template, a Princess cannot heal a Werewolf's rage or a Mad Scientist's madness. She also cannot heal Conditions gained from a Belief Compromise, an Integrity Breaking Point that was caused by perpetrating an immoral action or Conditions caused damage to other integrity traits that arose from acting immorally (by human standards). 

Belief Compromises caused by Lacrima Charms always count as immoral, Specchio does not automatically count as immoral but like any Invocation it can be used for good or ill. If the Condition was caused by using Speccho then the target's dots in Specchio are subtracted from the Princess' roll.

Reclaim requires a conscious target, but not a cooperative one; if the target does cooperate, the Princess does not subtract their Resolve from the roll.

\subsubsection*{Disenchant (Restore \textbullet\textbullet\textbullet\textbullet, Acqua \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant and resisted, Manipulation + Academics - sucesses rolled on the effect

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene or 1 day

The Princess relieves her target of a supernatural effect that alters his mind. This does not banish the effect, but only prevents it from swaying the target for the duration. On an ordinary success, the Charm lasts for the scene; on an exceptional success, it lasts for 1 day.

\subsubsection*{Regenerate (Restore \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Extended (10 minutes/roll), Intelligence  + Medicine

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: Lasting \\

\noindent The Princess may restore the permanently injured to their original full health. Regenerate can cure any Condition based on a physical disability, and restore Attribute dots lost from physical damage. The threshold depends on the extent of the damage (the Storyteller should use the table provided as a guide.) Any opposition from your target makes Regenerate fail; active cooperation isn't needed, so you can use Regenerate on unconscious targets, but a conscious refusal frustrates the Charm.

The Princess may use Regenerate to remove a Goalenu graft and restore the organ it replaced. In this case the target's Revelation subtracts from the activation roll. Rolling a dramatic failure causes the target's Goalenu parts to regard the Princess as a servant of Darkness, and she can never use Regenerate on that target again.

\begin{table}[H]
    \begin{tabular}{|l|l|}
        \hline
        Threshold & Injury                                                         \\ \hline
        3         & Non-Flaw injuries: scarring, missing tooth, lost finger joint  \\ \hline
        6         & Restoring lost function: 1 lost Attribute dot, paralyzed limbs \\ \hline
        9         & Full replacement of small organs: eye, muscle, skin, etc.      \\ \hline
        12        & Full replacement of large organs: arm, leg, stomach, etc.      \\
        \hline
    \end{tabular}
\end{table}

\subsubsection*{Resuscitate (Restore \textbullet\textbullet\textbullet\textbullet\textbullet)}

\noindent Action: 3 minutes of full concentration, Presence + Medicine

\noindent Cost: 3 Wisps, 1 permanent Willpower dot

\noindent Duration: Lasting \\

\noindent The Princess is able to stave off another's death and return him to life -- though the experience is not a pleasant one, nor does it come free. The target must have died within the current scene, or the Charm fails. The sheer mental and emotional exertion required, and the traumatic process of dying result in the loss of a dot of Willpower for both the Princess and her target, and the ebbing of his life force causes his highest Attribute (if there is a tie, she chooses) to be reduced by one dot. He returns to life with a number of Health boxes equal to the activation successes filled with lethal damage and the rest filled with aggravated, and a -3 penalty to all actions due to the Reaper's grasp upon him. Each week of rest and recuperation without any strenuous activity reduces this penalty by one.

On an Exceptional success, the target doesn't lose a dot from his highest Attribute.

\subsubsection*{Long May She Reign (Restore \textbullet\textbullet\textbullet\textbullet\textbullet, Lacrima \textbullet\textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant. Composure + Occult.

\noindent Cost: 5 Wisps, 1 Willpower dot (if successful)

\noindent Duration: Indefinite \\

\noindent This rare and powerful Charm is the source of the Ghostly Princesses who dwell within Alhambra and serve its Queen. Because of the enormous political power and prestige it brings the Protectorate of Amethyst guard all knowledge of it jealously.

The target Princess must be at death's door, but must not actually be dead. For instance, a Princess with a Health track filled with lethal and aggravated damage is a valid target for the Charm.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} Instead of creating a ghost, the Princess accidentally kills the target.

    \emph{Failure:} Nothing happens. The Princess may try again at a -1 penalty, if the target still lives.
    
    \emph{Success:} The target dies, and rises again as a Ghostly Princess. Long may she reign over us.
    
    \emph{Exceptional Success:} The target loses a dot of Shadows just before she dies and rises.\end{myindentpar}

The Princess using the Charm always spends the Wisps to activate it; she sacrifices a Willpower dot only if the Charm succeeds.

\subsection*{Shape}
The Shape Charms shape materials as you will, or make things out of nothing. Menders and Troubadours have affinity for them.
\subsubsection*{Always Prepared (Shape \textbullet)}

\noindent Action: Permanent

A small kit of crafting tools becomes part of the Princess' Regalia. She may apply an Invocation to mundane Crafts rolls within one of her specialities (fixed when she takes this Charm) and never suffers penalties from poor equipment or an improvised work area on these rolls.
\begin{myindentpar}{10pt}\textbf{Upgrade: High-grade}

Stacks, up to 3

The Princess' toolkit is of excellent quality. When she may apply an Invocation to a Crafts roll, she has a minimum equipment bonus of +1 for each time she takes this upgrade.

\textbf{Upgrade: Multi-tool}

Stacks, up to 2

The Princess has appropriate tools for two or three crafts in her kit. Each time she takes this upgrade, she adds another speciality to the Charm; she gets the benefits of the Charm for all Crafts rolls covered by any of the added specialities.

\textbf{Upgrade: Flexible}

Requires 2x Multi-tool

The Princess' kit has tools for any bit of crafting imaginable. If she spends 1 Wisp, she gets the benefits of the Charm for all mundane Crafts rolls made in the current scene.\end{myindentpar}
\subsubsection*{Bubble Shield (Shape \textbullet)}

\noindent Action: Instant or Reactive, Stamina + Crafts

\noindent Cost: 1 Wisp

\noindent Duration: 1 turn \\

\noindent The Princess manifests a protective shield around a circular area. She may create the shield around any area within sight, taking a penalty on the activation roll equal to the area’s radius in yards, and may do so in
response to any action taken by another character within her line of sight. A bubble shield cannot form when it contain someone who does not wish to be contained. As a rule of thumb non-combatants that the Princess wishes to protect are acceptable targets. 

Normally creating a Bubble Shield takes an instant action, the Princess may forgo her Defence for a turn to invoke the shield as a Reactive action. 

Bubble Shields only last for a turn but if a Princess uses Bubble Shield to protect the same area as her next action, the new shield replaces the old with no gap of time.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The shield fails to appear, and the Princess leaves herself open to attack. She has -2 to her Defense this turn; if she sacrificed Defense, she loses her action this turn.

\emph{Failure:} The shield does not appear.

\emph{Success:} The shield appears, taking the form of a spherical section with the area’s radius. It will not cut through any solid object; if the shield cannot enclose an object it will stop at the object’s surface. In such cases the shield still forms a fully enclosed shape that presses tightly against obstructions. If there are no obstacles the shield simply forms a perfect sphere. The shield is not subject to the force of gravity - as long as it exists, it stays exactly where the Princess created it.

The shield blocks both movement and attacks through itself, in either direction, until the Charm ends. Unlike normal objects the shield has no Durability, but it has a Structure of 3x the activation successes; attacks made on targets on its other side are absorbed by the shield until the last Structure point is gone. (Should this happen the shield breaks, ending the Charm.) Damage in excess of the shield’s Structure passes through to the intended target normally.

\emph{Exceptional Success:} The shield will take a great deal of punishment before breaking.

\textbf{Upgrade: Adamant}

The shield behaves like a normal material, with Durability and Structure both equal to the activation successes. It provides transparent cover [GMC 200] against all attacks that must pass through it, in either direction. Removing the shield’s last point of Structure breaks it and ends the Charm, as before.

\textbf{Upgrade: Elastic}

The shield stretches when struck, and springs back unharmed; it is immune to bashing damage. Only lethal or aggravated damage will reduce its Structure.

\textbf{Upgrade: Lasting}

\noindent Duration: Inner Light turns

The shield endures for several actions before it must be renewed.

\textbf{Upgrade: Partial}

The shield can be shaped to cover parts of the circle, without surrounding the whole area; it can also be shaped as a flat plane

\textbf{Upgrade: Rainbow (Acqua \textbullet)}

The shield manifests as an iridescent film, which bends light that passes through it. Attacks from outside on those inside, or vice versa, take a penalty equal to half your successes, rounded down. Attacks on the shield itself are not penalized. If Adamant is also applied, the shield instead provides opaque cover against attacks that pass through it.

\textbf{Upgrade: Confining (Lacrima \textbullet)}

The Princess may create the shield around anyone, even her enemies.

\textbf{Upgrade: Beauteous (Specchio \textbullet)}

Like a brilliant pearl, the shield gleams richly in the light of the Noble's soul. Against such beauty, who dares raise a hand? All sapient or sentient beings must pass a Resolve + Composure roll, with a penalty equal to the lower of the Princess' Inner Light or Specchio Invocation, to attack the Bubble Shield.\end{myindentpar}

\subsubsection*{Wellspring (Shape \textbullet, Acqua \textbullet)}

\noindent Action: Instant, Dexterity + Science

\noindent Cost: 1 Wisp

\noindent Duration: Lasting or Indefinite\\

\noindent The Earth is mostly water, and by speaking to the Earth the Princess can find fresh water whenever she needs it. If there is water in the Earth the Princess draws it up into her hands but when the ground is parched she instead turns earth into water. Drawing up water has a duration of Lasting while the Transformation lasts Indefinitely, either way she gains one pint of water per Success. (Drinking Indefinate water is perfectly safe. Digesting it destroys the water and thus it's supernatural identity a transformed soil).

\begin{myindentpar}{10pt}\textbf{Upgrade: Purified}

Other liquids turn into fresh water as the Princess stirs them. Each success turns 1 gallon of liquid into drinkable water. The Princess need not be touching the ground to change an existing liquid.

\textbf{Upgrade: Flavoured}

The Princess may create any liquid that is safe for humans to drink. Each success draws up 1/2 pint of the drink you desire. If she applies Purified, each success transmutes 1/2 gallon of a liquid into something drinkable.

\textbf{Upgrade: Oily (Acqua \textbullet\textbullet)}

\noindent Cost: +1 Wisp

\noindent Duration: Indefinite

\noindent The Princess may now create any organic compound that is liquid at current temperatures, at the same rates as Flavoured.\end{myindentpar}


\subsubsection*{Bubble Wrap (Shape \textbullet, Aria \textbullet)}
\noindent Action: Instant, Wits + Survival\\

\noindent Duration: Successes Minutes, pay 1 Wisp for Inner Light minutes\\

\noindent Cost: 1 Wisp, additional 1 Wisp to extend duration\\

\noindent A Princess needs to breathe, but fresh air may not be always available. When this happens, she may just make her own.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The Princess doesn't manage to weave an adequate protection, and the failure disorients her. She takes the Deprived (fresh air) Condition and can't attempt to cast this Charm again until it's resolved, or goes away.

\emph{Failure:} The Princess fails to create a bubble sturdy enough for her purposes.

\emph{Success:} The Princess creates a gust of air which hangs in a bubble around her head. The magic filters the surrounding atmosphere so that inside its protection the Noble can always enjoy a breath of clean, fresh air. The standard duration of this Charm is 1 minute/success, but at any time the Princess may reflexively spend a Wisp to lengthen the duration by Inner Light minutes.

\emph{Exceptional Success:} The bubble is woven so well it lasts an extra minute each time a Wisp is spent.

\textbf{Upgrade: Puff Up}

+1 Wisp

The Princess is so proud of her powers she can make the bubble swell! By paying a Wisp once when activating or refreshing the Charm she can extend the area the Charm covers up a radius of Inner Light yards, centered on herself.

The Bubble is not, however, a shield. Its function is to merely provide breathing space and therefore any direct attack can harmlessly enter and leave its confines. Any attempt to alter the air composition inside the bubble however forces an instant Clash of Wills between the Princess and her opponent.\end{myindentpar}


\subsubsection*{Fire's Warm Kiss (Shape \textbullet, Fuoco \textbullet)}

\noindent Action: Instant, Stamina + Survival

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene

Fires under the Princess' hands burn without consuming their fuel. Until the Charm ends, reduce the damage the target fire does by the number of successes rolled. Things ignited by the fire, but separated from it, burn normally. A Princess may use Fire's Warm Kiss multiple times on one fire, until its damage has been reduced to 0. If a fire's damage is reduced to 0, it cannot ignite anything and feels merely warm to the touch, though it still sheds light. It can even be scooped off its fuel source, held in cupped hands, and poured into a container, like a liquid with the consistency of thick syrup. Fire so treated ignites its container once the Charm wears off, or goes out after 1 turn if the container is not flammable.

\subsubsection*{Nature's Harvest (Shape \textbullet, Legno \textbullet)}

\noindent Action: Instant, Dexterity + Survival 

\noindent Cost: 1 Wisp

\noindent Duration: Lasting 

The Princess coaxes a plant to produce its harvest ahead of time. If she isn't touching a plant reasonably near maturity or at least large enough to produce its crop, or if anyone has used the Charm on the plant within the past season, the Charm fails. (The plant must also have adequate soil and not be severely deprived of water or sunlight, but it need not be in season.) The normal use of this Charm is to obtain edible fruits, nuts, and/or berries from appropriate trees and bushes -- in this case, each success is as effective as two successes in foraging by mundane methods, but successes in excess of the plant's Size are wasted. Alternatively, it's quite possible to use the Charm more frivolously (e.g. to produce lots of flowers) or productively (to get lots of acorns from an oak tree or other appropriate seeds, for example), at the Storyteller's discretion.

The crops are guaranteed to stay fresh at least one day per dot of Legno unless some supernatural effect gets in the way. Nature's Harvest does not harm the plant. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Ascending}

\noindent Cost: +1 Wisp

The plant grows under the Princess's touch, even if it began as a mere seed; it achieves up to (activation successes) or its natural maximum in Size, whichever is lower, over the same number of minutes, and produces the expected harvest in the process. (The plant's growth will generally be limited by available soil for its root system.) Once the Charm is complete, the newly-grown plant remains a normal plant of its species (although it's advisable to water it well if one wants to keep it around).

\textbf{Upgrade: Miraculous (Legno \textbullet\textbullet)}

The plant no longer requires adequate soil, sunlight, or anything else as long as there's enough room for its base to be planted in the earth. However, the Charm's magic will only sustain the plant for (Legno) minutes after its growth is complete -- if it doesn't have enough water and room to grow, it obviously won't last long.

\textbf{Upgrade: Transfigured (Legno \textbullet\textbullet\textbullet)}

\noindent Requires Ascending

\noindent Cost: +2 Wisps

At the Princess's discretion, the plant produces any crop she needs regardless of its actual species. She can grow oranges from an apple tree, apples from a pine tree, or roses from a barrel cactus if she chooses. A single activation produces a harvest of just one species of plant. 
\end{myindentpar}

\begin{myindentpar}{10pt}\textbf{Upgrade: Lasting}

\noindent Cost: +1 Wisp

The Princess releases the scent continuously for the duration; anyone who comes within her Inner Light in yards until the Charm ends is affected.

\textbf{Upgrade: Subtle (Legno \textbullet\textbullet)}

The Princess may permeate an object with her fragrance by touching it; the next person who touches or smells it afterward is affected by the scent. The scent fades after someone has breathed it, or when the Charm ends, whichever comes first. If the Princess applied Lasting, a scented object affects everyone who touches or smells it until the Charm ends.\end{myindentpar}

\subsubsection*{Painting Roses (Shape \textbullet)}

\noindent Action: Extended, Wits + Crafts (1 Turn/roll)

\noindent Cost: 1 Wisp \\

\noindent With a touch the Princess makes something explode in a riot of colour. She can affect a Size up to her dots in Inner Light or the applied Invocation and may do anything from simple blocks of colour to a masterpiece, if she has the skills. The effects of this charm last as long as average quality paint.

This charm is best used for leaving marks and clues in the field or making art. Some Princesses of Spades, politely described as \textquotedblleft urban artists\textquotedblright , use this Charm to avoid the suspicions of carrying spray paint around.

\subsubsection*{Shape Earth (Shape \textbullet, Terra \textbullet)}

\noindent Action: Instant, Strength + Crafts

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene \\

\noindent In the Princess' hands, dirt and stone become as malleable as clay. She may manipulate rock or hard-packed earth (but not man-made rocklike materials like asphalt or concrete) with her hands as if it had the consistency of modeling clay, and as soon as she lets go of it it will retain its shape and regain its normal hardness. To sculpt a complex shape from the stone, the Princess rolls Dexterity + Crafts.

On an exceptional success on the activation roll, the Princess adds her Terra to the rolls to shape rock.
\begin{myindentpar}{10pt}\textbf{Upgrade: Artificial}

The Princess may reshape man-made minerals, such as asphalt, concrete and glass.

\textbf{Upgrade: Metallic (Terra \textbullet\textbullet)}

\noindent Cost: +1 Wisp

The Princess may reshape metals as easily as earth and rock.\end{myindentpar}

\subsubsection*{Corrosive Grasp (Shape \textbullet, Tempesta \textbullet)}

\noindent Action: Instant, Dexterity + Brawl

\noindent Cost: 1 Wisp, 1 resistant bashing damage

\noindent Duration: 1 scene \\

\noindent The index finger of a single hand (the Princess' choice) secretes a powerful, sharp-smelling acid until the Charm ends.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The acid only burns the Princess' hand. She takes a -3 penalty to any action which uses that hand until the damage heals.

    \emph{Failure:} Although the Princess' hand may smell vaguely vinegary for a while, the acid isn't concentrated enough or has too high a pH to have an effect.

    \emph{Success:} The acid can be used to get an equipment bonus of the activation successes for any action where it is appropriate. For example, in an interrogation, the ability to scar with acid can be used to get a bonus to Intimidate, while when opening a lock, the ability to dissolve the hinges gives a bonus to Larceny. If the Princess attacks this is treated as a damage 0 weapon, but it will do Lethal damage. 

    \emph{Exceptional Success:} No additional bonus, beyond the extra successes.\end{myindentpar}

\subsubsection*{Mirrored Item (Shape \textbullet, Specchio \textbullet)}

\noindent Action: Instant, Wits + Larceny

\noindent Cost: 1 Wisp \\

Manipulating a reflection is child's play for a Brat, and it shows, by spending a wisp a Princess of Mirrors may reach into any mirror and pull the reflection of an item of a size up to her Specchio. This reflection works just like the original, guns fire, phones make calls with one exception: The reflection is a mirror image of the original, text is reversed and the grip may be uncomfortable.

Reflections last for Specchio turns, but the original item only gets it's reflection back one Scene after the reflection fades.
\begin{myindentpar}{10pt}\textbf{Upgrade: Lasting}

Reflections last for Specchio times two turns.

\textbf{Upgrade: Stored (Specchio \textbullet\textbullet)}

\noindent Requires: Miss Poppins Bottomless Bag

A reflection is not always be needed immediately but later instead. To make this possible a Princess that knows Miss Poppins Bottomless Bag may pull a reflection into her bag instead of using it right now. This item suffers the same limitations as any normal stored item. Reflections in the bag do not expire until they are pulled out, at which point they are considered the same as a reflection that has just been pulled from a mirror. A reflection may not be put back into the back after having been removed from it and it may also not have been used prior to being put into the bag.\end{myindentpar}

\subsubsection*{Miss Poppins' Bottomless Bag (Shape \textbullet\textbullet)}

\noindent Action: Instant, unrolled

\noindent Cost: 1 wisp

\noindent Duration: 1 scene \\

\noindent Upon purchasing this Charm, the Princess adds a securely fastened bag or pouch of some kind to her Regalia. Activating the Charm unlocks the bag for a scene, after which it can be used freely. The Princess may store any number of items in the bag indefinitely, as long as each item is small enough to fit through the opening, and is light enough for her to lift without help. The Size of an object being stored or removed cannot exceed half the Princess' Inner Light (rounded up), unless she applies an Invocation when she unlocks the bag. If she applies an Invocation, she can store objects of Size up to her dots in the Invocation; the objects are the Charm's targets, so to apply an Invocation at no cost, all the objects stored or removed must be costless targets for that Invocation.

Putting an object in the bag is an instant unrolled action. Taking an object out is also an instant action, and succeeds automatically as long as the number of items in the bag is less than Inner Light + Larceny. If the number equals or exceeds this limit, the Princess must roll Wits + Larceny to find the right item in among the clutter; she takes a penalty on this roll of -1 for each item in the bag over Inner Light + Larceny.

\begin{myindentpar}{10pt}    \emph{Dramatic failure:} The Princess finds nothing in the bag, and is so occupied with searching that she loses her Defense for 1 turn.

    \emph{Failure:} The Princess pulls out the wrong item.

    \emph{Success:} The Princess takes out the item she wanted.

    \emph{Exceptional success:} The Princess finds the item immediately; she removes it as a reflexive action.\end{myindentpar}

Items that are put into the bag are safe from harm and protected from loss, as they are bound to the Princess rather than the bag itself. However, they aren't held in stasis; food will spoil if kept long enough. Moreover, while the bag is closed air can't get into it, so anything living will suffocate if trapped inside when the bag locks. Should the Princess herself die all items in the bag are lost. With the appropriate supernatural power it is possible to steal from a Princesses bag, but doing so requires a Clash of Wills.

\begin{myindentpar}{10pt}\textbf{Upgrade: Enlarged}

Stacks, up to 4

Add Inner Light again to the maximum number of items that can be put into the bag safely.

\textbf{Upgrade: Deepened}

Stacks, up to 2

Add 1 to the maximum Size of the items that can be put into the bag.

\textbf{Upgrade: Stretched}

\noindent Cost: +1 Willpower

The Princess can stuff a very large object into her bag. Double the maximum Size of items the bag can normally hold; the Princess can put one object up to that Size into the bag at a time. As long as that object is in the bag, the Princess can't put anything more into it, or take anything else out - the large object must come out first. If the bag locks before she takes the large object out, the Princess must apply Stretched again to remove it.

\textbf{Upgrade: Lightened}

\noindent Cost: +1 Wisp

The Princess can lift extremely heavy objects, for just long enough to drop them into her bag or pull them out. Add the Princess' Inner Light to her Strength when checking whether an object being stored or retrieved is too heavy for her to move.

\textbf{Upgrade: Conjured (Aria \textbullet\textbullet)}

The Princess can pull things kept in the bag out of thin air. When she applies Aria to take something from the bag, it appears in her hand as a reflexive action, ready to be used in the same turn. The object so taken returns to the bag again just before the start of the next turn. (This allows weapons that give a bonus to Defense to do so even after they've been used to attack.)

\textbf{Upgrade: Ordered (Acqua \textbullet\textbullet)}

The Princess arranges the contents of her bag in careful order. She may choose a number of objects in the bag up to her Acqua; when she applies Acqua to take those objects from the bag, she finds and withdraws them without a roll, no matter how many other things are stored inside. She may rearrange the objects within the bag, putting a different set on top, as an instant unrolled action.\end{myindentpar}

\subsubsection*{Ghostly Hand (Shape \textbullet\textbullet)}

\noindent Action: Instant, Dexterity + Athletics

\noindent Cost: 1 Wisp

\noindent Duration: concentration

The Princess shapes a Wisp into an immaterial hand, which can grasp things and move them around, but not use them. The hand has a Strength equal to the activation successes, to a maximum of the Princess' transformed Strength; it forms around an object within sight, and can lift or move it if it has enough Strength. Its Speed, when moving a light object, equals the Princess'. It can drop an object to pick up another close to it, but it cannot move more than one thing at a time.

\begin{myindentpar}{10pt}\textbf{Upgrade: Dextrous}

The hand can now manipulate what it grasps. The Princess may distribute successes to the hand's Dexterity, to a maximum of her own transformed Dexterity. She may apply her Skills to perform tasks through the hand, but takes a -2 penalty on all rolls.

\textbf{Upgrade: Forceful}

\noindent Cost: +1 Wisp

The hand can exert a strong, momentary force, lifting objects too heavy for its sustained strength. Its Stamina for this purpose equals the Princess' Inner Light.

\textbf{Upgrade: Free}

\noindent Requires: Dextrous

\noindent Cost: +1 Willpower

\noindent Duration: 1 scene

The hand moves and acts without the Princess constantly steering it; she has only to give it directions. She may perform other actions while the hand manipulates objects. Because her attention is divided, all her actions take a -2 penalty, and in any turn she acts the hand cannot borrow her skills -- its Skill for any action becomes 0.

\textbf{Upgrade: Touch of Air (Aria \textbullet\textbullet)}

The Princess forms a hand out of air itself, it is completely invisible unless you can see magic itself.\end{myindentpar}

\subsubsection*{Tool Whispering (Shape \textbullet\textbullet)}
\noindent Action: Instant and resisted

Dice pool: Wits + appropriate Skill - object’s Size/2

Cost: 1 Wisp

Duration: concentration \\


The tools of a Princess’ craft are so eager to serve her desires that she may operate them
from afar. The Princess uses this Charm on a single object that she can see; the Skill she uses
to activate it is the one used normally to operate that object (e.g. Computer for electronics,
Drive for a vehicle, Firearms for guns, and so on.)

\begin{myindentpar}{10pt}

\emph{Dramatic  Failure:}  The  Princess’  occult  force  mishandles  the  targeted  object  and
breaks it. Remove 1 point of the object’s Structure.

\emph{Failure:} The object remains inert.

\emph{Success:} The object animates, responding to the Princess’ will. As long as the Princess
concentrates, she may take mundane actions that manipulate the object’s internal mech
anisms - pushing buttons, flipping switches, turning knobs, and so forth. She cannot pick
the object up, or directly move it from its location; actions which require that fail automatically. Thus, the scope of possible actions depends on the complexity of the target object. A
simple tool with no moving parts can’t do anything; a gun can be made to unlatch its clip, or to fire, but can’t be aimed; a car can be made to start its engine and drive itself; a computer
can be operated almost normally, except for plugging in cables and peripherals.
The Princess cannot control the object if she loses sight of it, and the Charm ends when
she stops controlling the object. If someone else is using the object at the same time the
Princess controls it, that starts a Clash of Wills; a m
undane operator uses the same dice
pool for the Clash as he does for operating the device.

\emph{Exceptional Success:} The Princess controls her tool with great skill. Her mundane
actions to control it gain a +2 bonus.

\textbf{Upgrade: Charged}\\
Cost: +1 Wisp

The modern world runs on electricity, but when that’s lacking, the Princess can create
a few sparks to get it moving. When the targeted object is a machine powered by electricity,
the Princess may turn an extra Wisp into the power it requires, so it will run with a dead
battery or while unplugged during the Charm’s duration. However, a dramatic failure when
activating the Charm overloads its circuits - remove points of Structure equal to the Princess’
Inner Light.

\textbf{Upgrade: Dancing}\\
Cost: +1 Willpower\\
Duration: 1 scene

The targeted object, once animated, will carry out the Princess’ wishes without her conscious attention. The Charm does not end if the Princess stops concentrating on the object;
during any turn when the Princess does not control it, the object repeats whatever action she
most recently used it for. The object can’t adapt to changed circumstances, and will continue
mindlessly repeating itself until the Princess controls it again or the Charm ends.

\textbf{Upgrade: Forceful}\\
Cost: +1 Wisp\\

The Princess can now lift, push or pull the targeted object without touching it, as easily
as she manipulates it; while she does so, the object is surrounded with a visible sign of her
attention, such as a glowing halo, a heat shimmer, or a swirl of dust or leaves. The Princess can
move the object remotely with the same Strength that her muscles give her, and at a Speed
up to her own running Speed. She may also throw the object with a standard Athletics action,
although doing so immediately ends the Charm.

\textbf{Upgrade: Thinking (Acqua ••)}\\
Requires Dancing

When the Princess releases her concentration, in addition to providing the object with
further instructions she may grant it a measure of adaptability. For each dot of Acqua she may
instruct the object to react to one condition, altering its behavior in response. For conditions
that require senses to recognize, the object has a Perception dice pool equal to the Charm’s
activation successes.\\

\textbf{Upgrade: Free (Aria ••)}
The Princess may set her will not on a solid machine, but on the air that surrounds her.
Until the Charm ends, she can manipulate any object that she can see, as long as operating that
object is covered by the Skill she used to activate the Charm. The Princess cannot manipulate
more than one object at a time; when she moves to a second object, the first is no longer
animated.

\end{myindentpar}
\subsubsection*{Royal Roads (Shape \textbullet\textbullet)}
\noindent Action: Instant, Dexterity + Crafts

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene\\

The Princess crafts a path from herself to her destination. She may target anywhere that can be reached in Inner Light * 10 yards of construction without penalty, every additional ten yards applies a -1 penalty.

\begin{myindentpar}{10pt} \emph{Dramatic Failure:} The Princess tangles herself up and cannot move until she succeeds on a roll with the same dicepool as she activated this charm with, each turn she gains a +1 bonus to escape.
 
\emph{Failure:} No road is formed.

\emph{Success:} The Princess creates a path to her destination. This path will be as straight as possible, baring intervening obstacles. If this path would be too steep to walk the Princess creates a ladder instead. The road is wide enough for a single person to walk or run comfortably.

\emph{Exceptional Success:} Anyone travelling on the road gets +2 to speed and +1 to Athletics rolls as the magic beneath their feet propels them onwards.

\textbf{Upgrade: Winter's Way (Acqua \textbullet\textbullet\textbullet)}

Touching water the Princess freezes a path of ice. Winters way can only be used to create flat paths across water but it allows for longer and wider paths. The maximum length doubles and the width increases to four meters. Though only the thinnest layer of ice it is magically reinforced and can carry even heavy traffic. Unless the Princess applies Skater's Paradise her magical ice will be steady beneath the feat and creates no Tilt. 

\textbf{Upgrade: Skater's Paradise (Acqua \textbullet\textbullet\textbullet)}

Cost: +1 Wisp

The Princess may apply the Ice tilt to any path created by Royal Roads.\end{myindentpar}

\subsubsection*{Hedge Magic (Shape \textbullet\textbullet, Legno \textbullet)}

\noindent Action: Instant, Stamina + Survival

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene

A dense thicket springs up somewhere in sight, forming a six foot high wall. The hedge-wall has a Structure of 3x the activation successes and 0 Durability however it can only be damaged by appropriate tools. Bullets won't do much. The length of the Hedge is Legno x5 Yards. When the Charm expires, the thicket wilts, losing all its Structure.

\begin{myindentpar}{10pt}\textbf{Upgrade: Thorny}

The hedge is covered in vicious thorns. Anyone who is thrown onto the hedge takes Bashing damage. Roll the Princess' Legno. If they try to climb the hedge they take the same damage every turn of climbing.\end{myindentpar}

\subsubsection*{Darkling's Treasure (Shape \textbullet\textbullet, Lacrima \textbullet)}

\noindent Action: Instant, Manipulation + Occult

\noindent Cost: 1 Wisp, Compromise at Belief 8+ with a +1 modifier

\noindent Duration: 1 scene \\

\noindent By brushing her hand across an object, the Princess makes it deeply attractive to the servants of the Darkness. She may apply the Dark Lure condition to any object, except the Focus of a Tainted Place. The Lure's radius is equal to the activation successes x 100 yards.

\begin{myindentpar}{10pt}\textbf{Upgrade: Trapped (Lacrima \textbullet\textbullet)}

When the Princess applies the Dark Lure modifier she may add the destructive modifier.\end{myindentpar}


\subsubsection*{Touch of Frost (Shape \textbullet\textbullet, Acqua \textbullet)}
\noindent Action: Instant and resisted, Dexterity + Crafts - target's Defense

\noindent Cost: 1 Wisp

\noindent Duration: 1 scene\\

\noindent With a touch the Princess freezes an inanimate object in place.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The Princess freezes herself, not what she touches; she suffers from the effect of an ordinary success, at a level equal to her Acqua.

\emph{Failure:} The target is chilled briefly, but suffers no impediment from it.

\emph{Success:} The target's temperature immediately drops below freezing. A solid object is encased in a thin layer of ice, and any attempt to use it during the current scene is penalized by the activation successes (maximum of -5, again) as the user's hands slip off it, though this effect is not magical and can be countered. Objects with buttons may be entirely inoperable.

\emph{Exceptional Success:} A targeted object is damaged if the Princess' Acqua exceeds its Durability - warping from the sudden chill removes 1 point of Structure.\end{myindentpar}

\subsubsection*{Made to Order (Shape \textbullet\textbullet\textbullet)}
\noindent Action: Extended , Dexterity + Crafts (1 turn/roll, threshold = object's Availability rating)

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene\\

\noindent The Princess crafts a useful tool from whatever material is at hand. Once she has reached the required successes she may continue rolling to add successes to the equipment bonus (with a maximum of +5). She can make anything that a skilled craftsman, such as a blacksmith, could create without power tools. Afterwords it functions as a mundane tool, the items created by this charm are not particularly well suited for combat, their primary function cannot be a weapon and they always suffer from the improvised weapons penalty.

\begin{myindentpar}{10pt}\textbf{Upgrade: Grown to Order (Legno \textbullet\textbullet)}

Duration: Lasting

With a seed in her hand the Princess compels it to grow, in mere seconds, into a suitable tool. The result must be made completely from wood but in exchange it will last permanently, unless it breaks.

\textbf{Upgrade: Ice Sculptures (Acqua \textbullet\textbullet)}

The Princess is freed from chains of logistics, she can craft tools from the very moisture in the air instead of any convenient nearby materials or the contents of her backpack. This costs an extra wisp unless there is dense fog or water nearby.

\textbf{Upgrade: Armoury (Tempesta \textbullet\textbullet)}

The Princess can create weapons as easily as any peaceful tool. She is still limited to what an expert can create with their hands, but even guns were hand-made once.\end{myindentpar}

\subsubsection*{Diamonds are Forever (Shape \textbullet\textbullet\textbullet, Terra \textbullet\textbullet\textbullet)}

\textbf{Action:} Instant\\
\textbf{Dice pool:} Dexterity + Crafts - target's availability\\
\textbf{Cost:} 2 Wisps, 1 Willpower\\
\textbf{Duration:} indefinite\\

\noindent A Princess of Hearts can always find a noble gift. The Princess can transmute the substance of small objects into minerals of her choice - earth, sand, rock, even precious stones. The penalty to her dice pool equals the Availability of the object after the Charm takes effect; it’s much harder to turn things into jade than granite. The Charm’s target must be an inanimate object of Size 1 or less, made of a nearly homogeneous material, that the Princess is holding in her hands.

\begin{myindentpar}{10pt}\emph{Dramatic Failure:} The object explodes into jagged shards. The Princess takes 1 lethal damage from fragments in her hands.

\emph{Failure:} The object is unchanged

\emph{Success:} The object is transmuted into the desired mineral.

\emph{Exceptional Success:} The object is transmuted into a perfect example of the desired mineral. If the mineral is valuable, the Availability of the object’s final form is one dot higher.\end{myindentpar}

\subsubsection*{My Home is My Castle (Shape \textbullet\textbullet\textbullet)}

\textbf{Action:} Extended, 30 minute/roll, threshold = Sanctuary Size + shield’s Structure (choose before rolling)\\
\textbf{Dice pool:} Resolve + Crafts\\
\textbf{Cost:} 2 Wisps, 1 Willpower\\
\textbf{Duration:} indefinite\\

\noindent The Princess enchants a Consecrated place, creating an enormous invisible dome of magic around it, the borders of this magical shield adhere to the edges of the consecrated ground. When any ranged attack, magical or mundane, attempts to cross the dome it instantly solidifies becoming both visible and impenetrable. For the remainder of the scene the barrier is essentially a solid transparent object. It has a structure equal to the Charm's Activation Successes - Sanctuary Size and a Durability equal to the Princess' Inner Light or any applied Invocation, whichever is higher. At the end of the scene where the barrier blocks an attack the Charm ends, unless the Princess spends a Wisp and a Willpower point to extend the duration for an additional scene. 

Like a solid object, any attack which penetrates the barrier will leave physical gaps. Attackers may use aimed shots to shoot through holes left by a successful attack or attempt to create an opening through which attackers can enter. Security minded Princesses make sure to choose defensible locations, because even a powerful Princess is unlikely to create a barrier that can stand up to a truck being driven into it at speed. Most Princesses just throw barriers around their family home because they don't get to choose where their loved ones will live. 

Until the barrier blocks an attack anyone may pass through. Once the barrier solidifies only the Princess herself may pass through the barrier and she does so as though it was not there. she may also shoot through the barrier using Levinbolt or other magic, however if the Princess uses a mundane gun the barrier will not recognise the bullets as the the Princess'. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Garrisoned}

Modify the roll by Commonality

The Princess names an organisation when she activates the Charm, and applies the Commonalty modifier for that organisation. Members of the organisation can pass through the barrier as though they were the Princess herself. Moreover, if any of these members has a pool of Wisps, he can spend Wisps to sustain the dome just as the Princess can. Beacons may use a point of Willpower in place of a Wisp. 

\textbf{Drawback:} Unless the Princess is a member of the organisation she looses all privileges of access and is treated as no better than a stranger by the shield.

\textbf{Upgrade: Barricades (Fuoco \textbullet\textbullet\textbullet)}

The time per roll decreases to one minute. 

\textbf{Drawback:} The duration also decreases to 1 scene. 

\textbf{Upgrade: Forward Base (Tempesta \textbullet\textbullet)}

Cost: +1 Aggravated Damage

The time per roll decreases to one minute and the Charm no longer requires consecrated ground to function. The Princess names whichever border she wishes.

\textbf{Drawback:} The duration also decreases to 1 scene. 

\textbf{Upgrade: Queen's Protection (Lacrima \textbullet)}

The Court of Tears will do anything to protect what they love, and the Ravens are among the best defenders in the Nobility. When calculating the durability of the barrier, double the Princess' Lacrima up to a maximum of 10. 

\textbf{Upgrade: Rebuilding (Legno \textbullet\textbullet\textbullet)}

When the barrier is destroyed the foundations remain and begin creating a fresh shield. They begin immediately after the barrier falls, either due to taking too much Structural damage or due to a scene ending. After approximately 24 hours the new shield is ready to go. 

\end{myindentpar}

\subsubsection*{Strength of the Tides (Shape \textbullet\textbullet\textbullet, Acqua \textbullet\textbullet)}

\noindent Action: Extended, Resolve + Athletics (1 turn/roll)

\noindent Cost: 2 Wisps/roll

\noindent Duration: concentration \\

\noindent The Princess takes control of a body of water within sight, making it flow and push as she wills. The Charm controls a circular area of water of the activation successes in yards, to a depth of 1 yard; left in that shape, it lifts and moves everything inside it with a Strength of 1. The Princess may gather the water into a taller mass of smaller radius to concentrate its power; each halving of the radius quadruples the water's depth or height, and adds 1 to its Strength. She may also move the water in a wave or spout, carrying along whatever floats in it; the water's top Speed is 8 if moved this way. The Charm does not create water -- if the Princess gets more successes than she needs to control all the water available, the extra successes have no effect.

\begin{myindentpar}{10pt}\textbf{Upgrade: Violent (Acqua \textbullet\textbullet\textbullet)}

The water becomes violently agitated, creating smashing waves and sucking undertows that batter anything caught within it. Each turn, the Princess may choose to inflict bashing damage equal to the water's current Strength on everything in or floating on the water.

\textbf{Upgrade: Free (Acqua \textbullet\textbullet\textbullet\textbullet)}

\noindent Cost: +1 Willpower

\noindent Duration: 1 scene

The Princess can release the water, do other things, and take control of it again. In any turn she is not shaping the water, it flows to its natural level, dropping anything it was lifting that doesn't float.\end{myindentpar}

\subsubsection*{Mist's Protection (Shape \textbullet\textbullet\textbullet, Aria \textbullet\textbullet)}

\noindent Action: Instant, Manipulation + Stealth

\noindent Cost: 2 Wisps

\noindent Duration: successes in turns \\

\noindent The Princess summons a thick fog that conceals her presence. An area with a radius equal to (10 x Inner Light) yards, centered on her, gains the Mist Tilt. This persists for at least as long as the Charm. In strong sunlight or moderate wind the cloud disperses when the Charm ends; in calm, cloudy weather, it may last as long as the Storyteller wishes.




\subsubsection*{Burrow (Shape \textbullet\textbullet\textbullet, Terra \textbullet\textbullet)}

\noindent Requires: Shape Earth

\noindent Action: Extended, Stamina + Crafts (5 minutes/roll)

\noindent Cost: 1 Wisp/roll

\noindent Duration: Lasting \\

\noindent Using her hands alone, the Princess digs a tunnel through earth, stone, or similar materials such as concrete or asphalt. Each activation success allows the Princess to shape or remove around 30 cubic feet of dirt or 15 cubic feet of stone in any arrangement she desires (though she must be able to touch the earth to move it, so the tunnel made should be at least wide enough to accommodate her.) The tunnel is permanent, but the Princess must roll Strength + Crafts to reinforce it properly; if this roll fails, the tunnel will collapse after an hour or so.

\subsubsection*{Shelter Sweet Shelter (Shape \textbullet\textbullet\textbullet\textbullet)}
\noindent Action: Strength, Intelligence + Crafts (15 minutes/roll, threshold = 15)

\noindent Cost: 2 Wisps

\noindent Duration: until sunrise\\

The Princess creates a small building, no larger than sixteen feet by sixteen feet. Her structure is well made and will protect her from any reasonable amount of rain or cold but not from extreme weather such as a hurricane or even a normal day in a harsh desert. Against physical danger the walls have a durability of five and the doors will not open to anyone but the Princess and her invited guests.

The drawback is that these buildings tend to be exceptionally noticeable, by default they follow a similar theme to the Princess' Regalia but applying an Invocation will instead follow the appropriate Queen's style:

\begin{itemize}
 \item Acqua: Art deco made from ice, crystal or glass on a modern frame.
 \item Aria: Straight out of Arabian Nights in gentle blues and greens.
 \item Fuoco: Ancient Inca with lots of gold.
 \item Legno: Brightly patterned tents on a living wooden frame.
 \item Terra: Gothic made from red granite and shining marble.
 \item Lacrima: Pagodas adorned with funerary flags
 \item Tempestra: Steel military fortresses
 \item Specchio: A fairytale palace covered with statues of the Princess.\end{itemize}

The Princess may build a more humble abode at a -3 penalty (though this breaks Specchio's Ban).

\begin{myindentpar}{10pt}\textbf{Upgrade: Forest Lodge (Legno \textbullet)}

The Princess enchants her palace to protect against the beasts of the Earth. No animal will attempt to enter her home uninvited, a good way to keep those pesky mosquitoes out. Supernatural animals are unaffected while animals under a supernatural compulsion that compels them to enter trigger a Clash of Wills roll between the Princess and their controller. 

\textbf{Upgrade: Summer Palace (Fuoco \textbullet\textbullet)}

The Princess enchants her palace to protect against the fiercest heat. It wouldn't do much good on Venus but it's good enough for just about anywhere on Earth. While inside the temperature will remain at 25 degrees or lower.

\textbf{Upgrade: Winter Palace (Acqua \textbullet\textbullet)}

The Princess enchants her palace to protect against the fiercest heat. It wouldn't do much good on Pluto but it's good enough for just about anywhere on Earth. While inside the temperature will remain at 20 degrees or higher. 

\end{myindentpar}

\subsubsection*{Breath of Boreas (Shape \textbullet\textbullet\textbullet\textbullet, Acqua \textbullet\textbullet\textbullet)}

\noindent Action: Extended, Intelligence + Science + weather modifier (5 minute/roll, threshold = 5)

\noindent Cost: 3 Wisps

\noindent Duration: 1 or more scenes\\

\noindent The North Wind blows and winter comes at the Princess' call. When she reaches the threshold, clouds come from the north and cover the sky in a 1 mile radius centred on the Princess, creating the Heavy Rain tilt [GMC 209]. The storm lasts for the rest of the current scene. The Princess is not protected from the weather she has summoned (not, at least, by this Charm.)

Furthermore, for every 3 successes the Princess accumulates over the threshold, she can tune the weather further to her liking, adding one of the following effects.

\begin{itemize}
    \item Biting: The North Wind brings forth the winter. The Extreme Cold Tilt [GMC 210] applies throughout the affected area with a -1 penalty or the existing penalty increases by -1 to a minimum of -5.
    \item Hailstones: Ice begins to fall from the sky. The Hailstones Tilt applies throughout the affected area. 
    \item Icy: Freezing rain falls in the area, coating all surfaces in ice. The Ice Tilt [GMC 210] applies throughout the affected area.
    \item Snowing: Snow falls in great quantities, imposing the Blizzard Tilt [GMC 208] throughout the affected area.
    \item Duration: The weather, and the tilts it creates, last for another scene.\end{itemize}
                                                                            
 
Current weather conditions modify the activation roll: cold extreme environment (+ level), other extreme environment (- level), already Raining (+3), thick clouds (+1), clear sky (-1), drought (-3). The Charm cannot be used more
than once a day in a single area.

\begin{myindentpar}{10pt}\textbf{Upgrade: Loyal (Acqua \textbullet\textbullet\textbullet\textbullet)}
The Charm encloses the Princess in a bubble of warm air, protecting her from the cold she has invoked. The Princess takes no penalties or damage from the extreme environment, and if she wishes she can suppress any or all Tilts imposed by the Charm within a radius of Inner Light yards of herself, or reimpose them, as an instant action. Each Tilt can be suppressed or released independently.\end{myindentpar}
                                                                                                                                                                                                                                                                                                                                                                                                       

\subsubsection*{Bring Down The Sky (Shape \textbullet\textbullet\textbullet\textbullet, Aria \textbullet\textbullet\textbullet)}

\noindent Action: Extended, Strength + Science(threshold = 5, 1 turn/roll)

\noindent Cost: 3 Wisps

\noindent Duration: 1 scene \\

\noindent The Princess raises her hands to the sky and summons the wrath of a storm. Once she reaches the threshold, the sky fills with dark clouds and winds start to blow in a radius of 1 mile, building in seconds to a gale (the Heavy Winds Tilt [GMC 209]) that lasts until the Charm ends. 

Furthermore, for every 3 successes the Princess accumulates over the threshold, she can apply one of the following effects. She may wait to choose which effects to apply until the turn she needs one.

\begin{itemize} 
 \item Heavy Winds: The winds grow even stronger, increasing level of the Heavy Winds Tilt [GMC 209] by one to a maximum of three
 \item Lightning: As an instant action, the Princess rolls her activation dice pool; a bolt of lightning strikes one target within sight, doing 1 lethal damage for each success. General armor reduces this damage.
 \item Duration: The Charm, and the Tilts it creates, last for another scene.\end{itemize}

Current weather conditions modify the activation roll: already windy (+3), thick clouds (+1), clear sky (-1), or calm (-3). The Charm cannot be used more than once a day in a single area.

\begin{myindentpar}{10pt}\textbf{Upgrade: Uplifting (Aria \textbullet\textbullet\textbullet\textbullet)}

The storm guides itself to help the Princess who summoned it. High winds do not penalize her actions, and hailstones do not strike her if she calls them to the place she stands. Moreover, she can apply accumulated successes for another effect:

\begin{itemize}\item    Speed - the storm winds always blow at the Princess' back, carrying her more swiftly to her destination. The Princess adds +1 to her Speed and Initiative until the Charm ends. She can apply this effect a maximum of 3 times.\end{itemize}\end{myindentpar}

\subsubsection*{Sacred Grove (Shape \textbullet\textbullet\textbullet\textbullet, Legno  \textbullet\textbullet\textbullet)}

\noindent Action: Extended, Presence + Crafts (1 hour/roll)

\noindent Cost: 2 Wisps/roll, 1 Willpower

\noindent Duration: 2 + Inner Light days \\

\noindent The Princess cultivates an area into a calm, tranquil garden that bolsters the abilities of herself and her allies. She takes the appropriate supplies (ie, plants, seeds, soil, water, etc.) and augments them with her magic to create a grove that instills peace, confidence, and competence. The garden may have any appearance, though most Princesses who take this Charm follow the lead of Bonnie Getsuei and make serene Japanese-style gardens, with cherry blossoms constantly floating through the air. 

Apply the Sacred Grove to Condition to the area, allocate blessings as you desire. Each activation success may be allocated to one of the following benefits, which apply to anyone within the garden:

  \begin{itemize} \item  +1 on rolls with a specific Skill (to a max of +3).
  \item  +1 Defense (to a max of +3).
  \item  +1 to meditation rolls.
  \item  +1 to social rolls to resolve differences peacefully.
  \item  +1 to Resistance Attributes when resisting or opposing supernatural effects. \end{itemize}

The total number of successes allocated may not exceed 10. The area of the garden (measures in square feet) cannot exceed 50x Inner Light square feet. The physical garden remains after the Charm ends, though the supernatural effects lapse, and the Princess may use the Charm again to re-create the garden's calming qualities. However, the Charm cannot be used on a garden already under its effects, or on any part of such a garden.
\begin{myindentpar}{10pt}\textbf{Upgrade: Blessed}

Stacks

Each time the Princess takes this upgrade, raise the total number of successes she may accumulate by 3.

\textbf{Upgrade: Tranquil (Legno \textbullet\textbullet\textbullet\textbullet\textbullet)}

The garden may be arranged to soothe disturbed minds and prick consciences. When cultivating it, the Princess may allocate up to two successess to preserve anyone in the garden from internal torment. For the purposes of Conditions that depend on Belief, Integrity or equivalents (such as Madness) or for the duration of Hauntings, treat Belief or it's equivalent as though it were one higher for each success. 

She may also allocate 2 successes to give +1 to Breaking Point or Compromise rolls made by people who have spent at least one hour in the garden within the past 48 hours. 

Finally, she may allocate 2 successes to give anyone who sleeps in the garden 1 additional Willpower point, on top of the point regained normally through rest.\end{myindentpar}

\subsubsection*{Earthquake (Shape \textbullet\textbullet\textbullet\textbullet, Terra \textbullet\textbullet\textbullet)}

\noindent Action: Instant and contested, Strength + Brawl vs. Dexterity + Composure

\noindent Cost: 2 Wisps

\noindent Duration: 1 scene

The Princess claps her hands, then touches them to the ground, and the earth buckles and shakes, pitching wildly and throwing her enemies off-balance. She applies the Earthquake tilt to a circular area with radius equal to the activation successes in yards. 

The Charm cannot be used if the Princess is above ground level. If she is underground the earthquake will be exceptionally potent, though it may simply cause a cave in destroying everything and potentially killing everyone nearby.

\begin{myindentpar}{10pt}\textbf{Upgrade: Sheltering (Terra \textbullet\textbullet\textbullet\textbullet)}

People the Princess chooses, up to her Inner Light, are not affected by the Tilt. Their balance is enhanced and falling rocks avoid them. This protective magic is powerful but limited, if the Princess completely destroys the area she is in or it is otherwise implausible for somebody to be unaffected she cannot protect them.\end{myindentpar}

\subsubsection*{Enduring Beauty (Shape \textbullet\textbullet\textbullet\textbullet, Specchio \textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Extended, Dexterity + Larceny (1 minute/roll, threshold = target's Stamina + supernatural advantage + dots in the Striking Looks Merit)

\noindent Cost: 2 Wisps, 1 Willpower

\noindent Duration: Lasting

Beauty is the only true constant in the world, the Queen of Mirrors knows. Not personal beauty, for that can fade and die, but the beauty that comes from righteousness and enduring strength. It is the calculus of rule that inspires her to take beauty from fools who might waste it. The Enlightened learns to peel the beauty from others, and craft it into valuable gems. These gems also have metaphysical potency, and can be used to enhance magic. This Charm must be used against a target who is asleep, or otherwise incapacitated or restrained.

\begin{myindentpar}{10pt}    \emph{Dramatic Failure:} The noble can only mar her own beauty. She inflicts 3 points of aggravated damage, as the beauty peels away from her flesh, and furthermore suffers the \textquotedblleft Ugly" Condition until all of this damage has healed.

    \emph{Failure:} She cannot properly get her fingers under the flesh, and inflicts a point of Bashing damage on the target, who if they are asleep can roll Wits + Stamina to wake. If she has not got the necessary number of successes by the time the roll has ended, the target wakes automatically, and the Princess suffers a point of Lethal damage, as her fingers wear away.

    \emph{Success:} Successes are gained. The target suffers a point of Bashing damage, and if they are asleep, may roll Wits + Stamina, at a -3 penalty to wake. Incapacitated or restrained targets have no such defence.

    \emph{Exceptional Success:} If 5 successes are gained in a single roll, the target does not take damage, and does not get a roll to wake. If five successes are gained over the target number, the Princess is feeling generous, and can leave a residual of beauty to the target; they do not gain the Ugly Condition, unless they had no dots in the Striking Looks merit to begin with. There's no helping some people.\end{myindentpar}

If the required number of successes are attained, the princess peels the metaphysical beauty away from the face of her target, which comes away like a thin layer of skin, which then coalesces into a gem. If the target had no dots in the Striking Looks merit, it is a cheap stone, dull and lacking lustre, worth Resources 1. If they had Striking Looks 1, it is attractive and valuable, a moderate value sapphire, emerald or ruby (frequently matching the colour of their eyes) worth Resources 3. If the Princess is lucky enough to find someone with Striking Looks 2, it is a diamond almost without compare, worth Resources 5. An individual targeted with this Charm loses all dots in the Striking Looks merit, if they had any, and gains the Ugly Condition. The effects on appearance are not obviously magical; even the most beautiful target is recognisable themselves after this is used, merely... lacking the gleam of beauty they once had.

The gems produced are metaphysically potent. When holding one in her hand, the Princess may, reflexively, cause it to crumble to dust, destroying it utterly. It adds a number of Successes equal to its resources value to any one roll of hers which are in line with the Specchio Invocation. If they are stolen, any Princess can use them for this purpose. In addition, if taken to Alhambra, the followers of the Queen of Tears convert them into lantern fuel. If the gem is returned to the person it was stolen to, it need only be pressed against their forehead to restore their former beauty.

Unless used on a consenting target, this is Inflicted Major Hardship on Another, and so is a Belief Compromise. Apply a -1 penalty. Knowingly using a gem created by Enduring Beauty without evidence that it was created consensually can also be a Compromise, there is no penalty to the roll.
	
\subsubsection*{Through the Looking Glass (Shape \textbullet\textbullet\textbullet\textbullet, Specchio \textbullet\textbullet\textbullet\textbullet\textbullet)}

\noindent Action: Instant, Dexterity + Occult

\noindent Cost: 3 Wisps, 1 Willpower

\noindent Duration: Indefinate \\

\noindent The Princess can enter the world behind any Mirror. Inside she will find a perfect reflection of everything the Mirror can see. This does mean that any text is backwards and climbing into a funhouse mirror is... weird. One thing worth noting about objects inside a mirror - including the counterpart of the mirror itself - is that they are entirely immovable and indestructible: the only way to affect them is to affect the real object they are reflections off. Real items the Princess brings with her behave as normal. Any person or item she brings into the mirror world will cast an intangible reflection back into the real world.

Inside a mirror any area that cannot be seen by that mirror (from any angle) is nothing more than solid glass that stretches on for infinity, or until the next place visible from that mirror. By rolling Specchio (no Wisp cost, this glass counts as targeting a Mirror) the Princess may carve out one Size point of Material per Success. This creates a little hidey hole invisible from the outside world perfect for storing weapons, valuable Bequests or bringing boyfriends you don't want your mother to know about. These hidey holes last until the mirror is destroyed or moved, Once either occurs nothing, not even returning the mirror to it's origonal spot can recover any stored items. No one knows what happens to a person lost this way but it probably isn't pretty.

While inside the mirror any area that usually can be seen by that mirror but cannot due to circumstance, say someone's thrown a blanket over the mirror in the real world, is covered by pure darkness (no relation to the Outer Dark) that numbs all five senses. This however is not any more dangerous than normal sensory deprivation and some Princesses even make use of it for such.

Two mirrors reflecting the same area will lead to the same mirror world, though parts of it may well be separated by walls of glass. This world would be safe until the last mirror is removed. However two mirrors set up to reflect each other can be quite dangerous. While inside the mirror world you can use the second mirror to recursively enter a second mirror world. Some Princesses use sequences of mirrors as elaborate \textquotedblleft passwords\textquotedblright\, but the risk of being lost forever in an ever deeper chain of worlds means most stay far away.

Exiting the mirror world requires using this Charm a second time. Any Princes who knows this Charm can also escape by simply jumping through the mirror. Knowing the Charm permanently gives a Princess the ability to bypass the usual indestructibility of reflected objects for this one purpose. Of course, this has all the usual effects of jumping through glass. 

\begin{myindentpar}{10pt}\textbf{Upgrade: Secure}

By spending 1 Wisp a Princess can fix a mirror in place. It gains Durability equal to her Specchio against both damage and any attempt to move it requires Specchio successes on a Strength + Athletics roll. This Upgrade is meant to provide security for a Princess' use of a mirror world, using indestructible mirrors as defensive positions should not be permitted. Charms do depend upon the emotions that invoke them.

This durability does not apply to deliberate attempts to smash (say, by jumping through) the mirror by the princess herself, it does however cover accidents.

\textbf{Upgrade: Leading}

With this Upgrade the Princess can now lead others through Mirrors. Each extra person or five Size points of equipment costs an additional Wisp.

The Princess does not have to go first. It is acceptable to push someone through with the intent of trapping them.\end{myindentpar}


\subsubsection*{Stone Servitor (Shape \textbullet\textbullet\textbullet\textbullet\textbullet, Terra \textbullet\textbullet\textbullet)}

\noindent Action: Extended, Presence + Crafts - Durability (1 minute/roll, threshold = 10)\\

\noindent Cost: 3 Wisps, 1 Willpower\\

\noindent Duration: 1 scene\\

\noindent More than any other Court the Princesses of Hearts wish to become leaders, and just sometimes when they have no followers they can create their own from the Earth itself. Performing this Charm requires eight size points worth of stone or Earth and the target material's Durability is subtracted from the roll, normally the bare soil beneath her feat will be sufficient (it's certainly easier and less destructive than animating a building's wall).

When the Princess reaches the Threshold make one final roll to determine the servitor’s attributes. If this roll scores no Successes the Servitor is still created, but weaker.

As a mindless being Servitors use the same Power, Finesse and Resistance attributes as Ephemerial Beings. They do not however have Banes or Bans. Servitors begin with one dot in each attribute and the Princess may assign an additional Inner Lights + Successes dots to each attribute, up to her own maximum Transformed Attributes. In addition a Servitor's size is seven and it's speed is equal to Power (they're not very fast), however if they get up a head of steam they can really get going. A Servitor can sprint up to four times it's normal speed, but it can only accelerate or decelerate by it's speed every turn without running into a wall (and sometimes not even then).

Unlike many such magical constructs a Princess' Servitor is powered by emotions, beliefs and intent. As such it is very good at understanding it's instructions. For example if a Princess instructs it to build a wall it will understand exactly where the Princess wants the wall and how she wants it, at least as well as the Princess herself knows her own desire. If she tells it to put a box in the car the Servitor will understand she wants it to open the door first (whether it's fingers can gently open a door is another question). What a Servitor can't do is react to changing circumstances without the Princess giving it fresh instructions, if she asks it to dig a well it will dig straight through any historical artefacts it might uncover.

In battle servitor's are deadly, but slow and clumsy. For this reason their attack dicepool is Finesse alone, however their fists are treated as weapons with a Damage rating equal to Power, maximum of five. Regardless of their actual strength, being hit by a large mass of stone is dangerous and causes lethal damage. Servitor's also have Armour equal to half their Resistance (round down). Servitors act at the same initiative ranking as the Princess who created it. They are also vulnerable to being hijacked by magic, though if their creator is nearby she can defend her creation by initiating a Clash of Wills. If a Servitor is injured it can be healed by magic, the Charm Stitch will do it, but without magic it has no ability to heal.

A Princess may only ever have one servitor at a time.

\begin{myindentpar}{10pt}\textbf{Upgrade: Tireless Duty}

Cost: +1 Willpower Dot

The Princess can create a Servitor that will last indefinitely, barring physical destruction. The drawback is that, in addition to the increased cost, the Princess cannot change it's instructions after it has been given it's first and only orders.

If the Princess changes her mind or the Servitor completes it's duty then she may regain her Willpower Dot (or her experience if she as already brought back her Willpower) by touching the Servitor and withdrawing her magic. Even if the Servitor is destroyed the Princess can recover her magic so long as it's ruby heart is intact. The ruby heart has only one point of structure but a Durability equal to the Princess' Inner Light + Terra. \end{myindentpar}




\section*{Queens}

To say that the Queens are impresive is an understatement. The leaders of the Nobility are nothing short of demigods. Currently there is only one living Queen that a Princess is likely to meet face to face, and The Lady of Alhambra certianly does live up to expectations. She has demonstrated a life span of melenia and her personal magic is strong enough to keep her city safe deep within the heart of the darkness. 

Becoming a Queen is not a core theme of Princess but it is a minor theme, one possibility among many, and it is entirely possible for the Queen of Tears to appear as a character in your game. So how does one become a Queen? What can her Royal Majesty acomplish with her magic? 

\subsection*{Coronation}
Becoming a Queen requires two things, an Inner Light of six or more and a people who follow you and love you as a leader. Specifically it requires at least a small country and an approval rating of around eighty percent to support one Queen. It goes without saying that the love and support of your people is by far the harder requirement. 

When a Princess has both she begins to feel a connection to her people growing within her soul. The churning mass of public opinion echos within her, looking towards her for gidance. The Princess must discover for herself what it means to be a leader and a figure of adoration, and she must learn how to channel other people's Belief in her into magic just as she uses her own Beliefs. In practical terms she must decide on her philosophies, and she must construct a new Invocation from those philosophies (in all honesty, if she has come this far she probably knows her philosophies already, but creating an invocation from them requires a significant amount of magical experimentation). 

When the Princess is ready she spends 12 exp to buy six dots in her own Invocation. The churning mass of her people's belief has been given direction, both in a mundane-political sense by her leadership and in a metaphysical sense by her Invocation. She is now a Queen.

\subsection*{Royal Magic}

The power wielded by the Queens is the power of a leader, the power of a people united. A Queen's Charms are not much greater than a Princess' but they are far larger. Just as a Queen makes her nation greater through her rule, she makes it greater through her magic. A Queen can combine both Intimacy and Commonality, spreading her blessings across millions almost as easily as a Princess might bless a small intimate gathering. Simply by existing a Queen's Philosophies resonate through the souls of every man and woman who shares her values, becoming an Invocation. 

On a personal level Queens benefit from some modest benefits. A Queen's maximum Attributes, Skills, and Invocations are increased by five, except for her own Invocation which may go up to fifteen. A Queen may also use both her own and the Courtless style of Practical Magic and use Royal Charms. The increase in power between a five dot Charm and a Royal Charm is comparable to the increase between a four and a five dot Charm.

\subsubsection*{Sample Royal Charms}

\textbf{Boolean Magic (Royal Govern)}\\

\noindent A personal favourite of The Lady of Clear Water. This Charm allows the Queen to create a free floating knot of magic that, if supplied with wisps, can run preprogrammed magical routines using boolean logic and if-than-else conditions, these conditions can depend upon information from the ordinary five senses or the results of other Charms (including information gathered from Learn Charms).\\

\noindent \textbf{Pocket Realm (Royal Shape)}\\

\noindent By using similar principles to Miss Poppin's Bottomless Bag, but on a much vaster scale, a Queen can create her own private reality. A pocket realm is entirely empty save for what the queen brings herself, it doesn’t even contain air. The realm's size is effectively unlimited, if the Queen wants more space she can simply invoke this Charm again to expand her realm.\\

Pocket Realm is one of the Royal Charms suspected to be used in the construction of Alhambra, but it is far from the only possibility. Some Princesses believe Alhambra exists on the inner surface of a city sized bubble shield that holds back whatever power destroyed the Kingdom. The Queen of Tears keeps the details of Alhambra's security close to her chest; like so much about The Fall, the truth is unknown.\\

\noindent \textbf{Resurrection (Royal Restore)}\\

\noindent A Queen's can bring back the dead, so can Princesses, but Queen's are better at it. Resurrection works just like the Charm Resuscitate, but with a couple of key advantages: Firstly it is possible to bring someone back who has been dead for up to a number of days equal to the Higher of the Queen's Inner Light and the Applied Invocation. Secondly the target does not loose a dot from her highest attribute. 

However after someone has been dead for a while, the power required restore life is enormously taxing, even for a Queen, and costs a Dot of Inner Light instead of a dot of Willpower. This dot can be brought back with experience, but even so no Queen brings back the dead casually.

\subsection*{Death and rebirth}

A Queen is not immortal without the aid of certain Royal Charms, and even if she can live forever it would not be psychologically healthy to go for more than a few centuries. None of this concerns the Queens, for they are able to reincarnate just as any other Princess. 

When a Queen dies her invocation does not immediately vanish from the world, it fades gradually along with her emotional and cultural legacy. So long as the kingdom she led remains stable this process can take generations, more than enough time for the Queen to be reborn. 

A reincarnated Queen is born without magic and Blossoms into a Princess, not a Queen. She has only one tiny innate advantage over any other Princess, she can always buy her own Invocation at it's favoured rate (and if her Invocation has faded from the world, this benefit fades with it). However the former queen can have enormous external advantages: The hardest part of becoming a Queen, building a Kingdom, is already done and her former people are probably eager to help the next incarnation of their beloved Queen regain her former splendour. This combined with memories and experience from her past lives is often enough for a Queen to retain her Kingdom across reincarnations. 

Something else must be mentioned, what happens if the Kingdom falls before the Queen? A Queen's power comes from her people, without them she is \textquotedblleft only\textquotedblright\, a Princess. She can retain her Attributes, Skills, Transformed Attribute and Transformed Skills even if they are beyond her normal maximum, all other benefits are lost. 

The active Queens shows that the magic behind this process is not quite as simple as that (is magic or emotions ever simple?). The inhabitants of their Kingdoms survive in the Dreamlands, and this is enough for them to retain their thrones, however their enormous powers only exist within the Dreamlands. Outside of those sleeping realms they have no power, save that Princesses can learn and use their Invocations. The Queen of Storms seems to need no kingdom and the Queen of Mirrors... well no one knows what's going on with Mirrors. 

\myframe{
\subsection*{Empresses?}

The Queen of Storms has led scholars among the Radiant to question if there is a stage even beyond the rank of Queen. Proponents of the \textquotedblleft Empress Theory\textquotedblright\, say that it is a logical progression to transition from resonating in the souls of those who believe in your ideals, to literally existing within the souls of humanity. Opponents of the theory point out that that the Queen of Storms is the only Queen known to have lost her fundamental humanity, something which goes against the principles of the Light.

\vspace{4 mm}

The question therefore becomes: Is the Queen of Storms an Empress gone wrong? Or is the very concept of an Empress a betrayal of the Light?
}