\chapquote{The Dreamlands}{I can't go back to yesterday because I was a different person then.\\ \textemdash Alice}

\phantomsection\label{cha:Dreamlands}


\begin{multicols}{2}\raggedcolumns

The home of the Five Queens, a land of infinite wonder that, for every Princess, lies just beyond the wall of sleep. The hopes, hearts and aspirations of all mankind are writ large into a patchwork of kingdoms and cities, ... and a land where, once upon a time, the Hopeful slumbered, trapped within in webs of illusion, drawing them away from the real world's pain.

\section*{The Trap}

The monstrous armies that conquered the Light's Kingdom in the age before history were led (or so modern Princesses assume) by subtle and devious generals who wished to secure the Darkness' victory for all time.  They found a way to prevent the return of Princesses, the Light's most capable servants, by constructing a trap for their souls, deep within the mind and soul of the world.  The trap was a mirror, reflecting the Light shining on the world; it drew to itself the souls of the Princesses who died in the Kingdom's fall, and enfolded them within an endless dream where the kingdom's glories stood eternal and it's armies fought the Darkness and defeated it at every turn, without disputing its sway over its new conquest.

And the trap worked, possibly beyond its makers' expectations: not only were the Princesses of the Kingdom's day drawn into the dream and held, but so was everyone whom the Light touched and empowered in all the long ages since.  And as the millenia passed the Queens basked in the memory of long forgotten glories deep within the Dreamlands while the Darkness shrouded the world.

\section*{The Release}

And then, everyone within the dreaming Kingdom was struck by revelation: they knew, quite abruptly, that they were dreaming, and life in a truer reality lay open to them.  Many of them took the opportunity immediately, returning to the bodies of fetuses just conceived; and these were born, and grew, and flourished, and before long they Blossomed, becoming the first Princesses of the modern age.  And as they Blossomed, the new Princesses discovered that the lands of dream they had left to become human again still existed; for gates to those lands stood open to them whenever they slept, and the souls they left behind welcomed their visits, begging for news of the waking world.  Many more souls have followed those first pioneers; new Princesses are born and Blossom every year.

Naturally, the Hopeful wondered what it was that revealed the Dreamlands' true nature to its inhabitants.  Over the decades since the Release, speculations have been floated, arguments proposed and refuted. No shortage of Lightbearers have claimed credit. It's now generally believed that the key event was the first landing on the Moon in July of 1969.  The Queen of Diamonds argues that the Dreamlands are in some metaphysical way linked to the Moon, that their property of reflecting a more fundamental reality is tied to the Moon's appearance of shedding light that in fact is reflected from the Sun.  And so, in her opinion, when a human foot trod the lunar surface, by proving the Moon to be not luminous in itself, it also proved the Dreamlands to be not real in themselves ...

\section*{Entering the Dreamlands} 

\begin{quote}Have you been half asleep and have you heard voices? I've heard them calling my name. \\
Is this the sweet sound that called the young sailors? The voice might be one and the same... \\
\rightline{\textemdash\, Kermit the Frog} \end{quote}

Even now, after the Release, the last fragments of the Trap call out to the Hopeful as they sleep, and it may show any Princess a passage back to the Dreamlands. The Trap, or what remains of it, finds it easiest to tempt a mind in pain, one who yearns for somewhere better to escape to. Most freshly Blossomed Princesses first discover the Dreamlands through the pain of Sensitivity, in the midst of their pain they feel a promise of comfort and guidance that lingers in the back of their mind. 

With the Trap's hook in her she will, apparently by chance, come across an entrance to her Crawlspace when she next falls asleep. Just how this happens varies \textendash\, one Princess notices an odd-looking animal and follows it to a burrow; another gets up in the middle of the night for a glass of water and notices a door that wasn't there before. The entrance is, however, always difficult to get through in some way; usually, it's too small to walk through standing up, forcing the Princess to crawl (This and the uncomfortable conditions inside the Crawlspace are essentially an attempt by the Princesses' subconscious to keep her out of the Dreamlands' trap, despite the Dreamlands no longer functioning as a prison). 

For most Princesses it can be assumed that they acquired and resolved the Girl Underground Condition before the game begins or during the prelude, and they might learn of the Queens and joining a Court in the process. More experienced Princesses can recognise the trap's siren song for what it is and are less likely to take the Girl Underground Condition, and those who do acquire the Condition often keep themselves awake until they can arrange for friends to meet her in the Dreamlands. Escaping the creaking remnants of the Trap might be easy these days but why take unnecessary risks?

A Princess who has visited the Dreamlands, even once, can deliberately search for a passage anywhere and those who haven't can still search for an entrance if they have guidance from someone who has. Shikigami are skilled at helping their students find the Dreamlands and a Court to join. Searching for an entrance to the Dreamlands calls for an extended Inner Light + Empathy + Shadows roll (for the trap calls loudest to those with a heavy heart), with a target of eight Successes, the Princess now rolls once every five minutes.

\begin{myindentpar}{10pt}    Dramatic Failure: The Princess cannot find an entrance in this location, or anywhere else before she's had a full night's rest.
    
    Failure: The Princess makes no progress. If the extended action fails the Princess cannot find an entrance in this location, or anywhere else before she's had a full night's rest.
    
    Success: The Princess progresses. Once she accumulates eight successes, she finds an entrance.
    
    Exceptional Success: The Princess makes great progress. The Princess also gains the Steadfast Condition, as she searches for an entrance into the Dreamlands the thought of stepping into the fantastic unkown fills her with excitement and resolve. 
    
    Modifiers: The Princess is sleepy (+1), the Princess is wide awake (-1), hot chocolate or warm milk (+1), old building with mysterious corners (+1), other people are present (-1 per witness)\end{myindentpar}

Once found, a Crawlspace entrance continues to exist as long as the Princess remembers it, and vanishes if she forgets it. (One Princess had a doorway in the depths of her bedroom closet, which faded while she went to university. A few days after coming home, when she needed to visit the Dreamlands, she remembered the old door and there it was.) Opening a known entrance is not quite automatic, but only a simple Inner Light + Empathy + Shadows roll is required, with modifiers as above. A dramatic failure on this roll means something has gone wrong with the entrance - the door remains locked, or sticks shut; or it seems to open, but the path is blocked by a deadfall too heavy to move; or the trail along a high cliff has washed out. Whichever it is, the Princess can't reach the Dreamlands that night.

\begin{mybox}

\subsection*{The Threshold of Sleep}

If the Princess enters the Dreamlands in the presence of witnesses it can be helpful to know when exactly she falls asleep.

If the Princess is awake when she travels to the Dreamlands, she falls asleep the instant she spends a Wisp to unlock the Crawlspace. She may collapse on the spot or sleepwalk to her bed. If the Princess' trip to the Dreamlands is triggered by the Girl Underground Condition or a White Rabbit she never wakes up at all. She transitions to the Dreamlands as part of REM sleep; climbing out of bed and into the Crawlspace is simply part of the dream. Footsteps, animal tracks, or other small reminders that she finds in the morning may be the result of sleepwalking or a subconscious use of magic. Usually that only happens the first time she opens a new Crawlspace.
\end{mybox}

Crawlspace entrances are not truly physical passages, though they appear as such; they are in fact mnemonic devices. Thus one Princess cannot use another's entrance \textendash\, in fact, she can't even see the other's entrance. It's possible, though, for one Princess to help another Princess or dream traveller find an entrance she knows of. This works as a form of teamwork; the Princess rolls Presence + Expression as she tries to get her friend excited about the \textquotedblleft\, magical door" she found. If the Princess succeeds her friend rolls the lower of her usual dice pool to enter the Dreamlands and the Princess' successes,. If the friend fails the roll than even the Princess cannot access the Crawlspace tonight (this restriction has led to quite a few dream travellers embarrassing themselves when they tried to show mortals a Crawlspace). 

Even if two Princesses can see the same Crawlspace they cannot enter together without invoking the Charm Ivory Gate. Without that Charm an experienced Princess who wishes to introduce a newcomer to the Queens must arrange to rendezvou at a location they can both find and then travel through the Dreamlands together. Shikigami do not have this restriction, they can follow any Princess they are bonded with into the Crawlspace. 

Entering the Crawlspace requires spending a Wisp. Exactly how a Crawlspace opens varies with the shape of the entrance. It could be as simple as turning a button handled key to unlock a small door, but spending the Wisp might instead make the Princess dexterous enough to squeeze through a rabbit hole, turn her insubstantial so she can slip between the join where two of her bedroom walls meet or shrink down until she's small enough to climb down the gap between her mattress and the tailboard of her bed. Onlookers, on the other hand, see the Princess drop off to sleep at this point, or walk off in a reverie to bed.

Inside the entrance, Crawlspace is narrow and claustrophobic, governed according to dream logic by both the Princesses subconscious and the form of the entrance. The Princess who climbs down the bottom of her own bed could spend the entire Crawlspace climbing down the folds of her bedsheets cramped between the mattress and the tailboard or she could quickly find herself climbing down actual cliffs with freezing winds and claustrophobic mists but she probably will find herself climbing.

Normally, a Princess in Crawlspace simply presses on to the Dreamlands, or turns back and awakens. Waking up in Crawlspace requires nothing more than a wish to do so. Pressing on calls for more effort, as the difficulty of the path is nothing more than the Princess' subconscious warning her about the Dreamland's Trap it cannot stand against a Princess' concious desire to press onwards. Even the weakest, least athletic Princess is guaranteed to scale to harshest cliffs if she only tries. A Princess who follows the Dreamlands' lure along the easiest path, never turning aside, always emerges somewhere in her Queen's capitol (Courtless Princesses arrive in the Dreamlands representation of something they have a strong Intimacy to) and no roll is required to do so. From that point (and only that point) the Princess can return and awaken at will. 

Side passages abound, though, and a Princess can find her way to almost anywhere in the Dreamlands she knows well by choosing her steps wisely. A side-path takes just as much time and labour to follow but also requires a Wits + Empathy roll to find the correct path. The roll has a modifier based on the strength of her Intimacy to whatever her intended destination is a reflection of in the real world, and a further modifier for each day's travel outwards from the centre of the Dreamlands that her destination lies.

   \begin{myindentpar}{10pt}  \emph{Dramatic Failure:} The Princess emerges in the wrong place within the Dreamlands, and cannot reopen Crawlspace there; she must find a useful landmark (a Dreamlands reflection of something she has Intimacy to). Take the Lost Condition.
   
    \emph{Failure:} The Princess emerges at her usual entrance point.
    
    \emph{Success:} The Princess emerges within an hour's walk of her desired destination.
    
    \emph{Exceptional Success:} The Princess emerges at her desired destination.
    
    \emph{Modifiers:} Emotional connection to whatever the destination area represents (Intimacy modifier); her entrance point, her Queen's domain or her Embassy's building (no Intimacy modifier); distance from the centre of the Dreamlands (-1 per day's travel outwards); the Princess takes others along (-1 per two people); the Princess is travelling a familiar route (+1); the Princess has some suitable prop for navigating her Crawlspace such as a torch for a dark cave, climbing gear or warm clothes for freezing cliffs (+1, regardless of the usual equipment bonus).\end{myindentpar}

Whatever form the Crawlspace takes, it is filled with memories from both her current and past lives. A Princess climbing down freezing cliffs might catch sight of cave after cave; one crawling through mud and crumbling brickwork at the bottom of a well could find peep-holes formed by cracks in the masonry. Often snatches of sound, smells, or fleeting glimpses try to grab the Princess' attention with promises of important forgotten knowledge or memories of happier times, another way the Princess' subconcious tries to keep her from the Trap. Many Princesses turn aside from the Crawlspace's main path to search through these memories, hoping to find bits of wisdom from a life in the Kingdom's day, or to witness again a scene that has faded from their conscious memory. 

If a player character tries this, she first names the memory she wishes to find. Something like \textquotedblleft the last time I saw my father before he mysteriously disappeared\textquotedblright\, or \textquotedblleft my previous life's first meeting with a Queen\textquotedblright . The description must be specific enough to identify a single memory, if a Princess wishes to trawl through her memories for useful information she needs to use the White Rabbits Merit. 

Once the Princess has chosen the object of her search she makes an extended Intelligence + Empathy roll; the Storyteller sets the threshold, according to the importance the memory being sought for has to the Princess.

   \begin{myindentpar}{10pt}  \emph{Dramatic Failure:} The Princess finds the wrong memory, or worse, she stumbles upon a nightmarish memory; the Storyteller may call for a Sensitivity check.
   
    \emph{Failure:} The Princess makes no progress to finding the memory.
    
    \emph{Success:} The Princess makes progress to finding a the memory she wants. If the memory doesn't exist she discovers this. If the roll passes the threshold the Princess experiences the memory in whatever way best fits the story: She may watch it through a keyhole, find it written in a book, pick up a memento and suddenly remember everything, relive the event, or even enter a fully interactive recreation of the past. 
    
    \emph{Exceptional Success:} When the Princess accumulates enough successes she will discover the memory is particularly useful. In addition to any other benefits she takes the Informed Condition. 
    
    \emph{Modifiers:} Eidetic Memory (+2), strong emotions attached to the memory (+1), dull memory such as hours spent in a library searching for an enemy's weaknesses (-1), the Princess has some suitable prop for navigating her Crawlspace such as a torch for a dark cave, climbing gear or warm clothes for freeing cliffs (+1, regardless of the usual equipment bonus).   
	\end{myindentpar} 
	
Once the Princess has found the memory the player may make an additional roll or rolls to derive some practical benefit from it. She could roll Resolve + Investigation to see past the distorted face of a childhood nightmare and see the real appearance of her father's terrifying business partner and gain a Clue into his disappearance. Or by revisiting an enormous row with her friend she can speak to representations of the emotions that overwhelmed her during the argument and roll Manipulation + Empathy to work through her feelings and create a proper Plan for repairing the relationship.

As a generalization Princesses search through their Crawlspace to confront complex emotional knots or to access memories that are impossible to connect to consciously such as those from a past life. A Princess who's simply forgotten her computer password will likely prefer to sit down and rack her brain than to crawl through a muddy thorny briar looking for it while the nature of dreams and memories means that dreaming your way into the memory of a crime scene can't provide the same purely factual record as photographs.  
    
\bigsidebarstart

\subsection*{Who can enter the Dreamlands?}

Princesses are not the only the only ones who can access the Dreamlands. The Dreamlands belongs to all of humanity after all.



Psychics and Thaumaturges with the Dream Travel Merit or Ritual are able to enter the Dreamlands of their own accord. The Dreamlands are not the only collective mindscape of mankind. As a rule an individual Psychic will only have access to one mindscape, one that's appropriate to his personality or perhaps his powers. Similarly Thaumaturges can only access one mindscape, but in this case the defining variable is which Tradition she belongs too.



It is worth noticing that most Psychics and Thamaturges have no greater connection to the Light than most Mortals. The Dreamlands trap is not targeted at them, and they have no subconscious warnings when entering the Dreamlands: To them the Crawlspace looks very different. It resembles the door to wherever they strongest associate with feelings of home, safety and security. Stepping through the door they find themselves in an idealised memory of that place. This functions identically to the crawlspace for all practical purposes: Including reliving memories and short-cutting through the Dreamlands.



Beacons and Sworn do not have the natural ability to enter the Draemlands, they must be lead by a Princess or another astral traveller. They can however allow themselves to be lifted into the Dreamlands by the mechanisms of the trap and may enter if they have the Girl Underground Condition.



Changelings can walk through and reshape dreams, when they are personal to the dreamers. The Dreamlands, though, aren’t private, but shared among all those touched by the Light. A changeling can observe them through a sleeping traveller, and even join the dreamer there, but attempts to shape the Dreamlands fail abjectly. A changeling treats a Dreamlands traveller as a dreamer in a Bastion with the normal traits; entering the Bastion takes the changeling to the Dreamlands near the traveller, and he may leave the Dreamlands as if they were a Bastion as long as the traveller has not left. However, if the traveller wakes before the changeling leaves, the changeling becomes trapped - he can leave only by finding another traveller and persuading her to guide him to the entrance she used. Dreamweaving doesn’t work at all.



The Beasts (from Beast: the Primordial) walk between supernatural realms with remarkable ease, and their nature as embodied nightmares makes the Dreamlands especially amenable to them. If a Beast successfully uses Under the Bed on a character in the Dreamlands, he appears next to the character’s Dream Form and may choose to stay there rather than continue to his Lair. Any Beast who knows of the Dreamlands may open a Primordial Pathway to a location within them, at the same modifier he uses for places in the Temenos. And Beasts can make Chambers in their Lairs from places in the Dreamlands just as they do in the waking world.



Finally some Mortals simply dream their way into the Dreamlands by accident. From their perspective it is nothing more than a particularly vivid dream.

\bigsidebarend

\section*{White Rabbits}

A White Rabbit, in the jargon of the Nobility refers to any time when the Princess is called to the Dreamlands. Her subconscious mind detects a change within the Dreamlands and sends a signal \textendash\, a White Rabbit \textendash\, to alert the conscious mind that there is something they should see. The creaking lures of the Dreamlands trap and the resulting Girl Underground Condition are not considered White Rabbits but this is just an arbitrary quirk of the definition chosen by Enlightened scholars. Quite a few Princesses really do see White Rabbits (sometimes straight out of Alice's Adventures in Wonderland). This appears to be a result of the Princess' unconscious associations, caused by Enlightened scholars using the term White Rabbit for the phenomenon.

\subsection*{Prophecy Rabbits}

A Prophecy Rabbit calls the Princess into the Dreamlands to witness an event that foretells the future on Earth. The Princess is fully present in the Dreamlands and may interact with the portentous events she witnesses in all the normal ways: She might investigate to uncover more clues, or perhaps try to derail the event in the Dreamlands. This doesn’t actually help, but it can feel very satisfying.

If two or more Princesses are experiencing a prophecy about the same event, they are both are in the same place within the Dreamlands and can simply start talking to each other. Debating the vision or making plans. In essence, this can be considered another clue both Princesses learn from the dreams. Something along the lines of \textquotedblleft This other Princess cares about the same issue, perhaps you could work together?\textquotedblright

How Prophecies work is unknown. It is generally accepted that the Princess is reacting to a pre-existing event in the Dreamlands but what causes those events is a mystery. The two most popular theories are the clairvoyant model and the analytical model. The clairvoyant suggests that every human has microscopic traces of psychic abilities which when combined in some sort of shared unconscious \textendash\, like the Dreamlands \textendash\, becomes effective on a practical level. The analytical model also sees the pooling of human talent and knowledge at the cause, but argues rather than psychically foretelling the future humanity simply predicts it using knowledge and reasoning.

Prophecy Rabbits are most common the result of the White Rabbits Merit, the Storyteller can also create a Prophecy Rabbit to get a story going.

\subsection*{Memory Rabbits}

Unlike most White Rabbits a Memory Rabbit leads a Princess not into the Dreamlands, but deep into her own Crawlspace. The Princess' subconscious mind is signalling her conscious that she has forgotten some vital information and calls her deep into her own mind and soul to fish it out. Most Memory Rabbits lead to memories from a past life, the ordinary human processes of memory are usually sufficient for memories gathered in this incarnation (and sometimes even for stronger memories from past lives). 

In game terms a Memory Rabbit functions as an alternative result when a player uses the Merit White Rabbits or when the Storyteller wishes to start a plot. If the Storyteller believes she can provide clues in a more interesting way by going to a memory from the Princess' past life than a prophecy in the collective dreamscape of mankind then she is free to do so. Memory Rabbits can also be used to justify buying Skills or Charms when the Princess knew them in a past life, or just to develop a character by confronting key issues from the Princess' past. 

\subsection*{Royal Rabbits}

Trapped within the Dreamlands the Queens cannot affect Earth, but they can affect the Dreamlands and a Princess' subconscious can notice such changes. The Queens have gotten quite good at making the precise changes needed to create a Royal Rabbit that summons a Princess to wait upon her liege.

Royal Rabbits typically manifest in some way appropriate to the Queen, such as a white rabbit wearing the royal colours and carrying a letter of summons stamped with the Queen's seal. They can serve as a third alternative to provide clues via the White Rabbits Merit or to kickstart a plot. 

\subsection*{Black Rabbits}

Black Rabbits are spoken of in hushed terms, their mere existence makes the Princess question her own mind and doubt her visions. It goes like this: If the Princess followed a Prophecy Rabbit to the dreamlands and saw a woman in green and white tearing through the reflection of her home town she might conclude that she better deal with any Princesses of Storms before it's too late.

Now what if this happened in reverse. Someone with access to the Dreamlands \textendash\, such as a Princess of Tears \textendash\, wants the Princess to go after local Furys. She could travel to the Dreamlands, dress in green and white and attack. The destruction in the Dreamlands would alert the Princess: A fake Prophecy Rabbit, a Black Rabbit.

Now it's not easy, the Dreamlanders will defend their home and the deception is only as good as the skill of the one who crafts it. This doesn't mean it hasn't happened, it has. Many times.

\subsection*{Empty Rabbits}

Empty Rabbits are almost as mythical as Black Rabbits. Sometimes a Princess' intuition is simply wrong. She follows a White Rabbit to the Dreamlands and finds nothing more than a mad tea party or a highly symbolic heap of nonsense. Some Princesses believe Empty Rabbits do not exist, that they actually mean the Princess has overlooked some vital clue pointing to one of the other Rabbits. But how would you tell?

Empty Rabbits rarely have an impact on the story, but sometimes Princesses can confuse a Rabbit for an Empty Rabbit, or a Empty Rabbits for a Rabbit.

\subsection*{March Hares}

While not as mythical as Black or Empty Rabbits the March Hares are considered to be the most unsettling of all the Rabbits. A Princess who follows a March Hare travels deep into her own Crawlspace and comes face to face with a deep division in her own psyche. She may do battle with her own madness or sit down for tea, scones and high brow debate with both sides of the ethical dilemma that has puzzled her all week. 

In game terms March Hares are simply an excuse for more roleplaying. A Princess who wins a battle with her own madness is not cured, but she understands what that madness means to her and might be energised to seek therapy (or less inclined if she lost the fight). Facing her own dilemmas gives screen time to the Princess' thoughts and feelings, and maybe even some character development. March Hares can even be used when under the effects of hostile magic: If the Princess is unaware of the enchantment or magically prevented from acknowledging her situation, then when the magic wares off going into her own Crawlsapce to fight the spell and unlock the memory vaults is a more dramatic way to reveal the truth than just saying the spell has worn off. 

Since March Hares are at heart a way to give screen time to important moments of a character’s internal conflicts the player is always entitled to forgo the dice and choose the result they prefer.

\section*{Topography}
The Dreamlands are an exceedingly varied place. Sometimes you can stumble across one man's neuroses writ large across the landscape (while most other humans never even feature), while in other places you can walk along a stairway made of light, up into the heavens to walk along the surface of a Mars covered in unknown ruins inscribed in runes which do not resemble the Royal Tongue. You may stumble across a town which appears almost like the real world, save that none of the brands match, and the streets are filled with a parade of strange, eternally dancing figures of bronze. A Princess could be walking down a quiet forest path only to turn a corner and find herself facing an elegant renaissance city where the buildings all merge together into a solid block that gently curves away from the ground. Or she might find arriving at a quiet country village where the people are friendly, the sun is shining but the buildings look like cubist art and the inhabitants seem to have stepped from the scrapbook of a 
slightly drunk dada artist. One Nakama found a cursed area, almost overshadowed by the Darkness, where the sharp-fanged folk ritually consumed their victims. Only one made it out alive, the monsters dragging the others to their altars and eating them in a way that killed them in the real world, hunks of flesh torn out of their sleeping bodies, in the name of the \textquotedblleft Red Word\textquotedblright.

The wild districts where these things can be found are all, however, some days' travel from the centre of the Dramlands \textendash\, the Dreamlands' cartographers say that one moves outward to find them, and inward to return.  The most confusing thing about navigating the Dreamlands is that \textquotedblleft inward\textquotedblright\,and \textquotedblleft outward\textquotedblright\,have no simple relationship with the ordinary three dimensions of space... and there are any number of districts that lie further inwards of other districts, but at the same north/south and east/west position. Dreamlanders say their home is folded on itself; north/south, east/west and up/down they call the traveling directions, and in/out are the folding directions. 

Arranging the Dreamlands' counties by their folding positions, ignoring their travelling positions, shows that the Dreamlands lie within a roughly circular area with the Foundation at its rim, and a trip straight from the Foundation to the Dreamlands' center (if that were possible) would take seven days' or so walking. Arranging the Dreamland's by it's travelling directions and ignoring the folding directions shows that the Dreamlands is a simple globe. Some Princesses describe the Dreamlands as a series of globes ordered from innermost to outermost. Moving north, south, east or west moves across the surface of a globe, walking inwards or outwards travels between the globes. This sounds a lot simpler than when you're standing on a Dreamlands crossroads and can see six directions, which in turn is a lot simpler than when you wake up the next morning and try to remember how you understood it. 

The Dreamlands often changes quickly as one travels. There's a feeling the the Foundation is below, and \textquotedblleft below\textquotedblright\,is consistent. Apart from that all bets are off. Despite appearances ranging from bizarre to normal places within the Dreamlands often seem to reflect places on Earth, or the popular idea of places of earth, or (more strangely) places found only in novels, or ideas, or concepts. Even odder is that regardless of how normal or how bizarre the places look, a visitor can (eventually) learn to understand how they work. A city might look like it was designed by a collaboration between M.C. Escher and Dr Seuss but it still has a government, an economy, trade with nearby settlements, residents with homes, jobs and families. With lots of time and effort a Princess can learn how it all works. Just as she can learn what it reflects from Earth, and even discover new things about what it reflects.

The distance outwards from the center has an importance in the Dreamlands beyond the way it allows districts to overlie each other.  The mysterious, reality-bending Gales that blow through them rise and fall constantly, but how swiftly they change depends on how far away the center is.  Near the center itself, when reflections of those concepts most stable within the hearts of humanity lie, the Gales hardly vary at all, and the districts there remain stable.  Going outwards, the districts have Gales that are normally calm, but gust occasionally and strongly, leaving behind drastically altered landscapes. At the outermost reaches the Gales are a constant maelstrom and the land shifts hourly at best.

A further oddity of these reflections is that, while they frequently contain things with writing on them, the writing never looks like the text that would appear in the reflected place.  In minor cases, Princesses might find a discarded fast-food box, but the script on it is flowing and cursive, elaborately decorated in gold leaf. In more extreme cases, everything is written backwards, or there are never any vowels, 
or the scripts are from another part of the world entirely. Less obvious is that these reflections are chock full of houses. Wherever the Princess travels she will occasionally catch a glimpse of a door, window or a snatch of a wall in the corner of her eye only to realise it was just a tree and a trick of the light. If the Princess really looks, the dream domains can seem to be built of nothing but houses folded in on each other in defiance of any sane geometry. Scholars are divided as to whether these houses are merely a representation of some human's connection to the place or concept this Dreamlands domain is reflecting. Or if these houses are physically a person's soul, visible everywhere in the Dreamlands they have an emotional connection too. Regardless, the question is academic. There is no way physically affect them and people almost never come out, they simply exist. These strange houses are unrelated too the dwellings used by Dreamlanders, which are much less mysterious and easier to enter.

In the most distant, farthest outward lands, the Gales blow wildly, falling still for a moment only to burst anew with immense force.  It is here that the traveler may find herself walking through a man's nightmare, magnified to a country of dread.  It is here, also, that she may find a space grown strangely thin and tenuous, where objects can sometimes vanish while her back is turned; or a place jumbled with curios and wonders brought together, though by no obvious means, from every corner of the world.  There are tales of monstrous or alien things to be found in the far outward districts: a redoubt of Alhambra in a district haunted by Darkness; a waste of ash and cinders where Goalenu mold porcelain figurines that hunt with burning green eyes; a snow-capped peak, topped by a fortress made of clockwork ticking away in a slow rotation, from which gray-robed figures gaze through telescopes at the Dreamlands' stars.

\section*{Travel}

For all that they function according to dream logic, the Dreamlands resemble something close to a coherent if surreal world. A Princess who wishes to get from one part to another can simply walk or (with the right Charm) fly to her destination. One wishing for an easier trip may negotiate passage with a Dreamlander. Depending on where she is she might find anything from 19th century sailing ships that glide across the ground, to friendly dragons happy to take a passenger, to Heath Robinson-esq contraptions piloted by anthropomorphic frogs, to a modern airport with helpful travel agents. All the Courts have established modes of transportation available to a Princess.

When travelling through this immense landscape, the Hopeful also have a unique advantage: as long as they have any Willpower left, they are able to open a way into Crawlspace from almost anywhere in the Dreamlands, and return through there to waking life or a place in the Dreamlands they already know well. A Princess trying this rolls Resolve + Empathy, with am Intimacy modifier for the strength of her emotional connection to her current location, and a further modifier for each day's travel she is outward from the Foundation. (If she is at her entrance point, no roll is needed.)

 \begin{myindentpar}{10pt}   Dramatic Failure: The Princess cannot open Crawlspace here; she must move at least an hour's walk before trying again.
 
    Failure: The Princess fails to open Crawlspace.
    
    Success: The Princess notices one of the many houses that forms the dreamlands and realises it is her home, she opens the door, steps inside and enters her Crawlspace.
    
    Exceptional Success: The Princess enters Crawlspace, and is at +2 to navigate it.
    
    Modifiers: Modifiers: Emotional connection (Intimacy modifier); her entrance point, her Queen's domain, her Embassy (no Intimacy modifier); distance from the center of the Dreamlands (-1 per day's travel outwards)\end{myindentpar}

Opening Crawlspace from the Dreamlands side does not cost Willpower, but a princess at 0 Willpower cannot manage it until she recovers at least 1 point. Once a Princess re-enters Crawlspace in this way, she must clamber through a maze of side-passages, looking for the main path back to waking life, or another door to the Dreamlands; the rolls for this are the same as those for reaching the Dreamlands from the waking world directly. 

\subsection*{Travel and Embassies}

One advantage to joining an Embassy is travel within a Dreamland. In all domains that have a strong connection to an Embassy, an actual embassy building appears. Fully staffed with Dreamlanders \textendash\, though usually only a Chorus \textendash\, who attend diplomatic conferences, socialise with high society and try to persuade political figures.

Any Princess who belongs to an Embassy is welcome at any of its embassy buildings. The staff treat her as appropriate for her position; only for the Chorus to forget her when she heads on her way. The staff will gladly provide her with information, office space and things of that nature. Depending on if she's a Secretary, Consul or an Ambassador they might give her orders or obey her orders. Most of this is quite pointless, the real benefit is that a Princess can look up the details of every embassy building run by her Embassy in the files, and can use a Crawlspace to travel between them without a penalty to the roll for an insufficient emotional connection.

Princesses cannot go further than the public parts of an embassy building unless she is a member of that Embassy. The Dreamlanders will make an exception if a Princesses who is a member of the Embassy vouches for her, however this is not without drawbacks. The embassy building are not just part of the Draemlands; joining an Embassy is a change to a Princesses magic and something of this seeps into the structure of an embassy building. Upon entering the private parts of an unrelated Embassy a Princess must roll Stamina + Resolve, on a failure she gets a headache that lasts for around an hour, and inflicts a -1 to all mental actions. If Princess is a member of an Embassy with a particularly incompatible concept this rises to -2.

\section*{Time}

The relationship between time in the Dreamlands and time in waking life is strangely variable; it seems to depend much more on the density of one's experience than on any objective clock.  So, for instance, an exciting fight can consume half an hour in the real world's time, but appear to last only five minutes or so; but a long journey through safe districts might compress a full day's experience into only an hour of dreaming time.  (As a rule of thumb, an event in the Dreamlands takes as much time in the waking world as it would take the players to play out the scene, while the time it takes in the Dreamlands is what it would require in real life.)  There are even cases of Princesses parting in the Dreamlands, and finding on their next meeting that one has experienced a few hours packed with incident, while the other has been traveling for days ...

Remaining Transformed in the Dreamlands is a good deal easier than it is in waking life. A Princess rolls to remain transformed only once every 24 hours, by the Dreamlands' clock. A dramatic failure on that roll, however, has a more serious consequence; even after the Princess recovers her phylactery, she cannot transform within the Dreamlands for 24 hours after her failure.

\section*{Inhabitants}

There are at least three different types of beings found within the Dreamlands.  They were named by a theatrically minded Princess as the chorus, the actors, and the stars.  The chorus, from all appearances, are less independent people, than moving parts of the places where they're found; they walk, and talk, and do what you would naturally expect people to do in the situation you find them in, and nothing else.  Actors, in contrast, are fully realized people, with minds, memories, desires and aspirations.  They differ from the stars (and the Princesses) in only one way: They are unaware that a waking world exists, and nearly all who are told of it refuse to credit it. The stars, finally, are Dreamlanders who realise the truth of their home. Most are human souls drawn into the Dreamlands who have not chosen to pass on to the true afterlife. Stars native to the Dreamlands are rare and usually trouble.  Many Actors and Stars can wield strange powers, and some Stars who were once living Princesses and inhabitants of the 
Kingdom still hold the Charms they knew in life.

Native Dreamlanders are Ephemeral Beings formed of Astral Ephemera, however in the Dreamlands everything is Ephemeral. Even a Princess, for she has left her body safely tucked in bed. Therefore in the Dreamlands everyone can touch each other easily. Build Dreamlanders as normal Ephemeral Beings but while in the Dreamlands ignore their Manifestations entirely, for simplicity Princesses and other dream travellers use their normal stats. However in her Ephemerial dream form a Princess uses Dream Health, see the section on Dream Combat below. 

A Dreamlander's Rank depends on how much humanity as a whole thinks of a concept (this is separate to how stable a concept is, which defines how far outwards to look for it's representations): An obscure philosophy would only have a small village of low Rank Dreamlanders while a universal concept such as friendship would have a mighty metropolis with inhabitants ranging from Rank one all the way up to mighty rank six or seven Dreamlander gods that tower over the Queens in power. 

The former inhabitants of the Kingdom and any Princess who chooses to stick around after her body dies are of course not astral beings. They are normal Beacons, Sworn, Princesses and, of course, Queens who happen to be without a body at the present time. No different from a sleeping Princess travelling the Dreamlands. 

\subsection*{Dreamlanders on Earth}

A Dreamlander who ends up on Earth are limited in what they can achieve. Like all Ephemeral Beings they need a Condition to prevent Essence Bleed, for a Dreamlander a place is Resonant if people are thinking about whatever concept the Dreamlander represents. Both conscious thought and subconscious or emotional thinking qualifies. If forced into Dormancy a Dreamlander will return home. 

Outside the Dreamlands a Dreamlander's power only affects thoughts and emotions: They retain their Influences, but can only use them to influence peoples thoughts. For example a Dreamlander with Influence: San Francisco could use it to Create or Strengthen a thought about San Francisco but, unlike back in the Dreamlands, it could not influence a building. 

Numina are under similar restructions: If a Dreamlander has Numina that affects thoughts. emotions or their own body they may use it, no other Numina will function outside the Dreamlands. A Dreamlander's restrictions on supernaturally affecting the physical also means they cannot heal their stolen bodies with Essence.

Dreamlanders do have Manifestations but they may only acquire Manifestations from the following list: 

\begin{itemize}
 \item Fetter \textendash A Dreamlander may only use Fetter on ordinary mortals and supernatural beings who have a connection to the Dreamlands, such as Princesses.
 \item Harmonious Merge \textendash This requires the Controlled condition and a target with a similar personality to the Dreamlander. The Dreamlander and the target trade control of the body frequently, over time their personalities become more similar until they become a single entity. 
 \item Possess \textendash no special rules. 
 \item Greater Possession \textendash As posses, but it lasts until the Dreamlander ends or is forced to end the possession.
 \item Unfetter \textendash no special rules. 
\end{itemize}

\subsection*{Sample Dreamlander: Harpy Pirates}
To mankind the seas have always represented the great unknown. Infinite possibilities lie just beyond  the next horizon, but the seas also carry the danger of the storm, and pirates. Who doesn't love a good pirate story? 

Harpy pirates have congealed out of stray ideas from Greek mythology, sword and sorcery, and fantasy tinged pirate stories. As they are loosely tied to several concepts they can be living in a wide verity of Dreamland locations, or traveling freely across the seas between them. They're not particularly powerful or populous, but despite their small number they always travel in crews looking for ships full of booty to plunder, preferably shiny objects. 

When they do find a prize, they isolate the ship using their ability to influence wind, then fall from the sky, attacking sailors and stealing what they can in the confusion. While they can, and will kill if necessary, most of the time they are happy with just stealing whatever they can before retreating.

\noindent \textbf{Attributes:} Power 3, Finesse 7, Resistance 4\\

\noindent \textbf{Rank:} 2\\

\noindent \textbf{Willpower:} 10\\

\noindent \textbf{Corpus:} 9\\

\noindent \textbf{Essence:} 15\\

\noindent \textbf{Initiative:} 11\\

\noindent \textbf{Speed:} 20 (Species Factor 10 thanks to flight)\\

\noindent \textbf{Defence:} 4\\

\noindent \textbf{Size:} 5\\

\noindent \textbf{Ban:} Pirate Harpies feel compelled to steal shiny objects. This doesn’t mean that’s the only thing they can still, but when offered the opportunity to steal two things, they will typically go for the shinier of the two.\\

\noindent \textbf{Bane:} Wax.\\

\noindent \textbf{Influence:} Wind 2\\

\noindent \textbf{Numina:} Blast (Guns), Speed, Starlwart, Innocuous, Firestarter (Incendiary bombs)

Harpy pirates inflict lethal damage in hand-to-hand combat thanks to their sharp talons.


\subsection*{Sample Dreamlander: Kitsune Trickster}
In times long ago foxes and humans lived close together on the islands of Nippon and kitsune became a staple of Japanese mythology. They were messangers of the Kami, they would adopt human guises to become guardians, friends or lovers. And of course to play tricks on humans. Kitsune can be found in regions of the Dreamlands that reflect Japanese mythology, folklore, or pop-culture. Kitsune Tricksters can of course be found in all these places, but tend to form a larger proportion of the Kitsune population in areas that are also influenced by Western folklore, where it's nearly universal for folklore to portray foxes as tricksters. 

Kitsune Tricksers are usually more mischievous than truly dangerous but they can prove a real threat if they feel threatened. Conversely, they can become precious allies to people they grow found of. Most are Actors, but some Princesses among the court of Spades have been able to convince a Trickster that there is a real world and thus recruit it as a Shikigami. 

\noindent \textbf{Attributes:} Power 4, Finesse 6, Resistance 3\\

\noindent \textbf{Rank:} 2\\

\noindent \textbf{Willpower:} 8\\

\noindent \textbf{Corpus:} 8\\

\noindent \textbf{Essence:} 15\\

\noindent \textbf{Initiative:} 8\\

\noindent \textbf{Speed:} 19 (Species Factor 7)\\

\noindent \textbf{Defence:} 6\\

\noindent \textbf{Size:} 5\\

\noindent \textbf{Ban:} Kitsune Tricksters cannot evade people who manage to grab their tail; until said tail is let go, they have to stand here.\\

\noindent \textbf{Bane:} The teeth of a hunting hound.\\

\noindent \textbf{Influence:} Luck 2\\

\noindent \textbf{Numina:} Blast (magical foxfire), Innocuous, Firestarter, Mortal mask, Hallucination

Note that while there are few true mortals within the Dreamlands, most areas are populated with Dreamlanders who reflect the concept of a normal human and so Mortal Mask remains a useful ability.

\section*{Dream Combat}

The inhabitants of the Dreamlands often wield strange powers that only make sense by the dreamlike logic of that place, and not all are nice. A Princess travelling the Dreamlands may well find her self in battle. 

A Princess entering the Dreamlands leaves her physical body behind her, and projects her mind and soul into a body formed from the Dreamlands' substance.  If she is injured there, she does not take damage on her Health track \textendash\, her physical Health simply isn't relevant.  Instead, Princesses have Dream Health equal to resolve plus her Attribute Maximum based on Inner Light. If she Transforms she uses the usual rules for having extra Health Boxes in one form. If the Princess dies in the Dreamlands she wakes up the next morning (or sometime later) with the Soul Shocked Condition.

Native Dreamlanders use the usual rules for ephemeral beings in combat, save that they they are always fully material within the Dreamlands. If Actors or members of the Chorus die the Gales usually form a replacement after a short time. Most Princesses, and indeed most native Dreamlanders, don't really consider this to be death in any meaningful sense. They do however feel pain, so casual violence is still unethical. Stars however are gone for good, Princesses are forced back into the cycle of reincarnation as though they died in the real world. Star Dreamlanders are replaced by an Actor without any of the experiences they developed through their knowledge of the real world. 

\section*{Phenomena}

\subsection*{The Gales}

The Dreamlands are the combined hopes, thoughts, feelings and aspirations of mankind. The risks of travelling such a place should be obvious: Humanities thoughts change on a daily, nay, a second by second basis. Against such a tide as all of humanity, what can one mind do to remain static? Any Princess who travels too far from the stable regions of the Dreamlands risks being blown away, transformed as just another fleeting thought in the vast collective identity. 

The Nobility do have a defence. Some say this is because a Princess is supposed to be a shepard that guides mankind's hopes, that helps people achieve their dreams. Others say it is because transformation includes is a thick layer of magical armour. Regardless, while transformed a Princess' is protected from the worst the Gales can do, and the farther outwards she travels, the more necessary its protection becomes. 

For every 24 hours (by the Dreamlands' clock) that a Princess remains in the Dreamlands, she must roll Resolve + Composure; if she remains in her mundane identity for an hour or more, she takes a penalty on the next such roll of -1 for each day's travel outwards from the centre she stood.

   \begin{myindentpar}{10pt} Dramatic Failure: The Gales' force envelops the Princess, body, mind and soul, catches her up in a chaotic whirl, and commingles some of the Dreamlands' essence with her sprit and self. The Princess gains a Galemark, partly adapting from a mere visitor into a permanent settler in the Dreamlands. 
   
    Failure: The Gales push the Princess off-balance, scattering odd thoughts and scraps of imagined memories in her mind. Nothing overt happens at this point, but future rolls to resist the Gales suffer a -1 penalty. These penalties accumulate until the Princess gains a Galemark, or wakes up, and they stack with the penalties for going unTransformed. 
    
    Success: The Princess resists the Gales' force. She remains as she was, getting neither better nor worse. 
    
    Exceptional Success: In a flash of insight, the Princess recognizes some of the Dreamlands' essence mixed into herself for the fiction it is. She loses one Galemark. The effects of the lost Galemark on the Princess' appearance, and on the Dreamlands, may remain or fade away at the player's discretion - if they remain, the Princess can enact the role the Dreamlands wish her to play, and not become lost in it. \end{myindentpar}

Galemarks track a Princess' progress along a path that ends with her as indistinguishable, even to herself, from a Dreamlands native who has nightmares of an unhappy world, overshadowed by fear and despair. The effects of a Galemark are threefold. First, the Princess' Dreamlands body changes \textendash\, in both mundane and transformed identities, she gains a new, exotic physical feature. The change reflects what the Princess has seen and done: if she travels much among trickster foxes, she becomes foxlike, with pointed ears or a pelt. Galemarks don't always turn Princesses into fantastical beings - many places in the Dreamlands have inhabitants who could pass for normal in waking life - but a Princess with several Galemarks always looks very unlike her waking self.

Second, the Dreamlands weaves the Princess into its history and society. As a Princess gains Galemarks, the chorus members she meets are likely to \textquotedblleft remember\textquotedblright\,past encounters with her, or \textquotedblleft recognize\textquotedblright\,her as a native of a particular district in the Dreamlands, or refer in some other way to a history that (before the Gales marked her) never really took place. Dreamlands locations sometimes change physically to support the false history, too. (If you want a rule for this, either the player or the Storyteller may roll the Princess' Galemarks as a dice pool once per scene; for each success, narrate one \textquotedblleft fact\textquotedblright\,from the imagined backstory that the local chorus \textquotedblleft knows\textquotedblright.) The life invented for the Princess is internally consistent - once a part of it is established further Galemarks don't alter it.

Third, and strangest, the Princess' own memories twist, and she finds that she also knows the details of her imaginary past which the chorus members know. Moreover, as her knowledge of that life grows, her memory of waking life becomes disjointed, surreal and incoherent, as if it were the dream. Each Galemark is attached to one of the Princess' Willpower dots, starting with the leftmost and moving right. When the Princess spends a point of Willpower from a dot with a Galemark, she temporarily assumes the role the Dreamlands have given her, abandoning thoughts of the waking world as fictions of no importance. This delusion lasts for the rest of the current scene; while it has no mechanical effect, the Storyteller should reward players for keeping to it.

When a Princess gains Galemarks equal to her Willpower, marking all her Willpower dots, the last of these effects becomes permanent - she ceases to believe in the waking world's reality, just as the actors disbelieve. The Gales' work is complete, and the Princess no longer checks for Galemarks; on the other hand, she also loses the power to open ways into Crawlspace, and therefore cannot wake up on her own. Only another Princess can rescue her, by tracking her down in the Dreamlands and opening Crawlspace for her.

Galemarks do not fade while a Princess remains in the Dreamlands. They begin to fade if a Princess chooses to avoid the Dreamlands for a while. After a Princess has had one full night's sleep for each Galemark she carries without entering the Dreamlands, she loses one Galemark, recovering from its baneful on her mind. As with an exceptional success on the roll to resist the Gales, the Princess' player chooses whether the changes to the Princess' Dreamlands body, and her imaginary past, remain when the Galemark is gone. 

\subsection*{The Darkness}
The Dreamlands reflects all of humanity, once you leave the Queen's domains this includes the bad as much as the good. Whenever the Dreamlands reflects a bad part of Earth; be it a reflection of a city that includes a reflection of the crime ridden ghetto, or a reflection of a historical period including long past atrocities. Visitors can find Tainted places, Darkened and even Darkspawn.

This is not the Darkness Princesses remember from Earth. It is a lesser Darkness or perhaps this a greater Darkness: Is the darkness in the back of every man's mind worse than the monster of rotting shadows attempting to eat you? Regardless of such debates; Dreamland equivalents of Tainted places, Darkened, Darkspawn and all the rest can be be found in the Dreamlands. Build them as normal Dreamland natives, including whether they are a Chorus, Actor or Star then add the Darkened, Darkspawn or other template.

Regardless of which Darkness is \textquotedblleft worse\textquotedblright\,the Darkness in the Dreamlands is closer to the Princess' psyche. Any Sensitivity roll caused by the Darkness \textendash\, be it Darkened, Tainted Place, Darkspawn or other \textendash\, has 9again.

The only other noteworthy difference is that there is no Dark World within the Dreamlands. So few humans have ever experienced it (and fewer survive) that it is not a part of the Dreamlands. The Tainted places within the Dreamlands to not permit entry to a Dark World. It is still possible to for a Darkened to use the Enter Darkness ability, but it functions more like a slow teleport between two Tainted spots. 

Fighting the Darkness in the Dreamlands can be a useful way to uncover clues about the Darkness on Earth, or a way to give new Princesses a lifelike training session with far less risk of permanent injuries. But attempting to cleanse Taint from the Dreamlands is a futile endeavour, so long as the thoughts and emotions still exist human hearts the Gales will continue to create Tainted Places every time the region is reworked. The only true way to cleanse the Dreamlands is to deal with the problem on Earth. Be it by cleaning up a crime ridden town or helping people heal from old wounds.  

\subsection*{The Light}
In Dreamlands domains that reflect something strong and positive it is possible for the Princess to come across a manifestation of the Light itself. This either requires a lot of luck, or an Extended roll to track it down. One the Princess finds a manifestation of the light she may choose to bathe her soul in it, this has three effects: The Princess may choose to fulfil her Virtue, if she has not done so already twice this chapter. The Princess may regain all her Willpower; or, the Princess gains 1 Luminous Experience.

But there is a danger, the longer the Princess spends in the Light the harder it is to return to the grubby shadowy mortal world where her duties lie.  The Princess’ Sensitivity dice pool increases by 1 die if she regained Willpower, and by 3 dice if she gained a Luminous Experience. After a number of days equal to her increase in Sensitivity the Princess’ Sensitivity returns to normal. If the Princess touches the Light again before this time not only does the timer reset, it stacks with any further benefit she may gain.

\section*{Places of Note}

\subsection*{The Foundation}
The Foundation is a mystery. As far as can be discerned the entire Dreamlands is built upon it's surface. As one approaches the borders of the Dreamlands the Foundation becomes exposed to the eye. It appears differently to every traveller but always gives the impression of being some form of stability in contrast to the wild unkowable places outside the Dreamlands. While a city-dweller might see a mighty concrete tower run through with pipes, wires and air-conditioning outlets a Princess from a remote desert dwelling tribe might see The Foundation as the edge of a lush oasis abruptly shifting into endless desert sands. Past The Foundation is a place usually called Beyond, or Outside. Beyond is a mystery to the Nobility. Like The Foundation Beyond appears differently to every viewer but it always has a feeling of vastness; of infinite wonder and potential. Yet Beyond also feels of danger, not hostility or anger but the impersonal danger of a storm wrecked sea or the harsh desert sand. Looking Outside is a 
very personal experience as awe, fear, wonder and desire flow through the Princess. Each will discover for herself which emotion dominates. 

\bigsidebarstart

\subsubsection*{Some Examples}

To give you some examples of what The Foundation and Beyond might look like here is how each Queen perceives it.

The Queen of Clubs sees The Foundation as the edge of a simple grassy clearing surrounded by enormous forests that comprise Outside. The forests are so dense and thick she cannot see more than a finger's length Beyond the Dreamlands. The Queen of Clubs is neither awed nor scared of Beyond. She simply accepts that it is something greater than herself, and so makes peace with it.

The Queen of Diamonds sees The Foundation as the beaches of her youth. Beyond lies a calm sea at night time. A perfect velvet black that mirrors the enormous stars and planets in the sky Outside the Dreamlands until you cannot tell where the sea ends and the sky beings.

The Queen of Hearts sees The Foundation as a marble tower. It is carved with a relief of people climbing to to the top over one another in a mass of humanity. They show nobility with the strong helping the weak, the old and the infirm. As they crest the top of The Foundation the carved faces show expressions of dignified triumph over adversity. Beyond The Foundation lies nothing more than simple barren rocky hills. The Queen claims she can sometimes see movement down there, and that it makes her feel uncertain like nothing else.

The Queen of Spades sees The Foundation as the undercarrage of an enormous airship holding the entire dreamlands aloft. With a practised eye she judges and concludes that all is ship-shape and airworthy. To this Queen Beyond looks like a vast plain of clouds drifting far bellow, if there is a ground further below she has not seen it.

To The Queen of Swords The Foundation looks much like her homeland. The crest of an enormous pyramid; Beyond which lies vast rainforests. The Queen claims to have spotted signs of ruins and signs of inhabitation. 

\bigsidebarend

No matter the appearance of the Foundation, it is always adorned with strange writing in every imaginable language, linguistic subdivision and even every imaginable appearance: From typed to archaic and cursive. Princesses can read the Foundation, or at least the parts in the languages they know, but they can learn nothing from it. Like a million voices talking at once the Foundation is just too much to understand. It's unknown if there even is something too be understood. Sometimes strange mists are released from the Foundation, a Princess who inhales them can comprehend any language created by humans (including the Royal Tongue and Alhambran) until she next leaves the Dreamlands. If she dedicates the nights sleep to memorisation and spends the exp she may retain a language permanently. 

\subsection*{The Lighthouse}
The five Queens have been curious about the Foundation and Outside ever since they were first noticed shortly after the Release. The Lighthouse is a small Danann outpost built in a retro rough stone style that pre-dates the Queen of Diamonds Coronation. Within is accommodation for a few scholars and some scientific equipment. It also has some mild fortifications; looking Outside makes a lot of Stars nervous (Actors can't see Outside at all). The torch itself is usually only lit if the Queen of Diamonds is present, not everyone sees Beyond as permanently night time. 

\subsection*{The Forests of Wen-Mung, domain of the Queen of Clubs}

Wen-Mung is the largest of the Queen's Kingdoms, and the most sparsely inhabited. Yet no matter how far you are from the nearest settlement sings of people are everywhere, colourful paper talismans and wind chimes adorn every tree. Even the animals show subtle signs of domestication: That rabbit wears a little bow, there's a deer with decorated antlers, this wild horse has a braid in her mane.

When the Princess finds the people they are a hardy folk who live in harmony with the forest. They build their homes between or around the trees – natural clearings are rare and reserved for important buildings like village halls or temples – and farm strange plants; as productive as wheat yet growing up the side of trees like ivy. The villages are simple, designed to be easily built for the people are occasionally nomadic. If the rains fail to come or disease beings to spread they'll build again elsewhere. Only important buildings such as temples are stone, and even these can be abandoned, left to wait patiently until they are needed once again.

Most of the population is employed in agriculture or forestry. Individual communities are usually entirely self sufficient. Though most residents posses only a basic education the citizens have impressive practical intelligences and a versatile array of skills useful to their daily lives. While they don't show any animalistic behaviours, they do occasionally show animalistic skills: After being asked for directions, a young farmer sniffs the air before pointing with confidence. An old woman clicks her tongue as she walks, only by looking closely does one realise it's because she's as blind as a bat. It would appear that as much as the forest itself has become slightly tame, the people have taken just a slight touch of the wild into themselves.

Wen-Mung exports food and timber and rarely imports anything. Centuries of a trade surplus have given the Queen of Clubs an enormous financial reserve, though not nearly as large as it should be. During the winter months, when the forests and farms sleep, the Queen sponsors enormous, pointless, public work projects to avoid too much of the economy stagnating in the royal treasury. Often these projects start by tearing down last year's work. The other Kingdoms consider Wen-Mung a perfect neighbour, it's quiet, respectful and exports at great prices. 

\begin{mybox}

\textbf{Gales in the Queen's Domains}

The five Queens hold their seats within the Dreamlands in districts a fair distance outward, though not in the most volatile lands; the Kingdoms are two days' walking outward from the centre. Conveniently, the Gales are not as dangerous within the Kingdoms (or the Lighthouse) - the roll to resist them takes no penalty there. The magical defences around the Queen's domains mean that everyone is treated as though they were a Transformed Princess.\end{mybox}

\subsection*{The Danann Archipelago, domain of the Queen of Diamonds}
The Danann Archipelago stretches for over a hundred islands. Most are either densely populated or uninhabited with the populated islands growing in the only direction they can: Up, in magnificent towers of ivory and glass. Sleek hydrofoils and flying wing aircraft surround the islands in a never ending dance of motion. Danann has a subarctic climate, the inhabitants consider central heating among the greatest miracles of technology. Cocooned in their artificial climate they prefer sleek future-chic fashions.

The people are a contented lot and welcoming to outsiders, although they tend to posture about their intelligence and education in front of foreigners. The observant visitor will quickly notice that everyone is either engaged in their pet scientific or creative projects, or they are obviously at leisure. The Queen of Diamonds had pretty much every necessary job replaced by machines long ago freeing the population to focus on the sciences and the arts. Though not quite the post scarcity society promised by futurists it's as close as most Princesses are likely to experience.

With an abundance of free time and ubiquitous communication technology the locals often form social groups based on common interest. Be it pre industrial music, advanced mathematics or abstract philosophy. Even though most people belong to several such groups the largest or most dedicated groups often develop residential clusters to be closer to their friends and any museums, concert halls, bulky equipment or social spaces they've appropriated or built. Though the Queen does not officially take part in this system, the topics she is most interested in \textendash\, technology and the physical sciences \textendash\, gravitate towards her. A vast academy of science, technology and academics has formed around the royal palace (Technically beneath, she lives in the penthouse).

Danann is an extroverted nation, the fisheries and hydroponics cannot keep up with the population and so the economy depends on foreign trade. They export technology, technicians, engineers and offer advanced education to citizens of other Kingdoms in return for food and raw materials. Dannan has formed an odd friendship with the Confederacy of the Four Winds, another leisure filled Kingdom heavily built around foreign trade; they do dislike admitting that their most advanced aircraft cannot match the Confederacy’s mastery of the winds. 

\subsection*{The City States of Andarta, domain of the Queen of Hearts}

Andarta is a land of flowing fields, peaceful rivers and gentle hills. The people are equally divided between urban and rural. No matter where you travel the architecture is ornate and beautiful. Even the smallest farming community is built of solid stone with masterly carved decorated touches. Following the paved roads or aqueducts to the cities reveals unsurpassed architecture splendour, from marble clad defensive walls to streets so clean they sparkle in the sunlight. The people too are fit looking and healthy who always manage to look sharply dressed and spotlessly clean, even when coming home covered in mud from a hard days work in the field.

The Queen of Hearts loves everything in it's proper place, and she has made her mark on her Kingdom. Andartan life is an organised one. The government is feudal with cleanly defined hierarchies. The trades and professions are organised into guilds. Stability is both prized and abundant, it leads to a sense of confidence. People know what's expected of them, how to deliver it, and who will help them if they get a little over their heads.

Social roles in Andarta are well defined, but social mobility is high. A simple farmer would be expected to obey his superiors but she would also have many opportunities to advance her position, she could become a skilled artificer, a scholar or a self employed merchant; advancing her position and earning new rights and responsibilities. Foreigners would quickly notice that while social climbing clearly does grant new rights Andaratns never use the word, a noble doesn’t have the right to give orders, they have the responsibility to govern. This is the direct influence of the Queen, she only ever uses the word responsibilities, her subjects usually take the hint.

Andarta is the most introverted of the Kingdoms. While they are not quite xenophobic they are highly resistant to new ideas and find it uncomfortable when foreigners don't fit their expectations. They possess the common courtesy to hide it of course, as a people Andartans are socially gifted, to anyone not as talented as the locals at reading people Andartans come across as trying too hard to be welcoming. 

\subsection*{The Confederacy of the Four Winds, domain of the Queen of Spades}

The Queen of Spades calls the Four Winds her home, a vast snow-capped mountain range. Actually four mountain ranges all smooshed together to the amusement of geologists. The population is predominantly urban and take great care on the placement of their cities, seeking out sun-facing river valleys with warm prevailing winds. Transportation is handled almost entirely by a wide variety of airships, balloons and gliders, from a very young age the inhabitants learn to pilot enormous kites. For a few specialized tasks the local species of giant mountain spiders are domesticated, they are favoured for their prodigal strength and peerless climbing abilities.

The kingdom is a mercantile one, trade is the backbone of the economy. The Confederacy also has a large amount of artisans and craftsmen who specialize in delicate hand crafted arts and crafts, for the Confederation lacks the raw resources to compete in bulk manufacturing. The Confederates take delight in foreign trade and the exotic wonders it brings to their homes. Enormous bazaars wind through the city streets. Stalls carry all manner of exotic goods and services from the five Kingdoms and the wider Dreamlands. The people are colourful and passionate. Any customer is a beloved friend. Haggling is a social requirement filled with blistering insults against the quality of the goods and blatantly nonsense stories about starving kids to feed. As soon has money is exchanged everyone is once again true friends.

The Confederacy is an anarchy, organized on an ad-hoc basis by it's residents. Admittedly the organization is somewhat haphazard and ramshackle. Along with the weekly general assemblies, anyone simply tells friends and strangers they are hosting a meeting and if people are interested word will spread. Everyone gets together then they go home and decide if they agreed with the consensus or if they plan to ignore it. Those who have the talent to get things done will lead the way and those who disagree, lacking that talent themselves, are unable to hold the kingdom in an argumentative paralysis. Reputation is supremely important. The unofficially officially unofficially non-binding congresses which discuss issues of national importance tend to meet wherever the Queen's palace has drifted to this month to take advantage of her wisdom. Somehow, everything that needs to be done gets done in a timely manner.

Of all the Kingdoms, the Confederacy is the most extroverted of them all. As masters of the winds no kingdom can match their mobility, their love of the foreign and exotic sends a steady stream of merchant airships beyond the five Kingdoms to trade with the wider Dreamlands. 

\subsection*{The Aztallan Alliance, domain of the Queen of Swords}

Aztallan is a land of lush rainforests, ever-blue skys and above all an enormous golden sun. The rainforest is hot, humid and teeming with life. They are also very dangerous to the unprepared traveller and unsuited for any population beyond small tribal societies. The Aztallani have overcome these limitations in their usual direct manner, by constructing enormous stepped pyramids and dwelling high above the rainforest. Houses, commerce and even farming all take place atop massive artificial plateaus. Aqueducts and bridges stretch for miles above the rainforest.

The people are a rugged independent sort, but loyal unto death to those who've won their trust. Self sufficiency is still a respected way of life and the more formal economy is dominated by small businesses and independent artisans who provide services to the local community. The cities often look less like a zoned metropolis than a large collection of individual towns and villages that grew into each other, usually because that's exactly what they are. Government is distributed and decentralised with local government at the level of town or city district being the most relevant to the average citizen's life.

The larger organisations and the government are best described as a meritocracy with posts decided purely by a person's skills. It is considered a sign of untrustworthiness if people know the identity of a candidate they might hire, it is suspected that they will choose their friends or family and to be fair with the Aztallani ideals of personal loyalty they probably would. \textquotedblleft Not even for the Queen's consort\textquotedblright\, is a common way of declaring integrity, you can guess how the term originated. Since they often work alone or in small groups many Aztallanis have a wide verity of skills, this attitude is carried on to the larger organisations. It is not uncommon to see one person with two or more vastly different jobs.

As a society Aztallan shows the same self sufficiency and independence that it's people do. While welcoming to outsiders the kingdom usually waits for foreigners to come to it. One noticeable exception is adventurers: bright young Aztallani often undertake a mission to develop or prove their merits. All forms of merit are valued but adventurers dominate the international perception of Aztallan as they are the largest group to wander beyond their homeland. 

\subsection*{Saint Frances' City}

In the middle of a wide field beneath an eternally sunny blue sky, cooled by gentle breezes travellers may catch sight of Saint Francis. The saint is dressed in the humble brown robes of a monk and sits unmoving on a simple wooden chair, at a simple wooden desk, endlessly copying \textquotedblleft Bibles \textquotedblright\,that actually contain a rough mixture of political speeches, travel guides and local news. All from San Francisco of course. Saint Francis is also three hundred foot tall.

As he writes Saint Frances supports an enormous bright red kite tied to his right shoulder by a tail that looks like someone took several golden gate bridges and wrapped them around each other like the threads in a length of twine. To this enormous kite several more kites are anchored, and to those even more. On and on in an enormous widening cone of many coloured kites. All interconnected by a labyrinthine network of bridges, cable cars and even subway tunnels hanging from the undersides.

This is Saint Frances' city, an enormous metropolis built onto the backs of thousands of kites. In many ways it is an exaggeration of the perception of San Francisco. In other ways it's as nuanced as the original but places the popular perception front and centre so it cannot help but colour a visitor's impressions. In the more tourist and commercial areas it seems every other building is a coffee shop where locals debate politics and recite amateur poetry or music. There is normally at least one parade every day. 

Atop the very highest kite is the imperial palace, where Saint Frances' City is ruled by it's beloved emperor. A Dreamlands reflection of the government of San Francisco; with the personality of Emperor Norton and the fashion sense of Napoleon Bonaparte. 

\section*{Note for those who have read Astral Realms}

The Dreamlands are similar to what the Atlantian Mages call the Astral Realms. How would a Princess perceive the Astral, and how would a Mage perceive the Dreamlands? In many ways the question is purely academic. Only in the most bizarre and unlikely circumstances could a Mage enter the Dreamlands or a Princess arrive within the Astral.

But for the sake of academic curiosity let us pluck a Princess of Diamonds and a Mage of the Mysterium from their lives and give each a copy of Princess: the Hopeful and Astral Realms to read. Over the course of much debating they would touch upon several ideas: They might say the two realms are one and the same, seen from different points of view. Perhaps they are different manifestations of the same phenomena. They may question the possibility that both the Dreamlands and the Astral Realms are like metaphysical \textquotedblleft web-browsers\textquotedblright; they are mostly separate but one may see the effects of the other by observing the changes in the \textquotedblleft website\textquotedblright\,they connect too. Perhaps one might propose that the two realms are simply unrelated. The possibility to test this theory is sure to delight both. What would happen if the Princess stood patiently in St Frances' City while the Mage used an ancient Atlantian artefact, The Scythe, to destroy the Tenemos realm of 
San Francisco. When the Princess sees the destruction St Frances' City followed by it's restoration when the Gales next blow through they would be forced to conclude that there is some overlap. At this point they would begin debating which of the earlier theories were true, but after much thought they would be unable to determine if the theories are even meaningfully different.

And what would our scholars think of their opposites realm? The Princess would look at the layers of the Astral with bafflement, and a little distaste. How can the Oneiros and the Tenemos be separate? The concept of an individual human is meaningless outside the context of humanity, and how can you have humanity without the individual humans that comprise it? While any follower of the Court of Diamonds would have little trouble understanding the concept of travelling through word or symbolic associations she would be baffled as to why the Astral runs on such principles. From a Princess' point of view they're far too small a part of human existence to underpin humanities collective unconscious. She might conclude that the Astral was built by something inhuman trying to understand humanity, and muse what this implies about the Mage. This can only end in a heated argument.

Wishing to map the unknowable The Mystagogue would focus on the structure of the Dreamlands. That part looks like the equivalent of this Tenemos realm. This section looks like an Oneiros. But how does it all fit together? While the two realms don't always map to each other this does not mean that progress cannot be made. Some deductions are clear; like the Foundation and the Omphalos being the same. It will not take long for the Mystagogue to broadly conclude that the Dreamlands are a very peculiar hybrid of the parts of the Astral that they call the Tenemos and the Dreamtime, constructed from sealed representations of millions of Oneiros. Trying to go past the low hanging fruit leads only to confusion. Inhabitants of The Kingdom are present in the Dreamlands but there is no trace of them in the Tenemos. Not even of the vast territories governed by the Queens. Attempting to find a relationship between the association-connections of the Tenemos and the physical distances in the Dreamlands gets nowhere. As the 
Mage works he might mutter words like \textquotedblleft Less True\textquotedblright\,or \textquotedblleft only Fallen\textquotedblright. This can only end in a heated argument. 


\end{multicols}